### 2013-09-16 paper/kbanotebook2013/content/abstract.tex
Added the skeleton files needed for the trec notebook submission

\begin{abstract}

% TODO this can be updated at the end

In this paper we will present the system design and algorithm adopted by the 
GatorDSR team, University of Florida to efficiently process TREC KBA 2013 --- 
SSF track. Here we will describe the system evolution as well as the details 
of our algorithm to extract slot values for the given slot name. Scalability 
and efficiency in precision and recall are the major   goals of this work, 
given the overly limited time limitation and available computational resources.

\end{abstract}

### 2013-09-16 paper/kbanotebook2013/content/conclusion.tex
Added the skeleton files needed for the trec notebook submission

\section{Conclusions}

% Note: Give a summary of our efforts and the
% high level contribution to society.

% Talk about the things we wanted to do and
% didnt get to do.

### 2013-09-16 paper/kbanotebook2013/content/discussion.tex
Added the skeleton files needed for the trec notebook submission

\section{Discussion}

% Note: Here we discuss why the results are the way they are
% Give pros and cons, talk about how the implemented algorithms
% performed in the actual implementation.
% Answer the `why' question about all the trends in the results section.

### 2013-09-16 paper/kbanotebook2013/content/implementation.tex
Added the skeleton files needed for the trec notebook submission

\section{Implementation}

% Note: Talk about how each of the algorithms were created

% Note: Give enough information for our algorithms to be
% reimplemented and verified.

### 2013-09-16 paper/kbanotebook2013/content/introduction.tex
Added the skeleton files needed for the trec notebook submission

\section{Introduction}

% Motivation

% KBA Task

% Evaluation Criteria

% Quick Discussion of our approach

### 2013-09-16 paper/kbanotebook2013/content/results.tex
Added the skeleton files needed for the trec notebook submission

\section{Results}

% Note: Here is where we give as much stats as possible on our runs

### 2013-09-16 paper/kbanotebook2013/content/system.tex
Added the skeleton files needed for the trec notebook submission

\section{System}
% Note: Describe the algorithms of each phase
% Talk in abstract terms not implementation.
% Use formal representations (Math, SQL etc)

\subsection{Cumulative Citation Recommentation}

\subsection{Streaming Slot Filling}

\subsection{Post Processing Algorithm}

### 2013-09-16 paper/kbanotebook2013/paper.tex
Added the skeleton files needed for the trec notebook submission

\documentclass{article}

\begin{document}

\title{GatorDSR: University of Florida Knowledge Base Acceleration Notebook}

\numberofauthors{3}

\author {

\alignauthor Morteza Shahriari\\
  \affaddr{University of Florida}\\
       \affaddr{Department of Computer \& Information Science \& Engineering}\\
       \affaddr{Gainesville, Florida, USA}\\
       \email{\{m.shahriarinia@ufl.edu}

\alignauthor Christan Grant, Yang Peng, Daisy Zhe Wang\\
  \affaddr{University of Florida}\\
       \affaddr{Department of Computer \& Information Science \& Engineering}\\
       \affaddr{Gainesville, Florida, USA}\\
       \email{\{cgrant,ypeng,daisyw\}@cise.ufl.edu}

\alignauthor Milenko Petrovic\\
  \affaddr{Institute for Human and Machine Cognition}\\
       %\affaddr{Department of Computer \& Information Science \& Engineering}\\
       \affaddr{Ocala, Florida, USA}\\
       \email{mpetrovic@ihmc.us}
}

\maketitle

\input{content/abstract.tex}

\input{content/introduction.tex}

\input{content/system.tex}

\input{content/implementation.tex}

\input{content/results.tex}

\input{content/discussion.tex}

\input{content/conclusion.tex}

\section*{Acknowledgements}
Christan Grant is funded by a National Science Foundation Graduate Research
Fellowship under Grant No. DGE-0802270.

\end{document}

### 2013-09-16 paper/kbanotebook2013/paper.tex
added the bibliography structure
changed the author format so it compiles with pdflatex

@@
 
-\numberofauthors{3}
+%\numberofauthors{3}
 
-\author {
-
-\alignauthor Morteza Shahriari\\
-  \affaddr{University of Florida}\\
-       \affaddr{Department of Computer \& Information Science \& Engineering}\\
-       \affaddr{Gainesville, Florida, USA}\\
-       \email{\{m.shahriarinia@ufl.edu}
-
-\alignauthor Christan Grant, Yang Peng, Daisy Zhe Wang\\
-  \affaddr{University of Florida}\\
-       \affaddr{Department of Computer \& Information Science \& Engineering}\\
-       \affaddr{Gainesville, Florida, USA}\\
-       \email{\{cgrant,ypeng,daisyw\}@cise.ufl.edu}
-
-\alignauthor Milenko Petrovic\\
-  \affaddr{Institute for Human and Machine Cognition}\\
+\author {%
+  Morteza Shahriari\\
+  University of Florida\\
+  Department of Computer \& Information Science \& Engineering\\
+  Gainesville, Florida, USA\\
+       {m.shahriarinia@ufl.edu}
+\and
+  Christan Grant, Yang Peng, Daisy Zhe Wang\\
+  University of Florida\\
+       Department of Computer \& Information Science \& Engineering\\
+       Gainesville, Florida, USA\\
+       {\{cgrant,ypeng,daisyw\}@cise.ufl.edu}
+\and
+  Milenko Petrovic\\
+  Institute for Human and Machine Cognition\\
        %\affaddr{Department of Computer \& Information Science \& Engineering}\\
-       \affaddr{Ocala, Florida, USA}\\
-       \email{mpetrovic@ihmc.us}
+       Ocala, Florida, USA\\
+       {mpetrovic@ihmc.us}
 }
@@
 
+\bibliographystyle{acm}
+\bibliographystyle{citation}
+
 \end{document}

### 2013-09-17 paper/kbanotebook2013/content/implementation.tex
Initial copy of the project report in Latex.

@@
 \section{Implementation}
+
+We extract aliases for entities from wikipedia automatically both using API and using the actual page content, then apply pattern matching rules for slot value extraction.
+
+\subsection{Alias Generation}
+
+We use Wikipedia API to get some aliases automatically.
+This is done by retrieving backlink references (redirects of a wiki entity).
+Unfortunately this is not good enough and to enhance recall we need more aliases.
+To have better use of a wiki page we parse HTML DOM of the page, then use regular expressions to extract the bold phrases of the first paragraph as alias of the actual entity.
+Based on our observation this is a very accurate heuristic and provides us with lots of famous aliases of the entities.
+To consider other typical cases we consider some generic first name last name order swapping conventions such as Bill Gates -> Gates, Bill.
+
+\subsection{Pattern Matching}
+
+In this system, we use pattern matching methods to find corresponding slot values for entities.
+The procedure is: 1) Find stream items that contain the entities by using alias names of the entities.
+2) Inside these stream items, fetch the sentences which contain entities by using alias names and the coreference information provided by Lingpipe tags.
+3) Use these sentences to match existing patterns.
+4) When patterns matched, generate SSF results.
+
+The format of the patterns is consist of five fields: 1) the type of the entity.
+2) the slot name.
+3) the pattern content.
+4) the direction of the slot valule to the entity.
+5) the type of the slot values.
+When we match one pattern, we match all the fields except the third field.
+The type of slot values could be the entity type tagged by Linpipe, noun phrase tagged by OpenNLP and the time phrases we hard-code.
+For these three kinds of patterns, we implement them in different ways accordingly.
+
+Next we will explain the patterns with more details.
+Lets’s first look at one example of the first kind of patterns.
+For slot FounderOf, we have this pattern: <PER, FounderOf, founder, right, ORG>.
+PER means that the entity we are finding slot values for is a PER entity; FounderOf means this is a pattern for FounderOf slot.
+founder is the ankor word we are trying to match in the sentence text; right means that we are going to the right part of the sentence to match the pattern and find the slot value; ORG means the slot value should be a ORG entity.
+
+Here is an example for the second type: <PER, AwardsWon, awarded, right, NP>, NP meaning noun phrase.
+This pattern can be interpreted as that we are looking for a noun phrase after the “awarded” since that noun phrase could possibly represent an award.
+Since titles and awards are usually not the Lingpipe entities, we use the OpenNLP noun phrase chunker to fetch the noun phrases.
+
+Another example for the third type: <PER, DateOfDeath, died, right, last night>.
+In this pattern, “last night” means we are looking for exactly the phrase “last night” to the right of “died”.
+This pattern is inspired by the intuition that in news articles, people often mention that somebody died last night instead of mentioning the accurate date information and Lingpipe tends not to tag phrases like “last night” as a DATE entity.
+
+To improve recall, we introduce generic patterns that can generate many results.
+But these patterns generate many errors, too.
+Thus there is a trade-off between the accuracy and recall.
+This is one drawback of using pattern matching method, meaning it is really hard to find good patterns with both high accuracy and recall.
+
+For accuracy, we have found that there are three major kinds of errors: 1) wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched by the patterns.
+We solve the first problem by using the wikipedia or twitter information of the entities to get better alias names.
+And we use post-processing to reduce the second and third types of errors.
+
+\subsection{Post Processing}
+
+The SSF output of many extractions is noisy.
+The data contains duplicates and incorrect extractions.
+We can define rules to sanitize the output only using the information present in the SSF file.
+The file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy.
+.
+We define two classes of rules deduplication rules and inference rules.
+
+The output contains many duplicate entries.
+As we read the list of extrated slots we create rules to define "duplicate".
+Duplicates can be present in a window of rows; we use a window size of 2 meaning we only be adjacent rows.
+Two rows are duplicates if 1) they have the same exact extraction, 2) if the rows have the same slot name and a similar slot value and 3) if the extracted sentence for a particular slot types come from the same sentence.
+
+ New slots can be deduced from existing slots by defineing inference rules.
+For example, two slots for the task are "FounderOf" and "FoundedBy".
+A safe assumtion is these slot names are biconditional logical connectives with the entities and slot values.
+Therefore, we can express a rule "X FounderOf Y" equals "Y FoundedBy X" where X and Y are single unique entities.
+Additionally, we found that the slot names "Contact\_Meet\_PlaceTime" could be infered as "Contact\_Meet\_Entity" if the Entity was a FAC and the extracted sentence contained an additional ORG/FAC tag.
+
+We also remove erronious slots that have extractions that are several pages in length or tool small.
+Errors of extracting long sentences can typically be attributed to poor sentence parsing of web documents.
+We have some valid "small" extractions.
+For example a comma may separate a name and a title (e.g.
+"John, Professor at MIT").
+But such extraction rules can be particularly noisy, so we check to see if the extracted values have good entity values.
+
+The aim in post processing was to sanitize the results increasing the precision of the results by eliminating spurrious results.
+
+\subsection{Shortcomings}
+
+The missing twitter entities are more than the 50\% of the twitter entities we need to work on and this is a very very bad performance.
+One reason could be that those entities are not very famous.
+For example Brenda Weiler google search result is 860,000 documents our of billions of web documents.
+For our small portion of the web it might make sense.
+If you pay attention to the histogram of the entities found you'll note that more than half of the entities have appeared in less than 10 StreamItems.
+A good portion have appeared only once.
+Which the document does not necessarily have good information for us.
+
+A theory is that we are falling behind because we are using the cleansed version of the corpus.
+We believe there has been a reason that TREC has included the actual HTML document as well as the cleansed version.
+This definitely will convey some information to us.
+If it was as easy as reading some clean text they wouldn't bother including so much data for teams to be useless.
+So we guess is that we are missing some information from not using the actual document.
+And, we are looking for tokens with entity value set which will depend us dramatically on the accuracy of lingpipe, which is a fast algorithm but is not as good as other NLP tools can be e.g.
+Stanford NLP.
 

### 2013-09-17 paper/kbanotebook2013/content/results.tex
Initial copy of the project report in Latex.

@@
 
+Document extraction using query entity matching with aliases, sentence extraction using alias matching and co-reference.
+Slot extraction using patterns, NER tags and NP tags.
+158,052 documents with query entities, 17885 unique extracted slot values for 8 slots and 139 entities, 4 slots and 31 entities missing.
+
+On the performance of the first submission run we performed some random sampling via two processes, the results of which are as follows:
+
+\begin{table}[b]
+\caption{SSF Performance Measure on Initial Submission }
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline 
+ & Correct & Incorrect Entity name & Incorrect Value \\ 
+\hline 
+Sampling \#1 & 55\% & 17\% & 27\% \\ 
+\hline Sampling \#2 & 54\% & 15\% & 31\%  \\ 
+\hline 
+\end{tabular} 
+\end{table}
+
+\begin{table}[b]
+\caption{SSF Performance Measure on Submission Infer }
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline 
+ & Correct & Incorrect Entity name & Incorrect Value \\ 
+\hline 
+Affiliate & \% & \% & \% \\ \hline 
+AssociateOf & \% & \% & \%  \\ \hline 
+AwardsWon & \% & \% & \%  \\ \hline 
+CauseOfDeath & \% & \% & \%  \\ \hline 
+Contact\_Meet\_Entity & \% & \% & \%  \\ \hline 
+Contact\_Meet\_PlaceTime & \% & \% & \%  \\ \hline 
+DateOfDeath & \% & \% & \%  \\ \hline 
+EmployeeOf & \% & \% & \%  \\ \hline 
+FoundedBy & \% & \% & \%  \\ \hline 
+FounderOf & \% & \% & \%  \\ \hline 
+Titles & \% & \% & \%  \\ \hline 
+TopMembers & \% & \% & \%  \\ \hline
+
+\end{tabular} 
+\end{table}
+
 % Note: Here is where we give as much stats as possible on our runs

### 2013-09-17 code/src/main/java/edu/ufl/cise/ToProcessBatchProcessor.java

@@ -1,0 +1,591 @@
+package edu.ufl.cise;
+
+import java.io.File;
+import java.io.FileNotFoundException;
+import java.io.InputStream;
+import java.io.PrintWriter;
+import java.io.UnsupportedEncodingException;
+import java.text.DateFormat;
+import java.text.DecimalFormat;
+import java.text.ParseException;
+import java.text.SimpleDateFormat;
+import java.util.Calendar;
+import java.util.Date;
+import java.util.Hashtable;
+import java.util.LinkedList;
+import java.util.List;
+import java.util.concurrent.atomic.AtomicInteger;
+import java.util.concurrent.atomic.AtomicLong;
+
+import org.apache.commons.compress.compressors.xz.XZCompressorInputStream;
+import org.apache.thrift.protocol.TBinaryProtocol;
+import org.apache.thrift.transport.TIOStreamTransport;
+import org.apache.thrift.transport.TTransportException;
+
+import streamcorpus.Sentence;
+import streamcorpus.StreamItem;
+import streamcorpus.Token;
+import edu.ufl.cise.pipeline.Entity;
+import edu.ufl.cise.pipeline.Preprocessor;
+
+/**
+ * This is a variant of CorpusBatchProcessor btu optimized for toProcess file
+ * list not for the entire corpus.
+ * 
+ * @author morteza
+ * 
+ */
+public class ToProcessBatchProcessor {
+
+	public final static String JSON_FILE = "resources/entity/trec-kba-ccr-and-ssf-query-topics-2013-04-08.json";
+
+	/** Corpus directory on server/local */
+	public final static String CORPUS_DIR_SERVER_SDE = "/media/sde/s3.amazonaws.com/aws-publicdatasets/trec/kba/kba-streamcorpus-2013-v0_2_0-english-and-unknown-language/";
+	public final static String CORPUS_DIR_SERVER_SDD = "/media/sdd/s3.amazonaws.com/aws-publicdatasets/trec/kba/kba-streamcorpus-2013-v0_2_0-english-and-unknown-language/";
+	public final static String CORPUS_DIR_LOCAL = "/home/morteza/2013Corpus/s3.amazonaws.com/aws-publicdatasets/trec/kba/kba-streamcorpus-2013-v0_2_0-english-and-unknown-language/";
+
+	public final static String BASE_DIR_SERVER = "/media/sde/submission/finalSubmission/sanityCheck/";
+	public final static String BASE_DIR_LOCAL = "/home/morteza/trec/";
+
+	/**
[…]

### 2013-09-18 paper/kbanotebook2013/content/discussion.tex

@@
 \section{Discussion}
+
+As mentioned before, when we evaluate the results of slot extraction, we find three kinds of problems for accuracy: 1) wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched by the patterns.
+We also have recall problems: 1) not enough good alias names to find all the entities.
+2) not enough and powerful patterns to capture all the slot values.
+
+We will use entity resolution methods and other advanced methods to improve the accuracy and recall of entity extraction part.
+
+For slot extraction part, in order to improve the performance, what we need to are: 1) Using multi-class classifiers instead of pattern matching method to extract slot values in order to increase both recall and accuracy for slots “Affiliate”, “AssociateOf”, “FounderOf”, “EmployeeOf”, “FoundedBy” “TopMembers”, “Contact\_Meet\_Entity” and so on.
+2) For special slots, like “Titles”, “DateOfDeath”, “CauseOfDeath”, “AwardsWon”, using different kind of advanced methods, e.g.
+classifiers, matching methods.
+3) Using other NLP tools or using classifiers to overcome the drawbacks of the LingPipe’s inaccurate tags.
+The first and second tasks are the most important tasks we need to do.
 

### 2013-09-18 paper/kbanotebook2013/content/introduction.tex

@@
 \section{Introduction}
+
+In this article we will describe the approach the GatorDSR team from the University of Florida takes at addressing the challenge at NIST’s Text REtrieval Conference (TREC) - Knowledge Base Acceleration track 2013 - Stream Slot Filling (SSF) section.
+In the first section of this article we describe the system design and articulate its evolution during the whole process, challenges and needs that we have overcome.
+In the second section we will go through the details of the NLP techniques we took at streaming slot filling (SSF): given a slot name (entity + relation type) we fill in the slot value (relation value) on structured text documents.
+
+The task is that given certain Wikipedia or Twitter entities (wiki/twitter URLs) and certain relations of interest given in Table 1, extract as many binary relations as possible (hence, slot filling).
+The corpus is in English and is a snapshot of part of the web containing arXiv, social, news, linking, weblog, forum, classifieds, reviews, and memetracker documents.
+Each document is annotated using lingpipe and is called StreamItem, a bundle of StreamItems are put together and serialized as Apache Thrift objects, then compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
+To have a sense of the scale of objects and compression is e.g.
+6mb gpg.xz files → 45 mb thrift objects.
+Some of the documents have null values for their annotation fields.
+
+Since this is \textit{streaming} slot filling, we are only interested in new slot values that were not substantiated earlier in the stream corpus, which ranges from October 2011 to February 2013.
+Below you can view the slot values and their types, the comprehensive description of which can be found at http://www.nist.gov/tac/
+2012/KBP/task\_guidelines/TAC\_KBP\_Slots\_V2.4.pdf and http://projects.ldc.up
+enn.edu/ace/docs/English-Events-Guidelines\_v5.4.3.pdf
+
+\begin{table}[b]
+\caption{Ontology of Slot Name Categories }
+\centering
+
+\begin{tabular}{|c|c|c|}
+\hline 
+PER & FAC & ORG \\ 
+\hline 
+\begin{tabular}{@{}l@{}}Affiliate \\ AssociateOf \\ Contact\_Meet\_PlaceTime \\ AwardsWon \\ 
+DateOfDeath \\ 
+CauseOfDeath\\
+Titles\\
+FounderOf\\
+EmployeeOf\end{tabular}
+  &
+   \begin{tabular}[b]{l}Affiliate \\ Contact\_Meet\_Entity \end{tabular} 
+   & 
+   \begin{tabular}{@{}l@{}}Affiliate \\ TopMembers \\ FoundedBy\end{tabular} \\ 
+\hline 
+\end{tabular} 
+\end{table}
+
+Example 1: "Matthew DeLorenzo and Josiah Vega, both 14 years old and students at Elysian Charter School, were honored Friday morning by C-SPAN and received \$1,500 as well as an iPod Touch after winning a nationwide video contest."
+
+target\_id:  http://en.wikipedia.org/wiki/Elysian\_Charter\_School
+
+Affiliate:  "Matthew DeLorenzo"
+Affiliate:  "Josiah Vega"
+
+NOT an affiliate:  "C-SPAN"
+NOT an affiliate:  "iPod Touch"
+
+Example 2: "Veteran songwriters and performers Ben Mason, Jeff Severson and Jeff Smith will perform on Saturday, April 14 at 7:30 pm at Creative Cauldron at ArtSpace, 410 S. Maple Avenue."
+
+target\_id: http://en.wikipedia.org/wiki/Jeff\_Severson
+
+Affiliate: "Ben Mason"
+Affiliate: "Jeff Severson"
+Affiliate: "Jeff Smith"
+
+NOT an Affiliate: "Creative Caldron"
+NOT an Affiliate: "Art Space"
+
+Example 3:  "Lt. Gov. Drew Wrigley and Robert Wefald, a retired North Dakota district judge and former state attorney general, unveiled the crest Friday during a ceremony at the North Dakota Capitol."
+
+target\_id: http://en.wikipedia.org/wiki/Hjemkomst\_Center
+
+Contact\_Meet\_PlaceTime: "Friday during a ceremony at the North Dakota Capitol"
 

### 2013-09-18 paper/kbanotebook2013/content/system.tex

@@
 \section{System}
+
+In this section we describe the system design for big data analysis regarding TREC KBA the Stream Slot Filling (SSF) task.
+Due to our limited time, human resources and the computational capabilities, we started off by trying to use the off-the-shelf tools for this task.
+Mainly we started by using Scala/Spark.
+But Spark was not as efficient as expected, then we got rid of it and tried to use Scala parallelization itself to do the job, and it didn’t satisfy our needs, there was excessive memory overhead.
+We migrated the core of the system to Java Parallelism APIs and that was not good enough either, we still needed better.
+So we built our own parallel system which in actual performance had the least of overhead, the least memory consumption and  the most robust memory model which avoided unpredictable CPU stalls.
+In what follows we will describe each step of this evolution in details.
+The system that we run our pipeline over was a 32 core server having 64GB of memory.
+
+\subsection{Spark}
+
+Spark is “an open source cluster computing system that aims to make data analytics fast — both fast to run and fast to write.
+To run programs faster, Spark provides primitives for in-memory cluster computing: your job can load data into memory and query it repeatedly much more quickly than with disk-based systems like Hadoop MapReduce.To make programming faster, Spark provides clean, concise APIs in Scala, Java and Python.
+You can also use Spark interactively from the Scala and Python shells to rapidly query big datasets” \cite{ferc11}.
+
+Spark is supposed to be an in memory map-reduce versus Hadoop which accesses disk in each iteration.
+Spark can also run on the multi-cores of a single processors by replicating the binary code of the system.
+For example by replicating Jar files of the system code into each process local memory and running each in parallel while having an abstract layers to merge/match results and recover from failures.
+We experimented with various parameters trying to maximize the performance of Spark in processing the corpus and extracting entity StreamItems.
+
+The initial system was coded in Scala (which has goals for scalability) with double systems being coded along side with each other to explore the capabilities of Scala/Spark and pick the best out of each world.
+One approach was trying to be as smart as possible trying to use all the cool features of Scala/Spark with the hope that all these optimizations will help us in the long run; another approach was looking into KISS metrics (Keep It Stupid Simple) the ideology to make sure we do as little processing per data unit as possible, keep as little data references as possible and taking care of everything ourselves instead of letting Spark decide for us.
+
+Unfortunately for our scenario it did not perform as expected.
+It seems to be targeted at large scale cluster systems whereas for small scale systems it was not as performant.
+JVM was too slow Garbage Collection caused large pauses because of memory fragmentation.
+We really needed more control over the memory usage.
+Spark suffered from huge memory dependencies in multi-stage map-reduce tasks which would be used in failure recovery in big data cluster processing.
+This is an essential need for such a system as otherwise there is no point to migrate from a generic Hadoop system to Spark.
+Reliability overhead was a very big disadvantage of Spark which sacrificed performance.
+The CPU usage was at 100% memory use at 100% Java heap to maximum, plentiful of monitoring threads and after a while the system started thrashing.
+We even got in touch with Matei Zaharia, one the main designers and developers of Spark at UC Berkeley but the overall conversation was not on our side with our constraints.
+Spark RDD does not perform better that parallel scala. The intermediate collections they create also cause GC problems and there is also a non-trivial startup time for each job.
+
+On huge memory consumption of spark, one of the features of spark we ignored is that in spark if a system fails while the map-reduce is still in progress it can specifically rebuild that section and doesn't need to do the whole job from scratch.
+It makes sense if they keep references of the upstream objects even if a piece of a multi-stage map-reduce is done for reliability and not release its memory.
+
+Given that the already generated lingpipe is not very accurate, our initial ambition was at using StanforNLP.
+Using Spark and StanfordNLP our statistics were at around 500 documents processing in an overnight execution which was unacceptably slow given our data scale challenge.
+
+\subsection{Scala Parallelism}
+
+From Spark to scala parallelization: In Scala, using 'map' or 'filter' to iterate over large collections creates intermediate collections.
+These variable may hold reference to large objects and delay their disposal.
+Instead using a mix between 'withFilter' and 'foreach' let's you iterate without creating another intermediate collection.
+Conceptually a reduce job is an aggregate over the set of tasks that have been mapped, in our scenario we could bypass this step and process the corpus regardless of different sections, hence avoiding map-reduce.
+Onthe other hand the the method scala offers to download/decrypt the files (ProcessBuilder class) leaks resources, which was a bug that was later on fixed in Scala 2.10 form version 2.92 that we were using on our server.
+
+The take-away was that Scala is a very powerful language and can help in concise code for map-reduce type of jobs that can be coded extremely fast.
+and Spark is a powerful tool but neither could prove their performance to us even after plenty experiments and parameter adjustments.
+In the long run, scala could not get rid of memory references and after a while we were clogged up in heap space.
+
+Below you can view the profiling of the system in scala using Java VisualVM. As you can see the CPU utilization is very unpredictable and we lose CPU utilization after a while.
+\begin{table}
+\caption{Ontology of Slot Name Categories }
+\centering
+\begin{tabular}[c]{ |l| c |r| } \hline
+  1 & 2 & 3 \\\hline
+  4 & 5 & 6 \\\hline
+  7 & 8 & 9 \\\hline
+\end{tabular}
+\end{table}
+
+Thus ended up being saturated as below - zero CPU utilization, Heap overloaded, almost all threads sleeping:
+
+\begin{table}
+\caption{Ontology of Slot Name Categories }
+\centering
+\begin{tabular}[c]{ |l| c |r| } \hline
+  1 & 2 & 3 \\\hline
+  4 & 5 & 6 \\\hline
+  7 & 8 & 9 \\\hline
+\end{tabular}
+\end{table}
+
+After fixing memory issues we could optimize to:
+
+\begin{table}
+\caption{Ontology of Slot Name Categories }
+\centering
+\begin{tabular}[c]{ |l| c |r| } \hline
+  1 & 2 & 3 \\\hline
+  4 & 5 & 6 \\\hline
+  7 & 8 & 9 \\\hline
+\end{tabular}
+\end{table}
+
+The jump in the number of the classes was due to the java profiling tool we use JVisualVM.
+
+\subsection{ Java Parallelism API}
+
+After porting the project to Java and migrating scala sbt to java's Maven build tool and going through some major optimizations we could achieve several major gains:
+
+\begin{itemize}
+  \item Reduce the memory usage by 73% (from peak 20GB to 5GB).
+  \item  We can use the newly available memory for fast clustering, classification, etc. for slot filling.
+  \item Reduce unwanted run-time class generation by 80% (from 8,000 loaded
+   classes to 1,500)
+   \item Reduce \# of threads by 47% (Live peak from 138 to 72)
+
+    \ldots
+\end{itemize}
+
+cons:
+
+\begin{itemize}
+  \item Increased run-time by 3% (MB/hour). scala parallel engine acts smarter
+   than we just manually trying to adjust the parameters in java.
+
+    \ldots
+\end{itemize}
+
+An interesting phenomona that happened was that JVM appeared to be adapting to the behavior of the system, after around 20-30 minutes of execution JVM adapted heap size by 50% while still maintaining near optimal performance.
+You can review this phenomena in the figures below.
+
+We tried various parameters (\# of threads 31,32, 64, 128, 256) and via extensive simulations 31 was the optimal one but the margin was very small from 32 (one thread per core), this could be due the race conditions at the server for other services running.
+The performance was linear over time.
+The code base is as simple as possible and as smart as possible to ensure scalability demands.
+
+\begin{table}
+\caption{Ontology of Slot Name Categories }
+\centering
+\begin{tabular}[c]{ |l| c |r| } \hline
+  1 & 2 & 3 \\\hline
+  4 & 5 & 6 \\\hline
+  7 & 8 & 9 \\\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{Ontology of Slot Name Categories }
+\centering
+\begin{tabular}[c]{ |l| c |r| } \hline
+  1 & 2 & 3 \\\hline
+  4 & 5 & 6 \\\hline
+  7 & 8 & 9 \\\hline
+\end{tabular}
+\end{table}
+
+The code is as simple as possible to ensure there's no reference kept any where and there is no extra processing.
+CPU utilization is at 98% without any kernel overhead (its all our threads unlike before that kernel took over the CPU after a while) and adding more threads just added to more delays.
+
+To put things into perspective and talk in numbers:
+
+\begin{itemize}
+  \item org.apache.thrift is the dominant CPU time user 
+\item Then is the decompression of thrift objects and decrypt the RSA encrypted data (note that asymetric cryptography is very expensive and we are looking at some thing like 2 seconds per file)
+\item Then is streamcorpus (the TREC KBA library to deserialize from their StreamItems objects). 
+\item Our code takes less than 3\% of the CPU time. 
+\end{itemize}
+
+\begin{table}
+\caption{Ontology of Slot Name Categories }
+\centering
+\begin{tabular}[c]{ |l| c |r| } \hline
+  1 & 2 & 3 \\\hline
+  4 & 5 & 6 \\\hline
+  7 & 8 & 9 \\\hline
+\end{tabular}
+\end{table}
+
+\subsection{Bare Java Thread Pool}
+
+Following our efforts to speed up the system we even went down more low level and created our own thread pool instead of using Java's ExecutorService Library.
+Still according to java visualvm more than 40\% of CPU time is  taken by sun.rmi.transport.tcp.TCPTransport\$ConnectionHandler.run().
+In ExecutorService this number was even higher at 60\%-80\%.
+We were expecting ExecutorService to be implicitly taking up TCP connections for inter-thread communications, but this experiment proves that this is not correct and this method call is related to even lower java issues which is out of our reach.
+
+At this point we are running at 20GB/hour on 64 threads with 98\% CPU utilization.
+A multi-processing idea that we had did not work and java was causing troubles at memory management.
+These changes increased processing speed by 65\% from 12-13 GB/hours that we were getting before.
+Not bad!
+Some more micro optimizations took us even farther to 22GB per hours of encrypted and compressed thrift objects.
+
+\subsection{Back to C++}
+
+At the end we developed a C++ version of the system to go through the corpus in batch process, as we didn’t have any more time on processing the data, but kept the entity matcher and pipeline in Java for ease of pipeline development as time was tight and we were short on human resources.
+With C++ it was going at about 74-100 GB/hour on bare string matching but this was not an option for the development of the pipeline and using NLP tools and libraries.
+
+\subsection{Other notes}
+
+Java’s library for decompressing the .xz files performed faster than using the Linux file systems.
+We believe this is because keeping a 45mb file in memory and moving it is slower than decompressing it in java and streaming into the output to the thrift builder.
+
 % Note: Describe the algorithms of each phase

### 2013-09-18 paper/kbanotebook2013/paper.tex

@@
 \documentclass{article}
+
+\usepackage{cite }
 
@@
 \author {%
-  Morteza Shahriari\\
+  Morteza Shahriari Nia\\
   University of Florida\\
-  Department of Computer \& Information Science \& Engineering\\
+  Department of Electrical \& Computer Engineering\\
   Gainesville, Florida, USA\\
@@
 
+%\bibliographystyle{acm}
+%\bibliography{citation}
+
 \bibliographystyle{acm}
-\bibliographystyle{citation}
+\bibliography{citation}
 

### 2013-09-22 paper/kbanotebook2013/content/introduction.tex
Major rewriting of paper in latex + schematic diagram + reference + precision/recall statistics

@@
 
-The task is that given certain Wikipedia or Twitter entities (wiki/twitter URLs) and certain relations of interest given in Table 1, extract as many binary relations as possible (hence, slot filling).
+The task is that given certain Wikipedia or Twitter entities (wiki/twitter URLs) and certain relations of interest given in Table 1, extract as many triple relations as possible (hence, slot filling).
+This can be used to automatically populate knowledgebases such as free-base or DBPedia or even filling in the information boxes at Wikipedia.
 The corpus is in English and is a snapshot of part of the web containing arXiv, social, news, linking, weblog, forum, classifieds, reviews, and memetracker documents.
 Each document is annotated using lingpipe and is called StreamItem, a bundle of StreamItems are put together and serialized as Apache Thrift objects, then compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
-To have a sense of the scale of objects and compression is e.g.
-6mb gpg.xz files → 45 mb thrift objects.
+To have a sense of the scale of objects and compression as an example a 6mb gpg.xz files would become 45 mb thrift objects which can contain a couple of thousand StreamItems depending on their size.
 Some of the documents have null values for their annotation fields.
@@
 Since this is \textit{streaming} slot filling, we are only interested in new slot values that were not substantiated earlier in the stream corpus, which ranges from October 2011 to February 2013.
-Below you can view the slot values and their types, the comprehensive description of which can be found at http://www.nist.gov/tac/
-2012/KBP/task\_guidelines/TAC\_KBP\_Slots\_V2.4.pdf and http://projects.ldc.up
-enn.edu/ace/docs/English-Events-Guidelines\_v5.4.3.pdf
+Below you can view the slot values and their types, the comprehensive description of which can be found at \cite{tackbp} and \cite{aec}
 
@@
 
+In our approach we will perform pattern matching that conforms to each slot value along with post-processings to eliminate noisy outputs.
+
 % Motivation

### 2013-09-22 paper/kbanotebook2013/content/system.tex
Major rewriting of paper in latex + schematic diagram + reference + precision/recall statistics

--- 2013-09-16 paper/kbanotebook2013/content/system.tex
@@
-\section{System}
+\begin{figure}[b]
+\centering
+\includegraphics[width=4.5in]{./images/system.eps}
+\vspace*{-.1in} \caption{Pipeline Design }\label{fig:system}
+\vspace*{-.2in}
+\end{figure}
+
+\section{Pipeline}
+
+In this section we provide a high level description of the pipeline(system) design for big data analysis regarding TREC KBA the Stream Slot Filling (SSF) task.
+Our pipeline of processing the corpus consists of a two layer indexing system main section in our system regarding indexing the corpus, We started off by trying to use the off-the-shelf tools for this task.
+Mainly we started by using Scala/Spark\cite{ferc11} to benefit from the paralellization performance there.
+Spark was not as efficient as expected and the overhead was much more than tolerable.
+We tried to use Scala parallelization itself to do the job, and unfortunately it did not satisfy our needs, there was excessive memory overhead on map reduce jobs.
+We migrated the core of the system to Java Parallelism APIs and that was not good enough either, we wanted better.
+So we built our own parallel system which in actual performance had the least of overhead, the least memory consumption and the most robust memory model which avoided unpredictable CPU stalls on garbage collections in processing the corpus.
+In what follows we will describe each step of this evolution in details.
+Figure \ref{fig:system} shows a schematic view of the system.
+The platform that we run our pipeline over was a 32 core server having 64GB of memory.
+
 % Note: Describe the algorithms of each phase
@@
 
-\subsection{Cumulative Citation Recommentation}
+\subsection{Cumulative Citation Recommendation}
+
+Regarding Cumulative Citation Recommendation we perform exact string matching and treat all the documents that mention an entity equally likely to be citable.
+For future iterations of the paper we have ideas on how to score documents based on their likelihood of citation worthiness but for this iterations we treat all mentioning documents equally likely.
+One of the reasons for this is that in former TREC KBA reports \cite{JFrank12} there were observations of how non-mentioning documents have highly low chance of being citeable in wikipedia.
+So we take on that and ignore non-citing documents.
+Regarding mentioning but garbage, neutral or central documents we produce more slot values which can be later on filtered out in the high accuracy filter section.
 
@@
 
+Stream slot filling is done by pattern matching documents with manually produced patterns for slots of interest.
+The way we do this is by observing a sentence that has a mention of the entity or one of its coreferences.
+An anchor word in the sentence related to the slot name is located and we match either left or right of the anchor word for potential slot values.
+
 \subsection{Post Processing Algorithm}
+
+The SSF output of many extractions is noisy.
+The data contains duplicates and incorrect extractions.
+We can define rules to sanitize the output only using the information present in the SSF file.
+The file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy.
+.
+We define two classes of rules deduplication rules and inference rules.

### 2013-09-22 paper/kbanotebook2013/content/implementation.tex

@@
 Based on our observation this is a very accurate heuristic and provides us with lots of famous aliases of the entities.
-To consider other typical cases we consider some generic first name last name order swapping conventions such as Bill Gates -> Gates, Bill.
+To consider other typical cases we consider some generic first name last name order swapping conventions such as Bill Gates -\textgreater Gates, Bill.
 
@@
 Lets’s first look at one example of the first kind of patterns.
-For slot FounderOf, we have this pattern: <PER, FounderOf, founder, right, ORG>.
+For slot FounderOf, we have this pattern: \textless PER, FounderOf, founder, right, ORG\textgreater.
 PER means that the entity we are finding slot values for is a PER entity; FounderOf means this is a pattern for FounderOf slot.
@@
 
-Here is an example for the second type: <PER, AwardsWon, awarded, right, NP>, NP meaning noun phrase.
+Here is an example for the second type: \textless PER, AwardsWon, awarded, right, NP\textgreater, NP meaning noun phrase.
 This pattern can be interpreted as that we are looking for a noun phrase after the “awarded” since that noun phrase could possibly represent an award.
@@
 
-Another example for the third type: <PER, DateOfDeath, died, right, last night>.
+Another example for the third type: \textless PER, DateOfDeath, died, right, last night\textgreater.
 In this pattern, “last night” means we are looking for exactly the phrase “last night” to the right of “died”.

### 2013-09-22 paper/kbanotebook2013/content/conclusion.tex

@@
 \section{Conclusions}
+
+We experimented through different tools and approaches to best process the massive amounts of data on the platform that we had available to us.
+We generate aliases for wikipedia entities using Wiki API and extract some aliases from wikipedia pages text itself.
+On twitter entities we extract aliases manually as it is part of the rule of the KBA track.
+We process   documents that mention entities for slot value extraction.
+Slot values are determined using pattern matching over coreferences of entities in sentences.
+Finally post processing will filter, cleanup and infers some new slot values to enhance recall and accuracy.
+
+We noticed that some tools that claim to be performant for using the hardware capabilities at hand sometimes don't really work as claimed and you should not always rely on one without a thorough A/B testing of performance which we ended up in generating our in-house system for processing the corpus and generating the index.
+Furthermore, on extracting slot values, pattern matching might not be the best options but definitely can produce some good results at hand.
+We have plans on generating classifiers for slot value extraction purposes.
+Entity resolution on the other hand was a topic we spent sometime on but could not get to stable grounds for it.
+Entity resolution will distinguish between entities of the same name but different contexts.
+Further improvements on this component of the system are required.
 

### 2013-09-22 paper/kbanotebook2013/content/results.tex

@@
 
-\begin{table}[b]
-\caption{SSF Performance Measure on Submission Infer }
+\begin{table}
+\caption{SSF Accuracy Measure on Submission Infer }
 \centering
@@
 \hline 
-Affiliate & \% & \% & \% \\ \hline 
-AssociateOf & \% & \% & \%  \\ \hline 
-AwardsWon & \% & \% & \%  \\ \hline 
-CauseOfDeath & \% & \% & \%  \\ \hline 
-Contact\_Meet\_Entity & \% & \% & \%  \\ \hline 
-Contact\_Meet\_PlaceTime & \% & \% & \%  \\ \hline 
-DateOfDeath & \% & \% & \%  \\ \hline 
-EmployeeOf & \% & \% & \%  \\ \hline 
-FoundedBy & \% & \% & \%  \\ \hline 
-FounderOf & \% & \% & \%  \\ \hline 
-Titles & \% & \% & \%  \\ \hline 
-TopMembers & \% & \% & \%  \\ \hline
+Affiliate & 1\% & 95\% & 5\% \\ \hline 
+AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
+AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
+CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
+Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 
+Contact\_Meet\_PlaceTime & 5\% & 20\% & 85\%  \\ \hline 
+DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
+EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
+FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
+FounderOf & 50\% & 0\% & 50\%  \\ \hline 
+Titles & 55\% & 0\% & 45\%  \\ \hline 
+TopMembers & 33\% & 17\% & 50\%  \\ \hline
+
+\end{tabular} 
+\end{table}
+
+\begin{table}
+\caption{Recall Measure on Submission Infer }
+\centering
+\begin{tabular}{|c|p{3cm}|p{4cm}|}
+\hline 
+ & Total instances of slot value found & \# of entities covered by slot value \\ 
+\hline 
+Affiliate & 108598 & 80 \\ \hline 
+AssociateOf & 25278 & 106 \\ \hline 
+AwardsWon & 38 & 14 \\ \hline 
+CauseOfDeath & 0 & 0 \\ \hline 
+Contact\_Meet\_Entity & 191 & 8 \\ \hline 
+Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
+DateOfDeath & 87 & 14 \\ \hline 
+EmployeeOf & 75 & 16 \\ \hline 
+FoundedBy & 326 & 30 \\ \hline 
+FounderOf & 302 &  29 \\ \hline 
+Titles & 26823 & 118 \\ \hline 
+TopMembers & 314 & 26 \\ \hline
 

### 2013-09-23 paper/kbanotebook2013/content/discussion.tex
added some formatting changes to make the file easier to edit

@@
 
-As mentioned before, when we evaluate the results of slot extraction, we find three kinds of problems for accuracy: 1) wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched by the patterns.
-We also have recall problems: 1) not enough good alias names to find all the entities.
-2) not enough and powerful patterns to capture all the slot values.
+As mentioned before, when we evaluate the results of slot extraction, we find 
+three kinds of problems for accuracy: 1) wrong entities found; 2) wrong tags 
+by the Lingpipe; 3) wrong results matched by the patterns.  We also have 
+recall problems: 1) not enough good alias names to find all the entities. 2) 
+not enough and powerful patterns to capture all the slot values.
 
-We will use entity resolution methods and other advanced methods to improve the accuracy and recall of entity extraction part.
+We will use entity resolution methods and other advanced methods to improve 
+the accuracy and recall of entity extraction part.
 
-For slot extraction part, in order to improve the performance, what we need to are: 1) Using multi-class classifiers instead of pattern matching method to extract slot values in order to increase both recall and accuracy for slots “Affiliate”, “AssociateOf”, “FounderOf”, “EmployeeOf”, “FoundedBy” “TopMembers”, “Contact\_Meet\_Entity” and so on.
-2) For special slots, like “Titles”, “DateOfDeath”, “CauseOfDeath”, “AwardsWon”, using different kind of advanced methods, e.g.
-classifiers, matching methods.
-3) Using other NLP tools or using classifiers to overcome the drawbacks of the LingPipe’s inaccurate tags.
-The first and second tasks are the most important tasks we need to do.
+For slot extraction part, in order to improve the performance, what we need to 
+are: 1) Using multi-class classifiers instead of pattern matching method to 
+extract slot values in order to increase both recall and accuracy for slots
+``Affiliate'', ``AssociateOf'', ``FounderOf'', ``EmployeeOf'', ``FoundedBy'',
+``TopMembers'', ``Contact\_Meet\_Entity'' and so on. 2) For special slots, 
+like “Titles”, “DateOfDeath”, “CauseOfDeath”, “AwardsWon”, using different 
+kind of advanced methods, e.g.\ classifiers, matching methods. 3) Using other 
+NLP tools or using classifiers to overcome the drawbacks of the LingPipe’s 
+inaccurate tags. The first and second tasks are the most important tasks we 
+need to do.
 

### 2013-09-23 paper/kbanotebook2013/content/implementation.tex
added some formatting changes to make the file easier to edit

@@
 
-We extract aliases for entities from wikipedia automatically both using API and using the actual page content, then apply pattern matching rules for slot value extraction.
+We extract aliases for entities from Wikipedia automatically both using API 
+and using the actual page content, then apply pattern matching rules for slot 
+value extraction.
 
@@
 
-We use Wikipedia API to get some aliases automatically.
-This is done by retrieving backlink references (redirects of a wiki entity).
-Unfortunately this is not good enough and to enhance recall we need more aliases.
-To have better use of a wiki page we parse HTML DOM of the page, then use regular expressions to extract the bold phrases of the first paragraph as alias of the actual entity.
-Based on our observation this is a very accurate heuristic and provides us with lots of famous aliases of the entities.
-To consider other typical cases we consider some generic first name last name order swapping conventions such as Bill Gates -\textgreater Gates, Bill.
+We use Wikipedia API to get some aliases automatically. This is done by 
+retrieving backlink references (redirects of a wiki entity). Unfortunately 
+this is not good enough and to enhance recall we need more aliases. To have 
+better use of a wiki page we parse HTML DOM of the page, then use regular 
+expressions to extract the bold phrases of the first paragraph as alias of the 
+actual entity. Based on our observation this is a very accurate heuristic and 
+provides us with lots of famous aliases of the entities. To consider other 
+typical cases we consider some generic first name last name order swapping 
+conventions such as Bill Gates -\textgreater Gates, Bill.
 
@@
 
-In this system, we use pattern matching methods to find corresponding slot values for entities.
-The procedure is: 1) Find stream items that contain the entities by using alias names of the entities.
-2) Inside these stream items, fetch the sentences which contain entities by using alias names and the coreference information provided by Lingpipe tags.
-3) Use these sentences to match existing patterns.
-4) When patterns matched, generate SSF results.
+In this system, we use pattern matching methods to find corresponding slot 
+values for entities. The procedure is: 1) Find stream items that contain the 
+entities by using alias names of the entities. 2) Inside these stream items, 
+fetch the sentences which contain entities by using alias names and the 
+coreference information provided by Lingpipe tags. 3) Use these sentences to 
+match existing patterns. 4) When patterns matched, generate SSF results.
 
-The format of the patterns is consist of five fields: 1) the type of the entity.
+The format of the patterns is consist of five fields:
+1) the type of the entity. 
 2) the slot name.
 3) the pattern content.
-4) the direction of the slot valule to the entity.
-5) the type of the slot values.
-When we match one pattern, we match all the fields except the third field.
-The type of slot values could be the entity type tagged by Linpipe, noun phrase tagged by OpenNLP and the time phrases we hard-code.
-For these three kinds of patterns, we implement them in different ways accordingly.
+4) the direction of the slot value to the entity.
+5) the type of the slot values. When we match one pattern, we match all the 
+fields except the third field. The type of slot values could be the entity 
+type tagged by Lingpipe, noun phrase tagged by OpenNLP and the time phrases we 
+hard-code. For these three kinds of patterns, we implement them in different 
+ways accordingly.
 
-Next we will explain the patterns with more details.
-Lets’s first look at one example of the first kind of patterns.
-For slot FounderOf, we have this pattern: \textless PER, FounderOf, founder, right, ORG\textgreater.
-PER means that the entity we are finding slot values for is a PER entity; FounderOf means this is a pattern for FounderOf slot.
-founder is the ankor word we are trying to match in the sentence text; right means that we are going to the right part of the sentence to match the pattern and find the slot value; ORG means the slot value should be a ORG entity.
+Next we will explain the patterns with more details. Lets’s first look at one 
+example of the first kind of patterns. For slot FounderOf, we have this
+pattern: \textless PER, FounderOf, founder, right, ORG\textgreater. PER means 
+that the entity we are finding slot values for is a PER entity; FounderOf 
+means this is a pattern for FounderOf slot. Founder is the anchor word we are 
+trying to match in the sentence text; right means that we are going to the 
+right part of the sentence to match the pattern and find the slot value; ORG 
+means the slot value should be a ORG entity.
 
-Here is an example for the second type: \textless PER, AwardsWon, awarded, right, NP\textgreater, NP meaning noun phrase.
-This pattern can be interpreted as that we are looking for a noun phrase after the “awarded” since that noun phrase could possibly represent an award.
-Since titles and awards are usually not the Lingpipe entities, we use the OpenNLP noun phrase chunker to fetch the noun phrases.
+Here is an example for the second type: \textless PER, AwardsWon, awarded, 
+right, NP\textgreater, NP meaning noun phrase. This pattern can be interpreted 
+as that we are looking for a noun phrase after the “awarded” since that noun 
+phrase could possibly represent an award. Since titles and awards are usually 
+not the Lingpipe entities, we use the OpenNLP noun phrase chunker to fetch the 
+noun phrases.
 
-Another example for the third type: \textless PER, DateOfDeath, died, right, last night\textgreater.
-In this pattern, “last night” means we are looking for exactly the phrase “last night” to the right of “died”.
-This pattern is inspired by the intuition that in news articles, people often mention that somebody died last night instead of mentioning the accurate date information and Lingpipe tends not to tag phrases like “last night” as a DATE entity.
+Another example for the third type: \textless PER, DateOfDeath, died, right, 
+last night\textgreater. In this pattern, “last night” means we are looking for 
+exactly the phrase “last night” to the right of “died”. This pattern is 
+inspired by the intuition that in news articles, people often mention that 
+somebody died last night instead of mentioning the accurate date information 
+and Lingpipe tends not to tag phrases like “last night” as a DATE entity.
 
 To improve recall, we introduce generic patterns that can generate many results.
-But these patterns generate many errors, too.
-Thus there is a trade-off between the accuracy and recall.
-This is one drawback of using pattern matching method, meaning it is really hard to find good patterns with both high accuracy and recall.
+But these patterns generate many errors, too. Thus there is a trade-off 
+between the accuracy and recall. This is one drawback of using pattern 
+matching method, meaning it is really hard to find good patterns with both 
+high accuracy and recall.
 
-For accuracy, we have found that there are three major kinds of errors: 1) wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched by the patterns.
-We solve the first problem by using the wikipedia or twitter information of the entities to get better alias names.
-And we use post-processing to reduce the second and third types of errors.
+For accuracy, we have found that there are three major kinds of errors: 1) 
+wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched 
+by the patterns. We solve the first problem by using the wikipedia or twitter 
+information of the entities to get better alias names. And we use
+post- processing to reduce the second and third types of errors.
 
@@
 
-The SSF output of many extractions is noisy.
-The data contains duplicates and incorrect extractions.
-We can define rules to sanitize the output only using the information present in the SSF file.
-The file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy.
-.
-We define two classes of rules deduplication rules and inference rules.
+The SSF output of many extractions is noisy. The data contains duplicates and 
+incorrect extractions. We can define rules to sanitize the output only using 
+the information present in the SSF file. The file is processed in time order, 
+in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
+two classes of rules deduplication rules and inference rules.
 
-The output contains many duplicate entries.
-As we read the list of extrated slots we create rules to define "duplicate".
-Duplicates can be present in a window of rows; we use a window size of 2 meaning we only be adjacent rows.
-Two rows are duplicates if 1) they have the same exact extraction, 2) if the rows have the same slot name and a similar slot value and 3) if the extracted sentence for a particular slot types come from the same sentence.
+The output contains many duplicate entries. As we read the list of extrated 
+slots we create rules to define "duplicate". Duplicates can be present in a 
+window of rows; we use a window size of 2 meaning we only be adjacent rows. 
+Two rows are duplicates if 1) they have the same exact extraction, 2) if the 
+rows have the same slot name and a similar slot value and 3) if the extracted 
+sentence for a particular slot types come from the same sentence.
 
  New slots can be deduced from existing slots by defineing inference rules. 
-For example, two slots for the task are "FounderOf" and "FoundedBy".
-A safe assumtion is these slot names are biconditional logical connectives with the entities and slot values.
-Therefore, we can express a rule "X FounderOf Y" equals "Y FoundedBy X" where X and Y are single unique entities.
-Additionally, we found that the slot names "Contact\_Meet\_PlaceTime" could be infered as "Contact\_Meet\_Entity" if the Entity was a FAC and the extracted sentence contained an additional ORG/FAC tag.
+ For example, two slots for the task are "FounderOf" and "FoundedBy". A safe 
+ assumtion is these slot names are biconditional logical connectives with the 
+ entities and slot values. Therefore, we can express a rule "X FounderOf Y" 
+ equals "Y FoundedBy X" where X and Y are single unique entities. Additionally,
+ we found that the slot names "Contact\_Meet\_PlaceTime" could be infered as
+ "Contact\_Meet\_Entity" if the Entity was a FAC and the extracted sentence 
+ contained an additional ORG/FAC tag.  
+We also remove erronious slots that have extractions that are several pages in 
+length or tool small. Errors of extracting long sentences can typically be 
+attributed to poor sentence parsing of web documents. We have some valid
+"small" extractions. For example a comma may separate a name and a title
+(e.g. "John, Professor at MIT"). But such extraction rules can be particularly 
+noisy, so we check to see if the extracted values have good entity values.
 
-We also remove erronious slots that have extractions that are several pages in length or tool small.
-Errors of extracting long sentences can typically be attributed to poor sentence parsing of web documents.
-We have some valid "small" extractions.
-For example a comma may separate a name and a title (e.g.
-"John, Professor at MIT").
-But such extraction rules can be particularly noisy, so we check to see if the extracted values have good entity values.
-
-The aim in post processing was to sanitize the results increasing the precision of the results by eliminating spurrious results.
+The aim in post processing was to sanitize the results increasing the 
+precision of the results by eliminating spurrious results.
 
@@
 
-The missing twitter entities are more than the 50\% of the twitter entities we need to work on and this is a very very bad performance.
-One reason could be that those entities are not very famous.
-For example Brenda Weiler google search result is 860,000 documents our of billions of web documents.
-For our small portion of the web it might make sense.
-If you pay attention to the histogram of the entities found you'll note that more than half of the entities have appeared in less than 10 StreamItems.
-A good portion have appeared only once.
-Which the document does not necessarily have good information for us.
+The missing twitter entities are more than the 50\% of the twitter entities we 
+need to work on and this is a very very bad performance. One reason could be 
+that those entities are not very famous. For example Brenda Weiler google 
+search result is 860,000 documents our of billions of web documents. For our 
+small portion of the web it might make sense. If you pay attention to the 
+histogram of the entities found you'll note that more than half of the 
+entities have appeared in less than 10 StreamItems. A good portion have 
+appeared only once. Which the document does not necessarily have good 
+information for us.
 
-A theory is that we are falling behind because we are using the cleansed version of the corpus.
-We believe there has been a reason that TREC has included the actual HTML document as well as the cleansed version.
-This definitely will convey some information to us.
-If it was as easy as reading some clean text they wouldn't bother including so much data for teams to be useless.
-So we guess is that we are missing some information from not using the actual document.
-And, we are looking for tokens with entity value set which will depend us dramatically on the accuracy of lingpipe, which is a fast algorithm but is not as good as other NLP tools can be e.g.
-Stanford NLP.
+A theory is that we are falling behind because we are using the cleansed 
+version of the corpus. We believe there has been a reason that TREC has 
+included the actual HTML document as well as the cleansed version. This 
+definitely will convey some information to us. If it was as easy as reading 
+some clean text they wouldn't bother including so much data for teams to be 
+useless. So we guess is that we are missing some information from not using 
+the actual document. And, we are looking for tokens with entity value set 
+which will depend us dramatically on the accuracy of lingpipe, which is a fast 
+algorithm but is not as good as other NLP tools can be e.g. Stanford NLP.
 

### 2013-09-23 paper/kbanotebook2013/content/introduction.tex
added some formatting changes to make the file easier to edit

@@
 
-In this article we will describe the approach the GatorDSR team from the University of Florida takes at addressing the challenge at NIST’s Text REtrieval Conference (TREC) - Knowledge Base Acceleration track 2013 - Stream Slot Filling (SSF) section.
-In the first section of this article we describe the system design and articulate its evolution during the whole process, challenges and needs that we have overcome.
-In the second section we will go through the details of the NLP techniques we took at streaming slot filling (SSF): given a slot name (entity + relation type) we fill in the slot value (relation value) on structured text documents.
+In this article we will describe the approach the GatorDSR team from the 
+University of Florida takes at addressing the challenge at NIST’s Text 
+REtrieval Conference (TREC) - Knowledge Base Acceleration track 2013 - Stream 
+Slot Filling (SSF) section. In the first section of this article we describe 
+the system design and articulate its evolution during the whole process, 
+challenges and needs that we have overcome. In the second section we will go 
+through the details of the NLP techniques we took at streaming slot filling
+(SSF): given a slot name (entity + relation type) we fill in the slot value
+(relation value) on structured text documents.
 
-The task is that given certain Wikipedia or Twitter entities (wiki/twitter URLs) and certain relations of interest given in Table 1, extract as many triple relations as possible (hence, slot filling).
-This can be used to automatically populate knowledgebases such as free-base or DBPedia or even filling in the information boxes at Wikipedia.
-The corpus is in English and is a snapshot of part of the web containing arXiv, social, news, linking, weblog, forum, classifieds, reviews, and memetracker documents.
-Each document is annotated using lingpipe and is called StreamItem, a bundle of StreamItems are put together and serialized as Apache Thrift objects, then compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
-To have a sense of the scale of objects and compression as an example a 6mb gpg.xz files would become 45 mb thrift objects which can contain a couple of thousand StreamItems depending on their size.
-Some of the documents have null values for their annotation fields.
+The task is that given certain Wikipedia or Twitter entities 
+(wiki/twitter URLs) and certain relations of interest given in Table 1, 
+extract as many triple relations as possible (hence, slot filling). This can 
+be used to automatically populate knowledgebases such as free-base or DBPedia 
+or even filling in the information boxes at Wikipedia. The corpus is in 
+English and is a snapshot of part of the web containing arXiv, social, news, 
+linking, weblog, forum, classifieds, reviews, and memetracker documents. Each 
+document is annotated using lingpipe and is called StreamItem, a bundle of 
+StreamItems are put together and serialized as Apache Thrift objects, then 
+compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
+and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
+To have a sense of the scale of objects and compression as an example a 6mb
+gpg.xz files would become 45 mb thrift objects which can contain a couple of 
+thousand StreamItems depending on their size. Some of the documents have null 
+values for their annotation fields.
 
-Since this is \textit{streaming} slot filling, we are only interested in new slot values that were not substantiated earlier in the stream corpus, which ranges from October 2011 to February 2013.
-Below you can view the slot values and their types, the comprehensive description of which can be found at \cite{tackbp} and \cite{aec}
+Since this is \textit{streaming} slot filling, we are only interested in new 
+slot values that were not substantiated earlier in the stream corpus, which 
+ranges from October 2011 to February 2013. Below you can view the slot values 
+and their types, the comprehensive description of which can be found at
+\cite{tackbp} and \cite{aec}
 
@@
 
-Example 1: "Matthew DeLorenzo and Josiah Vega, both 14 years old and students at Elysian Charter School, were honored Friday morning by C-SPAN and received \$1,500 as well as an iPod Touch after winning a nationwide video contest."
+Example 1: "Matthew DeLorenzo and Josiah Vega, both 14 years old and students 
+at Elysian Charter School, were honored Friday morning by C-SPAN and received 
+\$1,500 as well as an iPod Touch after winning a nationwide video contest."
 
@@
 
-Example 2: "Veteran songwriters and performers Ben Mason, Jeff Severson and Jeff Smith will perform on Saturday, April 14 at 7:30 pm at Creative Cauldron at ArtSpace, 410 S. Maple Avenue."
+Example 2: "Veteran songwriters and performers Ben Mason, Jeff Severson and 
+Jeff Smith will perform on Saturday, April 14 at 7:30 pm at Creative Cauldron 
+at ArtSpace, 410 S. Maple Avenue."
 
@@
 
-Example 3:  "Lt. Gov. Drew Wrigley and Robert Wefald, a retired North Dakota district judge and former state attorney general, unveiled the crest Friday during a ceremony at the North Dakota Capitol."
+Example 3:  "Lt. Gov. Drew Wrigley and Robert Wefald, a retired North Dakota 
+district judge and former state attorney general, unveiled the crest Friday 
+during a ceremony at the North Dakota Capitol."
 
@@
 
-In our approach we will perform pattern matching that conforms to each slot value along with post-processings to eliminate noisy outputs.
+In our approach we will perform pattern matching that conforms to each slot 
+value along with post-processings to eliminate noisy outputs.
 

### 2013-09-23 paper/kbanotebook2013/content/system.tex
added some formatting changes to make the file easier to edit

@@
 
-In this section we provide a high level description of the pipeline(system) design for big data analysis regarding TREC KBA the Stream Slot Filling (SSF) task.
-Our pipeline of processing the corpus consists of a two layer indexing system main section in our system regarding indexing the corpus, We started off by trying to use the off-the-shelf tools for this task.
-Mainly we started by using Scala/Spark\cite{ferc11} to benefit from the paralellization performance there.
-Spark was not as efficient as expected and the overhead was much more than tolerable.
-We tried to use Scala parallelization itself to do the job, and unfortunately it did not satisfy our needs, there was excessive memory overhead on map reduce jobs.
-We migrated the core of the system to Java Parallelism APIs and that was not good enough either, we wanted better.
-So we built our own parallel system which in actual performance had the least of overhead, the least memory consumption and the most robust memory model which avoided unpredictable CPU stalls on garbage collections in processing the corpus.
-In what follows we will describe each step of this evolution in details.
-Figure \ref{fig:system} shows a schematic view of the system.
-The platform that we run our pipeline over was a 32 core server having 64GB of memory.
+In this section we provide a high level description of the pipeline(system) 
+design for big data analysis regarding TREC KBA the Stream Slot Filling (SSF) 
+task. Our pipeline of processing the corpus consists of a two layer indexing 
+system main section in our system regarding indexing the corpus, We started 
+off by trying to use the off-the-shelf tools for this task. Mainly we started 
+by using Scala/Spark\cite{ferc11} to benefit from the parallelization 
+performance there.  Spark was not as efficient as expected and the overhead 
+was much more than tolerable. We tried to use Scala parallelization itself to 
+do the job, and unfortunately it did not satisfy our needs, there was 
+excessive memory overhead on map reduce jobs. We migrated the core of the 
+system to Java Parallelism APIs and that was not good enough either, we wanted 
+better. So we built our own parallel system which in actual performance had 
+the least of overhead, the least memory consumption and the most robust memory 
+model which avoided unpredictable CPU stalls on garbage collections in 
+processing the corpus. In what follows we will describe each step of this 
+evolution in details. Figure~\ref{fig:system} shows a schematic view of the 
+system. The platform that we run our pipeline over was a 32 core server having 
+64GB of memory.
 
@@
 
-Regarding Cumulative Citation Recommendation we perform exact string matching and treat all the documents that mention an entity equally likely to be citable.
-For future iterations of the paper we have ideas on how to score documents based on their likelihood of citation worthiness but for this iterations we treat all mentioning documents equally likely.
-One of the reasons for this is that in former TREC KBA reports \cite{JFrank12} there were observations of how non-mentioning documents have highly low chance of being citeable in wikipedia.
-So we take on that and ignore non-citing documents.
-Regarding mentioning but garbage, neutral or central documents we produce more slot values which can be later on filtered out in the high accuracy filter section.
+Regarding Cumulative Citation Recommendation we perform exact string matching 
+and treat all the documents that mention an entity equally likely to be citable.
+For future iterations of the paper we have ideas on how to score documents 
+based on their likelihood of citation worthiness but for this iterations we 
+treat all mentioning documents equally likely. One of the reasons for this is 
+that in former TREC KBA reports \cite{JFrank12} there were observations of how 
+non-mentioning documents have highly low chance of being citable in Wikipedia.
+So we take on that and ignore non-citing documents. Regarding mentioning but 
+garbage, neutral or central documents we produce more slot values which can be 
+later on filtered out in the high accuracy filter section.
 
@@
 
-Stream slot filling is done by pattern matching documents with manually produced patterns for slots of interest.
-The way we do this is by observing a sentence that has a mention of the entity or one of its coreferences.
-An anchor word in the sentence related to the slot name is located and we match either left or right of the anchor word for potential slot values.
+Stream slot filling is done by pattern matching documents with manually 
+produced patterns for slots of interest. The way we do this is by observing a 
+sentence that has a mention of the entity or one of its coreferences. An 
+anchor word in the sentence related to the slot name is located and we match 
+either left or right of the anchor word for potential slot values.
 
@@
 
-The SSF output of many extractions is noisy.
-The data contains duplicates and incorrect extractions.
-We can define rules to sanitize the output only using the information present in the SSF file.
-The file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy.
-.
-We define two classes of rules deduplication rules and inference rules.
+The SSF output of many extractions is noisy. The data contains duplicates and 
+incorrect extractions. We can define rules to sanitize the output only using 
+the information present in the SSF file. The file is processed in time order, 
+in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
+two classes of rules deduplication rules and inference rules.

### 2013-09-23 paper/kbanotebook2013/content/implementation.tex
added comments to morteza's changes

@@
 
+\ceg{Instead of this paragraph we talk about what this section will
+contain. We can discuss the input/output of the system too.
+}
 We extract aliases for entities from Wikipedia automatically both using API 
@@
 typical cases we consider some generic first name last name order swapping 
-conventions such as Bill Gates -\textgreater Gates, Bill.
+conventions such as Bill Gates $\rightarrow$ Gates, Bill.
 

### 2013-09-23 paper/kbanotebook2013/content/introduction.tex
added comments to morteza's changes

@@
 In this article we will describe the approach the GatorDSR team from the 
-University of Florida takes at addressing the challenge at NIST’s Text 
-REtrieval Conference (TREC) - Knowledge Base Acceleration track 2013 - Stream 
-Slot Filling (SSF) section. In the first section of this article we describe 
+University of Florida in addressing the challenge at NIST’s Text 
+REtrieval Conference (TREC) --- Knowledge Base Acceleration track 2013 
+In the first section we describe 
 the system design and articulate its evolution during the whole process, 
@@
 
+\ceg{Add a discussion of why machine driven kb population is important.}
 The task is that given certain Wikipedia or Twitter entities 
@@
 
+\ceg{How will each submission be evaluated?}
+
 % Motivation

### 2013-09-23 paper/kbanotebook2013/content/system.tex
added comments to morteza's changes

@@
 
+\ceg{Discuss current system first. If you want to keep the decisions points
+that led to the current architecture, make it a subsection.}
 In this section we provide a high level description of the pipeline(system) 
@@
 
+\ceg{This section should be structured as follows:
+1: Introduce CCR (Motivation, Expectations)
+2: Our high level approach
+3: Discussion of our design (Like already discussed)
+}
 Regarding Cumulative Citation Recommendation we perform exact string matching 
@@
 \subsection{Streaming Slot Filling}
-
+\ceg{See the previous note.}
 Stream slot filling is done by pattern matching documents with manually 

### 2013-09-27 paper/kbanotebook2013/content/results.tex
added some formatting changes to make the file easier to edit
added comments to morteza's changes
Revision 2 on paper.

@@
 
-Document extraction using query entity matching with aliases, sentence extraction using alias matching and co-reference.
-Slot extraction using patterns, NER tags and NP tags.
-158,052 documents with query entities, 17885 unique extracted slot values for 8 slots and 139 entities, 4 slots and 31 entities missing.
+%\ceg{We can add data on the total document size, The %number of each document type.  } 
+ We had a single node cluster.
+The configuration of the server running the jobs is according to Table \ref{table:serverspec}.
+All together, The total size of the data after XZ compression and GPG encryption is 4.5TB and just over 500M StreamItems \cite{s3}.
+Data is stored in date-hour directories: From 2011-20-05-00 (12am) ) until 2013-02-13-23 (11pm) there are 11952 date-hour combinations.
+The source code of our system is stored as an open source project where enthusiasts can also contribute to \cite{github}, also the relevant discussion mailing list is accessible here \cite{googlegroups}.
 
-On the performance of the first submission run we performed some random sampling via two processes, the results of which are as follows:
+ Our results are as follows: Document extraction using query entity matching with aliases, sentence 
+extraction using alias matching and co-reference. Slot extraction using 
+patterns, NER tags and NP tags. 158,052 documents with query entities, 17885 
+unique extracted slot values for 8 slots and 139 entities, 4 slots and 31 
+entities missing.
+
+On the performance of the first submission run we performed some random 
+sampling via two processes, the results of which are as in Table \ref{table:initialresult}.
+Our final submission has been elaborated in Tables \ref{table:finalresultaccuracy} and \ref{table:finalresultrecall}.
+You can observe that only CauseOfDeath is missing from the set of found slot values.
 
 \begin{table}[b]
+\caption{Benchmark Server Specifications }
+\centering
+\label{table:serverspec}
+\begin{tabular}{|c|l|}
+\hline 
+Model & Dell xxx 32 cores \\ \hline 
+OS & CentOS release 6.4 Final \\ \hline 
+Software Stack & GCC version 4.4.7, Java 1.7.0\_25, Scala 2.9.2, SBT 0.12.3 \\ \hline 
+ RAM & 64GB\\ \hline 
+ Drives & 2x2.7TB disks, 6Gbps, 7200RPM\\ \hline 
+\end{tabular} 
+\end{table}
+
+\begin{table}[t]
 \caption{SSF Performance Measure on Initial Submission }
 \centering
+\label{table:initialresult}
+
 \begin{tabular}{|c|c|c|c|}
@@
 
-\begin{table}
+\begin{table}[b]
 \caption{SSF Accuracy Measure on Submission Infer }
 \centering
+\label{table:finalresultaccuracy}
 \begin{tabular}{|c|c|c|c|}
@@
 
-\begin{table}
+\begin{table}[t]
 \caption{Recall Measure on Submission Infer }
 \centering
+\label{table:finalresultrecall}
 \begin{tabular}{|c|p{3cm}|p{4cm}|}

### 2013-09-27 paper/kbanotebook2013/paper.tex
added comments to morteza's changes
Revision 2 on paper.

@@
-\documentclass{article}
+\documentclass[10pt]{article}
 
+\usepackage{xcolor}
 \usepackage{cite }
+\usepackage{graphicx, epsfig}
+\usepackage[margin=1in]{geometry}
+\usepackage[hyphens]{url}
+
+\pagenumbering{gobble} %Do not print page numbers
+
+\newcommand\ceg[1]{\textcolor{red}{#1}}
 
@@
 
-\author {%
-  Morteza Shahriari Nia\\
-  University of Florida\\
-  Department of Electrical \& Computer Engineering\\
-  Gainesville, Florida, USA\\
+\author {
+  Morteza Shahriari Nia\footnote{ Department of Electrical \& Computer Engineering, University of Florida, Gainesville, Florida, USA}\\
        {m.shahriarinia@ufl.edu}
 \and
-  Christan Grant, Yang Peng, Daisy Zhe Wang\\
-  University of Florida\\
-       Department of Computer \& Information Science \& Engineering\\
-       Gainesville, Florida, USA\\
-       {\{cgrant,ypeng,daisyw\}@cise.ufl.edu}
+  Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{Department of Computer \& Information Science \& Engineering, University of Florida, Gainesville, Florida, USA}\\
+       {\{cgrant, ypeng, daisyw\}@cise.ufl.edu}
 \and
-  Milenko Petrovic\\
-  Institute for Human and Machine Cognition\\
-       %\affaddr{Department of Computer \& Information Science \& Engineering}\\
-       Ocala, Florida, USA\\
+  Milenko Petrovic\footnote{Institute for Human and Machine Cognition, Ocala, Florida, USA}\\
        {mpetrovic@ihmc.us}
@@
 
-\bibliographystyle{acm}
+\bibliographystyle{unsrt}
 \bibliography{citation}

### 2013-09-27 paper/kbanotebook2013/content/implementation.tex

--- 2013-09-23 paper/kbanotebook2013/content/implementation.tex
@@
 \section{Implementation}
+\label{section:implementation}
 
-We extract aliases for entities from Wikipedia automatically both using API 
+Our contribution is that we perform pattern matching that conforms to each slot 
+value along with post-processings to eliminate noisy outputs. We extract aliases for entities from Wikipedia automatically both using API 
 and using the actual page content, then apply pattern matching rules for slot 
 value extraction.
+
+%\ceg{Instead of this paragraph we talk about what this %section will
+%contain. We can discuss the input/output of the system %too.
+%}
 
@@
 typical cases we consider some generic first name last name order swapping 
-conventions such as Bill Gates -\textgreater Gates, Bill.
+conventions such as Bill Gates $\rightarrow$ Gates, Bill.
 
-\subsection{Pattern Matching}
+\subsection{Streaming Slot Value Extraction}
 
 In this system, we use pattern matching methods to find corresponding slot 
-values for entities. The procedure is: 1) Find stream items that contain the 
+values for entities. This is done by observing the training data which is the first four months of the corpus(Oct 2011 - Feb 2012). The procedure is: 1) Find stream items that contain the 
 entities by using alias names of the entities. 2) Inside these stream items, 
@@
 right, NP\textgreater, NP meaning noun phrase. This pattern can be interpreted 
-as that we are looking for a noun phrase after the “awarded” since that noun 
+as that we are looking for a noun phrase after the “awarded'' since that noun 
 phrase could possibly represent an award. Since titles and awards are usually 
@@
 Another example for the third type: \textless PER, DateOfDeath, died, right, 
-last night\textgreater. In this pattern, “last night” means we are looking for 
-exactly the phrase “last night” to the right of “died”. This pattern is 
+last night\textgreater. In this pattern, “last night'' means we are looking for 
+exactly the phrase ``last night'' to the right of ``died''. This pattern is 
 inspired by the intuition that in news articles, people often mention that 
 somebody died last night instead of mentioning the accurate date information 
-and Lingpipe tends not to tag phrases like “last night” as a DATE entity.
+and Lingpipe tends not to tag phrases like ``last night'' as a DATE entity.
 
@@
 wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched 
-by the patterns. We solve the first problem by using the wikipedia or twitter 
+by the patterns. We solve the first problem by using the Wikipedia or twitter 
 information of the entities to get better alias names. And we use
@@
 
-\subsection{Post Processing}
+\subsection{High Accuracy Filter}
 
@@
 
-The output contains many duplicate entries. As we read the list of extrated 
-slots we create rules to define "duplicate". Duplicates can be present in a 
+The output contains many duplicate entries. As we read the list of extracted 
+slots we create rules to define ``duplicate''. Duplicates can be present in a 
 window of rows; we use a window size of 2 meaning we only be adjacent rows. 
-Two rows are duplicates if 1) they have the same exact extraction, 2) if the 
-rows have the same slot name and a similar slot value and 3) if the extracted 
+Two rows are duplicates if they have the same exact extraction, or if the 
+rows have the same slot name and a similar slot value or if the extracted 
 sentence for a particular slot types come from the same sentence.
 
- New slots can be deduced from existing slots by defineing inference rules. 
- For example, two slots for the task are "FounderOf" and "FoundedBy". A safe 
- assumtion is these slot names are biconditional logical connectives with the 
- entities and slot values. Therefore, we can express a rule "X FounderOf Y" 
- equals "Y FoundedBy X" where X and Y are single unique entities. Additionally,
- we found that the slot names "Contact\_Meet\_PlaceTime" could be infered as
- "Contact\_Meet\_Entity" if the Entity was a FAC and the extracted sentence 
+ New slots can be deduced from existing slots by defining inference rules. 
+ For example, two slots for the task are ``FounderOf'' and ``FoundedBy''. A safe 
+ assumption is these slot names are biconditional logical connectives with the 
+ entities and slot values. Therefore, we can express a rule ``X FounderOf Y'' 
+ equals ``Y FoundedBy X'' where X and Y are single unique entities. Additionally,
+ we found that the slot names ``Contact\_Meet\_PlaceTime'' could be inferred as
+ ``Contact\_Meet\_Entity'' if the Entity was a FAC and the extracted sentence 
  contained an additional ORG/FAC tag.  
@@
 attributed to poor sentence parsing of web documents. We have some valid
-"small" extractions. For example a comma may separate a name and a title
-(e.g. "John, Professor at MIT"). But such extraction rules can be particularly 
+``small'' extractions. For example a comma may separate a name and a title
+(e.g. ``John, Professor at MIT''). But such extraction rules can be particularly 
 noisy, so we check to see if the extracted values have good entity values.
@@
 
-\subsection{Shortcomings}
-
-The missing twitter entities are more than the 50\% of the twitter entities we 
-need to work on and this is a very very bad performance. One reason could be 
-that those entities are not very famous. For example Brenda Weiler google 
-search result is 860,000 documents our of billions of web documents. For our 
-small portion of the web it might make sense. If you pay attention to the 
-histogram of the entities found you'll note that more than half of the 
-entities have appeared in less than 10 StreamItems. A good portion have 
-appeared only once. Which the document does not necessarily have good 
-information for us.
-
-A theory is that we are falling behind because we are using the cleansed 
-version of the corpus. We believe there has been a reason that TREC has 
-included the actual HTML document as well as the cleansed version. This 
-definitely will convey some information to us. If it was as easy as reading 
-some clean text they wouldn't bother including so much data for teams to be 
-useless. So we guess is that we are missing some information from not using 
-the actual document. And, we are looking for tokens with entity value set 
-which will depend us dramatically on the accuracy of lingpipe, which is a fast 
-algorithm but is not as good as other NLP tools can be e.g. Stanford NLP.
-
 % Note: Talk about how each of the algorithms were created

### 2013-09-27 paper/kbanotebook2013/content/introduction.tex

@@
 \section{Introduction}
+
+One of the important challenges in maintaining the most popular free, web-based, collaborative, multilingual encyclopedia in the internet (Wikipedia) is to make sure its descriptions are upto date.
+It has been observed that there is a considerable time lag between the publication date of cited news articles and the date of an edit to Wikipedia (WP) creating the citation.
+In a case-study, the time lag for a sample of \~60,000 web pages cited by WP articles in the Living\_people category, The median time is over a year and the distribution has a long and heavy tail\cite{JFrank12}.
+It is also noted that the majority of wikipedia entities have updates on their WP article much less frequently than their mention frequency.
+
+Such stale entries are the norm in any large knowledge base (KB), because the number of humans maintaining the knowledge base is far fewer than the number of entities in the KB.
+Further, the number of mentions is much larger than the number of entities.
+This mismatch between human maintainers and the large stream of mentions to entities of interest is effectively a definition of a ``large'' KB \cite{JFrank12}.
+So, knowledge-bases are important and we are working on accelerating populating them.
 
@@
 (SSF): given a slot name (entity + relation type) we fill in the slot value
-(relation value) on structured text documents.
+(relation value) on structured text documents. For similar approaches regarding last year's track you can refer to \cite{ji2011knowledge}.
 
-\ceg{Add a discussion of why machine driven kb population is important.}
+%\ceg{Add a discussion of why machine driven kb population is important.}
 The task is that given certain Wikipedia or Twitter entities 
-(wiki/twitter URLs) and certain relations of interest given in Table 1, 
-extract as many triple relations as possible (hence, slot filling). This can 
-be used to automatically populate knowledgebases such as free-base or DBPedia 
+(wiki/twitter URLs) and certain relations of interest given in Table  \ref{table:slotNameOntology}, extract as many triple relations as possible (hence, slot filling).
+This can be used to automatically populate knowledgebases such as free-base or DBPedia
 or even filling in the information boxes at Wikipedia. The corpus is in 
-English and is a snapshot of part of the web containing arXiv, social, news, 
-linking, weblog, forum, classifieds, reviews, and memetracker documents. Each 
-document is annotated using lingpipe and is called StreamItem, a bundle of 
+English and is a snapshot of part of the web containing document types described in Table \ref{table:documentsDist}. Each document is annotated using lingpipe and is called StreamItem, a bundle of 
 StreamItems are put together and serialized as Apache Thrift objects, then 
@@
 slot values that were not substantiated earlier in the stream corpus, which 
-ranges from October 2011 to February 2013. Below you can view the slot values 
+ranges from October 2011 to February 2013. Below you can view some slot values 
 and their types, the comprehensive description of which can be found at
-\cite{tackbp} and \cite{aec}
+\cite{tackbp} and \cite{aec}.
+These examples demonstrate that out of an ordinary sentence in the general web, which parts are of interest for us and which should be avoided to be returned as slot values of a given entity.
+You can view that sometimes it can get fairly complex, so a good extraction scheme is essential.
+The evaluation metric is that the extractions will be submitted to KBA assessors and they will determine the overall performance for comparison.
+
+Assessors were instructed to ``use the wikipedia article to identify (disambiguate) the entity, and then imagine forgetting all info in the WP article and asking whether the text provides any information about the entity''\cite{JFrank12}.
+Documents would be devided according to two metrics: 1) mentioning the entity or not, 2) relevance level to the entity:
+\begin{itemize}
+\item \textbf{Mention} 
+\begin{itemize}
+\item \textbf{Mention:} Document explicitly mentions target entity, such as full name, partial name, nickname, pseudonym, title, stage name.
+\item \textbf{Zero-mention:} Document does not directly mention target.
+Could still be relevant, e.g.
+metonymic references like ``this administration'' -- \textgreater ``Obama''.
+See also synecdoche.
+A document could also be relevant to target entity through relation to entities mentioned in document -- apply this test question: can I learn something from this document about target entity using whatever other information I have about entity?
+\end{itemize}
+\item \textbf{Relevance}
+\begin{itemize}
+\item \textbf{Garbage:} not relevant, e.g. spam.
+\item \textbf{Neutral:} Not relevant, i.e.
+no info could be deduced about entity, e.g., entity name used in product name, or only pertains to community of target such that no information could be learned about entity, although you can see how an automatic algorithm might have thought it was relevant.
+\item \textbf{Relevant:} Relates indirectly, e.g., tangential with substantive implications, or topics or events of likely
+impact on entity.
+\item \textbf{Central:} Relates directly to target such that you would cite it in the WP article for this entity, e.g. entity is a
+central figure in topics/events.
+
+\end{itemize}
+\end{itemize}
+
+The details of the metric for SSF will favor systems that most closely match the changes in the ground truth time line of slot values.
+This is done by searching for other documents that mentioned an entity and exactly matched the slot fill strings selected by the assessors.
 
@@
 \centering
+\label{table:slotNameOntology}
 
@@
 \hline 
-PER & FAC & ORG \\ 
+\textbf{PER} & \textbf{FAC} & \textbf{ORG} \\ 
 \hline 
@@
 
-Example 1: "Matthew DeLorenzo and Josiah Vega, both 14 years old and students 
+\begin{table}[b]
+\caption{Document Chunks Distribution }
+\centering
+\label{table:documentsDist}
+
+\begin{tabular}{|c|l|}
+\hline 
+\textbf{\# of Documents} & \textbf{Document Type}\\ 
+\hline 
+10988 & 	arxiv (full text, abstracts in StreamItem.other\_content) \\ \hline
+34887 & CLASSIFIED (spinn3r)  \\ \hline
+77674 & FORUM (spinn3r)  \\ \hline
+12947 & linking (reprocessed from kba-stream-corpus-2012, same stream\_id)  \\ \hline
+141936 & MAINSTREAM\_NEWS (spinn3r)  \\ \hline
+4137 & MEMETRACKER (spinn3r)  \\ \hline
+280629 & news (reprocessed from kba-stream-corpus-2012, same stream\_id)  \\ \hline
+6347 &  REVIEW (spinn3r) \\ \hline
+688848 & 	 social (reprocessed from kba-stream-corpus-2012 plus extension, same stream\_id)  \\ \hline
+740987 & WEBLOG (spinn3r)  \\ \hline
+
+\hline 
+\end{tabular} 
+\end{table}
+
+\noindent Example 1: ``Matthew DeLorenzo and Josiah Vega, both 14 years old and students 
 at Elysian Charter School, were honored Friday morning by C-SPAN and received 
-\$1,500 as well as an iPod Touch after winning a nationwide video contest."
+\$1,500 as well as an iPod Touch after winning a nationwide video contest.''
 
@@
 
-Affiliate:  "Matthew DeLorenzo"
-Affiliate:  "Josiah Vega"
+Affiliate:  ``Matthew DeLorenzo''
+Affiliate:  ``Josiah Vega''
 
-NOT an affiliate:  "C-SPAN"
-NOT an affiliate:  "iPod Touch"
+NOT an affiliate:  ``C-SPAN''
+NOT an affiliate:  ``iPod Touch''
 
-Example 2: "Veteran songwriters and performers Ben Mason, Jeff Severson and 
+\noindent Example 2: ``Veteran songwriters and performers Ben Mason, Jeff Severson and 
 Jeff Smith will perform on Saturday, April 14 at 7:30 pm at Creative Cauldron 
-at ArtSpace, 410 S. Maple Avenue."
+at ArtSpace, 410 S. Maple Avenue.''
 
@@
 
-Affiliate: "Ben Mason"
-Affiliate: "Jeff Severson"
-Affiliate: "Jeff Smith"
+Affiliate: ``Ben Mason''
+Affiliate: ``Jeff Severson''
+Affiliate: ``Jeff Smith''
 
-NOT an Affiliate: "Creative Caldron"
-NOT an Affiliate: "Art Space"
+NOT an Affiliate: ``Creative Caldron''
+NOT an Affiliate: ``Art Space''
 
-Example 3:  "Lt. Gov. Drew Wrigley and Robert Wefald, a retired North Dakota 
+\noindent Example 3:  ``Lt. Gov. Drew Wrigley and Robert Wefald, a retired North Dakota 
 district judge and former state attorney general, unveiled the crest Friday 
-during a ceremony at the North Dakota Capitol."
+during a ceremony at the North Dakota Capitol.''
 
@@
 
-Contact\_Meet\_PlaceTime: "Friday during a ceremony at the North Dakota Capitol"
+Contact\_Meet\_PlaceTime: ``Friday during a ceremony at the North Dakota Capitol''
 
-In our approach we will perform pattern matching that conforms to each slot 
-value along with post-processings to eliminate noisy outputs.
-
-\ceg{How will each submission be evaluated?}
+%\ceg{How will each submission be evaluated?}
 

### 2013-09-27 paper/kbanotebook2013/content/system.tex

--- 2013-09-23 paper/kbanotebook2013/content/system.tex
@@
-\begin{figure}[b]
+\begin{figure}
 \centering
-\includegraphics[width=4.5in]{./images/system.eps}
+%\includegraphics[width=4.5in]{./images/system.eps}
+\includegraphics[width=6in]{./images/SystemBW.eps}
 \vspace*{-.1in} \caption{Pipeline Design }\label{fig:system}
@@
 
-\section{Pipeline}
+\section{System Architecture}
 
-In this section we provide a high level description of the pipeline(system) 
-design for big data analysis regarding TREC KBA the Stream Slot Filling (SSF) 
-task. Our pipeline of processing the corpus consists of a two layer indexing 
-system main section in our system regarding indexing the corpus, We started 
-off by trying to use the off-the-shelf tools for this task. Mainly we started 
-by using Scala/Spark\cite{ferc11} to benefit from the parallelization 
-performance there.  Spark was not as efficient as expected and the overhead 
-was much more than tolerable. We tried to use Scala parallelization itself to 
-do the job, and unfortunately it did not satisfy our needs, there was 
-excessive memory overhead on map reduce jobs. We migrated the core of the 
-system to Java Parallelism APIs and that was not good enough either, we wanted 
-better. So we built our own parallel system which in actual performance had 
-the least of overhead, the least memory consumption and the most robust memory 
-model which avoided unpredictable CPU stalls on garbage collections in 
-processing the corpus. In what follows we will describe each step of this 
-evolution in details. Figure~\ref{fig:system} shows a schematic view of the 
-system. The platform that we run our pipeline over was a 32 core server having 
-64GB of memory.
+As shown in Figure \ref{fig:system}, our system is built in a pipeline manner which gives it the advantage to run each section separately and allow stream processing without wasting resources being clogged by one operation while others are waiting.
+Below, we describe each component briefly and in Section \ref{section:implementation} we will go through technical details.
 
-% Note: Describe the algorithms of each phase
-% Talk in abstract terms not implementation.
-% Use formal representations (Math, SQL etc)
+%\ceg{Discuss current system first. If you want to keep the decisions points that led to the current architecture, make it a subsection.}
+
+\subsection{Preprocessing}
+
+To begin, we need to have real world aliases of entities.
+TREC KBA prohibits Wikipedia entities to have any manual aliases being added and only allows automatic ways.
+We use Wikipedia API backlink references (redirects to a wiki entity) as aliases of the entity.
+We also use some techniques to extract some aliases from within the text of a wiki entity, which will be described later on.
+This whole process is referred to as \textbf{Alias Extraction (Wiki API, Wiki text)} Regarding Twitter entities this limit is lifted and participants are allowed to manually add aliases for them.
+Part of the reason is that Twitter environment is composed of so much informal and dialectic language which makes it extremely difficult to extract context out of tweets or entities descriptions in their profiles.
+This process of extracting aliases for Twitter entities is referred to as \textbf{Manual Alias Extraction (Twitter)}.
+
+Once aliases are available we pass them through some rules of generating proper name orders which will produce various instances of writing a name.
+As a basic example Bill Gates can be written as Gates, Bill.
+This will allow the system to capture various notation forms of aliases.
+This part of the system is referred to as \textbf{Name Order Generator}.
 
@@
 
+The main goal of Cumulative Citation Recommendation is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page.
 Regarding Cumulative Citation Recommendation we perform exact string matching
@@
 
+Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textbf{Chunk Files Index Generator} and \textbf{StreamItems Index Generator}.
+Chunk Files Index Generator will generate indexes of the chunk files that contain a mention of any of the desired entities.
+StreamItems Index Generator on the other hand will index StreamItems that contain a mention of a given entity respectively.
+This two level indexing will eliminate the need to process each and every ChunkFile/StreamItem for every entity.
+
+% Note: Describe the algorithms of each phase
+% Talk in abstract terms not implementation.
+% Use formal representations (Math, SQL etc)
+
+%\ceg{This section should be structured as follows:
+%1: Introduce CCR (Motivation, Expectations)
+%2: Our high level approach
+%3: Discussion of our design (Like already discussed)
+%}
+
 \subsection{Streaming Slot Filling}
-
+%\ceg{See the previous note.}
+As described in the Introduction, the general purpose of slot filling is to extract proper values for relations of interest, some of which can be found in Table \ref{table:slotNameOntology}.
+This is called Stream Slot Filling due to the fact that it is assumed that data is being generated as time goes on and for each extraction we should only consider current or past data.
+In our schematic diagram we refer to this as \textbf{Streaming Slot Value Extraction}.
 Stream slot filling is done by pattern matching documents with manually
@@
 in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
-two classes of rules deduplication rules and inference rules.
+two classes of rules deduplication rules and inference rules. In our diagram we refer to this component as \textbf{High Accuracy Filter}.

### 2013-09-27 paper/kbanotebook2013/content/discussion.tex

@@
 \section{Discussion}
+
+ We started 
+off by trying to use the off-the-shelf tools for this task. Mainly we started 
+by using Scala/Spark\cite{ferc11} to benefit from the parallelization 
+performance there.  Spark was not as efficient as expected and the overhead 
+was much more than tolerable. We tried to use Scala parallelization itself to 
+do the job, and unfortunately it did not satisfy our needs, there was 
+excessive memory overhead on map reduce jobs. We migrated the core of the 
+system to Java Parallelism APIs and that was not good enough either, we wanted 
+better. So we built our own parallel system which in actual performance had 
+the least of overhead, the least memory consumption and the most robust memory 
+model which avoided unpredictable CPU stalls on garbage collections in 
+processing the corpus. In what follows we will describe each step of this 
+evolution in details. Figure~\ref{fig:system} shows a schematic view of the 
+system.
 
@@
 ``TopMembers'', ``Contact\_Meet\_Entity'' and so on. 2) For special slots, 
-like “Titles”, “DateOfDeath”, “CauseOfDeath”, “AwardsWon”, using different 
+like ``Titles'', ``DateOfDeath'', ``CauseOfDeath'', ``AwardsWon'', using different 
 kind of advanced methods, e.g.\ classifiers, matching methods. 3) Using other 
@@
 
+\subsection{Shortcomings}
+
+The missing twitter entities are more than the 50\% of the twitter entities we 
+need to work on and this is a very very bad performance. One reason could be 
+that those entities are not very famous. For example Brenda Weiler google 
+search result is 860,000 documents our of billions of web documents. For our 
+small portion of the web it might make sense. If you pay attention to the 
+histogram of the entities found you'll note that more than half of the 
+entities have appeared in less than 10 StreamItems. A good portion have 
+appeared only once. Which the document does not necessarily have good 
+information for us.
+
+A theory is that we are falling behind because we are using the cleansed 
+version of the corpus. We believe there has been a reason that TREC has 
+included the actual HTML document as well as the cleansed version. This 
+definitely will convey some information to us. If it was as easy as reading 
+some clean text they wouldn't bother including so much data for teams to be 
+useless. So we guess is that we are missing some information from not using 
+the actual document. And, we are looking for tokens with entity value set 
+which will depend us dramatically on the accuracy of lingpipe, which is a fast 
+algorithm but is not as good as other NLP tools can be e.g. Stanford NLP.
+
 % Note: Here we discuss why the results are the way they are

### 2013-10-02 paper/kbanotebook2013/content/introduction.tex

@@
 
-One of the important challenges in maintaining the most popular free, web-based, collaborative, multilingual encyclopedia in the internet (Wikipedia) is to make sure its descriptions are upto date.
-It has been observed that there is a considerable time lag between the publication date of cited news articles and the date of an edit to Wikipedia (WP) creating the citation.
-In a case-study, the time lag for a sample of \~60,000 web pages cited by WP articles in the Living\_people category, The median time is over a year and the distribution has a long and heavy tail\cite{JFrank12}.
-It is also noted that the majority of wikipedia entities have updates on their WP article much less frequently than their mention frequency.
+In this article we describe the approach the GatorDSR team from 
+University of Florida has adopted in addressing the challenge at NIST’s Text 
+REtrieval Conference (TREC) --- Knowledge Base Acceleration track 2013.
+There are two main sections designed for this track.
+Cumulative Citation Recommendation and Streaming Slot Filling.
+Due to the importance of knowledgebases, both of these tracks aim to accelerating populating them, hence the title Knowledgebase Acceleration (KBA).
+Below we describe each of these tracks and their purposes in full detail.
 
+\subsection{Cumulative Citation Recommendation (CCR)}
+
+An important challenge in maintaining Wikipedia (WP) which is the most popular free, web-based, collaborative, multilingual encyclopedia in the internet, is to make sure its contents are uptodate.
+Currently, there is considerable time lag between the publication date of cited news articles and the date of an edit to WP creating the citation.
+As an example, the median time lag for a sample of about 60,000 web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail\cite{JFrank12}.
+It is also noted that the majority of Wikipedia entities have updates on their associated Wiki article much less frequently than their mention frequency.
 Such stale entries are the norm in any large knowledge base (KB), because the number of humans maintaining the knowledge base is far fewer than the number of entities in the KB.
-Further, the number of mentions is much larger than the number of entities.
-This mismatch between human maintainers and the large stream of mentions to entities of interest is effectively a definition of a ``large'' KB \cite{JFrank12}.
-So, knowledge-bases are important and we are working on accelerating populating them.
+Further, the number of mentions is much larger than the number of entities\cite{JFrank12}.
 
-In this article we will describe the approach the GatorDSR team from the 
-University of Florida in addressing the challenge at NIST’s Text 
-REtrieval Conference (TREC) --- Knowledge Base Acceleration track 2013 
-In the first section we describe 
-the system design and articulate its evolution during the whole process, 
-challenges and needs that we have overcome. In the second section we will go 
-through the details of the NLP techniques we took at streaming slot filling
-(SSF): given a slot name (entity + relation type) we fill in the slot value
-(relation value) on structured text documents. For similar approaches regarding last year's track you can refer to \cite{ji2011knowledge}.
-
-%\ceg{Add a discussion of why machine driven kb population is important.}
-The task is that given certain Wikipedia or Twitter entities 
-(wiki/twitter URLs) and certain relations of interest given in Table  \ref{table:slotNameOntology}, extract as many triple relations as possible (hence, slot filling).
-This can be used to automatically populate knowledgebases such as free-base or DBPedia
-or even filling in the information boxes at Wikipedia. The corpus is in 
-English and is a snapshot of part of the web containing document types described in Table \ref{table:documentsDist}. Each document is annotated using lingpipe and is called StreamItem, a bundle of 
-StreamItems are put together and serialized as Apache Thrift objects, then 
-compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
-and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
-To have a sense of the scale of objects and compression as an example a 6mb
-gpg.xz files would become 45 mb thrift objects which can contain a couple of 
-thousand StreamItems depending on their size. Some of the documents have null 
-values for their annotation fields.
-
-Since this is \textit{streaming} slot filling, we are only interested in new 
-slot values that were not substantiated earlier in the stream corpus, which 
-ranges from October 2011 to February 2013. Below you can view some slot values 
-and their types, the comprehensive description of which can be found at
-\cite{tackbp} and \cite{aec}.
-These examples demonstrate that out of an ordinary sentence in the general web, which parts are of interest for us and which should be avoided to be returned as slot values of a given entity.
-You can view that sometimes it can get fairly complex, so a good extraction scheme is essential.
-The evaluation metric is that the extractions will be submitted to KBA assessors and they will determine the overall performance for comparison.
-
-Assessors were instructed to ``use the wikipedia article to identify (disambiguate) the entity, and then imagine forgetting all info in the WP article and asking whether the text provides any information about the entity''\cite{JFrank12}.
-Documents would be devided according to two metrics: 1) mentioning the entity or not, 2) relevance level to the entity:
+For this track, assessors were instructed to ``use the wikipedia article to identify (disambiguate) the entity, and then imagine forgetting all info in the WP article and asking whether the text provides any information about the entity''\cite{JFrank12}.
+Documents would be divided according to two metrics: 1) mentioning the entity or not, 2) relevance level to the entity:
 \begin{itemize}
@@
 
+\subsection{Streaming Slot Filling (SSF)}
+The task is that given certain Wikipedia or Twitter entities 
+(wiki/twitter URLs) and certain relations of interest (given in Table  \ref{table:slotNameOntology}), extract as many triple relations as possible (hence, slot filling).
+This can be used to automatically populate knowledgebases such as free-base or DBPedia
+or even fill-in the information boxes at Wikipedia.
+Below, you can view some examples of what it means to fill in a slot value; in each example there is a sentence of interest that we wish to extract slot values from, an entity that the slot value is related to, and a slot name which can be thought of as the topic of the slot value:
+
+\noindent \textbf{Example 1:} ``Matthew DeLorenzo and Josiah Vega, both 14 years old and students 
+at Elysian Charter School, were honored Friday morning by C-SPAN and received 
+\$1,500 as well as an iPod Touch after winning a nationwide video contest.''
+
+Entity:  http://en.wikipedia.org/wiki/Elysian\_Charter\_School
+
+Slot name: Affiliate
+
+Possible slot values: ``Matthew DeLorenzo'', ``Josiah Vega''
+
+Incorrect slot values: ``C-SPAN'', ``iPod Touch''
+
+\noindent \textbf{Example 2:} ``Veteran songwriters and performers Ben Mason, Jeff Severson and 
+Jeff Smith will perform on Saturday, April 14 at 7:30 pm at Creative Cauldron 
+at ArtSpace, 410 S. Maple Avenue.''
+
+Entity: http://en.wikipedia.org/wiki/Jeff\_Severson
+
+Slot name: Affiliate
+
+Possible slot values: ``Ben Mason'', ``Jeff Severson'', ``Jeff Smith''
+
+Incorrect slot values: ``Creative Caldron'', ``Art Space''
+
+\noindent \textbf{Example 3:}  ``Lt. Gov. Drew Wrigley and Robert Wefald, a retired North Dakota 
+district judge and former state attorney general, unveiled the crest Friday 
+during a ceremony at the North Dakota Capitol.''
+
+Entity: http://en.wikipedia.org/wiki/Hjemkomst\_Center
+
+Slot name: Contact\_Meet\_PlaceTime
+
+Slot value: ``Friday during a ceremony at the North Dakota Capitol''
+
+\noindent Since this is \textit{streaming} slot filling, we are only interested in new 
+slot values that were not substantiated earlier in the stream corpus. In Table \ref{table:slotNameOntology} you can view some slot values 
+and their types, the comprehensive description of which can be found at
+\cite{tackbp} and \cite{aec}.
 The details of the metric for SSF will favor systems that most closely match the changes in the ground truth time line of slot values.
 This is done by searching for other documents that mentioned an entity and exactly matched the slot fill strings selected by the assessors.
+
+In the rest of the paper, we address the following material.
+In Section 2, we sketch the main components of the system and their purposes.
+In Section 3, describe the details of how we designed and implemented certain components critical to the behavior of the system.
+Section 4 addresses the performance and the results we achieved.
+Section 5, goes through a discussion of the challenges we had to produce reliable results over the massive amount of information available, and how we overcome these issues.
+For similar approaches regarding last year's track you can refer to \cite{ji2011knowledge}.
+
+%\ceg{Add a discussion of why machine driven kb population is important.}
 
@@
 
-\begin{table}[b]
-\caption{Document Chunks Distribution }
-\centering
-\label{table:documentsDist}
-
-\begin{tabular}{|c|l|}
-\hline 
-\textbf{\# of Documents} & \textbf{Document Type}\\ 
-\hline 
-10988 & 	arxiv (full text, abstracts in StreamItem.other\_content) \\ \hline
-34887 & CLASSIFIED (spinn3r)  \\ \hline
-77674 & FORUM (spinn3r)  \\ \hline
-12947 & linking (reprocessed from kba-stream-corpus-2012, same stream\_id)  \\ \hline
-141936 & MAINSTREAM\_NEWS (spinn3r)  \\ \hline
-4137 & MEMETRACKER (spinn3r)  \\ \hline
-280629 & news (reprocessed from kba-stream-corpus-2012, same stream\_id)  \\ \hline
-6347 &  REVIEW (spinn3r) \\ \hline
-688848 & 	 social (reprocessed from kba-stream-corpus-2012 plus extension, same stream\_id)  \\ \hline
-740987 & WEBLOG (spinn3r)  \\ \hline
-
-\hline 
-\end{tabular} 
-\end{table}
-
-\noindent Example 1: ``Matthew DeLorenzo and Josiah Vega, both 14 years old and students 
-at Elysian Charter School, were honored Friday morning by C-SPAN and received 
-\$1,500 as well as an iPod Touch after winning a nationwide video contest.''
-
-target\_id:  http://en.wikipedia.org/wiki/Elysian\_Charter\_School
-
-Affiliate:  ``Matthew DeLorenzo''
-Affiliate:  ``Josiah Vega''
-
-NOT an affiliate:  ``C-SPAN''
-NOT an affiliate:  ``iPod Touch''
-
-\noindent Example 2: ``Veteran songwriters and performers Ben Mason, Jeff Severson and 
-Jeff Smith will perform on Saturday, April 14 at 7:30 pm at Creative Cauldron 
-at ArtSpace, 410 S. Maple Avenue.''
-
-target\_id: http://en.wikipedia.org/wiki/Jeff\_Severson
-
-Affiliate: ``Ben Mason''
-Affiliate: ``Jeff Severson''
-Affiliate: ``Jeff Smith''
-
-NOT an Affiliate: ``Creative Caldron''
-NOT an Affiliate: ``Art Space''
-
-\noindent Example 3:  ``Lt. Gov. Drew Wrigley and Robert Wefald, a retired North Dakota 
-district judge and former state attorney general, unveiled the crest Friday 
-during a ceremony at the North Dakota Capitol.''
-
-target\_id: http://en.wikipedia.org/wiki/Hjemkomst\_Center
-
-Contact\_Meet\_PlaceTime: ``Friday during a ceremony at the North Dakota Capitol''
-
 %\ceg{How will each submission be evaluated?}

### 2013-10-02 paper/kbanotebook2013/paper.tex

@@
 
-\newcommand\ceg[1]{\textcolor{red}{#1}}
+\newcommand\ceg[1]{\textcolor{red}{#1}} % Red marker to declare errors.
 
@@
 \author {
-  Morteza Shahriari Nia\footnote{ Department of Electrical \& Computer Engineering, University of Florida, Gainesville, Florida, USA}\\
-       {m.shahriarinia@ufl.edu}
-\and
-  Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{Department of Computer \& Information Science \& Engineering, University of Florida, Gainesville, Florida, USA}\\
-       {\{cgrant, ypeng, daisyw\}@cise.ufl.edu}
+ Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{ University of Florida, Gainesville, Florida, USA}\\
+       { \{msnia, cgrant, ypeng, daisyw\}@cise.ufl.edu}
 \and

### 2013-10-02 paper/kbanotebook2013/content/discussion.tex

@@
-\section{Discussion}
+\section{Discussion \& Future Works}
 
- We started 
+In this section we address some of the challenges that we faced during the course of this project. We started 
 off by trying to use the off-the-shelf tools for this task. Mainly we started 
 by using Scala/Spark\cite{ferc11} to benefit from the parallelization 
-performance there.  Spark was not as efficient as expected and the overhead 
-was much more than tolerable. We tried to use Scala parallelization itself to 
-do the job, and unfortunately it did not satisfy our needs, there was 
-excessive memory overhead on map reduce jobs. We migrated the core of the 
-system to Java Parallelism APIs and that was not good enough either, we wanted 
+performance there. Unfortunately Spark was not performant and the distributed reliability overhead 
+was much more than tolerable. We moved on to use Scala parallelization  framework itself, and unfortunately it did not satisfy our needs as well; there was 
+excessive memory overhead on map-reduce jobs. We migrated the core of the 
+system to Java Parallelism APIs and that was not good enough either, we still demanded 
 better. So we built our own parallel system which in actual performance had 
@@
 model which avoided unpredictable CPU stalls on garbage collections in 
-processing the corpus. In what follows we will describe each step of this 
-evolution in details. Figure~\ref{fig:system} shows a schematic view of the 
-system.
+processing the corpus.
 
@@
 
-For slot extraction part, in order to improve the performance, what we need to 
+For slot extraction part, in order to improve the performance, what we need
 are: 1) Using multi-class classifiers instead of pattern matching method to 
@@
 
-\subsection{Shortcomings}
-
-The missing twitter entities are more than the 50\% of the twitter entities we 
-need to work on and this is a very very bad performance. One reason could be 
+About 50\% of twitter entities are missing. One reason could be 
 that those entities are not very famous. For example Brenda Weiler google 
-search result is 860,000 documents our of billions of web documents. For our 
+search result has 860,000 documents over the whole web. For our 
 small portion of the web it might make sense. If you pay attention to the 
@@
 
-A theory is that we are falling behind because we are using the cleansed 
+A theory is that we are falling behind because we are using the cleansed (from HTML tags)
 version of the corpus. We believe there has been a reason that TREC has 

### 2013-10-02 paper/kbanotebook2013/content/results.tex

@@
 %\ceg{We can add data on the total document size, The %number of each document type.  } 
- We had a single node cluster.
-The configuration of the server running the jobs is according to Table \ref{table:serverspec}.
-All together, The total size of the data after XZ compression and GPG encryption is 4.5TB and just over 500M StreamItems \cite{s3}.
-Data is stored in date-hour directories: From 2011-20-05-00 (12am) ) until 2013-02-13-23 (11pm) there are 11952 date-hour combinations.
+ Our system was composed of a single node cluster, which we refer to as the \textit{server}; the configuration of which is as described in Table \ref{table:serverspec}.
+The corpus is a snapshot of the web in English.
+Each document is annotated using lingpipe and is called StreamItem, a bundle of
+StreamItems are put together and serialized as Apache Thrift objects, then 
+compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
+and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
+The total size of the data after XZ compression and GPG encryption is 4.5TB and just over 500M StreamItems \cite{s3}.
+Data is stored in directories the naming of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am) until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952 date-hour combinations.
+This corpora consists of various media types the distribution of which can be found in \ref{table:documentsDist}.
+To have a sense of the scale of objects and compression as an example a 6mb
+gpg.xz files would become 45 mb thrift objects which can contain a couple of 
+thousand StreamItems depending on their size. Some of the documents have null 
+values for their annotation fields. The first portion of the data which 
+ranges from October 2011 to February 2013 is considered as training data.
 The source code of our system is stored as an open source project where enthusiasts can also contribute to \cite{github}, also the relevant discussion mailing list is accessible here \cite{googlegroups}.
+
+\begin{table}[b]
+\caption{Document Chunks Distribution }
+\centering
+\label{table:documentsDist}
+
+\begin{tabular}{|c|l|}
+\hline 
+\textbf{\# of Documents} & \textbf{Document Type}\\ 
+\hline 
+10988 & 	arxiv (full text, abstracts in StreamItem.other\_content) \\ \hline
+34887 & CLASSIFIED (spinn3r)  \\ \hline
+77674 & FORUM (spinn3r)  \\ \hline
+12947 & linking (reprocessed from kba-stream-corpus-2012, same stream\_id)  \\ \hline
+141936 & MAINSTREAM\_NEWS (spinn3r)  \\ \hline
+4137 & MEMETRACKER (spinn3r)  \\ \hline
+280629 & news (reprocessed from kba-stream-corpus-2012, same stream\_id)  \\ \hline
+6347 &  REVIEW (spinn3r) \\ \hline
+688848 & 	 social (reprocessed from kba-stream-corpus-2012 plus extension, same stream\_id)  \\ \hline
+740987 & WEBLOG (spinn3r)  \\ \hline
+
+\hline 
+\end{tabular} 
+\end{table}
 
@@
 
-On the performance of the first submission run we performed some random 
-sampling via two processes, the results of which are as in Table \ref{table:initialresult}.
-Our final submission has been elaborated in Tables \ref{table:finalresultaccuracy} and \ref{table:finalresultrecall}.
-You can observe that only CauseOfDeath is missing from the set of found slot values.
+On the performance of the first submission run we performed random 
+sampling via two processes, the results of which are according to Table \ref{table:initialresult}.
+You can view that we have had an accuracy of around 55\%, and about 15\% wrong entity identified and 30\% incorrect value extracted across all entities and slot types.
+For our final submission, we provide a more detailed statistics, which has been elaborated in Tables \ref{table:finalresultrecall} and \ref{table:finalresultaccuracy}.
+Table \ref{table:finalresultrecall} shows the extent of search outreach for each slot name.
+You can see that \textit{Affiliate} has been the slot name with highest hits and \textit{CauseOfDeath} our lowest hit with 0 instances found matching our patterns, after that \textit{AwardsWon} has been the next with 38 instances found.
+Table \ref{table:finalresultaccuracy} addresses the relative accuracy measure per slot value.
+There you can view that we have had the highest accuracy of 63.6\% for \textit{AssociateOf} and the lowest of 1\% - 5\%  for \textit{Affiliate}, \textit{Contact\_Meet\_PlaceTime} and \textit{EmployeeOf}.
 
-\begin{table}[b]
+\begin{table}
 \caption{Benchmark Server Specifications }
@@
 
-\begin{table}[t]
+\begin{table}
 \caption{SSF Performance Measure on Initial Submission }
@@
 
-\begin{table}[b]
+\begin{table}
+\caption{Recall Measure on Submission Infer }
+\centering
+\label{table:finalresultrecall}
+\begin{tabular}{|c|p{3cm}|p{4cm}|}
+\hline 
+ Slot Name & Total instances of slot value found & \# of entities covered by slot value \\ 
+\hline 
+Affiliate & 108598 & 80 \\ \hline 
+AssociateOf & 25278 & 106 \\ \hline 
+AwardsWon & 38 & 14 \\ \hline 
+CauseOfDeath & 0 & 0 \\ \hline 
+Contact\_Meet\_Entity & 191 & 8 \\ \hline 
+Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
+DateOfDeath & 87 & 14 \\ \hline 
+EmployeeOf & 75 & 16 \\ \hline 
+FoundedBy & 326 & 30 \\ \hline 
+FounderOf & 302 &  29 \\ \hline 
+Titles & 26823 & 118 \\ \hline 
+TopMembers & 314 & 26 \\ \hline
+
+\end{tabular} 
+\end{table}
+
+\begin{table}
 \caption{SSF Accuracy Measure on Submission Infer }
@@
 \hline 
- & Correct & Incorrect Entity name & Incorrect Value \\ 
+ Slot Name  & Correct & Incorrect Entity name & Incorrect Value \\ 
 \hline 
@@
 
-\begin{table}[t]
-\caption{Recall Measure on Submission Infer }
-\centering
-\label{table:finalresultrecall}
-\begin{tabular}{|c|p{3cm}|p{4cm}|}
-\hline 
- & Total instances of slot value found & \# of entities covered by slot value \\ 
-\hline 
-Affiliate & 108598 & 80 \\ \hline 
-AssociateOf & 25278 & 106 \\ \hline 
-AwardsWon & 38 & 14 \\ \hline 
-CauseOfDeath & 0 & 0 \\ \hline 
-Contact\_Meet\_Entity & 191 & 8 \\ \hline 
-Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
-DateOfDeath & 87 & 14 \\ \hline 
-EmployeeOf & 75 & 16 \\ \hline 
-FoundedBy & 326 & 30 \\ \hline 
-FounderOf & 302 &  29 \\ \hline 
-Titles & 26823 & 118 \\ \hline 
-TopMembers & 314 & 26 \\ \hline
-
-\end{tabular} 
-\end{table}
-
 % Note: Here is where we give as much stats as possible on our runs

### 2013-10-02 paper/kbanotebook2013/content/system.tex

@@
 
-\section{System Architecture}
+\section{System Overview}
 
-As shown in Figure \ref{fig:system}, our system is built in a pipeline manner which gives it the advantage to run each section separately and allow stream processing without wasting resources being clogged by one operation while others are waiting.
-Below, we describe each component briefly and in Section \ref{section:implementation} we will go through technical details.
+In this section, we sketch out the main components of the system.
+Our system is built with a pipeline architecture in mind which gives it the advantage to run each section separately and allow stream processing without resources being wasted by one operation while others are awaiting (Figure \ref{fig:system}).
+This consists of a section to perform pre-processing to prepare the required data, Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming Slot Filling which generates the actual slot values and Post processing to increase precision/recall.
 
@@
 
-To begin, we need to have real world aliases of entities.
+To begin, we need to have real-world aliases of entities of interest.
 TREC KBA prohibits Wikipedia entities to have any manual aliases being added and only allows automatic ways.
 We use Wikipedia API backlink references (redirects to a wiki entity) as aliases of the entity.
-We also use some techniques to extract some aliases from within the text of a wiki entity, which will be described later on.
-This whole process is referred to as \textbf{Alias Extraction (Wiki API, Wiki text)} Regarding Twitter entities this limit is lifted and participants are allowed to manually add aliases for them.
-Part of the reason is that Twitter environment is composed of so much informal and dialectic language which makes it extremely difficult to extract context out of tweets or entities descriptions in their profiles.
-This process of extracting aliases for Twitter entities is referred to as \textbf{Manual Alias Extraction (Twitter)}.
+We also use some techniques to extract  aliases from within the text of a wiki entity, which will be described later on.
+This whole process is referred to as \textit{Alias Extraction (Wiki API, Wiki text)}.
+On the other hand, regarding Twitter entities this limit is lifted and participants are allowed to manually add aliases for them.
+Part of the reason is that Twitter environment is composed of so much informal and dialectic language which makes it extremely difficult to extract alias out of tweets or entities descriptions in their profiles.
+This process of extracting aliases for Twitter entities is referred to as \textit{Manual Alias Extraction (Twitter)}.
 
-Once aliases are available we pass them through some rules of generating proper name orders which will produce various instances of writing a name.
+Once aliases are available we pass them through some rules of generating proper name orders which will produce various forms of writing a name.
 As a basic example Bill Gates can be written as Gates, Bill.
 This will allow the system to capture various notation forms of aliases.
-This part of the system is referred to as \textbf{Name Order Generator}.
+We refer to this part as \textit{Name Order Generator}.
 
-\subsection{Cumulative Citation Recommendation}
+\subsection{CCR}
 
-The main goal of Cumulative Citation Recommendation is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page.
-Regarding Cumulative Citation Recommendation we perform exact string matching
+The main goal of Cumulative Citation Recommendation is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page. Regarding CCR we perform exact string matching 
 and treat all the documents that mention an entity equally likely to be citable.
 For future iterations of the paper we have ideas on how to score documents 
-based on their likelihood of citation worthiness but for this iterations we 
+based on their likelihood of citation worthiness, but for this iterations we 
 treat all mentioning documents equally likely. One of the reasons for this is 
@@
 
-Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textbf{Chunk Files Index Generator} and \textbf{StreamItems Index Generator}.
+Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textit{Chunk Files Index Generator} and \textit{StreamItems Index Generator}.
 Chunk Files Index Generator will generate indexes of the chunk files that contain a mention of any of the desired entities.
@@
 
-\subsection{Streaming Slot Filling}
+\subsection{SSF}
 %\ceg{See the previous note.}
@@
 This is called Stream Slot Filling due to the fact that it is assumed that data is being generated as time goes on and for each extraction we should only consider current or past data.
-In our schematic diagram we refer to this as \textbf{Streaming Slot Value Extraction}.
+In our schematic diagram we refer to this as \textit{Streaming Slot Value Extraction}.
 Stream slot filling is done by pattern matching documents with manually

### 2013-10-07 paper/kbanotebook2013/content/system.tex
Write up v4

@@
 %\includegraphics[width=4.5in]{./images/system.eps}
-\includegraphics[width=6in]{./images/SystemBW.eps}
+\includegraphics[width=6in]{./images/sdl.eps}
+% http://convert.neevia.com/pdfconvert/
+%SystemDiagramLanguages-pdf.eps
 \vspace*{-.1in} \caption{Pipeline Design }\label{fig:system}
@@
 We use Wikipedia API backlink references (redirects to a wiki entity) as aliases of the entity.
-We also use some techniques to extract  aliases from within the text of a wiki entity, which will be described later on.
-This whole process is referred to as \textit{Alias Extraction (Wiki API, Wiki text)}.
+We also extract  aliases from within the text of a wiki entity, which will be described in Section \ref{section:aliasgeneration}.
+This whole process is referred to as \textit{Alias Extraction}.
 On the other hand, regarding Twitter entities this limit is lifted and participants are allowed to manually add aliases for them.
 Part of the reason is that Twitter environment is composed of so much informal and dialectic language which makes it extremely difficult to extract alias out of tweets or entities descriptions in their profiles.
-This process of extracting aliases for Twitter entities is referred to as \textit{Manual Alias Extraction (Twitter)}.
+This process of extracting aliases for Twitter entities is referred to as \textit{Manual Alias Extraction}.
 
-Once aliases are available we pass them through some rules of generating proper name orders which will produce various forms of writing a name.
+Once aliases are available we pass them through rules of generating proper name orders which will produce various forms of writing a name.
 As a basic example Bill Gates can be written as Gates, Bill.
@@
 
-The main goal of Cumulative Citation Recommendation is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page. Regarding CCR we perform exact string matching 
-and treat all the documents that mention an entity equally likely to be citable.
-For future iterations of the paper we have ideas on how to score documents 
-based on their likelihood of citation worthiness, but for this iterations we 
-treat all mentioning documents equally likely. One of the reasons for this is 
+The main goal of Cumulative Citation Recommendation is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page. We perform exact string matching 
+and treat all the documents that mention an entity equally likely to be citable. One of the reasons for this is 
 that in former TREC KBA reports \cite{JFrank12} there were observations of how 
-non-mentioning documents have highly low chance of being citable in Wikipedia.
-So we take on that and ignore non-citing documents. Regarding mentioning but 
-garbage, neutral or central documents we produce more slot values which can be 
-later on filtered out in the high accuracy filter section.
+non-mentioning documents have a low chance of being citable in Wikipedia.
+So we take on that and ignore non-citing documents.
 
@@
 This two level indexing will eliminate the need to process each and every ChunkFile/StreamItem for every entity.
+The reason for splitting this task into two steps is that not all chunk files contain any mention of the entities and we want to get rid of them as soon as possible.
+Chunk Files Index Generator which is written in C++ will discard non-mentioning chunk files and will stop further processing a chunk file as soon as it finds a mention there.
+Each chunk file can contain up to thousands of SIs which can be so time consuming if we were to process them in our Java base code.Processing StreamItems on the other hand is done in Java with ideas in mind for later on extensibility by adding other Java libraries.
 
@@
 %\ceg{See the previous note.}
-As described in the Introduction, the general purpose of slot filling is to extract proper values for relations of interest, some of which can be found in Table \ref{table:slotNameOntology}.
-This is called Stream Slot Filling due to the fact that it is assumed that data is being generated as time goes on and for each extraction we should only consider current or past data.
-In our schematic diagram we refer to this as \textit{Streaming Slot Value Extraction}.
+The purpose of slot filling is to extract proper values for relations of interest, which can be found in Table \ref{table:slotNameOntology}.
+This is called Stream Slot Filling because data is being generated as time goes on and for each extraction we should only consider current or past data.
+In figure \ref{fig:system} we refer to this as \textit{Streaming Slot Value Extraction}.
 Stream slot filling is done by pattern matching documents with manually

### 2013-10-07 paper/kbanotebook2013/content/discussion.tex

@@
 
-For slot extraction part, in order to improve the performance, what we need
-are: 1) Using multi-class classifiers instead of pattern matching method to 
+For slot extraction, to improve the performance, we need: 1) Using multi-class classifiers instead of pattern matching method to 
 extract slot values in order to increase both recall and accuracy for slots
@@
 
-About 50\% of twitter entities are missing. One reason could be 
+About 50\% of twitter entities are not found by the system. One reason could be 
 that those entities are not very famous. For example Brenda Weiler google 

### 2013-10-07 paper/kbanotebook2013/content/introduction.tex

@@
 
-\subsection{Cumulative Citation Recommendation (CCR)}
-
-An important challenge in maintaining Wikipedia (WP) which is the most popular free, web-based, collaborative, multilingual encyclopedia in the internet, is to make sure its contents are uptodate.
+An important challenge in maintaining Wikipedia.org (WP) which is the most popular free, web-based, collaborative, multilingual encyclopedia in the internet, is to make sure its contents are uptodate.
 Currently, there is considerable time lag between the publication date of cited news articles and the date of an edit to WP creating the citation.
@@
 
+\subsection{Cumulative Citation Recommendation (CCR)}
+
 For this track, assessors were instructed to ``use the wikipedia article to identify (disambiguate) the entity, and then imagine forgetting all info in the WP article and asking whether the text provides any information about the entity''\cite{JFrank12}.
-Documents would be divided according to two metrics: 1) mentioning the entity or not, 2) relevance level to the entity:
+Documents would be divided according to two metrics: a) mentioning the entity or not, b) relevance level to the entity:
 \begin{itemize}
@@
 \subsection{Streaming Slot Filling (SSF)}
-The task is that given certain Wikipedia or Twitter entities 
+The task is that given certain WP or Twitter entities 
 (wiki/twitter URLs) and certain relations of interest (given in Table  \ref{table:slotNameOntology}), extract as many triple relations as possible (hence, slot filling).
@@
 
-\noindent Since this is \textit{streaming} slot filling, we are only interested in new 
+\noindent In \textit{streaming} slot filling, we are only interested in new 
 slot values that were not substantiated earlier in the stream corpus. In Table \ref{table:slotNameOntology} you can view some slot values 

### 2013-10-07 paper/kbanotebook2013/content/results.tex

@@
 values for their annotation fields. The first portion of the data which 
-ranges from October 2011 to February 2013 is considered as training data.
+ranges from October 2011 to February 2012 is considered as training data.
 The source code of our system is stored as an open source project where enthusiasts can also contribute to \cite{github}, also the relevant discussion mailing list is accessible here \cite{googlegroups}.
@@
 \hline 
+\textbf{Spec} & \textbf{Details} \\ \hline
 Model & Dell xxx 32 cores \\ \hline 
@@
 \hline 
- & Correct & Incorrect Entity name & Incorrect Value \\ 
+ & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
 \hline 
@@
 \label{table:finalresultrecall}
-\begin{tabular}{|c|p{3cm}|p{4cm}|}
+\begin{tabular}{|c|p{3.5cm}|p{4cm}|}
 \hline 
- Slot Name & Total instances of slot value found & \# of entities covered by slot value \\ 
+ \textbf{Slot Name} & \textbf{Total instances of slot value found} & \textbf{\# of entities covered by slot value} \\ 
 \hline 
@@
 \hline 
- Slot Name  & Correct & Incorrect Entity name & Incorrect Value \\ 
+ \textbf{Slot Name}  & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
 \hline 

### 2013-10-07 paper/kbanotebook2013/content/implementation.tex
Improving paper structure.

@@
 
-Our contribution is that we perform pattern matching that conforms to each slot 
-value along with post-processings to eliminate noisy outputs. We extract aliases for entities from Wikipedia automatically both using API 
+We extract aliases for entities from Wikipedia automatically both using API 
 and using the actual page content, then apply pattern matching rules for slot 
-value extraction.
+value extraction. Our contribution is that we perform pattern matching that conforms to each slot 
+value along with post-processings to eliminate noisy outputs.
 
@@
 \subsection{Alias Generation}
+\label{section:aliasgeneration}
 
@@
 conventions such as Bill Gates $\rightarrow$ Gates, Bill.
+Meanwhile, William Henry Gates is an alias for Bill Gates in WP as a backlink reference.
+These kinds of aliases are also included in matching entities.
 
@@
 
+\begin{figure}
+\centering
+%\includegraphics[width=4.5in]{./images/system.eps}
+\includegraphics[width=6in]{./images/Pattern.eps}
+\vspace*{-.1in} \caption{Pattern Matching with Slot Value on the Right Side of Entity. }\label{fig:pattern}
+\vspace*{-.2in}
+\end{figure}
+
 In this system, we use pattern matching methods to find corresponding slot 
-values for entities. This is done by observing the training data which is the first four months of the corpus(Oct 2011 - Feb 2012). The procedure is: 1) Find stream items that contain the 
-entities by using alias names of the entities. 2) Inside these stream items, 
+values for entities.
+This is done by observing the training data which is the first four months of the corpus (October 2011 - February 2012).
+The procedure is: First Find stream items that contain the
+entities by using alias names of the entities. Then Inside these stream items, 
 fetch the sentences which contain entities by using alias names and the 
-coreference information provided by Lingpipe tags. 3) Use these sentences to 
-match existing patterns. 4) When patterns matched, generate SSF results.
+coreference information provided by Lingpipe tags. Use these sentences to 
+match existing patterns, and when patterns matched, generate SSF results.
 
-The format of the patterns is consist of five fields:
-1) the type of the entity. 
-2) the slot name.
-3) the pattern content.
-4) the direction of the slot value to the entity.
-5) the type of the slot values. When we match one pattern, we match all the 
-fields except the third field. The type of slot values could be the entity 
+Each pattern consists of five fields:
+
+\begin{itemize}
+\item Type of the entity
+\item Slot name
+\item Pattern content
+\item Direction of the slot value to the entity
+\item Type of the slot values
+\end{itemize}
+
+ When we match one pattern, we match all the 
+fields except the third field, which is extracted as the final result.
+
+ The type of slot values could be the entity 
 type tagged by Lingpipe, noun phrase tagged by OpenNLP and the time phrases we 
 hard-code. For these three kinds of patterns, we implement them in different 
-ways accordingly.
+ways accordingly. Next we will explain the patterns with more details, a brief example can be found in Figure \ref{fig:pattern}.
 
-Next we will explain the patterns with more details. Lets’s first look at one 
-example of the first kind of patterns. For slot FounderOf, we have this
-pattern: \textless PER, FounderOf, founder, right, ORG\textgreater. PER means 
+\textbf{Slot value type, tagged by Lingpipe:} For slot FounderOf, we have this
+pattern: \textless \texttt{PER, FounderOf, founder, right, ORG}\textgreater. PER means 
 that the entity we are finding slot values for is a PER entity; FounderOf 
@@
 
-Here is an example for the second type: \textless PER, AwardsWon, awarded, 
-right, NP\textgreater, NP meaning noun phrase. This pattern can be interpreted 
+\textbf{Slot value tagged as noun phrase by OpenNLP:} \textless \texttt{PER, AwardsWon, awarded, 
+right, NP}\textgreater, NP meaning noun phrase. This pattern can be interpreted 
 as that we are looking for a noun phrase after the “awarded'' since that noun 
@@
 
-Another example for the third type: \textless PER, DateOfDeath, died, right, 
-last night\textgreater. In this pattern, “last night'' means we are looking for 
+\textbf{Slot value of time phrases, hard coded:} \textless \texttt{PER, DateOfDeath, died, right, 
+last night}\textgreater. In this pattern, “last night'' means we are looking for 
 exactly the phrase ``last night'' to the right of ``died''. This pattern is 
@@
 
-For accuracy, we have found that there are three major kinds of errors: 1) 
-wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched 
+For accuracy, we have found that there are three major kinds of errors: First,  
+wrong entities found; next, wrong tags by the Lingpipe; and finally wrong results matched 
 by the patterns. We solve the first problem by using the Wikipedia or twitter 
 information of the entities to get better alias names. And we use
-post- processing to reduce the second and third types of errors.
+post-processing to reduce the second and third types of errors (Section \ref{section:highAccuracyFilter}).
 
 \subsection{High Accuracy Filter}
+\label{section:highAccuracyFilter}
 
@@
 in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
-two classes of rules deduplication rules and inference rules.
+two classes of rules: deduplication rules and inference rules.
 
@@
 
-The aim in post processing was to sanitize the results increasing the 
-precision of the results by eliminating spurrious results.
-
 % Note: Talk about how each of the algorithms were created

### 2013-10-09 paper/kbanotebook2013/content/introduction.tex
Updated citations so they compile correctly. Changed the figure resources so they compile easily with pdflatex. I updated the introduction to make it a little more indepth. I still have more work to do when making this pass

@@
 
-In this article we describe the approach the GatorDSR team from 
-University of Florida has adopted in addressing the challenge at NIST’s Text 
-REtrieval Conference (TREC) --- Knowledge Base Acceleration track 2013.
-There are two main sections designed for this track.
-Cumulative Citation Recommendation and Streaming Slot Filling.
-Due to the importance of knowledgebases, both of these tracks aim to accelerating populating them, hence the title Knowledgebase Acceleration (KBA).
-Below we describe each of these tracks and their purposes in full detail.
+An important challenge in maintaining Wikipedia.org (WP), the most popular 
+web-based, collaborative, multilingual encyclopedia in the internet, is to 
+make sure its contents are up-to-date. Presently, there is considerable time lag 
+between the publication date of cited news and the date of an edit to WP 
+creating the citation. The median time lag for a sample of about 60K
+web pages cited by WP articles in the \textit{living\_people} category is over 
+a year and the distribution has a long and heavy tail~\cite{JFrank12}. 
+Also, the majority of WP entities have updates on their associated article much 
+less frequently than their mention frequency. Such stale entries 
+are the norm in any large knowledge base (KB) because the number of humans 
+maintaining the KB is far fewer than the number of entities. 
+%Further, the number of mentions is much larger than the number of entities~\cite{JFrank12}. 
+Reducing latency keeps KBs such as WP relevant and helpful it users.
 
-An important challenge in maintaining Wikipedia.org (WP) which is the most popular free, web-based, collaborative, multilingual encyclopedia in the internet, is to make sure its contents are uptodate.
-Currently, there is considerable time lag between the publication date of cited news articles and the date of an edit to WP creating the citation.
-As an example, the median time lag for a sample of about 60,000 web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail\cite{JFrank12}.
-It is also noted that the majority of Wikipedia entities have updates on their associated Wiki article much less frequently than their mention frequency.
-Such stale entries are the norm in any large knowledge base (KB), because the number of humans maintaining the knowledge base is far fewer than the number of entities in the KB.
-Further, the number of mentions is much larger than the number of entities\cite{JFrank12}.
+Given a set of entities, possible citations may come from a large variety of sources.
+To attack this problem we develop a system to read streaming data and
+filter out articles that are candidates for citations.
+Given these documents, we extract the pairs of information in the 
+article that is recommended for citations.
+
+Our system contains three main components. First, we pre-process the data and
+build models representing the knowledge base entries.
+Next, we use the models to filter a stream of documents so they only contain 
+candidate recommendations.
+Lastly, we processes sentences from candidate extractions and return 
+specific information to be cited.
+
+We built this system as part of a formal task described in Section~\ref{sec:kbatask}.
+The data set from this task drop most our our design systems.
+Overall, our contributions are the following:
+\begin{itemize}[noitemsep,nolistsep]
+\item we built a system to filter a large amount of diverse documents (Section~\ref{},\ref{});
+\item we extract entity-slot-value triples of information to be added to KB (Section~\ref{},\ref{});
+\item we self-evaluate our results over a 4.5 TB data set (Section~\ref{},\ref{}).
+\end{itemize}
+
+\section{KBA Task Background\ceg{Move this to appendix?}}
+\label{sec:kbatask}
+The National Institute of Standards (NIST) hosted the
+Text REtrieval Conference (TREC) --- Knowledge Base Acceleration challenge in 2013. The task
+contains two main sections designed for this track, Cumulative Citation Recommendation 
+and Streaming Slot Filling. Due to the importance of knowledgebases, both of these 
+tracks aim to accelerating populating them, hence the title Knowledgebase Acceleration (KBA).
+Below we describe each of these tracks and their purposes.
 
@@
 
-For this track, assessors were instructed to ``use the wikipedia article to identify (disambiguate) the entity, and then imagine forgetting all info in the WP article and asking whether the text provides any information about the entity''\cite{JFrank12}.
-Documents would be divided according to two metrics: a) mentioning the entity or not, b) relevance level to the entity:
+For this track, assessors were instructed to ``use the Wikipedia article to 
+identify (disambiguate) the entity, and then imagine forgetting all info in the WP 
+article and asking whether the text provides any information about the entity'' \cite{JFrank12}.
+Documents would be divided according to two metrics: a) mentioning the entity or 
+not, b) relevance level to the entity:
 \begin{itemize}
@@
     \begin{itemize}
-\item \textbf{Mention:} Document explicitly mentions target entity, such as full name, partial name, nickname, pseudonym, title, stage name.
-\item \textbf{Zero-mention:} Document does not directly mention target.
-Could still be relevant, e.g.
-metonymic references like ``this administration'' -- \textgreater ``Obama''.
-See also synecdoche.
-A document could also be relevant to target entity through relation to entities mentioned in document -- apply this test question: can I learn something from this document about target entity using whatever other information I have about entity?
+      \item \textbf{Mention:} Document explicitly mentions target entity, such as full 
+        name, partial name, nickname, pseudonym, title, stage name.
+      \item \textbf{Zero-mention:} Document does not directly mention target. Could 
+        still be relevant, e.g.\ metonymic references like ``this administration'' --
+        \textgreater ``Obama''. See also synecdoche. A document could also be relevant to 
+        target entity through relation to entities mentioned in document -- apply this 
+        test question: can I learn something from this document about target entity using 
+        whatever other information I have about entity?
     \end{itemize}
@@
     \begin{itemize}
-\item \textbf{Garbage:} not relevant, e.g. spam.
-\item \textbf{Neutral:} Not relevant, i.e.
-no info could be deduced about entity, e.g., entity name used in product name, or only pertains to community of target such that no information could be learned about entity, although you can see how an automatic algorithm might have thought it was relevant.
-\item \textbf{Relevant:} Relates indirectly, e.g., tangential with substantive implications, or topics or events of likely
+      \item \textbf{Garbage:} not relevant, e.g.\ spam.
+      \item \textbf{Neutral:} Not relevant, i.e.\ no info could be deduced about entity, 
+        e.g., entity name used in product name, or only pertains to community of target 
+        such that no information could be learned about entity, although you can see how 
+        an automatic algorithm might have thought it was relevant.
+      \item \textbf{Relevant:} Relates indirectly, e.g., tangential with substantive 
+        implications, or topics or events of likely
         impact on entity.
-\item \textbf{Central:} Relates directly to target such that you would cite it in the WP article for this entity, e.g. entity is a
+      \item \textbf{Central:} Relates directly to target such that you would cite it in 
+        the WP article for this entity, e.g.\ entity is a
         central figure in topics/events.
@@
 The task is that given certain WP or Twitter entities 
-(wiki/twitter URLs) and certain relations of interest (given in Table  \ref{table:slotNameOntology}), extract as many triple relations as possible (hence, slot filling).
-This can be used to automatically populate knowledgebases such as free-base or DBPedia
-or even fill-in the information boxes at Wikipedia.
-Below, you can view some examples of what it means to fill in a slot value; in each example there is a sentence of interest that we wish to extract slot values from, an entity that the slot value is related to, and a slot name which can be thought of as the topic of the slot value:
+(wiki/twitter URLs) and certain relations of interest (given in
+Table~\ref{table:slotNameOntology}), extract as many triple relations as possible (
+hence, slot filling). This can be used to automatically populate knowledgebases 
+such as free-base or DBPedia or even fill-in the information boxes at Wikipedia. 
+Below, you can view some examples of what it means to fill in a slot value; in 
+each example there is a sentence of interest that we wish to extract slot values 
+from, an entity that the slot value is related to, and a slot name which can be 
+thought of as the topic of the slot value:
 
@@
 \noindent In \textit{streaming} slot filling, we are only interested in new 
-slot values that were not substantiated earlier in the stream corpus. In Table \ref{table:slotNameOntology} you can view some slot values 
+slot values that were not substantiated earlier in the stream corpus.
+In Table~\ref{table:slotNameOntology} you can view some slot values 
 and their types, the comprehensive description of which can be found at
-\cite{tackbp} and \cite{aec}.
-The details of the metric for SSF will favor systems that most closely match the changes in the ground truth time line of slot values.
-This is done by searching for other documents that mentioned an entity and exactly matched the slot fill strings selected by the assessors.
+\cite{tackbp} and \cite{aec}. The details of the metric for SSF will favor systems 
+that most closely match the changes in the ground truth time line of slot values. 
+This is done by searching for other documents that mentioned an entity and exactly 
+matched the slot fill strings selected by the assessors.
 
-In the rest of the paper, we address the following material.
-In Section 2, we sketch the main components of the system and their purposes.
-In Section 3, describe the details of how we designed and implemented certain components critical to the behavior of the system.
-Section 4 addresses the performance and the results we achieved.
-Section 5, goes through a discussion of the challenges we had to produce reliable results over the massive amount of information available, and how we overcome these issues.
-For similar approaches regarding last year's track you can refer to \cite{ji2011knowledge}.
+In the rest of the paper, we address the following material. In Section 2, we 
+sketch the main components of the system and their purposes. In Section 3, 
+describe the details of how we designed and implemented certain components 
+critical to the behavior of the system. Section 4 addresses the performance and 
+the results we achieved. Section 5, goes through a discussion of the challenges we 
+had to produce reliable results over the massive amount of information available, 
+and how we overcome these issues. For similar approaches regarding last year's 
+track you can refer to \cite{ji2011knowledge}.
 

### 2013-10-10 paper/kbanotebook2013/content/implementation.tex
Updated citations so they compile correctly. Changed the figure resources so they compile easily with pdflatex. I updated the introduction to make it a little more indepth. I still have more work to do when making this pass
Rearranged a lot of text. Still need to fix the language

@@
 typical cases we consider some generic first name last name order swapping 
-conventions such as Bill Gates $\rightarrow$ Gates, Bill.
-Meanwhile, William Henry Gates is an alias for Bill Gates in WP as a backlink reference.
-These kinds of aliases are also included in matching entities.
+conventions such as Bill Gates $\rightarrow$ Gates, Bill.  Meanwhile, William Henry
+Gates is an alias for Bill Gates in WP as a backlink reference. These kinds of
+aliases are also included in matching entities.
+
+\subsection{Cumulative Citation Recommendation}
+\label{sec:ccrimpl}
+
+Our pipeline of processing the corpus consists of a two layer indexing system 
+referred to as \textit{Chunk Files Index Generator} and \textit{StreamItems Index Generator}.
+Chunk Files Index Generator will generate indexes of the chunk files 
+that contain a mention of any of the desired entities. StreamItems Index Generator 
+on the other hand will index StreamItems that contain a mention of a given entity 
+respectively. This two level indexing will eliminate the need to process each and 
+every ChunkFile/StreamItem for every entity. The reason for splitting this task 
+into two steps is that not all chunk files contain any mention of the entities and 
+we want to get rid of them as soon as possible. Chunk Files Index Generator which 
+is written in C++ will discard non-mentioning chunk files and will stop further 
+processing a chunk file as soon as it finds a mention there. Each chunk file can 
+contain up to thousands of SIs which can be so time consuming if we were to 
+process them in our Java base code.Processing StreamItems on the other hand is 
+done in Java with ideas in mind for later on extensibility by adding other Java libraries.
 
 \subsection{Streaming Slot Value Extraction}
-
+\label{sec:ssve}
 \begin{figure}
@@
 %\includegraphics[width=4.5in]{./images/system.eps}
-\includegraphics[width=6in]{./images/Pattern.eps}
+%\includegraphics[width=6in]{./images/Pattern.eps}
+\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
 \vspace*{-.1in} \caption{Pattern Matching with Slot Value on the Right Side of Entity. }\label{fig:pattern}
@@
 hard-code. For these three kinds of patterns, we implement them in different 
-ways accordingly. Next we will explain the patterns with more details, a brief example can be found in Figure \ref{fig:pattern}.
+ways accordingly. Next we will explain the patterns with more details, a brief
+example can be found in Figure~\ref{fig:pattern}.
 
@@
 information of the entities to get better alias names. And we use
-post-processing to reduce the second and third types of errors (Section \ref{section:highAccuracyFilter}).
+post-processing to reduce the second and third types of errors (Section~\ref{section:highAccuracyFilter}).
 

### 2013-10-10 paper/kbanotebook2013/content/introduction.tex
Rearranged a lot of text. Still need to fix the language

@@
 
-Given a set of entities, possible citations may come from a large variety of sources.
-To attack this problem we develop a system to read streaming data and
-filter out articles that are candidates for citations.
+Given an entity page, possible citations may come from a variety of sources.
+The actual citable information is a small percentage of the total documents that appear on the web.
+We develop a system to read streaming data and filter out articles that are candidates for citations.
 Given these documents, we extract the pairs of information in the 
-article that is recommended for citations.
+article that is recommended for citations for each knowledge base page.
+\ceg{add details}
 
@@
 specific information to be cited.
+\ceg{add details}
 
@@
 \begin{itemize}[noitemsep,nolistsep]
-\item we built a system to filter a large amount of diverse documents (Section~\ref{},\ref{});
-\item we extract entity-slot-value triples of information to be added to KB (Section~\ref{},\ref{});
-\item we self-evaluate our results over a 4.5 TB data set (Section~\ref{},\ref{}).
+\item we introduce a method to build models of name variations (Section~\ref{sec:preproc},~\ref{section:aliasgeneration});
+\item we built a system to filter a large amount of diverse documents (Section~\ref{sec:ccr1},~\ref{sec:ccrimpl});
+\item we extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssf1},~\ref{sec:ssve});
+\item we filter the final results using deduplication and inference (Section~\ref{sec:postproc},~\ref{section:highAccuracyFilter});
+\item we self-evaluate our results over a 4.5 TB data set (Section~\ref{sec:results}).
 \end{itemize}
@@
 contains two main sections designed for this track, Cumulative Citation Recommendation 
-and Streaming Slot Filling. Due to the importance of knowledgebases, both of these 
-tracks aim to accelerating populating them, hence the title Knowledgebase Acceleration (KBA).
+and Streaming Slot Filling. Due to the importance of knowledge bases, both of these 
+tracks aim to accelerating populating them, hence the title Knowledge Base Acceleration (KBA).
 Below we describe each of these tracks and their purposes.

### 2013-10-10 paper/kbanotebook2013/content/results.tex
Rearranged a lot of text. Still need to fix the language

@@
 \section{Results}
+\label{sec:results}
 
 %\ceg{We can add data on the total document size, The %number of each document type.  } 
- Our system was composed of a single node cluster, which we refer to as the \textit{server}; the configuration of which is as described in Table \ref{table:serverspec}.
-The corpus is a snapshot of the web in English.
+ Our system was composed of a single node cluster, which we refer to as the
+ \textit{server}; the configuration of which is as described in
+ Table~\ref{table:serverspec}. The corpus is a snapshot of the web in English.
  Each document is annotated using lingpipe and is called StreamItem, a bundle of 
@@
 and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
-The total size of the data after XZ compression and GPG encryption is 4.5TB and just over 500M StreamItems \cite{s3}.
-Data is stored in directories the naming of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am) until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952 date-hour combinations.
-This corpora consists of various media types the distribution of which can be found in \ref{table:documentsDist}.
-To have a sense of the scale of objects and compression as an example a 6mb
+The total size of the data after XZ compression and GPG encryption is 4.5TB and
+just over 500M StreamItems \cite{s3}. Data is stored in directories the naming
+of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am)
+until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952
+date-hour combinations. This corpora consists of various media types the
+distribution of which can be found in Table~\ref{table:documentsDist}. To have a
+sense of the scale of objects and compression as an example a 6mb
 gpg.xz files would become 45 mb thrift objects which can contain a couple of 
@@
 ranges from October 2011 to February 2012 is considered as training data.
-The source code of our system is stored as an open source project where enthusiasts can also contribute to \cite{github}, also the relevant discussion mailing list is accessible here \cite{googlegroups}.
+The source code of our system is stored as an open source project where
+enthusiasts can also contribute to \cite{github}, also the relevant discussion
+mailing list is accessible here \cite{googlegroups}.
 
@@
 On the performance of the first submission run we performed random 
-sampling via two processes, the results of which are according to Table \ref{table:initialresult}.
-You can view that we have had an accuracy of around 55\%, and about 15\% wrong entity identified and 30\% incorrect value extracted across all entities and slot types.
-For our final submission, we provide a more detailed statistics, which has been elaborated in Tables \ref{table:finalresultrecall} and \ref{table:finalresultaccuracy}.
-Table \ref{table:finalresultrecall} shows the extent of search outreach for each slot name.
-You can see that \textit{Affiliate} has been the slot name with highest hits and \textit{CauseOfDeath} our lowest hit with 0 instances found matching our patterns, after that \textit{AwardsWon} has been the next with 38 instances found.
-Table \ref{table:finalresultaccuracy} addresses the relative accuracy measure per slot value.
-There you can view that we have had the highest accuracy of 63.6\% for \textit{AssociateOf} and the lowest of 1\% - 5\%  for \textit{Affiliate}, \textit{Contact\_Meet\_PlaceTime} and \textit{EmployeeOf}.
+sampling via two processes, the results of which are according to
+Table~\ref{table:initialresult}. You can view that we have had an accuracy of
+around 55\%, and about 15\% wrong entity identified and 30\% incorrect value
+extracted across all entities and slot types. For our final submission, we
+provide a more detailed statistics, which has been elaborated in
+Table~\ref{table:finalresultrecall} and Table~\ref{table:finalresultaccuracy}.
+Table~\ref{table:finalresultrecall} shows the extent of search outreach for
+each slot name. You can see that \textit{Affiliate} has been the slot name with
+highest hits and \textit{CauseOfDeath} our lowest hit with 0 instances found
+matching our patterns, after that \textit{AwardsWon} has been the next with 38
+instances found. Table~\ref{table:finalresultaccuracy} addresses the relative
+accuracy measure per slot value. There you can view that we have had the
+highest accuracy of 63.6\% for \textit{AssociateOf} and the lowest of
+1\% - 5\%  for \textit{Affiliate}, \textit{Contact\_Meet\_PlaceTime} and \textit{EmployeeOf}.
 

### 2013-10-10 paper/kbanotebook2013/content/system.tex
Updated citations so they compile correctly. Changed the figure resources so they compile easily with pdflatex. I updated the introduction to make it a little more indepth. I still have more work to do when making this pass
Rearranged a lot of text. Still need to fix the language

@@
 \centering
-%\includegraphics[width=4.5in]{./images/system.eps}
-\includegraphics[width=6in]{./images/sdl.eps}
+%\includegraphics[width=6in]{./images/sdl.eps}
+\includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
 % http://convert.neevia.com/pdfconvert/
-%SystemDiagramLanguages-pdf.eps
 \vspace*{-.1in} \caption{Pipeline Design }\label{fig:system}
@@
 
-In this section, we sketch out the main components of the system.
-Our system is built with a pipeline architecture in mind which gives it the advantage to run each section separately and allow stream processing without resources being wasted by one operation while others are awaiting (Figure \ref{fig:system}).
-This consists of a section to perform pre-processing to prepare the required data, Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming Slot Filling which generates the actual slot values and Post processing to increase precision/recall.
+In this section, we sketch out the main components of the system. Our system is 
+built with a pipeline architecture in mind which gives it the advantage to run 
+each section separately and allow stream processing without resources being wasted 
+by one operation while others are awaiting (Figure~\ref{fig:system}).
+This consists of a section to perform pre-processing to prepare the required data, 
+Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming 
+Slot Filling which generates the actual slot values and Post processing to 
+increase precision/recall.
 
@@
 \subsection{Preprocessing}
+\label{sec:preproc}
 
-To begin, we need to have real-world aliases of entities of interest.
-TREC KBA prohibits Wikipedia entities to have any manual aliases being added and only allows automatic ways.
-We use Wikipedia API backlink references (redirects to a wiki entity) as aliases of the entity.
-We also extract  aliases from within the text of a wiki entity, which will be described in Section \ref{section:aliasgeneration}.
-This whole process is referred to as \textit{Alias Extraction}.
-On the other hand, regarding Twitter entities this limit is lifted and participants are allowed to manually add aliases for them.
-Part of the reason is that Twitter environment is composed of so much informal and dialectic language which makes it extremely difficult to extract alias out of tweets or entities descriptions in their profiles.
-This process of extracting aliases for Twitter entities is referred to as \textit{Manual Alias Extraction}.
+To begin, we need to have real-world aliases of entities of interest. TREC KBA
+prohibits Wikipedia entities to have any manual aliases being added and only
+allows automatic ways. We use Wikipedia API backlink references
+(redirects to a wiki entity) as aliases of the entity. We also extract 
+aliases from within the text of a wiki entity, which will be described in
+Section~\ref{section:aliasgeneration}. This whole process is referred to as
+\textit{Alias Extraction}. On the other hand, regarding Twitter entities this
+limit is lifted and participants are allowed to manually add aliases for them.
+Part of the reason is that Twitter environment is composed of so much informal
+and dialectic language which makes it extremely difficult to extract alias out
+of tweets or entities descriptions in their profiles. This process of extracting
+aliases for Twitter entities is referred to as \textit{Manual Alias Extraction}.
 
@@
 \subsection{CCR}
+\label{sec:ccr1}
 
@@
 So we take on that and ignore non-citing documents.
-
-Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textit{Chunk Files Index Generator} and \textit{StreamItems Index Generator}.
-Chunk Files Index Generator will generate indexes of the chunk files that contain a mention of any of the desired entities.
-StreamItems Index Generator on the other hand will index StreamItems that contain a mention of a given entity respectively.
-This two level indexing will eliminate the need to process each and every ChunkFile/StreamItem for every entity.
-The reason for splitting this task into two steps is that not all chunk files contain any mention of the entities and we want to get rid of them as soon as possible.
-Chunk Files Index Generator which is written in C++ will discard non-mentioning chunk files and will stop further processing a chunk file as soon as it finds a mention there.
-Each chunk file can contain up to thousands of SIs which can be so time consuming if we were to process them in our Java base code.Processing StreamItems on the other hand is done in Java with ideas in mind for later on extensibility by adding other Java libraries.
 
@@
 \subsection{SSF}
+\label{sec:ssf1}
 %\ceg{See the previous note.}
-The purpose of slot filling is to extract proper values for relations of interest, which can be found in Table \ref{table:slotNameOntology}.
-This is called Stream Slot Filling because data is being generated as time goes on and for each extraction we should only consider current or past data.
-In figure \ref{fig:system} we refer to this as \textit{Streaming Slot Value Extraction}.
+The purpose of slot filling is to extract proper values for relations of
+interest, which can be found in Table~\ref{table:slotNameOntology}.
+This is called Stream Slot Filling because data is being generated as time goes
+on and for each extraction we should only consider current or past data.
+In Figure~\ref{fig:system} we refer to this as \textit{Streaming Slot Value Extraction}.
 Stream slot filling is done by pattern matching documents with manually 
@@
 \subsection{Post Processing Algorithm}
+\label{sec:postproc}
 

### 2013-10-10 paper/kbanotebook2013/paper.tex
Updated citations so they compile correctly. Changed the figure resources so they compile easily with pdflatex. I updated the introduction to make it a little more indepth. I still have more work to do when making this pass
Rearranged a lot of text. Still need to fix the language

@@
 \usepackage[hyphens]{url}
+\usepackage{enumitem}
 
@@
 
-\author {
- Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{ University of Florida, Gainesville, Florida, USA}\\
-       { \{msnia, cgrant, ypeng, daisyw\}@cise.ufl.edu}
+\author{Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{University of Florida, Gainesville, Florida, USA}\\
+       {\{msnia, cgrant, ypeng, daisyw\}@cise.ufl.edu}
 \and

### 2013-10-10 paper/kbanotebook2013/content/implementation.tex
integrated a bunch of changes, only integrated half of yangs changes

@@
 
-In this system, we use pattern matching methods to find corresponding slot 
-values for entities.
-This is done by observing the training data which is the first four months of the corpus (October 2011 - February 2012).
-The procedure is: First Find stream items that contain the
-entities by using alias names of the entities. Then Inside these stream items, 
+In the data set, we are given 4 months of data (October 2011 - February 2012) as training data.
+Instead of building a classifier we use pattern matching methods to find
+corresponding slot values for entities. 
+Pattern matching is simple to manipulate results and implement.
+Additionally, we can simply to explain and evaluate results.
+
+The procedure to extract slots with the patterns is to 
+first find Streamitems that contain the 
+entities by using alias names of the entities. Next, inside these Streamitems, 
 fetch the sentences which contain entities by using alias names and the 
@@
 
-Each pattern consists of five fields:
+\begin{algorithm}
+  \textbf{Given a set of Streamitems $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
+  \textbf{Set of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
+  \begin{algorithmic}[1]
+    \FOR{$si \in \mathcal{S}$}
+    \FOR{$s \in si$}
+    \IF{$ check\_one\_of\_the\_patterns$}
+    \STATE Emit(sentence, pattern)
+  \ENDIF
+\ENDFOR
+\ENDFOR
+\end{algorithmic}
+\end{algorithm}
 
-\begin{itemize}
-\item Type of the entity
-\item Slot name
-\item Pattern content
-\item Direction of the slot value to the entity
-\item Type of the slot values
-\end{itemize}
+A pattern is defined as a record representing knowledge going to be added to a knowledge base.
+A pattern $\mathcal{P}$ is represented as $\mathcal{P} = \langle p_1, p_2, p_3, p_4, p_5 \rangle$.
 
- When we match one pattern, we match all the 
-fields except the third field, which is extracted as the final result.
-
- The type of slot values could be the entity 
-type tagged by Lingpipe, noun phrase tagged by OpenNLP and the time phrases we 
-hard-code. For these three kinds of patterns, we implement them in different 
+The first value, $p_1$ represents the type of entity. These entity types are in
+the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC}
+represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER}
+represents a person.
+The $p_2$ represents a slot name.
+A list of slot names is present in Table~\ref{table:slotNameOntology}.
+The third element $p_3$ is the pattern content. This is a string found in the sentence.
+The extractor looks for this exact string or pattern in a sentence.
+The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in
+$p_4$ to explore sentence.
+The final element $p_5$ represent the slot value of a pattern. Thois
+%When we match one pattern, we match all the 
+%fields except the third field, which is extracted as the final result.
+The type of slot value may be the entity 
+type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP or a hard-coded phrase. 
+For these three kinds of patterns, we implement them in different 
 ways accordingly. Next we will explain the patterns with more details, a brief
@@
 \textbf{Slot value type, tagged by Lingpipe:} For slot FounderOf, we have this
-pattern: \textless \texttt{PER, FounderOf, founder, right, ORG}\textgreater. PER means 
+pattern: \textless \texttt{PER, FounderOf, ``founder'', right, ORG}\textgreater. PER means 
 that the entity we are finding slot values for is a PER entity; FounderOf 
@@
 
-\textbf{Slot value tagged as noun phrase by OpenNLP:} \textless \texttt{PER, AwardsWon, awarded, 
+\textbf{Slot value tagged as noun phrase by OpenNLP:} \textless \texttt{PER, AwardsWon, ``awarded'', 
 right, NP}\textgreater, NP meaning noun phrase. This pattern can be interpreted 
-as that we are looking for a noun phrase after the “awarded'' since that noun 
+as that we are looking for a noun phrase after the ``awarded'' since that noun 
 phrase could possibly represent an award. Since titles and awards are usually 
@@
 
-\textbf{Slot value of time phrases, hard coded:} \textless \texttt{PER, DateOfDeath, died, right, 
-last night}\textgreater. In this pattern, “last night'' means we are looking for 
+\textbf{Slot value of time phrases, hard coded:} \textless \texttt{PER, DateOfDeath, ``died'', right, 
+``last night''}\textgreater. In this pattern, ``last night'' means we are looking for 
 exactly the phrase ``last night'' to the right of ``died''. This pattern is 
@@
 
-To improve recall, we introduce generic patterns that can generate many results.
-But these patterns generate many errors, too. Thus there is a trade-off 
-between the accuracy and recall. This is one drawback of using pattern 
-matching method, meaning it is really hard to find good patterns with both 
-high accuracy and recall.
-
-For accuracy, we have found that there are three major kinds of errors: First,  
-wrong entities found; next, wrong tags by the Lingpipe; and finally wrong results matched 
+We have found that there are three major classes of accuracy errors:
+wrong entities found, wrong tags by the Lingpipe, and finally wrong results matched 
 by the patterns. We solve the first problem by using the Wikipedia or twitter 

### 2013-10-10 paper/kbanotebook2013/content/introduction.tex
integrated a bunch of changes, only integrated half of yangs changes

@@
 \begin{itemize}[noitemsep,nolistsep]
-\item we introduce a method to build models of name variations (Section~\ref{sec:preproc},~\ref{section:aliasgeneration});
-\item we built a system to filter a large amount of diverse documents (Section~\ref{sec:ccr1},~\ref{sec:ccrimpl});
-\item we extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssf1},~\ref{sec:ssve});
-\item we filter the final results using deduplication and inference (Section~\ref{sec:postproc},~\ref{section:highAccuracyFilter});
+\item we introduce a method to build models of name variations (Section~\ref{section:aliasgeneration});
+\item we built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
+\item we extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
+\item we filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
 \item we self-evaluate our results over a 4.5 TB data set (Section~\ref{sec:results}).
@@
 
-\section{KBA Task Background\ceg{Move this to appendix?}}
+\section{KBA Task Background}
 \label{sec:kbatask}
@@
 article and asking whether the text provides any information about the entity'' \cite{JFrank12}.
-Documents would be divided according to two metrics: a) mentioning the entity or 
-not, b) relevance level to the entity:
-\begin{itemize}
-  \item \textbf{Mention} 
-    \begin{itemize}
+Documents are divided according if an entity is mentioned and a relevance level to the entity.
+
+More specifically, a document may have a mention or be without a mention.
+\begin{itemize}[noitemsep]
   \item \textbf{Mention:} Document explicitly mentions target entity, such as full 
@@
   \item \textbf{Zero-mention:} Document does not directly mention target. Could 
-        still be relevant, e.g.\ metonymic references like ``this administration'' --
-        \textgreater ``Obama''. See also synecdoche. A document could also be relevant to 
+    still be relevant, e.g.\ metonymic references like ``this administration'' 
+    $\rightarrow$ ``Obama''. See also synecdoche. A document could also be relevant to 
     target entity through relation to entities mentioned in document -- apply this 
@@
 \end{itemize}
-  \item \textbf{Relevance}
-    \begin{itemize}
+
+The relevance of a document to a query is split into the four classifications.
+\begin{itemize}[noitemsep]
   \item \textbf{Garbage:} not relevant, e.g.\ spam.
@@
     central figure in topics/events.
-
-    \end{itemize}
 \end{itemize}

### 2013-10-10 paper/kbanotebook2013/content/system.tex
integrated a bunch of changes, only integrated half of yangs changes

@@
+\section{System Overview}
+
+In this section, we introduce the main components of the system. Our system is 
+built with a pipeline architecture in mind giving it the advantage to run 
+each section separately to allow stream processing without blocking the data flow of components 
+(Figure~\ref{fig:system}).
+The three logical components include sections for performing preprocessing to prepare the required data, 
+Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming 
+Slot Filling to generate the actual slot values and PostProcessing to 
+increase precision/recall. 
+TREC provides a streaming data set and  entities from Twitter or WP to query.
+
+%\ceg{Discuss current system first. If you want to keep the decisions points that led to the current architecture, make it a subsection.}
+
 \begin{figure}
@@
 % http://convert.neevia.com/pdfconvert/
-\vspace*{-.1in} \caption{Pipeline Design }\label{fig:system}
+  \vspace*{-.1in} 
+  \caption{The GatorDSR team System Architecture.
+  Components are logically groups with dotted boxes.
+  Color details the programing language implementation of components.}
+  \label{fig:system}
   \vspace*{-.2in}
@@
 
-\section{System Overview}
-
-In this section, we sketch out the main components of the system. Our system is 
-built with a pipeline architecture in mind which gives it the advantage to run 
-each section separately and allow stream processing without resources being wasted 
-by one operation while others are awaiting (Figure~\ref{fig:system}).
-This consists of a section to perform pre-processing to prepare the required data, 
-Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming 
-Slot Filling which generates the actual slot values and Post processing to 
-increase precision/recall.
-
-%\ceg{Discuss current system first. If you want to keep the decisions points that led to the current architecture, make it a subsection.}
-
-\subsection{Preprocessing}
+\textbf{Preprocessing.}
 \label{sec:preproc}
-
-To begin, we need to have real-world aliases of entities of interest. TREC KBA
-prohibits Wikipedia entities to have any manual aliases being added and only
+The contest prohibits Wikipedia entities to have any manual aliases being added and only
 allows automatic ways. We use Wikipedia API backlink references
@@
 Section~\ref{section:aliasgeneration}. This whole process is referred to as
-\textit{Alias Extraction}. On the other hand, regarding Twitter entities this
-limit is lifted and participants are allowed to manually add aliases for them.
-Part of the reason is that Twitter environment is composed of so much informal
-and dialectic language which makes it extremely difficult to extract alias out
-of tweets or entities descriptions in their profiles. This process of extracting
+\textit{Alias Extraction}. 
+The manual extraction rule is lifted and participants are allowed to manually add aliases for Twitter entities.
+This is allowed because the Twitter website does not provide an example page from the beginning of the document stream.
+This process of extracting
 aliases for Twitter entities is referred to as \textit{Manual Alias Extraction}.
 
-Once aliases are available we pass them through rules of generating proper name orders which will produce various forms of writing a name.
-As a basic example Bill Gates can be written as Gates, Bill.
-This will allow the system to capture various notation forms of aliases.
-We refer to this part as \textit{Name Order Generator}.
+Once aliases are available we pass them through rules of generating proper name 
+orders which will produce various forms of writing a name. As a basic example Bill 
+Gates can be written as Gates, Bill. This will allow the system to capture various 
+notation forms of aliases. We refer to this part as \textit{Name Order Generator}.
 
-\subsection{CCR}
+\textbf{Cumulative Citation Recommendation.}
 \label{sec:ccr1}
-
-The main goal of Cumulative Citation Recommendation is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page. We perform exact string matching 
+The main goal of CCR is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page. We perform exact string matching 
 and treat all the documents that mention an entity equally likely to be citable. One of the reasons for this is 
@@
 
-\subsection{SSF}
+\textbf{Streaming Slot Filling.}
 \label{sec:ssf1}
 %\ceg{See the previous note.}
-The purpose of slot filling is to extract proper values for relations of
+The purpose of SSF is to extract proper values for relations of
 interest, which can be found in Table~\ref{table:slotNameOntology}.
@@
 
-\subsection{Post Processing Algorithm}
+\textbf{Post Processing Algorithm.}
 \label{sec:postproc}
-
 The SSF output of many extractions is noisy. The data contains duplicates and 

### 2013-10-11 paper/kbanotebook2013/content/appendix.tex
moved description to appendix, made some other small wording changtes

--- 2013-10-10 paper/kbanotebook2013/content/introduction.tex
@@
-\section{Introduction}
-
-An important challenge in maintaining Wikipedia.org (WP), the most popular 
-web-based, collaborative, multilingual encyclopedia in the internet, is to 
-make sure its contents are up-to-date. Presently, there is considerable time lag 
-between the publication date of cited news and the date of an edit to WP 
-creating the citation. The median time lag for a sample of about 60K
-web pages cited by WP articles in the \textit{living\_people} category is over 
-a year and the distribution has a long and heavy tail~\cite{JFrank12}. 
-Also, the majority of WP entities have updates on their associated article much 
-less frequently than their mention frequency. Such stale entries 
-are the norm in any large knowledge base (KB) because the number of humans 
-maintaining the KB is far fewer than the number of entities. 
-%Further, the number of mentions is much larger than the number of entities~\cite{JFrank12}. 
-Reducing latency keeps KBs such as WP relevant and helpful it users.
-
-Given an entity page, possible citations may come from a variety of sources.
-The actual citable information is a small percentage of the total documents that appear on the web.
-We develop a system to read streaming data and filter out articles that are candidates for citations.
-Given these documents, we extract the pairs of information in the 
-article that is recommended for citations for each knowledge base page.
-\ceg{add details}
-
-Our system contains three main components. First, we pre-process the data and
-build models representing the knowledge base entries.
-Next, we use the models to filter a stream of documents so they only contain 
-candidate recommendations.
-Lastly, we processes sentences from candidate extractions and return 
-specific information to be cited.
-\ceg{add details}
-
-We built this system as part of a formal task described in Section~\ref{sec:kbatask}.
-The data set from this task drop most our our design systems.
-Overall, our contributions are the following:
-\begin{itemize}[noitemsep,nolistsep]
-\item we introduce a method to build models of name variations (Section~\ref{section:aliasgeneration});
-\item we built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
-\item we extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
-\item we filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
-\item we self-evaluate our results over a 4.5 TB data set (Section~\ref{sec:results}).
-\end{itemize}
+\appendix
 
@@
 
-In the rest of the paper, we address the following material. In Section 2, we 
-sketch the main components of the system and their purposes. In Section 3, 
-describe the details of how we designed and implemented certain components 
-critical to the behavior of the system. Section 4 addresses the performance and 
-the results we achieved. Section 5, goes through a discussion of the challenges we 
-had to produce reliable results over the massive amount of information available, 
-and how we overcome these issues. For similar approaches regarding last year's 
-track you can refer to \cite{ji2011knowledge}.
+%In the rest of the paper, we address the following material. In Section 2, we 
+%sketch the main components of the system and their purposes. In Section 3, 
+%describe the details of how we designed and implemented certain components 
+%critical to the behavior of the system. Section 4 addresses the performance and 
+%the results we achieved. Section 5, goes through a discussion of the challenges we 
+%had to produce reliable results over the massive amount of information available, 
+%and how we overcome these issues.
+For similar approaches regarding last year's track you can refer to \cite{ji2011knowledge}.
 
@@
 
-\begin{table}[b]
+\begin{table}[h]
 \caption{Ontology of Slot Name Categories }
@@
 % KBA Task
-
-% Evaluation Criteria
-
-% Quick Discussion of our approach

### 2013-10-11 paper/kbanotebook2013/content/introduction.tex
moved description to appendix, made some other small wording changtes

@@
 An important challenge in maintaining Wikipedia.org (WP), the most popular 
-web-based, collaborative, multilingual encyclopedia in the internet, is to 
-make sure its contents are up-to-date. Presently, there is considerable time lag 
+web-based, collaborative, multilingual knowledge base on the internet, is  
+making sure its contents are up-to-date. Presently, there is considerable time lag 
 between the publication date of cited news and the date of an edit to WP 
@@
 article that is recommended for citations for each knowledge base page.
-\ceg{add details}
 
@@
 specific information to be cited.
-\ceg{add details}
 
 We built this system as part of a formal task described in Section~\ref{sec:kbatask}.
-The data set from this task drop most our our design systems.
+In this paper, we describe the system we built to process the data.
+Our approach to this task is to build a modular system
+that allows us to explore the nuances of the training data and queries.
 Overall, our contributions are the following:
@@
 
-\section{KBA Task Background}
-\label{sec:kbatask}
-The National Institute of Standards (NIST) hosted the
-Text REtrieval Conference (TREC) --- Knowledge Base Acceleration challenge in 2013. The task
-contains two main sections designed for this track, Cumulative Citation Recommendation 
-and Streaming Slot Filling. Due to the importance of knowledge bases, both of these 
-tracks aim to accelerating populating them, hence the title Knowledge Base Acceleration (KBA).
-Below we describe each of these tracks and their purposes.
-
-\subsection{Cumulative Citation Recommendation (CCR)}
-
-For this track, assessors were instructed to ``use the Wikipedia article to 
-identify (disambiguate) the entity, and then imagine forgetting all info in the WP 
-article and asking whether the text provides any information about the entity'' \cite{JFrank12}.
-Documents are divided according if an entity is mentioned and a relevance level to the entity.
-
-More specifically, a document may have a mention or be without a mention.
-\begin{itemize}[noitemsep]
-  \item \textbf{Mention:} Document explicitly mentions target entity, such as full 
-    name, partial name, nickname, pseudonym, title, stage name.
-  \item \textbf{Zero-mention:} Document does not directly mention target. Could 
-    still be relevant, e.g.\ metonymic references like ``this administration'' 
-    $\rightarrow$ ``Obama''. See also synecdoche. A document could also be relevant to 
-    target entity through relation to entities mentioned in document -- apply this 
-    test question: can I learn something from this document about target entity using 
-    whatever other information I have about entity?
-\end{itemize}
-
-The relevance of a document to a query is split into the four classifications.
-\begin{itemize}[noitemsep]
-  \item \textbf{Garbage:} not relevant, e.g.\ spam.
-  \item \textbf{Neutral:} Not relevant, i.e.\ no info could be deduced about entity, 
-    e.g., entity name used in product name, or only pertains to community of target 
-    such that no information could be learned about entity, although you can see how 
-    an automatic algorithm might have thought it was relevant.
-  \item \textbf{Relevant:} Relates indirectly, e.g., tangential with substantive 
-    implications, or topics or events of likely
-    impact on entity.
-  \item \textbf{Central:} Relates directly to target such that you would cite it in 
-    the WP article for this entity, e.g.\ entity is a
-    central figure in topics/events.
-\end{itemize}
-
-\subsection{Streaming Slot Filling (SSF)}
-The task is that given certain WP or Twitter entities 
-(wiki/twitter URLs) and certain relations of interest (given in
-Table~\ref{table:slotNameOntology}), extract as many triple relations as possible (
-hence, slot filling). This can be used to automatically populate knowledgebases 
-such as free-base or DBPedia or even fill-in the information boxes at Wikipedia. 
-Below, you can view some examples of what it means to fill in a slot value; in 
-each example there is a sentence of interest that we wish to extract slot values 
-from, an entity that the slot value is related to, and a slot name which can be 
-thought of as the topic of the slot value:
-
-\noindent \textbf{Example 1:} ``Matthew DeLorenzo and Josiah Vega, both 14 years old and students 
-at Elysian Charter School, were honored Friday morning by C-SPAN and received 
-\$1,500 as well as an iPod Touch after winning a nationwide video contest.''
-
-Entity:  http://en.wikipedia.org/wiki/Elysian\_Charter\_School
-
-Slot name: Affiliate
-
-Possible slot values: ``Matthew DeLorenzo'', ``Josiah Vega''
-
-Incorrect slot values: ``C-SPAN'', ``iPod Touch''
-
-\noindent \textbf{Example 2:} ``Veteran songwriters and performers Ben Mason, Jeff Severson and 
-Jeff Smith will perform on Saturday, April 14 at 7:30 pm at Creative Cauldron 
-at ArtSpace, 410 S. Maple Avenue.''
-
-Entity: http://en.wikipedia.org/wiki/Jeff\_Severson
-
-Slot name: Affiliate
-
-Possible slot values: ``Ben Mason'', ``Jeff Severson'', ``Jeff Smith''
-
-Incorrect slot values: ``Creative Caldron'', ``Art Space''
-
-\noindent \textbf{Example 3:}  ``Lt. Gov. Drew Wrigley and Robert Wefald, a retired North Dakota 
-district judge and former state attorney general, unveiled the crest Friday 
-during a ceremony at the North Dakota Capitol.''
-
-Entity: http://en.wikipedia.org/wiki/Hjemkomst\_Center
-
-Slot name: Contact\_Meet\_PlaceTime
-
-Slot value: ``Friday during a ceremony at the North Dakota Capitol''
-
-\noindent In \textit{streaming} slot filling, we are only interested in new 
-slot values that were not substantiated earlier in the stream corpus.
-In Table~\ref{table:slotNameOntology} you can view some slot values 
-and their types, the comprehensive description of which can be found at
-\cite{tackbp} and \cite{aec}. The details of the metric for SSF will favor systems 
-that most closely match the changes in the ground truth time line of slot values. 
-This is done by searching for other documents that mentioned an entity and exactly 
-matched the slot fill strings selected by the assessors.
-
-In the rest of the paper, we address the following material. In Section 2, we 
-sketch the main components of the system and their purposes. In Section 3, 
-describe the details of how we designed and implemented certain components 
-critical to the behavior of the system. Section 4 addresses the performance and 
-the results we achieved. Section 5, goes through a discussion of the challenges we 
-had to produce reliable results over the massive amount of information available, 
-and how we overcome these issues. For similar approaches regarding last year's 
-track you can refer to \cite{ji2011knowledge}.
-
-%\ceg{Add a discussion of why machine driven kb population is important.}
-
-\begin{table}[b]
-\caption{Ontology of Slot Name Categories }
-\centering
-\label{table:slotNameOntology}
-
-\begin{tabular}{|c|c|c|}
-\hline 
-\textbf{PER} & \textbf{FAC} & \textbf{ORG} \\ 
-\hline 
-\begin{tabular}{@{}l@{}}Affiliate \\ AssociateOf \\ Contact\_Meet\_PlaceTime \\ AwardsWon \\ 
-DateOfDeath \\ 
-CauseOfDeath\\
-Titles\\
-FounderOf\\
-EmployeeOf\end{tabular}
-  &
-   \begin{tabular}[b]{l}Affiliate \\ Contact\_Meet\_Entity \end{tabular} 
-   & 
-   \begin{tabular}{@{}l@{}}Affiliate \\ TopMembers \\ FoundedBy\end{tabular} \\ 
-\hline 
-\end{tabular} 
-\end{table}
-
-%\ceg{How will each submission be evaluated?}
-
-% Motivation
-
-% KBA Task
-
 % Evaluation Criteria

### 2013-10-11 paper/kbanotebook2013/content/implementation.tex
small changes in the algorithm

@@
 \begin{algorithm}
-  \textbf{Given a set of Streamitems $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
-  \textbf{Set of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
-  \begin{algorithmic}[1]
+  \textbf{List of entities $\mathcal{E} = \{e_0, \ldots, e_{170}\}$}\\
+  \textbf{List of Streamitems $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
+  \textbf{List of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
+  \begin{algorithmic}%[1]
     \FOR{$si \in \mathcal{S}$}
-    \FOR{$s \in si$}
-    \IF{$ check\_one\_of\_the\_patterns$}
-    \STATE Emit(sentence, pattern)
+      \FOR{$sentence \in si$}
+        %%\IF{check\_pattern(sentence, pattern)}
+        \FOR{$pattern \in P$}
+          \IF{Satisfies($sentence$, $pattern$)}
+            \STATE Emit($sentence$, $pattern$)
           \ENDIF
+        \ENDFOR
       \ENDFOR
@@
 For these three kinds of patterns, we implement them in different 
-ways accordingly. Next we will explain the patterns with more details, a brief
+ways accordingly. Next, we will explain the patterns with more details, an
 example can be found in Figure~\ref{fig:pattern}.
@@
 \textbf{Slot value type, tagged by Lingpipe:} For slot FounderOf, we have this
-pattern: \textless \texttt{PER, FounderOf, ``founder'', right, ORG}\textgreater. PER means 
+pattern: $\langle$ \texttt{PER, FounderOf, ``founder'', right, ORG} $\rangle$. PER means 
 that the entity we are finding slot values for is a PER entity; FounderOf 
@@
 
-\textbf{Slot value tagged as noun phrase by OpenNLP:} \textless \texttt{PER, AwardsWon, ``awarded'', 
-right, NP}\textgreater, NP meaning noun phrase. This pattern can be interpreted 
+\textbf{Slot value tagged as noun phrase by OpenNLP:} $\langle$ \texttt{PER, AwardsWon, ``awarded'', 
+right, NP}$\rangle$, NP meaning noun phrase. This pattern can be interpreted 
 as that we are looking for a noun phrase after the ``awarded'' since that noun 
@@
 
-\textbf{Slot value of time phrases, hard coded:} \textless \texttt{PER, DateOfDeath, ``died'', right, 
-``last night''}\textgreater. In this pattern, ``last night'' means we are looking for 
+\textbf{Slot value of time phrases, hard coded:} $\langle$ \texttt{PER, DateOfDeath, ``died'', right, 
+``last night''}$\rangle$. In this pattern, ``last night'' means we are looking for 
 exactly the phrase ``last night'' to the right of ``died''. This pattern is 

### 2013-10-18 paper/kbanotebook2013/content/implementation.tex
Updated yangs section for him to reviews

@@
 we want to get rid of them as soon as possible. Chunk Files Index Generator which 
-is written in C++ will discard non-mentioning chunk files and will stop further 
+is written in C++ discards non-mentioning chunk files and will stop further 
 processing a chunk file as soon as it finds a mention there. Each chunk file can 
@@
 Pattern matching is simple to manipulate results and implement.
-Additionally, we can simply to explain and evaluate results.
+Additionally, a classifier approach is more difficult to evaluate and explain results.
 
@@
 \begin{algorithm}
+  \caption{Streaming Slot Value Extraction Pseudocode}
   \textbf{List of entities $\mathcal{E} = \{e_0, \ldots, e_{170}\}$}\\
@@
           \IF{Satisfies($sentence$, $pattern$)}
-            \STATE Emit($sentence$, $pattern$)
+            \STATE Emit($sentence$, $pattern$) // Deal specifically with the three types
           \ENDIF
@@
 
+\subsubsection{Types of patterns}
 A pattern is defined as a record representing knowledge going to be added to a knowledge base.
-A pattern $\mathcal{P}$ is represented as $\mathcal{P} = \langle p_1, p_2, p_3, p_4, p_5 \rangle$.
+A pattern $\mathcal{P}$ is represented as a five-tuple $\mathcal{P} = \langle p_1, p_2, p_3, p_4, p_5 \rangle$.
 
@@
 For these three kinds of patterns, we implement them in different 
-ways accordingly. Next, we will explain the patterns with more details, an
+ways accordingly. Next, we explain the patterns with more details, an
 example can be found in Figure~\ref{fig:pattern}.
 
-\textbf{Slot value type, tagged by Lingpipe:} For slot FounderOf, we have this
-pattern: $\langle$ \texttt{PER, FounderOf, ``founder'', right, ORG} $\rangle$. PER means 
-that the entity we are finding slot values for is a PER entity; FounderOf 
-means this is a pattern for FounderOf slot. Founder is the anchor word we are 
-trying to match in the sentence text; right means that we are going to the 
+\textbf{Type I.} This pattern type is driven by the slot value type, a pattern
+tagged by Lingpipe. For example, pattern
+$\langle$\texttt{PER, FounderOf, \textit{founder}, right, ORG}$\rangle$. \texttt{PER} means 
+that the entity we are finding slot values for a PER entity; \texttt{FounderOf} 
+means this is a pattern for FounderOf slot. \textit{founder} is the anchor word we are 
+match in a sentence; \texttt{right} means that we are going to the 
 right part of the sentence to match the pattern and find the slot value; ORG 
@@
 
-\textbf{Slot value tagged as noun phrase by OpenNLP:} $\langle$ \texttt{PER, AwardsWon, ``awarded'', 
-right, NP}$\rangle$, NP meaning noun phrase. This pattern can be interpreted 
-as that we are looking for a noun phrase after the ``awarded'' since that noun 
-phrase could possibly represent an award. Since titles and awards are usually 
-not the Lingpipe entities, we use the OpenNLP noun phrase chunker to fetch the 
+\textbf{Type II.} This pattern type is unique because it only looks for a
+slot value tagged as noun phrase (NP) by OpenNLP.\@ For example,
+pattern $\langle$\texttt{PER, AwardsWon, \textit{awarded}, 
+right, NP}$\rangle$. This pattern can be interpreted 
+as that we are looking for a noun phrase after the \textit{awarded} since that noun 
+phrase may represent an award. Titles and awards are usually 
+not the Lingpipe entities, hence the use of the OpenNLP noun phrase chunker to fetch the 
 noun phrases.
 
-\textbf{Slot value of time phrases, hard coded:} $\langle$ \texttt{PER, DateOfDeath, ``died'', right, 
-``last night''}$\rangle$. In this pattern, ``last night'' means we are looking for 
-exactly the phrase ``last night'' to the right of ``died''. This pattern is 
+\textbf{Type III.} Some relations are best discovered by hard coding the slot values.
+Examples of these include time phrases: $\langle$\texttt{PER, DateOfDeath, \textit{died}, right, 
+\textit{last night}}$\rangle$. In this pattern, \textit{last night} means we are looking for 
+exactly the phrase \textit{last night} to the right of \textit{died}. This pattern is 
 inspired by the intuition that in news articles, people often mention that 
 somebody died last night instead of mentioning the accurate date information 
-and Lingpipe tends not to tag phrases like ``last night'' as a DATE entity.
+and Lingpipe tends not to tag phrases like \textit{last night} as a DATE entity.
 
-We have found that there are three major classes of accuracy errors:
-wrong entities found, wrong tags by the Lingpipe, and finally wrong results matched 
-by the patterns. We solve the first problem by using the Wikipedia or twitter 
-information of the entities to get better alias names. And we use
+We sampled documents from the training data period to generate an initial set of
+patterns. We then use these patterns to generate SSF results. By manully looking at these results, we
+prune some patterns with poor­performance and add more patterns that we identified from these results.
+We use several iterations to find the best patterns.
+We found that it is time consuming to identity quality pattern.
+
+We found three major classes of accuracy errors:
+incorrect entities selected, incorrect tags by Lingpipe and incorrect pattern extractions.
+The first issue is ameliorated by generating better aliases (Section~\ref{section:aliasgeneration}). And we use
 post-processing to reduce the second and third types of errors (Section~\ref{section:highAccuracyFilter}).
+We didn't use more advanced NLP packages such as Stanford NLP because of the large size of the data set.
+The post-processing step to improve the results is discussed in the next section.
 
@@
 
-The SSF output of many extractions is noisy. The data contains duplicates and 
+The SSF output of streaming slot value extraction is noisy. The data contains duplicates and 
 incorrect extractions. We can define rules to sanitize the output only using 
@@
 in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
-two classes of rules: deduplication rules and inference rules.
+two classes of rules: \textit{deduplication} and \textit{inference} rules.
 

### 2013-10-18 paper/kbanotebook2013/content/introduction.tex
small changes in the algorithm
Updated yangs section for him to reviews

@@
 
+In this paper, we describe the system we built to process the data.
 We built this system as part of a formal task described in Section~\ref{sec:kbatask}.
-In this paper, we describe the system we built to process the data.
 Our approach to this task is to build a modular system
 that allows us to explore the nuances of the training data and queries.
-Overall, our contributions are the following:
+Overall, we contribute the following:
 \begin{itemize}[noitemsep,nolistsep]
-\item we introduce a method to build models of name variations (Section~\ref{section:aliasgeneration});
-\item we built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
-\item we extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
-\item we filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
-\item we self-evaluate our results over a 4.5 TB data set (Section~\ref{sec:results}).
+\item introduce a method to build models of name variations (Section~\ref{section:aliasgeneration});
+\item built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
+\item extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
+\item filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
+\item self-evaluate our results over a 4.5 TB data set (Section~\ref{sec:results}).
 \end{itemize}

### 2013-10-22 paper/kbanotebook2013/content/implementation.tex
Fix some typos, add minor explanations

@@
 contain up to thousands of SIs which can be so time consuming if we were to 
-process them in our Java base code.Processing StreamItems on the other hand is 
+process them in our Java base code. Processing StreamItems on the other hand is 
 done in Java with ideas in mind for later on extensibility by adding other Java libraries.
@@
 %\includegraphics[width=6in]{./images/Pattern.eps}
-\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
+%\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
+\includegraphics[width=6in]{./images/Pattern-crop.pdf}
+% cropped pdf created using $ pdfcrop Pattern.pdf
 \vspace*{-.1in} \caption{Pattern Matching with Slot Value on the Right Side of Entity. }\label{fig:pattern}
@@
 
-We sampled documents from the training data period to generate an initial set of
-patterns. We then use these patterns to generate SSF results. By manully looking at these results, we
-prune some patterns with poor­performance and add more patterns that we identified from these results.
+We sampled documents from the training data period to generate an initial set of patterns.
+We then use these patterns to generate SSF results.
+By manully looking at these results, we prune some patterns with poor­performance and add more patterns that we identified from these results.
 We use several iterations to find the best patterns.

### 2013-10-22 paper/kbanotebook2013/content/results.tex

@@
 
+We have 135 extraction patterns coverin each slot-name/entity-type combinations.
+Our final submission was named \textit{submission\_infer}.
 Our results are as follows: Document extraction using query entity matching with aliases, sentence
@@
 
-On the performance of the first submission run we performed random 
+On the performance of our initial submission run we performed random 
 sampling via two processes, the results of which are according to
@@
 around 55\%, and about 15\% wrong entity identified and 30\% incorrect value
-extracted across all entities and slot types. For our final submission, we
+extracted across all entities and slot types.
+Most of our issues for this submission were regarding poor slot value extraction patterns and incomplete aliases whih were tried to be mtigated later on.
+For our final submission, we
 provide a more detailed statistics, which has been elaborated in
@@
 matching our patterns, after that \textit{AwardsWon} has been the next with 38
-instances found. Table~\ref{table:finalresultaccuracy} addresses the relative
+instances found.
+Affiliate is a very generic term and extracting real affiliates can be quite challenging using the extraction patterns provided.
+This can lead to noisy results.
+On the other hand for more precise terms our accuracy increases but we have less recall.
+Table~\ref{table:finalresultaccuracy} addresses the relative
 accuracy measure per slot value. There you can view that we have had the
@@
 \begin{table}
-\caption{SSF Performance Measure on Initial Submission }
+\caption{SSF Performance Measure on \textit{initial\_submission} }
 \centering
@@
 \begin{table}    
-\caption{Recall Measure on Submission Infer }
+\caption{ Recall Measure on \textit{submission\_infer}: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath }
 \centering
@@
 \begin{table}
-\caption{SSF Accuracy Measure on Submission Infer }
+\caption{SSF Accuracy Measure on \textit{submission\_infer}: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something }
 \centering

### 2013-10-23 paper/kbanotebook2013/content/discussion.tex
a few changes on Implementation and Discussion

@@
 processing the corpus.
+
+In table 4, there are a lot more values extracted for some slots than other slots. This may be caused by several reasons.
+First, some slots naturally have more results than other slots.
+For example, AssociateOf and Affiliate definitely have more slot values than DateOfDeath and CauseOfDeath, since there are only so few entities that are dead.
+Second, it also depends on the patterns we use.
+For example, for Affiliate, we use "and", "with" as ankor words.
+These words are more common than "dead" or "died" or "founded" in other patterns.
 

### 2013-10-24 paper/kbanotebook2013/content/results.tex
added changes removed some coloquial sentences

@@
 %\ceg{We can add data on the total document size, The %number of each document type.  } 
- Our system was composed of a single node cluster, which we refer to as the
- \textit{server}; the configuration of which is as described in
+ Our system was developed on a 32-core server described in
  Table~\ref{table:serverspec}. The corpus is a snapshot of the web in English.
@@
 
-\begin{table}[b]
+\begin{table}
 \caption{Document Chunks Distribution }
@@
 \begin{table}
-\caption{ Recall Measure on \textit{submission\_infer}: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath }
-\centering
-\label{table:finalresultrecall}
-\begin{tabular}{|c|p{3.5cm}|p{4cm}|}
-\hline 
- \textbf{Slot Name} & \textbf{Total instances of slot value found} & \textbf{\# of entities covered by slot value} \\ 
-\hline 
-Affiliate & 108598 & 80 \\ \hline 
-AssociateOf & 25278 & 106 \\ \hline 
-AwardsWon & 38 & 14 \\ \hline 
-CauseOfDeath & 0 & 0 \\ \hline 
-Contact\_Meet\_Entity & 191 & 8 \\ \hline 
-Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
-DateOfDeath & 87 & 14 \\ \hline 
-EmployeeOf & 75 & 16 \\ \hline 
-FoundedBy & 326 & 30 \\ \hline 
-FounderOf & 302 &  29 \\ \hline 
-Titles & 26823 & 118 \\ \hline 
-TopMembers & 314 & 26 \\ \hline
-
-\end{tabular} 
-\end{table}
-
-\begin{table}
-\caption{SSF Accuracy Measure on \textit{submission\_infer}: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something }
+\caption{SSF Accuracy Measure on \textit{submission\_infer}: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}
 \centering
 \label{table:finalresultaccuracy}
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|l|c|c|c|}
 \hline 

### 2013-10-25 paper/flairs27/content/abstract.tex
added the paper for FLAIRS27. It needs a LOT of work

--- 2013-09-16 paper/kbanotebook2013/content/abstract.tex
@@
 GatorDSR team, University of Florida to efficiently process TREC KBA 2013 --- 
-SSF track. Here we will describe the system evolution as well as the details 
-of our algorithm to extract slot values for the given slot name. Scalability 
-and efficiency in precision and recall are the major   goals of this work, 
+SSF track. Here we will describe the system as well as the details 
+the algorithms used to extract slot values for the given slot name. Scalability, efficiency, precision and recall are the major goals of this work, 
 given the overly limited time limitation and available computational resources.

### 2013-10-25 paper/flairs27/content/discussion.tex
added the paper for FLAIRS27. It needs a LOT of work

\section{Discussion \& Future Works}

%In this section we address some of the challenges that we faced during the course of this project. We started 
%off by trying to use the off-the-shelf tools for this task. We started 
%by using Scala/Spark~\cite{ferc11} to benefit from the parallelization 
%performance there. Unfortunately Spark was not performant and the distributed reliability overhead 
%was much more than tolerable. We moved on to use Scala parallelization  framework itself, and unfortunately it did not satisfy our needs as well; there was 
%excessive memory overhead on map-reduce jobs. We migrated the core of the 
%system to Java Parallelism APIs and that was not good enough either, we still demanded 
%better. So we built our own parallel system which in actual performance had 
%the least of overhead, the least memory consumption and the most robust memory 
%model which avoided unpredictable CPU stalls on garbage collections in 
%processing the corpus.

Table~\ref{table:finalresultrecall} show a varied distribution of 
extracted slot names.
Some slots naturally have more results than other slots. For example,
AssociateOf and Affiliate have more slot values than DateOfDeath and
CauseOfDeath, since there are only so few entities that are deceased.
Also, some patterns are more general causing more extractions.
For example, for Affiliate, we use \textit{and},
\textit{with} as anchor words. These words are more common than \textit{dead} or \textit{died} or \textit{founded} in other patterns.

\begin{table}    
\caption{Recall Measure on \textit{submission\_infer}: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
\centering
\label{table:finalresultrecall}
\begin{tabular}{|l|p{3.5cm}|p{4cm}|}
\hline 
 \textbf{Slot Name} & \textbf{Total instances of slot value found} & \textbf{\# of entities covered by slot value} \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
CauseOfDeath & 0 & 0 \\ \hline 
Contact\_Meet\_Entity & 191 & 8 \\ \hline 
Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline

\end{tabular} 
\end{table}

When we evaluate the results of slot extraction, we find 
three kinds of problems for accuracy: 1) wrong entities found; 2) wrong tags 
by the Lingpipe; 3) wrong results matched by the patterns.  We also have 
recall problems: 1) not enough good alias names to find all the entities. 2) 
not enough and powerful patterns to capture all the slot values.

We will use entity resolution methods and other advanced methods to improve 
the accuracy and recall of entity extraction part.

For slot extraction, to improve the performance, we need: 1) Using multi-class classifiers instead of pattern matching method to 
extract slot values in order to increase both recall and accuracy for slots
``Affiliate'', ``AssociateOf'', ``FounderOf'', ``EmployeeOf'', ``FoundedBy'',
``TopMembers'', ``Contact\_Meet\_Entity'' and so on. 2) For special slots, 
like ``Titles'', ``DateOfDeath'', ``CauseOfDeath'', ``AwardsWon'', using different 
kind of advanced methods, e.g.\ classifiers, matching methods. 3) Using other 
NLP tools or using classifiers to overcome the drawbacks of the LingPipe’s 
inaccurate tags. The first and second tasks are the most important tasks we 
need to do.

About 50\% of twitter entities are not found by the system. One reason
is those entities are not popular. For example, a `Brenda Weiler' Google 
search result has 860,000 documents over the whole web. For our 
small portion of the web it might make sense. The 
histogram of the entities shows that more than half of the 
entities have appeared in less than 10 StreamItems. A good portion have 
appeared only once.

%A theory is that we are falling behind because we are using the cleansed (from HTML tags)
%version of the corpus. We believe there has been a reason that TREC has 
%included the actual HTML document as well as the cleansed version. This 
%definitely will convey some information to us. If it was as easy as reading 
%some clean text they wouldn't bother including so much data for teams to be 
%useless. So we guess is that we are missing some information from not using 
%the actual document. And, we are looking for tokens with entity value set 
%which will depend us dramatically on the accuracy of lingpipe, which is a fast 
%algorithm but is not as good as other NLP tools can be e.g. Stanford NLP.

% Note: Here we discuss why the results are the way they are
% Give pros and cons, talk about how the implemented algorithms
% performed in the actual implementation.
% Answer the `why' question about all the trends in the results section.

### 2013-10-25 paper/flairs27/content/implementation.tex
added the paper for FLAIRS27. It needs a LOT of work

--- 2013-10-22 paper/kbanotebook2013/content/implementation.tex
@@
 
-The procedure to extract slots with the patterns is to 
-first find Streamitems that contain the
-entities by using alias names of the entities. Next, inside these Streamitems, 
-fetch the sentences which contain entities by using alias names and the 
-coreference information provided by Lingpipe tags. Use these sentences to 
-match existing patterns, and when patterns matched, generate SSF results.
+With the Streamitem indexes generated by the CCR, we first fetch the sentences containing entites
+by using alias names and coreference information provided by Lingpipe tags. Then use these senteces 
+to match patterns and when patterns matched, generate SSF results.
 
@@
   \textbf{List of entities $\mathcal{E} = \{e_0, \ldots, e_{170}\}$}\\
-  \textbf{List of Streamitems $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
   \textbf{List of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
+  \textbf{List of streamitems containing entities $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
+
   \begin{algorithmic}%[1]
@@
       \FOR{$sentence \in si$}
+        \FOR{$entity \in \mathcal{E}$}
+	  \IF{Contains($sentence$, $entity$)}
           %%\IF{check\_pattern(sentence, pattern)}
-        \FOR{$pattern \in P$}
+            \FOR{$pattern \in P $ suitable for $entity$} 
               \IF{Satisfies($sentence$, $pattern$)}
-            \STATE Emit($sentence$, $pattern$) // Deal specifically with the three types
+                \STATE Emit($sentence$, $pattern$)
+              \ENDIF
+	    \ENDFOR
           \ENDIF
@@
 
-\subsubsection{Types of patterns}
+\subsubsection{Format of patterns}
 A pattern is defined as a record representing knowledge going to be added to a knowledge base.
@@
 represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER}
-represents a person.
+represents a person. \texttt{FAC}, \texttt{ORG} and \texttt{PER} are Lingpipe entity types.
 The $p_2$ represents a slot name.
@@
 example can be found in Figure~\ref{fig:pattern}.
+
+\subsubsection{Types of patterns}
+There are three types of patterns distinguished by different types of slot values in the patterns. 
+The matching methods using these three types of patterns are implememented according to the different information and structures of slot values.
 
@@
 
+\subsubsection{A short discussion}
 We sampled documents from the training data period to generate an initial set of patterns.

### 2013-10-25 paper/flairs27/content/introduction.tex
added the paper for FLAIRS27. It needs a LOT of work

--- 2013-10-18 paper/kbanotebook2013/content/introduction.tex
@@
 web pages cited by WP articles in the \textit{living\_people} category is over 
-a year and the distribution has a long and heavy tail~\cite{JFrank12}. 
+a year and the distribution has a long and heavy tail \cite{JFrank12}. 
 Also, the majority of WP entities have updates on their associated article much 

### 2013-10-29 paper/flairs27/content/discussion.tex
Updating paper independent of trek kba terminology

@@
 \textit{with} as anchor words. These words are more common than \textit{dead} or \textit{died} or \textit{founded} in other patterns.
-
-\begin{table}    
-\caption{Recall Measure on \textit{submission\_infer}: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
-\centering
-\label{table:finalresultrecall}
-\begin{tabular}{|l|p{3.5cm}|p{4cm}|}
-\hline 
- \textbf{Slot Name} & \textbf{Total instances of slot value found} & \textbf{\# of entities covered by slot value} \\ 
-\hline 
-Affiliate & 108598 & 80 \\ \hline 
-AssociateOf & 25278 & 106 \\ \hline 
-AwardsWon & 38 & 14 \\ \hline 
-CauseOfDeath & 0 & 0 \\ \hline 
-Contact\_Meet\_Entity & 191 & 8 \\ \hline 
-Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
-DateOfDeath & 87 & 14 \\ \hline 
-EmployeeOf & 75 & 16 \\ \hline 
-FoundedBy & 326 & 30 \\ \hline 
-FounderOf & 302 &  29 \\ \hline 
-Titles & 26823 & 118 \\ \hline 
-TopMembers & 314 & 26 \\ \hline
-
-\end{tabular} 
-\end{table}
 

### 2013-10-29 paper/flairs27/content/results.tex
Updating paper independent of trek kba terminology

--- 2013-10-24 paper/kbanotebook2013/content/results.tex
@@
 
-\begin{table}
+\begin{table*}
 \caption{Document Chunks Distribution }
@@
 \end{tabular} 
-\end{table}
+\end{table*}
 
@@
 \label{table:serverspec}
-\begin{tabular}{|c|l|}
+\begin{tabular}{| c | p{5cm} |}
 \hline 
@@
 
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{ | c | c | p{2cm} | p{13mm} |}
 \hline 
@@
 
-\begin{table}
+\begin{table*}    
+\caption{Recall Measure on \textit{submission\_infer}: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
+\centering
+\label{table:finalresultrecall}
+\begin{tabular}{|l|p{3.5cm}|p{4cm}|}
+\hline 
+ \textbf{Slot Name} & \textbf{Total instances of slot value found} & \textbf{\# of entities covered by slot value} \\ 
+\hline 
+Affiliate & 108598 & 80 \\ \hline 
+AssociateOf & 25278 & 106 \\ \hline 
+AwardsWon & 38 & 14 \\ \hline 
+CauseOfDeath & 0 & 0 \\ \hline 
+Contact\_Meet\_Entity & 191 & 8 \\ \hline 
+Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
+DateOfDeath & 87 & 14 \\ \hline 
+EmployeeOf & 75 & 16 \\ \hline 
+FoundedBy & 326 & 30 \\ \hline 
+FounderOf & 302 &  29 \\ \hline 
+Titles & 26823 & 118 \\ \hline 
+TopMembers & 314 & 26 \\ \hline
+
+\end{tabular} 
+\end{table*}
+
+\begin{table*}
 \caption{SSF Accuracy Measure on \textit{submission\_infer}: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}

### 2013-10-29 paper/flairs27/paper.tex
added the paper for FLAIRS27. It needs a LOT of work
Updating paper independent of trek kba terminology

--- 2013-10-10 paper/kbanotebook2013/paper.tex
@@
-\documentclass[10pt]{article}
-
+\documentclass[letterpaper]{article}
+\usepackage{aaai}
+\usepackage{times}
+\usepackage{helvet}
+\usepackage{courier}
 \usepackage{xcolor}
@@
 \usepackage{enumitem}
+\usepackage{amsmath}
+\usepackage{algorithm}
+\usepackage{algorithmic}
+
+    \usepackage{cite}
+    \usepackage{natbib}
 
@@
 
-\title{GatorDSR: University of Florida Knowledge Base Acceleration Notebook}
+\title{Central Slot Value Extraction from Internet for Wikipedia Entities}
 
@@
 
-\author{Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{University of Florida, Gainesville, Florida, USA}\\
-       {\{msnia, cgrant, ypeng, daisyw\}@cise.ufl.edu}
-\and
-  Milenko Petrovic\footnote{Institute for Human and Machine Cognition, Ocala, Florida, USA}\\
+\author{Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{University of Florida, Gainesville, Florida, USA}, Milenko Petrovic\footnote{Institute for Human and Machine Cognition, Ocala, Florida, USA}\\
+       \\
+       {\{msnia, cgrant, ypeng, daisyw\}@cise.ufl.edu,}
        {mpetrovic@ihmc.us}
@@
 
-\bibliographystyle{unsrt}
 \bibliography{citation}
+\bibliographystyle{aaai}
+
+\input{content/appendix.tex}
 

### 2013-10-29 paper/flairs27/content/abstract.tex

@@
 
-In this paper we will present the system design and algorithm adopted by the 
-GatorDSR team, University of Florida to efficiently process TREC KBA 2013 --- 
-SSF track. Here we will describe the system as well as the details 
-the algorithms used to extract slot values for the given slot name. Scalability, efficiency, precision and recall are the major goals of this work, 
-given the overly limited time limitation and available computational resources.
+In this paper we address extracting central knowledge from internet pertinent to entities in wikipedia, which is the most popular web-based, colaborative multilingual encyclopieda on the internet.
+This is comparable to Freebase in a query-driven manner.
+Our contributions are two fold, first we design a system to efficiently find central documents on the internet that contain direct information regarding a given wikipedia entity; second, we design a system to extract specific features of that entity from central documents which is refered to as slot filling.
+Our results demonstrate that the system is very efficient in the web scale nature of the problem: being highly memory and I/O efficient and that we can achieve high accuracy for given slot values.
 

### 2013-11-01 paper/flairs27/content/implementation.tex
Updating paper independent of trek kba terminology
remove extra newlines instead of wrap

@@
 
-We extract aliases for entities from Wikipedia automatically both using API 
-and using the actual page content, then apply pattern matching rules for slot 
-value extraction. Our contribution is that we perform pattern matching that conforms to each slot 
-value along with post-processings to eliminate noisy outputs.
+We extract aliases for entities from Wikipedia automatically both using API and using the actual page content, then apply pattern matching rules for slot value extraction.
+Our contribution is that we perform pattern matching that conforms to each slot value along with post-processings to eliminate noisy outputs.
 
@@
 
-We use Wikipedia API to get some aliases automatically. This is done by 
-retrieving backlink references (redirects of a wiki entity). Unfortunately 
-this is not good enough and to enhance recall we need more aliases. To have 
-better use of a wiki page we parse HTML DOM of the page, then use regular 
-expressions to extract the bold phrases of the first paragraph as alias of the 
-actual entity. Based on our observation this is a very accurate heuristic and 
-provides us with lots of famous aliases of the entities. To consider other 
-typical cases we consider some generic first name last name order swapping 
-conventions such as Bill Gates $\rightarrow$ Gates, Bill.  Meanwhile, William Henry
-Gates is an alias for Bill Gates in WP as a backlink reference. These kinds of
-aliases are also included in matching entities.
+We use Wikipedia API to get some aliases automatically.
+This is done by retrieving backlink references (redirects of a wiki entity).
+Unfortunately this is not good enough and to enhance recall we need more aliases.
+To have better use of a wiki page we parse HTML DOM of the page, then use regular expressions to extract the bold phrases of the first paragraph as alias of the actual entity.
+Based on our observation this is a very accurate heuristic and provides us with lots of famous aliases of the entities.
+To consider other
+typical cases we consider some generic first name last name order swapping conventions such as Bill Gates $\rightarrow$ Gates, Bill.
+Meanwhile, William Henry Gates is an alias for Bill Gates in WP as a backlink reference.
+These kinds of aliases are also included in matching entities.
 
@@
 
-Our pipeline of processing the corpus consists of a two layer indexing system 
-referred to as \textit{Chunk Files Index Generator} and \textit{StreamItems Index Generator}.
-Chunk Files Index Generator will generate indexes of the chunk files 
-that contain a mention of any of the desired entities. StreamItems Index Generator 
-on the other hand will index StreamItems that contain a mention of a given entity 
-respectively. This two level indexing will eliminate the need to process each and 
-every ChunkFile/StreamItem for every entity. The reason for splitting this task 
-into two steps is that not all chunk files contain any mention of the entities and 
-we want to get rid of them as soon as possible. Chunk Files Index Generator which 
-is written in C++ discards non-mentioning chunk files and will stop further 
-processing a chunk file as soon as it finds a mention there. Each chunk file can 
-contain up to thousands of SIs which can be so time consuming if we were to 
-process them in our Java base code. Processing StreamItems on the other hand is 
-done in Java with ideas in mind for later on extensibility by adding other Java libraries.
+Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textit{Chunk Files Index Generator} and \textit{StreamItems Index Generator}.
+Chunk Files Index Generator will generate indexes of the chunk files that contain a mention of any of the desired entities.
+StreamItems Index Generator
+on the other hand will index StreamItems that contain a mention of a given entity respectively.
+This two level indexing will eliminate the need to process each and every ChunkFile/StreamItem for every entity.
+The reason for splitting this task into two steps is that not all chunk files contain any mention of the entities and
+we want to get rid of them as soon as possible.
+Chunk Files Index Generator which is written in C++ discards non-mentioning chunk files and will stop further processing a chunk file as soon as it finds a mention there.
+Each chunk file can contain up to thousands of SIs which can be so time consuming if we were to process them in our Java base code.
+Processing StreamItems on the other hand is done in Java with ideas in mind for later on extensibility by adding other Java libraries.
 
@@
 %\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
-\includegraphics[width=6in]{./images/Pattern-crop.pdf}
+\includegraphics[width = 13cm]{./images/Pattern-crop.pdf}
 % cropped pdf created using $ pdfcrop Pattern.pdf
@@
 In the data set, we are given 4 months of data (October 2011 - February 2012) as training data.
-Instead of building a classifier we use pattern matching methods to find
-corresponding slot values for entities. 
-Pattern matching is simple to manipulate results and implement.
-Additionally, a classifier approach is more difficult to evaluate and explain results.
+Instead of building a classifier we use pattern matching methods to find corresponding slot values for entities.
+Pattern matching is simple to manipulate results and implement. Additionally, a classifier approach is more difficult to evaluate and explain results.
 
-With the Streamitem indexes generated by the CCR, we first fetch the sentences containing entites
-by using alias names and coreference information provided by Lingpipe tags. Then use these senteces 
-to match patterns and when patterns matched, generate SSF results.
+With the Streamitem indexes generated by the CCR, we first fetch the sentences containing entites by using alias names and coreference information provided by Lingpipe tags.
+Then use these senteces to match patterns and when patterns matched, generate SSF results.
 
@@
 
-The first value, $p_1$ represents the type of entity. These entity types are in
-the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC}
-represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER}
-represents a person. \texttt{FAC}, \texttt{ORG} and \texttt{PER} are Lingpipe entity types.
+The first value, $p_1$ represents the type of entity.
+These entity types are in the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC} represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER} represents a person.
+\texttt{FAC}, \texttt{ORG} and \texttt{PER} are Lingpipe entity types.
 The $p_2$ represents a slot name.
 A list of slot names is present in Table~\ref{table:slotNameOntology}.
-The third element $p_3$ is the pattern content. This is a string found in the sentence.
+The third element $p_3$ is the pattern content.
+This is a string found in the sentence.
 The extractor looks for this exact string or pattern in a sentence.
-The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in
-$p_4$ to explore sentence.
-The final element $p_5$ represent the slot value of a pattern. Thois
-%When we match one pattern, we match all the 
+The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in $p_4$ to explore sentence.
+The final element $p_5$ represent the slot value of a pattern.
+This %When we match one pattern, we match all the
 %fields except the third field, which is extracted as the final result.
-The type of slot value may be the entity 
-type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP or a hard-coded phrase. 
+The type of slot value may be the entity type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP or a hard-coded phrase.
 For these three kinds of patterns, we implement them in different
-ways accordingly. Next, we explain the patterns with more details, an
-example can be found in Figure~\ref{fig:pattern}.
+ways accordingly. Next, we explain the patterns with more details, an example can be found in Figure~\ref{fig:pattern}.
 
@@
 
-\textbf{Type I.} This pattern type is driven by the slot value type, a pattern
-tagged by Lingpipe. For example, pattern
-$\langle$\texttt{PER, FounderOf, \textit{founder}, right, ORG}$\rangle$. \texttt{PER} means 
-that the entity we are finding slot values for a PER entity; \texttt{FounderOf} 
-means this is a pattern for FounderOf slot. \textit{founder} is the anchor word we are 
-match in a sentence; \texttt{right} means that we are going to the 
-right part of the sentence to match the pattern and find the slot value; ORG 
-means the slot value should be a ORG entity.
+\textbf{Type I.} This pattern type is driven by the slot value type, a pattern tagged by Lingpipe.
+For example, pattern $\langle$\texttt{PER, FounderOf, \textit{founder}, right, ORG}$\rangle$.
+\texttt{PER} means
+that the entity we are finding slot values for a PER entity; \texttt{FounderOf} means this is a pattern for FounderOf slot.
+\textit{founder} is the anchor word we are match in a sentence; \texttt{right} means that we are going to the right part of the sentence to match the pattern and find the slot value; ORG means the slot value should be a ORG entity.
 
-\textbf{Type II.} This pattern type is unique because it only looks for a
-slot value tagged as noun phrase (NP) by OpenNLP.\@ For example,
-pattern $\langle$\texttt{PER, AwardsWon, \textit{awarded}, 
-right, NP}$\rangle$. This pattern can be interpreted 
-as that we are looking for a noun phrase after the \textit{awarded} since that noun 
-phrase may represent an award. Titles and awards are usually 
-not the Lingpipe entities, hence the use of the OpenNLP noun phrase chunker to fetch the 
-noun phrases.
+\textbf{Type II.} This pattern type is unique because it only looks for a slot value tagged as noun phrase (NP) by OpenNLP.\@ For example, pattern $\langle$\texttt{PER, AwardsWon, \textit{awarded}, right, NP}$\rangle$.
+This pattern can be interpreted as that we are looking for a noun phrase after the \textit{awarded} since that noun phrase may represent an award.
+Titles and awards are usually not the Lingpipe entities, hence the use of the OpenNLP noun phrase chunker to fetch the noun phrases.
 
 \textbf{Type III.} Some relations are best discovered by hard coding the slot values.
-Examples of these include time phrases: $\langle$\texttt{PER, DateOfDeath, \textit{died}, right, 
-\textit{last night}}$\rangle$. In this pattern, \textit{last night} means we are looking for 
-exactly the phrase \textit{last night} to the right of \textit{died}. This pattern is 
-inspired by the intuition that in news articles, people often mention that 
-somebody died last night instead of mentioning the accurate date information 
-and Lingpipe tends not to tag phrases like \textit{last night} as a DATE entity.
+Examples of these include time phrases: $\langle$\texttt{PER, DateOfDeath, \textit{died}, right, \textit{last night}}$\rangle$.
+In this pattern, \textit{last night} means we are looking for exactly the phrase \textit{last night} to the right of \textit{died}.
+This pattern is inspired by the intuition that in news articles, people often mention that somebody died last night instead of mentioning the accurate date information and Lingpipe tends not to tag phrases like \textit{last night} as a DATE entity.
 
@@
 
-We found three major classes of accuracy errors:
-incorrect entities selected, incorrect tags by Lingpipe and incorrect pattern extractions.
-The first issue is ameliorated by generating better aliases (Section~\ref{section:aliasgeneration}). And we use
-post-processing to reduce the second and third types of errors (Section~\ref{section:highAccuracyFilter}).
+We found three major classes of accuracy errors: incorrect entities selected, incorrect tags by Lingpipe and incorrect pattern extractions.
+The first issue is ameliorated by generating better aliases (Section~\ref{section:aliasgeneration}).
+And we use post-processing to reduce the second and third types of errors (Section~\ref{section:highAccuracyFilter}).
 We didn't use more advanced NLP packages such as Stanford NLP because of the large size of the data set.
@@
 
-The SSF output of streaming slot value extraction is noisy. The data contains duplicates and 
-incorrect extractions. We can define rules to sanitize the output only using 
-the information present in the SSF file. The file is processed in time order, 
-in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
-two classes of rules: \textit{deduplication} and \textit{inference} rules.
+The SSF output of streaming slot value extraction is noisy.
+The data contains duplicates and incorrect extractions.
+We can define rules to sanitize the output only using the information present in the SSF file.
+The file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy.
+We define two classes of rules: \textit{deduplication} and \textit{inference} rules.
 
-The output contains many duplicate entries. As we read the list of extracted 
-slots we create rules to define ``duplicate''. Duplicates can be present in a 
-window of rows; we use a window size of 2 meaning we only be adjacent rows. 
-Two rows are duplicates if they have the same exact extraction, or if the 
-rows have the same slot name and a similar slot value or if the extracted 
-sentence for a particular slot types come from the same sentence.
+The output contains many duplicate entries.
+As we read the list of extracted slots we create rules to define ``duplicate''.
+Duplicates can be present in a window of rows; we use a window size of 2 meaning we only be adjacent rows.
+Two rows are duplicates if they have the same exact extraction, or if the rows have the same slot name and a similar slot value or if the extracted sentence for a particular slot types come from the same sentence.
 
  New slots can be deduced from existing slots by defining inference rules.
- For example, two slots for the task are ``FounderOf'' and ``FoundedBy''. A safe 
- assumption is these slot names are biconditional logical connectives with the 
- entities and slot values. Therefore, we can express a rule ``X FounderOf Y'' 
- equals ``Y FoundedBy X'' where X and Y are single unique entities. Additionally,
- we found that the slot names ``Contact\_Meet\_PlaceTime'' could be inferred as
- ``Contact\_Meet\_Entity'' if the Entity was a FAC and the extracted sentence 
- contained an additional ORG/FAC tag.  
-We also remove erronious slots that have extractions that are several pages in 
-length or tool small. Errors of extracting long sentences can typically be 
-attributed to poor sentence parsing of web documents. We have some valid
-``small'' extractions. For example a comma may separate a name and a title
-(e.g. ``John, Professor at MIT''). But such extraction rules can be particularly 
-noisy, so we check to see if the extracted values have good entity values.
+For example, two slots for the task are ``FounderOf'' and ``FoundedBy''.
+A safe assumption is these slot names are biconditional logical connectives with the entities and slot values.
+Therefore, we can express a rule ``X FounderOf Y'' equals ``Y FoundedBy X'' where X and Y are single unique entities.
+Additionally, we found that the slot names ``Contact\_Meet\_PlaceTime'' could be inferred as ``Contact\_Meet\_Entity'' if the Entity was a FAC and the extracted sentence contained an additional ORG/FAC tag.
+We also remove erronious slots that have extractions that are several pages in length or tool small.
+Errors of extracting long sentences can typically be
+attributed to poor sentence parsing of web documents.
+We have some valid ``small'' extractions.
+For example a comma may separate a name and a title (e.g.
+``John, Professor at MIT'').
+But such extraction rules can be particularly noisy, so we check to see if the extracted values have good entity values.
 

### 2013-11-01 paper/flairs27/content/introduction.tex
remove extra newlines instead of wrap

@@
 
-An important challenge in maintaining Wikipedia.org (WP), the most popular 
-web-based, collaborative, multilingual knowledge base on the internet, is  
-making sure its contents are up-to-date. Presently, there is considerable time lag 
-between the publication date of cited news and the date of an edit to WP 
-creating the citation. The median time lag for a sample of about 60K
-web pages cited by WP articles in the \textit{living\_people} category is over 
-a year and the distribution has a long and heavy tail \cite{JFrank12}. 
-Also, the majority of WP entities have updates on their associated article much 
-less frequently than their mention frequency. Such stale entries 
-are the norm in any large knowledge base (KB) because the number of humans 
-maintaining the KB is far fewer than the number of entities. 
+In this paper we develop an efficient query-driven slot value extraction for certain wikipedia entities from a timely stream of documents on internet.
+Entities from three categories of \textit{person}, \textit{organization} and \textit{facility} are considered.
+This can be regarded as an automatic way to expand and automate Wikipedia citation system and a way to automatically populate knowledge bases such as freebase.
+The challenges that we address are the scale, precision and recall of the extent we can extract slot values from internet for entities of interest.
+Examples of these facts are 'Who a person has met during a certain period of time?', 'Who are the employees of this organization?', 'Who has met who in this facility at a certain time?'
+
+ An important challenge in maintaining Wikipedia.org (WP), the most popular web-based, collaborative, multilingual knowledge base on the internet, is making sure its contents are up-to-date.
+Presently, there is considerable time lag between the publication date of cited news and the date of an edit to WP creating the citation.
+The median time lag for a sample of about 60K web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail \cite{JFrank12}.
+Also, the majority of WP entities have updates on their associated article much less frequently than their mention frequency.
+Such stale entries are the norm in any large knowledge base (KB) because the number of humans maintaining the KB is far fewer than the number of entities.
 %Further, the number of mentions is much larger than the number of entities~\cite{JFrank12}.
@@
 We develop a system to read streaming data and filter out articles that are candidates for citations.
-Given these documents, we extract the pairs of information in the 
-article that is recommended for citations for each knowledge base page.
+Given these documents, we extract the pairs of information in the article that is recommended for citations for each entity page in  WP.
+Some of the challenges that we face in this regard includes: having to balance between infamous and obscure enitities, ambiguous entities (entities of exact same name that are differnet in real life), facts that can very broad e.g.
+things that an entity is affiliated with or very specific such as cause of death of a \textit{person} entity.
 
-Our system contains three main components. First, we pre-process the data and
-build models representing the knowledge base entries.
+Our system contains three main components.
+First, we pre-process the data and build models representing the knowledge base entries.
 Next, we use the models to filter a stream of documents so they only contain
 candidate recommendations.
-Lastly, we processes sentences from candidate extractions and return 
-specific information to be cited.
+Lastly, we processes sentences from candidate extractions and return specific information to be cited.
+The system can handle infrequent entities, but adding of new entities requries going thorugh full dataset.
 
@@
 Our approach to this task is to build a modular system
-that allows us to explore the nuances of the training data and queries.
-Overall, we contribute the following:
+that allows us to explore the nuances of the training data and queries. Overall, we contribute the following:
 \begin{itemize}[noitemsep,nolistsep]
-\item introduce a method to build models of name variations (Section~\ref{section:aliasgeneration});
-\item built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
-\item extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
-\item filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
-\item self-evaluate our results over a 4.5 TB data set (Section~\ref{sec:results}).
+\item Introduce a method to build models of name variations (Section \ref{section:aliasgeneration});
+\item Built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
+\item Extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
+\item Filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
+\item Self-evaluate our results over a 4.5 TB data set (Section\ref{sec:results}).
 \end{itemize}

### 2013-11-03 paper/flairs27/content/introduction.tex
New review, check image

@@
 %Further, the number of mentions is much larger than the number of entities~\cite{JFrank12}.
-Reducing latency keeps KBs such as WP relevant and helpful it users.
+Reducing latency keeps KBs such as WP relevant and helpful to it users.
 
@@
 Given these documents, we extract the pairs of information in the article that is recommended for citations for each entity page in  WP.
-Some of the challenges that we face in this regard includes: having to balance between infamous and obscure enitities, ambiguous entities (entities of exact same name that are differnet in real life), facts that can very broad e.g.
-things that an entity is affiliated with or very specific such as cause of death of a \textit{person} entity.
+Some of the challenges that we face in this regard includes: having to balance between infamous and obscure enitities, ambiguous entities (entities of exact same name that are differnet in real life), facts that can very broad (e.g.
+things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).
 

### 2013-11-03 paper/flairs27/content/results.tex
remove extra newlines instead of wrap
New review, check image

@@
-\section{Results}
+\section{Evaluation}
 \label{sec:results}
@@
 %\ceg{We can add data on the total document size, The %number of each document type.  } 
- Our system was developed on a 32-core server described in
- Table~\ref{table:serverspec}. The corpus is a snapshot of the web in English.
- Each document is annotated using lingpipe and is called StreamItem, a bundle of 
-StreamItems are put together and serialized as Apache Thrift objects, then 
-compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
-and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
-The total size of the data after XZ compression and GPG encryption is 4.5TB and
-just over 500M StreamItems \cite{s3}. Data is stored in directories the naming
-of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am)
-until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952
-date-hour combinations. This corpora consists of various media types the
-distribution of which can be found in Table~\ref{table:documentsDist}. To have a
-sense of the scale of objects and compression as an example a 6mb
-gpg.xz files would become 45 mb thrift objects which can contain a couple of 
-thousand StreamItems depending on their size. Some of the documents have null 
-values for their annotation fields. The first portion of the data which 
-ranges from October 2011 to February 2012 is considered as training data.
-The source code of our system is stored as an open source project where
-enthusiasts can also contribute to \cite{github}, also the relevant discussion
-mailing list is accessible here \cite{googlegroups}.
+ Our system was developed on a 32-core server described in Table~\ref{table:serverspec}.
+The corpus is a snapshot of the web in English.
+Each document is annotated using lingpipe and is called StreamItem, a bundle of StreamItems are put together and serialized as Apache Thrift objects, then compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
+The total size of the data after XZ compression and GPG encryption is 4.5TB and just over 500M StreamItems \cite{s3}.
+Data is stored in directories the naming of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am) until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952 date-hour combinations, 4 months of data (October 2011 - February 2012) is for training purposes.
+This corpora consists of various media types the distribution of which can be found in Table~\ref{table:documentsDist}.
+To have a sense of the scale of objects and compression as an example a 6mb gpg.xz files would become 45 mb thrift objects which can contain a couple of thousand StreamItems depending on their size.
+Some of the documents have null values for their annotation fields.
+The first portion of the data which ranges from October 2011 to February 2012 is considered as training data.
+The source code of our system is stored as an open source project where enthusiasts can also contribute to \cite{github}, also the relevant discussion mailing list is accessible here \cite{googlegroups}.
 
@@
 Our final submission was named \textit{submission\_infer}.
-Our results are as follows: Document extraction using query entity matching with aliases, sentence
-extraction using alias matching and co-reference. Slot extraction using 
-patterns, NER tags and NP tags. 158,052 documents with query entities, 17885 
-unique extracted slot values for 8 slots and 139 entities, 4 slots and 31 
-entities missing.
+Our results are as follows: Document extraction using query entity matching with aliases, sentence extraction using alias matching and co-reference.
+Slot extraction using patterns, NER tags and NP tags.
+158,052 documents with query entities, 17885 unique extracted slot values for 8 slots and 139 entities, 4 slots and 31 entities missing.
 
-On the performance of our initial submission run we performed random 
-sampling via two processes, the results of which are according to
-Table~\ref{table:initialresult}. You can view that we have had an accuracy of
-around 55\%, and about 15\% wrong entity identified and 30\% incorrect value
-extracted across all entities and slot types.
+On the performance of our initial submission run we performed random sampling via two processes, the results of which are according to Table~\ref{table:initialresult}.
+You can view that we have had an accuracy of around 55\%, and about 15\% wrong entity identified and 30\% incorrect value extracted across all entities and slot types.
 Most of our issues for this submission were regarding poor slot value extraction patterns and incomplete aliases whih were tried to be mtigated later on.
-For our final submission, we
-provide a more detailed statistics, which has been elaborated in
-Table~\ref{table:finalresultrecall} and Table~\ref{table:finalresultaccuracy}.
+For our final submission, we provide a more detailed statistics, which has been elaborated in Table~\ref{table:finalresultrecall} and Table~\ref{table:finalresultaccuracy}.
 Table~\ref{table:finalresultrecall} shows the extent of search outreach for
-each slot name. You can see that \textit{Affiliate} has been the slot name with
-highest hits and \textit{CauseOfDeath} our lowest hit with 0 instances found
-matching our patterns, after that \textit{AwardsWon} has been the next with 38
-instances found.
+each slot name.
+You can see that \textit{Affiliate} has been the slot name with highest hits and \textit{CauseOfDeath} our lowest hit with 0 instances found matching our patterns, after that \textit{AwardsWon} has been the next with 38 instances found.
 Affiliate is a very generic term and extracting real affiliates can be quite challenging using the extraction patterns provided.
@@
 On the other hand for more precise terms our accuracy increases but we have less recall.
-Table~\ref{table:finalresultaccuracy} addresses the relative
-accuracy measure per slot value. There you can view that we have had the
-highest accuracy of 63.6\% for \textit{AssociateOf} and the lowest of
-1\% - 5\%  for \textit{Affiliate}, \textit{Contact\_Meet\_PlaceTime} and \textit{EmployeeOf}.
+Table~\ref{table:finalresultaccuracy} addresses the relative accuracy measure per slot value.
+There you can view that we have had the highest accuracy of 63.6\% for \textit{AssociateOf} and the lowest of 1\% - 5\%  for \textit{Affiliate}, \textit{Contact\_Meet\_PlaceTime} and \textit{EmployeeOf}.
 

### 2013-11-03 paper/flairs27/content/system.tex
Updating paper independent of trek kba terminology
remove extra newlines instead of wrap
New review, check image

--- 2013-10-10 paper/kbanotebook2013/content/system.tex
@@
 
-In this section, we introduce the main components of the system. Our system is 
-built with a pipeline architecture in mind giving it the advantage to run 
-each section separately to allow stream processing without blocking the data flow of components 
-(Figure~\ref{fig:system}).
-The three logical components include sections for performing preprocessing to prepare the required data, 
-Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming 
-Slot Filling to generate the actual slot values and PostProcessing to 
-increase precision/recall. 
-TREC provides a streaming data set and  entities from Twitter or WP to query.
+In this section, we introduce the main components of the system.
+Our system is built with a pipeline architecture in mind giving it the advantage to run each section separately to allow stream processing without blocking the data flow of components (Figure~\ref{fig:system}).
+The three logical components include sections for performing preprocessing to prepare the required data, Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming Slot Filling to generate the actual slot values and PostProcessing to increase precision/recall.
+We work on a streaming data set and entities are from Twitter or WP to query.
+
+To walk you through the steps we take, assume we only care about on single WP entity, the first step is to extract aliases of the entity.
+We use several approaches to get as many viable aliases as possible.
+Then we look into the stream of content that is being generated on the internet, apply two levels of filtering to finally end up with the documents are central to that entity.
+To extract the relevnat slot values we perform pattern matching in each sentence or coreferent sentence to see if we can find a match.
+As a match is found from the content of the sentence to the patterns that we have generated regarding slot name, the associated slot value is extracted as a final result.
+
+As mentioned before the time lag from an event occurance until it is cited in WP is in average over a year due to the fact that human maintainers are much less than the number of entities in WP and that the frequency of news update on entities escalates this difference.
+Hence having an automatic way to extract this knowldge for entities can be a very valuable asset.
 
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
-%\includegraphics[width=6in]{./images/sdl.eps}
-  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
+%  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
+  \includegraphics[width=6in]{./images/System_Diagram_with_model_Vertical.pdf}
 % http://convert.neevia.com/pdfconvert/
@@
   \vspace*{-.2in}
-\end{figure}
+\end{figure*}
 
-\textbf{Preprocessing.}
-\label{sec:preproc}
-The contest prohibits Wikipedia entities to have any manual aliases being added and only
-allows automatic ways. We use Wikipedia API backlink references
-(redirects to a wiki entity) as aliases of the entity. We also extract 
-aliases from within the text of a wiki entity, which will be described in
-Section~\ref{section:aliasgeneration}. This whole process is referred to as
-\textit{Alias Extraction}. 
+\textit{Preprocessing.}
+The contest prohibits Wikipedia entities to have any manual aliases being added and only allows automatic ways.
+We use Wikipedia API backlink references (redirects to a wiki entity) as aliases of the entity.
+We also extract aliases from within the text of a wiki entity, which will be described in Section~\ref{section:aliasgeneration}.
+This whole process is referred to as \textit{Alias Extraction}.
 The manual extraction rule is lifted and participants are allowed to manually add aliases for Twitter entities.
 This is allowed because the Twitter website does not provide an example page from the beginning of the document stream.
-This process of extracting
-aliases for Twitter entities is referred to as \textit{Manual Alias Extraction}.
+This process of extracting aliases for Twitter entities is referred to as \textit{Manual Alias Extraction}.
 
-Once aliases are available we pass them through rules of generating proper name 
-orders which will produce various forms of writing a name. As a basic example Bill 
-Gates can be written as Gates, Bill. This will allow the system to capture various 
-notation forms of aliases. We refer to this part as \textit{Name Order Generator}.
+Once aliases are available we pass them through rules of generating proper name orders which will produce various forms of writing a name.
+As a basic example Bill Gates can be written as Gates, Bill.
+This will allow the system to capture various notation forms of aliases.
+We refer to this part as \textit{Name Order Generator}.
 
-\textbf{Cumulative Citation Recommendation.}
-\label{sec:ccr1}
-The main goal of CCR is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page. We perform exact string matching 
-and treat all the documents that mention an entity equally likely to be citable. One of the reasons for this is 
-that in former TREC KBA reports \cite{JFrank12} there were observations of how 
-non-mentioning documents have a low chance of being citable in Wikipedia.
+\textit{Cumulative Citation Recommendation.}
+The main goal of CCR is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page.
+We perform exact string matching and treat all the documents that mention an entity equally likely to be citable.
+One of the reasons for this is that in former TREC KBA reports \cite{JFrank12} there were observations of how non-mentioning documents have a low chance of being citable in Wikipedia.
 So we take on that and ignore non-citing documents.
@@
 
-\textbf{Streaming Slot Filling.}
-\label{sec:ssf1}
+\textit{Streaming Slot Filling.}
 %\ceg{See the previous note.}
-The purpose of SSF is to extract proper values for relations of
-interest, which can be found in Table~\ref{table:slotNameOntology}.
+The purpose of SSF is to extract proper values for relations of interest, which can be found in Table~\ref{table:slotNameOntology}.
 This is called Stream Slot Filling because data is being generated as time goes
@@
 In Figure~\ref{fig:system} we refer to this as \textit{Streaming Slot Value Extraction}.
-Stream slot filling is done by pattern matching documents with manually 
-produced patterns for slots of interest. The way we do this is by observing a 
-sentence that has a mention of the entity or one of its coreferences. An 
-anchor word in the sentence related to the slot name is located and we match 
-either left or right of the anchor word for potential slot values.
+Stream slot filling is done by pattern matching documents with manually produced patterns for slots of interest.
+The way we do this is by observing a sentence that has a mention of the entity or one of its coreferences.
+An anchor word in the sentence related to the slot name is located and we match either left or right of the anchor word for potential slot values.
 
-\textbf{Post Processing Algorithm.}
-\label{sec:postproc}
-The SSF output of many extractions is noisy. The data contains duplicates and 
-incorrect extractions. We can define rules to sanitize the output only using 
-the information present in the SSF file. The file is processed in time order, 
-in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
-two classes of rules deduplication rules and inference rules. In our diagram we refer to this component as \textbf{High Accuracy Filter}.
+\textit{Post Processing Algorithm.}
+The SSF output of many extractions is noisy.
+The data contains duplicates and incorrect extractions.
+We can define rules to sanitize the output only using the information present in the SSF file.
+The file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy.
+We define two classes of rules deduplication rules and inference rules.
+In our diagram we refer to this component as \textbf{High Accuracy Filter}.

### 2013-11-03 paper/flairs27/content/abstract.tex

--- 2013-10-25 paper/flairs27/content/abstract.tex
@@
 
-In this paper we will present the system design and algorithm adopted by the 
-GatorDSR team, University of Florida to efficiently process TREC KBA 2013 --- 
-SSF track. Here we will describe the system as well as the details 
-the algorithms used to extract slot values for the given slot name. Scalability, efficiency, precision and recall are the major goals of this work, 
-given the overly limited time limitation and available computational resources.
+In this paper we address extracting central slot values from internet pertinent to entities in wikipedia, which is the most popular web-based, colaborative multilingual encyclopieda on the internet.
+This is comparable to Freebase in a query-driven manner.
+Our contributions are two fold, first we design a system to efficiently find central documents on the internet that contain directly citable information regarding a given wikipedia entity; second, we design a system to extract specific features of that entity from central documents which is refered to as slot filling.
+Our results demonstrate that the system is very efficient in the web scale nature of the problem: being highly memory and I/O efficient and that we can achieve high accuracy and recall for given slot values.
 

### 2013-11-03 paper/flairs27/content/appendix.tex
Updating paper independent of trek kba terminology

--- 2013-10-11 paper/kbanotebook2013/content/appendix.tex
@@
 \label{sec:kbatask}
-The National Institute of Standards (NIST) hosted the
-Text REtrieval Conference (TREC) --- Knowledge Base Acceleration challenge in 2013. The task
-contains two main sections designed for this track, Cumulative Citation Recommendation 
-and Streaming Slot Filling. Due to the importance of knowledge bases, both of these 
-tracks aim to accelerating populating them, hence the title Knowledge Base Acceleration (KBA).
-Below we describe each of these tracks and their purposes.
+The National Institute of Standards (NIST) hosted the Text REtrieval Conference (TREC) --- Knowledge Base Acceleration challenge in 2013.
+The task contains two main sections designed for this track, Cumulative Citation Recommendation and Streaming Slot Filling.
+Due to the importance of knowledge bases, both of these
+tracks aim to accelerating populating them, hence the title Knowledge Base Acceleration (KBA). Below we describe each of these tracks and their purposes.
 
@@
 
-For this track, assessors were instructed to ``use the Wikipedia article to 
-identify (disambiguate) the entity, and then imagine forgetting all info in the WP 
-article and asking whether the text provides any information about the entity'' \cite{JFrank12}.
+For this track, assessors were instructed to ``use the Wikipedia article to identify (disambiguate) the entity, and then imagine forgetting all info in the WP article and asking whether the text provides any information about the entity'' \cite{JFrank12}.
 Documents are divided according if an entity is mentioned and a relevance level to the entity.
@@
 \subsection{Streaming Slot Filling (SSF)}
-The task is that given certain WP or Twitter entities 
-(wiki/twitter URLs) and certain relations of interest (given in
-Table~\ref{table:slotNameOntology}), extract as many triple relations as possible (
-hence, slot filling). This can be used to automatically populate knowledgebases 
-such as free-base or DBPedia or even fill-in the information boxes at Wikipedia. 
-Below, you can view some examples of what it means to fill in a slot value; in 
-each example there is a sentence of interest that we wish to extract slot values 
-from, an entity that the slot value is related to, and a slot name which can be 
-thought of as the topic of the slot value:
+The task is that given certain WP or Twitter entities (wiki/twitter URLs) and certain relations of interest (given in Table~\ref{table:slotNameOntology}), extract as many triple relations as possible (hence, slot filling).
+This can be used to automatically populate knowledgebases such as free-base or DBPedia or even fill-in the information boxes at Wikipedia.
+Below, you can view some examples of what it means to fill in a slot value; in each example there is a sentence of interest that we wish to extract slot values from, an entity that the slot value is related to, and a slot name which can be thought of as the topic of the slot value:
 
-\noindent \textbf{Example 1:} ``Matthew DeLorenzo and Josiah Vega, both 14 years old and students 
-at Elysian Charter School, were honored Friday morning by C-SPAN and received 
-\$1,500 as well as an iPod Touch after winning a nationwide video contest.''
+\noindent \textbf{Example 1:} ``Matthew DeLorenzo and Josiah Vega, both 14 years old and students at Elysian Charter School, were honored Friday morning by C-SPAN and received \$1,500 as well as an iPod Touch after winning a nationwide video contest.''
 
@@
 
-\noindent \textbf{Example 2:} ``Veteran songwriters and performers Ben Mason, Jeff Severson and 
-Jeff Smith will perform on Saturday, April 14 at 7:30 pm at Creative Cauldron 
-at ArtSpace, 410 S. Maple Avenue.''
+\noindent \textbf{Example 2:} ``Veteran songwriters and performers Ben Mason, Jeff Severson and Jeff Smith will perform on Saturday, April 14 at 7:30 pm at Creative Cauldron at ArtSpace, 410 S.
+Maple Avenue.''
 
@@
 
-\noindent \textbf{Example 3:}  ``Lt. Gov. Drew Wrigley and Robert Wefald, a retired North Dakota 
-district judge and former state attorney general, unveiled the crest Friday 
-during a ceremony at the North Dakota Capitol.''
+\noindent \textbf{Example 3:}  ``Lt.
+Gov.
+Drew Wrigley and Robert Wefald, a retired North Dakota district judge and former state attorney general, unveiled the crest Friday during a ceremony at the North Dakota Capitol.''
 
@@
 
-\noindent In \textit{streaming} slot filling, we are only interested in new 
-slot values that were not substantiated earlier in the stream corpus.
-In Table~\ref{table:slotNameOntology} you can view some slot values 
-and their types, the comprehensive description of which can be found at
-\cite{tackbp} and \cite{aec}. The details of the metric for SSF will favor systems 
-that most closely match the changes in the ground truth time line of slot values. 
+\noindent In \textit{streaming} slot filling, we are only interested in new slot values that were not substantiated earlier in the stream corpus.
+In Table~\ref{table:slotNameOntology} you can view some slot values and their types, the comprehensive description of which can be found at \cite{tackbp} and \cite{aec}.
+The details of the metric for SSF will favor systems that most closely match the changes in the ground truth time line of slot values.
 This is done by searching for other documents that mentioned an entity and exactly
@@
 
-\begin{table}[h]
+\begin{table}[T]
 \caption{Ontology of Slot Name Categories }

### 2013-11-03 paper/flairs27/content/discussion.tex
remove extra newlines instead of wrap

@@
-\section{Discussion \& Future Works}
+\section{Discussions \& Conclusion}
 
@@
 
-Table~\ref{table:finalresultrecall} show a varied distribution of 
-extracted slot names.
-Some slots naturally have more results than other slots. For example,
-AssociateOf and Affiliate have more slot values than DateOfDeath and
-CauseOfDeath, since there are only so few entities that are deceased.
+Table~\ref{table:finalresultrecall} show a varied distribution of extracted slot names.
+Some slots naturally have more results than other slots.
+For example, AssociateOf and Affiliate have more slot values than DateOfDeath and CauseOfDeath, since there are only so few entities that are deceased.
 Also, some patterns are more general causing more extractions.
-For example, for Affiliate, we use \textit{and},
-\textit{with} as anchor words. These words are more common than \textit{dead} or \textit{died} or \textit{founded} in other patterns.
+For example, for Affiliate, we use \textit{and}, \textit{with} as anchor words.
+These words are more common than \textit{dead} or \textit{died} or \textit{founded} in other patterns.
 
-When we evaluate the results of slot extraction, we find 
-three kinds of problems for accuracy: 1) wrong entities found; 2) wrong tags 
-by the Lingpipe; 3) wrong results matched by the patterns.  We also have 
-recall problems: 1) not enough good alias names to find all the entities. 2) 
-not enough and powerful patterns to capture all the slot values.
-
+When we evaluate the results of slot extraction, we find three kinds of problems for accuracy: 1) wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched by the patterns.
+We also have
+recall problems: 1) not enough good alias names to find all the entities.
+2) not enough and powerful patterns to capture all the slot values.
 We will use entity resolution methods and other advanced methods to improve
@@
 
-For slot extraction, to improve the performance, we need: 1) Using multi-class classifiers instead of pattern matching method to 
-extract slot values in order to increase both recall and accuracy for slots
-``Affiliate'', ``AssociateOf'', ``FounderOf'', ``EmployeeOf'', ``FoundedBy'',
-``TopMembers'', ``Contact\_Meet\_Entity'' and so on. 2) For special slots, 
-like ``Titles'', ``DateOfDeath'', ``CauseOfDeath'', ``AwardsWon'', using different 
-kind of advanced methods, e.g.\ classifiers, matching methods. 3) Using other 
-NLP tools or using classifiers to overcome the drawbacks of the LingPipe’s 
-inaccurate tags. The first and second tasks are the most important tasks we 
-need to do.
+For slot extraction, to improve the performance, we need: 1) Using multi-class classifiers instead of pattern matching method to extract slot values in order to increase both recall and accuracy for slots ``Affiliate'', ``AssociateOf'', ``FounderOf'', ``EmployeeOf'', ``FoundedBy'', ``TopMembers'', ``Contact\_Meet\_Entity'' and so on.
+2) For special slots, like ``Titles'', ``DateOfDeath'', ``CauseOfDeath'', ``AwardsWon'', using different kind of advanced methods, e.g.\ classifiers, matching methods.
+3) Using other NLP tools or using classifiers to overcome the drawbacks of the LingPipe’s inaccurate tags.
+The first and second tasks are the most important tasks we need to do.
 
-About 50\% of twitter entities are not found by the system. One reason
-is those entities are not popular. For example, a `Brenda Weiler' Google 
-search result has 860,000 documents over the whole web. For our 
-small portion of the web it might make sense. The 
-histogram of the entities shows that more than half of the 
-entities have appeared in less than 10 StreamItems. A good portion have 
-appeared only once.
+About 50\% of twitter entities are not found by the system.
+One reason is those entities are not popular.
+For example, a `Brenda Weiler' Google search result has 860,000 documents over the whole web.
+For our small portion of the web it might make sense.
+The histogram of the entities shows that more than half of the entities have appeared in less than 10 StreamItems.
+A good portion have appeared only once.
 
@@
 % Answer the `why' question about all the trends in the results section.
+
+Alltogether, We experimented through different tools and approaches to best process the massive amounts of data on the platform that we had available to us.
+We generate aliases for wikipedia entities using Wiki API and extract some aliases from wikipedia pages text itself.
+On twitter entities we extract aliases manually as it is part of the rule of the KBA track.
+We process documents that mention entities for slot value extraction.
+Slot values are determined using pattern matching over coreferences of entities in sentences.
+Finally post processing will filter, cleanup and infers some new slot values to enhance recall and accuracy.
+
+We noticed that some tools that claim to be performant for using the hardware capabilities at hand sometimes don't really work as claimed and you should not always rely on one without a thorough A/B testing of performance which we ended up in generating our in-house system for processing the corpus and generating the index.
+Furthermore, on extracting slot values, pattern matching might not be the best options but definitely can produce some good results at hand.
+We have plans on generating classifiers for slot value extraction
+purposes.
+Entity resolution on the other hand was a topic we spent sometime on but could not get to stable grounds for it.
+Entity resolution will distinguish between entities of the same name but different contexts.
+Further improvements on this component of the system are required.

### 2013-11-03 paper/flairs27/content/implementation.tex

@@
 
-We use Wikipedia API to get some aliases automatically.
+We consider some generic first name last name order swapping conventions such as Bill Gates $\rightarrow$ Gates, Bill.
+Meanwhile, William Henry Gates is an alias for Bill Gates in WP as a backlink reference.
+These kinds of aliases are also included in matching entities.
+We use Wikipedia API to get these aliases automatically.
 This is done by retrieving backlink references (redirects of a wiki entity).
@@
 Based on our observation this is a very accurate heuristic and provides us with lots of famous aliases of the entities.
-To consider other
-typical cases we consider some generic first name last name order swapping conventions such as Bill Gates $\rightarrow$ Gates, Bill.
-Meanwhile, William Henry Gates is an alias for Bill Gates in WP as a backlink reference.
-These kinds of aliases are also included in matching entities.
+As an example of when this might not wirk, is that there might be occasions that some other topic is written in bold typesetting in the first paraph apart from the entity aliases itself but these are very rare
 
@@
 we want to get rid of them as soon as possible.
-Chunk Files Index Generator which is written in C++ discards non-mentioning chunk files and will stop further processing a chunk file as soon as it finds a mention there.
+Chunk Files Index Generator which discards non-mentioning chunk files and will stop further processing a chunk file as soon as it finds a mention there.
 Each chunk file can contain up to thousands of SIs which can be so time consuming if we were to process them in our Java base code.
@@
 
-In the data set, we are given 4 months of data (October 2011 - February 2012) as training data.
-Instead of building a classifier we use pattern matching methods to find corresponding slot values for entities.
+In the data set, we are given a date range of documents as training data. Instead of building a classifier we use pattern matching methods to find corresponding slot values for entities. 
 Pattern matching is simple to manipulate results and implement. Additionally, a classifier approach is more difficult to evaluate and explain results.
 
-With the Streamitem indexes generated by the CCR, we first fetch the sentences containing entites by using alias names and coreference information provided by Lingpipe tags.
+With the StreamItem indexes generated by the CCR, we first fetch the sentences containing entites by using alias names and coreference information provided by Lingpipe tags.
 Then use these senteces to match patterns and when patterns matched, generate SSF results.

### 2013-11-03 paper/flairs27/content/introduction.tex

@@
 \begin{itemize}[noitemsep,nolistsep]
-\item Introduce a method to build models of name variations (Section \ref{section:aliasgeneration});
-\item Built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
-\item Extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
-\item Filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
-\item Self-evaluate our results over a 4.5 TB data set (Section\ref{sec:results}).
+\item Introduce a method to build models of name variations %(Section \ref{section:aliasgeneration});
+\item Built a system to filter a large amount of diverse documents %(Section~\ref{sec:ccrimpl});
+\item Extract entity-slot-value triples of information to be added to KB %(Section~\ref{sec:ssve});
+\item Filter the final results using deduplication and inference %(Section~\ref{section:highAccuracyFilter});
+\item Self-evaluate our results over a 4.5 TB data set %(Section\ref{sec:results}).
 \end{itemize}

### 2013-11-04 paper/flairs27/content/implementation.tex
first half milenko's comments

@@
 \label{section:aliasgeneration}
-
-We consider some generic first name last name order swapping conventions such as Bill Gates $\rightarrow$ Gates, Bill.
-Meanwhile, William Henry Gates is an alias for Bill Gates in WP as a backlink reference.
-These kinds of aliases are also included in matching entities.
-We use Wikipedia API to get these aliases automatically.
-This is done by retrieving backlink references (redirects of a wiki entity).
-Unfortunately this is not good enough and to enhance recall we need more aliases.
-To have better use of a wiki page we parse HTML DOM of the page, then use regular expressions to extract the bold phrases of the first paragraph as alias of the actual entity.
-Based on our observation this is a very accurate heuristic and provides us with lots of famous aliases of the entities.
-As an example of when this might not wirk, is that there might be occasions that some other topic is written in bold typesetting in the first paraph apart from the entity aliases itself but these are very rare
 

### 2013-11-04 paper/flairs27/content/introduction.tex
first half milenko's comments

--- 2013-11-03 paper/flairs27/content/introduction.tex
@@
 
-In this paper we develop an efficient query-driven slot value extraction for certain wikipedia entities from a timely stream of documents on internet.
+In this paper we develop an efficient query-driven slot value extraction for given Wikipedia.org (WP) entities from a timely stream of documents on internet as they are being created.
+Slot value extraction is formally defined as follows: match each sentence to the generic sentence structure of [\textit{Subject} - \textit{Verb} - \textit{Adverbial/Complement}]\cite{sentencePatterns08}, where  \textit{Subject} represents the entity and \textit{Verb} is the relation type we are interested in (e.g.
+Table~\ref{table:slotNameOntology}).
+If a sentence matches these two components of the sentence pattern, \textit{Adverbial/Complement} would be returned as the other side of the relation (which we refer to as slot value).
+Slot value extraction is a challenging task in current state of the art Knowldge Bases (KB).
+Popular graphical KB such as Freebase or DBPedia keep data in structured format where entities are connected via relationships (\textit{Verb}) and the associated attributes (\textit{Adverbial/Compelement}).
+Our system can be used to automatically populate such KBs or even fill-in the information boxes at entity WP page itself.
+
 Entities from three categories of \textit{person}, \textit{organization} and \textit{facility} are considered.
-This can be regarded as an automatic way to expand and automate Wikipedia citation system and a way to automatically populate knowledge bases such as freebase.
-The challenges that we address are the scale, precision and recall of the extent we can extract slot values from internet for entities of interest.
-Examples of these facts are 'Who a person has met during a certain period of time?', 'Who are the employees of this organization?', 'Who has met who in this facility at a certain time?'
+The challenges that we address are: first finding documents that contain useful information about the entity (avoid spams, documents that do not have direct information about the entity even though they mention them, etc), the scale where \textit{stream processing} nature of the system makes it suitable to avoid batch processing natures of Hadoop and operate in the realm of streams such as twitter storm\footnote{http://storm-project.net/} which similarly processes unblounded streams of twitter data or Spark Streaming \footnote{http://spark.incubator.apache.org/}.
+As other Natural Language Processing tasks, precision and recall of the extent we can extract slot values are very important metrics that we will discuss later on.
+Having to balance between infamous and obscure enitities, dealing with slots that can be very broad (e.g.
+things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).
 
- An important challenge in maintaining Wikipedia.org (WP), the most popular web-based, collaborative, multilingual knowledge base on the internet, is making sure its contents are up-to-date.
+To take on an example assume we are analyzing a sentence from the internet such as "\underline{Boris Berezovsky} made his fortune in Russia in the 1990s when the country went through privatisation of state property and 'robber capitalism', and passed away March 2013.".
+First we have to pay attemtion that there are two \textit{Boris Berezovsky} entities in WP, one a businessman and the other a pianist.
+Any slot value extraction shall take this into account and try to come up with a viable distinguishing policy (Entity Resolution).
+Then, we match the sentence to find a slot value such as \textit{DateOfDeath} valued at March 2013.
+Other examples that this system can answer could be 'Who a person has met during a certain period of time?', 'Who are the employees of this organization?', 'Who has met who in this facility at a certain time?'.
+
+ An important challenge in maintaining WP, the most popular web-based, collaborative, multilingual KB on the internet, is making sure its contents are up-to-date.
 Presently, there is considerable time lag between the publication date of cited news and the date of an edit to WP creating the citation.
@@
 Also, the majority of WP entities have updates on their associated article much less frequently than their mention frequency.
-Such stale entries are the norm in any large knowledge base (KB) because the number of humans maintaining the KB is far fewer than the number of entities.
+Such stale entries are the norm in any large KB because the number of humans maintaining the KB is far fewer than the number of entities.
 %Further, the number of mentions is much larger than the number of entities~\cite{JFrank12}.
-Reducing latency keeps KBs such as WP relevant and helpful to it users.
-
+Reducing latency keeps KBs and WP relevant and helpful to its users.
 Given an entity page, possible citations may come from a variety of sources.
@@
 We develop a system to read streaming data and filter out articles that are candidates for citations.
-Given these documents, we extract the pairs of information in the article that is recommended for citations for each entity page in  WP.
-Some of the challenges that we face in this regard includes: having to balance between infamous and obscure enitities, ambiguous entities (entities of exact same name that are differnet in real life), facts that can very broad (e.g.
-things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).
 
 Our system contains three main components.
-First, we pre-process the data and build models representing the knowledge base entries.
-Next, we use the models to filter a stream of documents so they only contain
-candidate recommendations.
-Lastly, we processes sentences from candidate extractions and return specific information to be cited.
-The system can handle infrequent entities, but adding of new entities requries going thorugh full dataset.
-
-In this paper, we describe the system we built to process the data.
-We built this system as part of a formal task described in Section~\ref{sec:kbatask}.
-Our approach to this task is to build a modular system
-that allows us to explore the nuances of the training data and queries. Overall, we contribute the following:
+First, we pre-process the data and build models representing the KB entries.
+Next, we use the models to filter a stream of documents so they only contain candidate citations.
+Lastly, we processes sentences from candidate extractions and return slot values.
+% EITHER SAY WHAT IT MEANS OR GIVE EXAMPLES OR COMMENT IT
+%We build a modular system that allows us to explore the nuances of the training data and queries. 
+Overall, we contribute the following:
 \begin{itemize}[noitemsep,nolistsep]
-\item Introduce a method to build models of name variations (Section \ref{section:aliasgeneration});
-\item Built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
-\item Extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
-\item Filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
-\item Self-evaluate our results over a 4.5 TB data set (Section\ref{sec:results}).
+\item Introduce a method to build models of name variations
+\item Built a system to filter a large amount of diverse documents
+\item Extract, infer and filter entity-slot-value triples of information to be added to KB 
 \end{itemize}
 
+\begin{table}
+\caption{Ontology of Slots }
+\centering
+\label{table:slotNameOntology}
+
+\begin{tabular}{|c|c|c|}
+\hline 
+\textbf{PER} & \textbf{FAC} & \textbf{ORG} \\ 
+\hline 
+\begin{tabular}{@{}l@{}}Affiliate \\ AssociateOf \\ Contact\_Meet\_PlaceTime \\ AwardsWon \\ 
+DateOfDeath \\ 
+CauseOfDeath\\
+Titles\\
+FounderOf\\
+EmployeeOf\end{tabular}
+  &
+   \begin{tabular}[b]{l}Affiliate \\ Contact\_Meet\_Entity \end{tabular} 
+   & 
+   \begin{tabular}{@{}l@{}}Affiliate \\ TopMembers \\ FoundedBy\end{tabular} \\ 
+\hline 
+\end{tabular} 
+\end{table}
 % Evaluation Criteria

### 2013-11-04 paper/flairs27/content/system.tex
first half milenko's comments

@@
-\section{System Overview}
+\section{System}
 
@@
 Our system is built with a pipeline architecture in mind giving it the advantage to run each section separately to allow stream processing without blocking the data flow of components (Figure~\ref{fig:system}).
-The three logical components include sections for performing preprocessing to prepare the required data, Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming Slot Filling to generate the actual slot values and PostProcessing to increase precision/recall.
-We work on a streaming data set and entities are from Twitter or WP to query.
+The three logical components include sections on \textit{Model} for entity resolution purposes, \textit{Wiki Citation} to annotate cite-worthy documents, \textit{Slot Filling} to generate the actual slot values.
 
@@
 
-As mentioned before the time lag from an event occurance until it is cited in WP is in average over a year due to the fact that human maintainers are much less than the number of entities in WP and that the frequency of news update on entities escalates this difference.
-Hence having an automatic way to extract this knowldge for entities can be a very valuable asset.
-
 %\ceg{Discuss current system first. If you want to keep the decisions points that led to the current architecture, make it a subsection.}
 
-\begin{figure*}
+\begin{figure}
   \centering
 %  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
-  \includegraphics[width=6in]{./images/System_Diagram_with_model_Vertical.pdf}
+  \includegraphics[width=3in]{./images/System_Diagram_with_model_Vertical-crop.pdf}
 % http://convert.neevia.com/pdfconvert/
   \vspace*{-.1in} 
-  \caption{The GatorDSR team System Architecture.
-  Components are logically groups with dotted boxes.
-  Color details the programing language implementation of components.}
+  \caption{System Architecture.
+  Components are logical groups noted with dotted boxes.}
   \label{fig:system}
   \vspace*{-.2in}
-\end{figure*}
+\end{figure}
 
-\textit{Preprocessing.}
-The contest prohibits Wikipedia entities to have any manual aliases being added and only allows automatic ways.
-We use Wikipedia API backlink references (redirects to a wiki entity) as aliases of the entity.
-We also extract aliases from within the text of a wiki entity, which will be described in Section~\ref{section:aliasgeneration}.
-This whole process is referred to as \textit{Alias Extraction}.
-The manual extraction rule is lifted and participants are allowed to manually add aliases for Twitter entities.
-This is allowed because the Twitter website does not provide an example page from the beginning of the document stream.
-This process of extracting aliases for Twitter entities is referred to as \textit{Manual Alias Extraction}.
+\subsection{Model}
+
+We use Wikipedia API to get these aliases automatically.
+This is done by retrieving backlink references (redirects of a wiki entity), e.g.
+William Henry Gates is an alias for Bill Gates in WP as a backlink reference.
+Unfortunately this is not good enough and to enhance recall we need more aliases.
+To have better use of a wiki page we parse HTML DOM of the page, then use regular expressions to extract the bold phrases of the first paragraph as alias of the actual entity.
+Based on our observation this is a very accurate heuristic and provides us with lots of famous aliases of the entities.
+As an example of when this might not wirk, is that there might be occasions that some other topic is written in bold typesetting in the first paraph apart from the entity aliases itself but these are very rare.
 
 Once aliases are available we pass them through rules of generating proper name orders which will produce various forms of writing a name.
-As a basic example Bill Gates can be written as Gates, Bill.
+As a basic example Bill Gates can be written as Gates, Bill also.
 This will allow the system to capture various notation forms of aliases.
-We refer to this part as \textit{Name Order Generator}.
+We refer to this part as \textit{Alias Order Generator}.
 

### 2013-11-04 paper/flairs27/content/abstract.tex

@@
 
-In this paper we address extracting central slot values from internet pertinent to entities in wikipedia, which is the most popular web-based, colaborative multilingual encyclopieda on the internet.
+In this paper we address extracting slot values from internet pertinent to entities in wikipedia, which is the most popular web-based, colaborative multilingual encyclopieda on the internet.
 This is comparable to Freebase in a query-driven manner.
-Our contributions are two fold, first we design a system to efficiently find central documents on the internet that contain directly citable information regarding a given wikipedia entity; second, we design a system to extract specific features of that entity from central documents which is refered to as slot filling.
+Our contributions are two fold, first we design a system to efficiently find central documents on the internet that contain directly citable content regarding a given wikipedia entity; second, we design a system to extract certain slot-values of the entity from those documents.
 Our results demonstrate that the system is very efficient in the web scale nature of the problem: being highly memory and I/O efficient and that we can achieve high accuracy and recall for given slot values.

### 2013-11-04 paper/flairs27/content/discussion.tex
Merged Implementation and system

@@
-\section{Discussions \& Conclusion}
+\section{Discussions}
 
@@
 Further improvements on this component of the system are required.
+
+We sampled documents from the training data period to generate an initial set of patterns.
+We then use these patterns to generate SSF results.
+By manully looking at these results, we prune some patterns with poor­performance and add more patterns that we identified from these results.
+We use several iterations to find the best patterns.
+We found that it is time consuming to identity quality pattern.
+
+We found three major classes of accuracy errors: incorrect entities selected, incorrect tags by Lingpipe and incorrect pattern extractions.
+The first issue is ameliorated by generating better aliases .
+And we use post-processing to reduce the second and third types of errors.
+We didn't use more advanced NLP packages such as Stanford NLP because of the large size of the data set.
+The post-processing step to improve the results is discussed in the next section.
+
+\textit{Post Processing Algorithm.}
+The SSF output of many extractions is noisy.
+The data contains duplicates and incorrect extractions.
+We can define rules to sanitize the output only using the information present in the SSF file.
+The file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy.
+We define two classes of rules deduplication rules and inference rules.
+In our diagram we refer to this component as \textbf{High Accuracy Filter}.

### 2013-11-04 paper/flairs27/content/implementation.tex

@@
 
-Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textit{Chunk Files Index Generator} and \textit{StreamItems Index Generator}.
-Chunk Files Index Generator will generate indexes of the chunk files that contain a mention of any of the desired entities.
-StreamItems Index Generator
-on the other hand will index StreamItems that contain a mention of a given entity respectively.
-This two level indexing will eliminate the need to process each and every ChunkFile/StreamItem for every entity.
-The reason for splitting this task into two steps is that not all chunk files contain any mention of the entities and
-we want to get rid of them as soon as possible.
-Chunk Files Index Generator which discards non-mentioning chunk files and will stop further processing a chunk file as soon as it finds a mention there.
-Each chunk file can contain up to thousands of SIs which can be so time consuming if we were to process them in our Java base code.
-Processing StreamItems on the other hand is done in Java with ideas in mind for later on extensibility by adding other Java libraries.
-
 \subsection{Streaming Slot Value Extraction}
-\label{sec:ssve}
-\begin{figure}
-\centering
-%\includegraphics[width=4.5in]{./images/system.eps}
-%\includegraphics[width=6in]{./images/Pattern.eps}
-%\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
-\includegraphics[width = 13cm]{./images/Pattern-crop.pdf}
-% cropped pdf created using $ pdfcrop Pattern.pdf
-\vspace*{-.1in} \caption{Pattern Matching with Slot Value on the Right Side of Entity. }\label{fig:pattern}
-\vspace*{-.2in}
-\end{figure}
-
-In the data set, we are given a date range of documents as training data. Instead of building a classifier we use pattern matching methods to find corresponding slot values for entities. 
-Pattern matching is simple to manipulate results and implement. Additionally, a classifier approach is more difficult to evaluate and explain results.
-
-With the StreamItem indexes generated by the CCR, we first fetch the sentences containing entites by using alias names and coreference information provided by Lingpipe tags.
-Then use these senteces to match patterns and when patterns matched, generate SSF results.
-
-\begin{algorithm}
-  \caption{Streaming Slot Value Extraction Pseudocode}
-  \textbf{List of entities $\mathcal{E} = \{e_0, \ldots, e_{170}\}$}\\
-  \textbf{List of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
-  \textbf{List of streamitems containing entities $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
-
-  \begin{algorithmic}%[1]
-    \FOR{$si \in \mathcal{S}$}
-      \FOR{$sentence \in si$}
-        \FOR{$entity \in \mathcal{E}$}
-	  \IF{Contains($sentence$, $entity$)}
-          %%\IF{check\_pattern(sentence, pattern)}
-            \FOR{$pattern \in P $ suitable for $entity$} 
-              \IF{Satisfies($sentence$, $pattern$)}
-                \STATE Emit($sentence$, $pattern$)
-              \ENDIF
-	    \ENDFOR
-          \ENDIF
-        \ENDFOR
-      \ENDFOR
-    \ENDFOR
-  \end{algorithmic}
-\end{algorithm}
-
-\subsubsection{Format of patterns}
-A pattern is defined as a record representing knowledge going to be added to a knowledge base.
-A pattern $\mathcal{P}$ is represented as a five-tuple $\mathcal{P} = \langle p_1, p_2, p_3, p_4, p_5 \rangle$.
-
-The first value, $p_1$ represents the type of entity.
-These entity types are in the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC} represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER} represents a person.
-\texttt{FAC}, \texttt{ORG} and \texttt{PER} are Lingpipe entity types.
-The $p_2$ represents a slot name.
-A list of slot names is present in Table~\ref{table:slotNameOntology}.
-The third element $p_3$ is the pattern content.
-This is a string found in the sentence.
-The extractor looks for this exact string or pattern in a sentence.
-The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in $p_4$ to explore sentence.
-The final element $p_5$ represent the slot value of a pattern.
-This %When we match one pattern, we match all the
-%fields except the third field, which is extracted as the final result.
-The type of slot value may be the entity type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP or a hard-coded phrase.
-For these three kinds of patterns, we implement them in different
-ways accordingly. Next, we explain the patterns with more details, an example can be found in Figure~\ref{fig:pattern}.
-
-\subsubsection{Types of patterns}
-There are three types of patterns distinguished by different types of slot values in the patterns.
-The matching methods using these three types of patterns are implememented according to the different information and structures of slot values.
-
-\textbf{Type I.} This pattern type is driven by the slot value type, a pattern tagged by Lingpipe.
-For example, pattern $\langle$\texttt{PER, FounderOf, \textit{founder}, right, ORG}$\rangle$.
-\texttt{PER} means
-that the entity we are finding slot values for a PER entity; \texttt{FounderOf} means this is a pattern for FounderOf slot.
-\textit{founder} is the anchor word we are match in a sentence; \texttt{right} means that we are going to the right part of the sentence to match the pattern and find the slot value; ORG means the slot value should be a ORG entity.
-
-\textbf{Type II.} This pattern type is unique because it only looks for a slot value tagged as noun phrase (NP) by OpenNLP.\@ For example, pattern $\langle$\texttt{PER, AwardsWon, \textit{awarded}, right, NP}$\rangle$.
-This pattern can be interpreted as that we are looking for a noun phrase after the \textit{awarded} since that noun phrase may represent an award.
-Titles and awards are usually not the Lingpipe entities, hence the use of the OpenNLP noun phrase chunker to fetch the noun phrases.
-
-\textbf{Type III.} Some relations are best discovered by hard coding the slot values.
-Examples of these include time phrases: $\langle$\texttt{PER, DateOfDeath, \textit{died}, right, \textit{last night}}$\rangle$.
-In this pattern, \textit{last night} means we are looking for exactly the phrase \textit{last night} to the right of \textit{died}.
-This pattern is inspired by the intuition that in news articles, people often mention that somebody died last night instead of mentioning the accurate date information and Lingpipe tends not to tag phrases like \textit{last night} as a DATE entity.
-
-\subsubsection{A short discussion}
-We sampled documents from the training data period to generate an initial set of patterns.
-We then use these patterns to generate SSF results.
-By manully looking at these results, we prune some patterns with poor­performance and add more patterns that we identified from these results.
-We use several iterations to find the best patterns.
-We found that it is time consuming to identity quality pattern.
-
-We found three major classes of accuracy errors: incorrect entities selected, incorrect tags by Lingpipe and incorrect pattern extractions.
-The first issue is ameliorated by generating better aliases (Section~\ref{section:aliasgeneration}).
-And we use post-processing to reduce the second and third types of errors (Section~\ref{section:highAccuracyFilter}).
-We didn't use more advanced NLP packages such as Stanford NLP because of the large size of the data set.
-The post-processing step to improve the results is discussed in the next section.
-
-\subsection{High Accuracy Filter}
-\label{section:highAccuracyFilter}
-
-The SSF output of streaming slot value extraction is noisy.
-The data contains duplicates and incorrect extractions.
-We can define rules to sanitize the output only using the information present in the SSF file.
-The file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy.
-We define two classes of rules: \textit{deduplication} and \textit{inference} rules.
-
-The output contains many duplicate entries.
-As we read the list of extracted slots we create rules to define ``duplicate''.
-Duplicates can be present in a window of rows; we use a window size of 2 meaning we only be adjacent rows.
-Two rows are duplicates if they have the same exact extraction, or if the rows have the same slot name and a similar slot value or if the extracted sentence for a particular slot types come from the same sentence.
-
- New slots can be deduced from existing slots by defining inference rules.
-For example, two slots for the task are ``FounderOf'' and ``FoundedBy''.
-A safe assumption is these slot names are biconditional logical connectives with the entities and slot values.
-Therefore, we can express a rule ``X FounderOf Y'' equals ``Y FoundedBy X'' where X and Y are single unique entities.
-Additionally, we found that the slot names ``Contact\_Meet\_PlaceTime'' could be inferred as ``Contact\_Meet\_Entity'' if the Entity was a FAC and the extracted sentence contained an additional ORG/FAC tag.
-We also remove erronious slots that have extractions that are several pages in length or tool small.
-Errors of extracting long sentences can typically be
-attributed to poor sentence parsing of web documents.
-We have some valid ``small'' extractions.
-For example a comma may separate a name and a title (e.g.
-``John, Professor at MIT'').
-But such extraction rules can be particularly noisy, so we check to see if the extracted values have good entity values.
 

### 2013-11-04 paper/flairs27/content/system.tex

@@
 
-\textit{Cumulative Citation Recommendation.}
+\subsection{Wikipedia Citation}
 The main goal of CCR is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page.
@@
 So we take on that and ignore non-citing documents.
+
+Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textit{Document Chunks Indexer} and \textit{Document Filter}.
+Document chunks Indexer will generate indexes of the chunk files that contain a mention of any of the desired entities.
+Document Filter on the other hand will index documents that contain a mention of a given entity respectively.
+This two level indexing will eliminate the need to process each and every chunk file/document for every entity.
+The reason for splitting this task into two steps is that not all chunk files contain any mention of the entities and we want to get rid of them as soon as possible.
+Document Chunks Indexer which discards non-mentioning chunk files and will stop further processing a chunk file as soon as it finds a mention there.
+Each chunk file can contain up to thousands of documents which can be so time consuming if we were to process them in our Java base code.
+Processing StreamItems on the other hand is done in Java with ideas in mind for later on extensibility by adding other Java libraries.
 
@@
 
-\textit{Streaming Slot Filling.}
+\subsection{Slot Filling}
 %\ceg{See the previous note.}
 The purpose of SSF is to extract proper values for relations of interest, which can be found in Table~\ref{table:slotNameOntology}.
-This is called Stream Slot Filling because data is being generated as time goes
-on and for each extraction we should only consider current or past data.
-In Figure~\ref{fig:system} we refer to this as \textit{Streaming Slot Value Extraction}.
-Stream slot filling is done by pattern matching documents with manually produced patterns for slots of interest.
+In Figure~\ref{fig:system} we refer to this as \textit{Slot Filling}.
+
+Slot filling is done by pattern matching documents with manually produced patterns for slots of interest.
 The way we do this is by observing a sentence that has a mention of the entity or one of its coreferences.
@@
 
-\textit{Post Processing Algorithm.}
-The SSF output of many extractions is noisy.
+\begin{figure}
+\centering
+%\includegraphics[width=4.5in]{./images/system.eps}
+%\includegraphics[width=6in]{./images/Pattern.eps}
+%\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
+\includegraphics[width = 13cm]{./images/Pattern-crop.pdf}
+% cropped pdf created using $ pdfcrop Pattern.pdf
+\vspace*{-.1in} \caption{Pattern Matching with Slot Value on the Right Side of Entity. }\label{fig:pattern}
+\vspace*{-.2in}
+\end{figure}
+
+In the data set, we are given a date range of documents as training data. Instead of building a classifier we use pattern matching methods to find corresponding slot values for entities. 
+Pattern matching is simple to manipulate results and implement. Additionally, a classifier approach is more difficult to evaluate and explain results due to the lack of proper training data.
+
+With the documents indexes generated by the Wikipedia Citation, we first fetch the sentences containing entites by using alias names and coreference information provided by Lingpipe tags\footnote{http://alias-i.com/lingpipe/}.
+Then use these senteces to match patterns and when patterns matched, generate SSF results.
+
+\begin{algorithm}
+  \caption{Slot Value Extraction Pseudocode}
+  \textbf{List of entities $\mathcal{E} = \{e_0, \ldots, e_{170}\}$}\\
+  \textbf{List of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
+  \textbf{List of streamitems containing entities $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
+
+  \begin{algorithmic}%[1]
+    \FOR{$si \in \mathcal{S}$}
+      \FOR{$sentence \in si$}
+        \FOR{$entity \in \mathcal{E}$}
+	  \IF{Contains($sentence$, $entity$)}
+          %%\IF{check\_pattern(sentence, pattern)}
+            \FOR{$pattern \in P $ suitable for $entity$} 
+              \IF{Satisfies($sentence$, $pattern$)}
+                \STATE Emit($sentence$, $pattern$)
+              \ENDIF
+	    \ENDFOR
+          \ENDIF
+        \ENDFOR
+      \ENDFOR
+    \ENDFOR
+  \end{algorithmic}
+\end{algorithm}
+
+\subsubsection{Rule Engine}
+
+\textbf{Format of Patterns.} A pattern is defined as a record representing knowledge going to be added to a KB.
+A pattern $\mathcal{P}$ is represented as a five-tuple $\mathcal{P} = \langle p_1, p_2, p_3, p_4, p_5 \rangle$.
+
+The first value, $p_1$ represents the type of entity.
+These entity types are in the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC} represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER} represents a person.
+\texttt{FAC}, \texttt{ORG} and \texttt{PER} are Lingpipe entity types.
+The $p_2$ represents a slot name.
+A list of slot names is present in Table~\ref{table:slotNameOntology}.
+The third element $p_3$ is the pattern content.
+This is a string found in the sentence.
+The extractor looks for this exact string or pattern in a sentence.
+The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in $p_4$ to explore sentence.
+The final element $p_5$ represent the slot value of a pattern.
+This %When we match one pattern, we match all the
+%fields except the third field, which is extracted as the final result.
+The type of slot value may be the entity type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP or a hard-coded phrase.
+For these three kinds of patterns, we implement them in different
+ways accordingly. Next, we explain the patterns with more details, an example can be found in Figure~\ref{fig:pattern}.
+
+\textbf{Types of patterns}
+There are three types of patterns distinguished by different types of slot values in the patterns.
+The matching methods using these three types of patterns are implememented according to the different information and structures of slot values.
+
+\textbf{Type I.} This pattern type is driven by the slot value type, a pattern tagged by Lingpipe.
+For example, pattern $\langle$\texttt{PER, FounderOf, \textit{founder}, right, ORG}$\rangle$.
+\texttt{PER} means
+that the entity we are finding slot values for a PER entity; \texttt{FounderOf} means this is a pattern for FounderOf slot.
+\textit{founder} is the anchor word we are match in a sentence; \texttt{right} means that we are going to the right part of the sentence to match the pattern and find the slot value; ORG means the slot value should be a ORG entity.
+
+\textbf{Type II.} This pattern type is unique because it only looks for a slot value tagged as noun phrase (NP) by OpenNLP.\@ For example, pattern $\langle$\texttt{PER, AwardsWon, \textit{awarded}, right, NP}$\rangle$.
+This pattern can be interpreted as that we are looking for a noun phrase after the \textit{awarded} since that noun phrase may represent an award.
+Titles and awards are usually not the Lingpipe entities, hence the use of the OpenNLP noun phrase chunker to fetch the noun phrases.
+
+\textbf{Type III.} Some relations are best discovered by hard coding the slot values.
+Examples of these include time phrases: $\langle$\texttt{PER, DateOfDeath, \textit{died}, right, \textit{last night}}$\rangle$.
+In this pattern, \textit{last night} means we are looking for exactly the phrase \textit{last night} to the right of \textit{died}.
+This pattern is inspired by the intuition that in news articles, people often mention that somebody died last night instead of mentioning the accurate date information and Lingpipe tends not to tag phrases like \textit{last night} as a DATE entity.
+
+\subsubsection{Constraints - Inference}
+
+The SSF output of streaming slot value extraction is noisy.
 The data contains duplicates and incorrect extractions.
-We can define rules to sanitize the output only using the information present in the SSF file.
-The file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy.
-We define two classes of rules deduplication rules and inference rules.
-In our diagram we refer to this component as \textbf{High Accuracy Filter}.
+We can define rules to sanitize the output only using the information present at this stage.
+The input file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy.
+We define two classes of rules: \textit{deduplication} and \textit{inference} rules.
+
+The output contains many duplicate entries.
+As we read the list of extracted slots we create rules to define ``duplicate''.
+Duplicates can be present in a window of rows; we use a window size of 2 meaning we only be adjacent rows.
+Two rows are duplicates if they have the same exact extraction, or if the rows have the same slot name and a similar slot value or if the extracted sentence for a particular slot types come from the same sentence.
+
+ New slots can be deduced from existing slots by defining inference rules.
+For example, two slots for the task are ``FounderOf'' and ``FoundedBy''.
+A safe assumption is these slot names are biconditional logical connectives with the entities and slot values.
+Therefore, we can express a rule ``X FounderOf Y'' equals ``Y FoundedBy X'' where X and Y are single unique entities.
+Additionally, we found that the slot names ``Contact\_Meet\_PlaceTime'' could be inferred as ``Contact\_Meet\_Entity'' if the Entity was a FAC and the extracted sentence contained an additional ORG/FAC tag.
+We also remove erronious slots that have extractions that are several pages in length or tool small.
+Errors of extracting long sentences can typically be
+attributed to poor sentence parsing of web documents.
+We have some valid ``small'' extractions.
+For example a comma may separate a name and a title (e.g.
+``John, Professor at MIT'').
+But such extraction rules can be particularly noisy, so we check to see if the extracted values have good entity values.
+
+\subsubsection{A short discussion}

### 2013-11-04 paper/flairs27/content/introduction.tex
More fine tuning

@@
 The challenges that we address are: first finding documents that contain useful information about the entity (avoid spams, documents that do not have direct information about the entity even though they mention them, etc), the scale where \textit{stream processing} nature of the system makes it suitable to avoid batch processing natures of Hadoop and operate in the realm of streams such as twitter storm\footnote{http://storm-project.net/} which similarly processes unblounded streams of twitter data or Spark Streaming \footnote{http://spark.incubator.apache.org/}.
+Further, this is called streaming because data is being generated as time goes
+on and for each extraction we should only consider current or past data.
 As other Natural Language Processing tasks, precision and recall of the extent we can extract slot values are very important metrics that we will discuss later on.
@@
 \hline 
-\begin{tabular}{@{}l@{}}Affiliate \\ AssociateOf \\ Contact\_Meet\_PlaceTime \\ AwardsWon \\ 
+\begin{tabular}{@{}l@{}}Affiliate \\ AssociateOf \\ {\small Contact\_Meet\_PlaceTime} \\ AwardsWon \\ 
 DateOfDeath \\ 
@@
   &
-   \begin{tabular}[b]{l}Affiliate \\ Contact\_Meet\_Entity \end{tabular} 
+   \begin{tabular}[b]{l}Affiliate \\ {\small Contact\_Meet\_Entity} \end{tabular} 
    & 

### 2013-11-05 paper/flairs27/content/introduction.tex
Fix Table width

@@
 
+\setlength{\tabcolsep}{2pt}
+
 \begin{tabular}{|c|c|c|}
 \hline 
-\textbf{PER} & \textbf{FAC} & \textbf{ORG} \\ 
+\textbf{Person} & \textbf{Facility} & \textbf{Organization} \\ 
 \hline 
-\begin{tabular}{@{}l@{}}Affiliate \\ AssociateOf \\ {\small Contact\_Meet\_PlaceTime} \\ AwardsWon \\ 
+\begin{tabular}{@{}l@{}}Affiliate \\ AssociateOf \\  {\tiny Contact\_Meet\_PlaceTime} \\ AwardsWon \\ 
 DateOfDeath \\ 
@@
    & 
-   \begin{tabular}{@{}l@{}}Affiliate \\ TopMembers \\ FoundedBy\end{tabular} \\ 
+   \begin{tabular}{@{}l@{}}Affiliate \\ {\small TopMembers} \\ FoundedBy\end{tabular} \\ 
 \hline 

### 2013-11-05 paper/flairs27/content/introduction.tex
rearranhged the introduction

@@
 \section{Introduction}
-
-In this paper we develop an efficient query-driven slot value extraction for given Wikipedia.org (WP) entities from a timely stream of documents on internet as they are being created.
-Slot value extraction is formally defined as follows: match each sentence to the generic sentence structure of [\textit{Subject} - \textit{Verb} - \textit{Adverbial/Complement}]\cite{sentencePatterns08}, where  \textit{Subject} represents the entity and \textit{Verb} is the relation type we are interested in (e.g.
-Table~\ref{table:slotNameOntology}).
-If a sentence matches these two components of the sentence pattern, \textit{Adverbial/Complement} would be returned as the other side of the relation (which we refer to as slot value).
-Slot value extraction is a challenging task in current state of the art Knowldge Bases (KB).
-Popular graphical KB such as Freebase or DBPedia keep data in structured format where entities are connected via relationships (\textit{Verb}) and the associated attributes (\textit{Adverbial/Compelement}).
-Our system can be used to automatically populate such KBs or even fill-in the information boxes at entity WP page itself.
-
-Entities from three categories of \textit{person}, \textit{organization} and \textit{facility} are considered.
-The challenges that we address are: first finding documents that contain useful information about the entity (avoid spams, documents that do not have direct information about the entity even though they mention them, etc), the scale where \textit{stream processing} nature of the system makes it suitable to avoid batch processing natures of Hadoop and operate in the realm of streams such as twitter storm\footnote{http://storm-project.net/} which similarly processes unblounded streams of twitter data or Spark Streaming \footnote{http://spark.incubator.apache.org/}.
-Further, this is called streaming because data is being generated as time goes
-on and for each extraction we should only consider current or past data.
-As other Natural Language Processing tasks, precision and recall of the extent we can extract slot values are very important metrics that we will discuss later on.
-Having to balance between infamous and obscure enitities, dealing with slots that can be very broad (e.g.
-things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).
-
-To take on an example assume we are analyzing a sentence from the internet such as "\underline{Boris Berezovsky} made his fortune in Russia in the 1990s when the country went through privatisation of state property and 'robber capitalism', and passed away March 2013.".
-First we have to pay attemtion that there are two \textit{Boris Berezovsky} entities in WP, one a businessman and the other a pianist.
-Any slot value extraction shall take this into account and try to come up with a viable distinguishing policy (Entity Resolution).
-Then, we match the sentence to find a slot value such as \textit{DateOfDeath} valued at March 2013.
-Other examples that this system can answer could be 'Who a person has met during a certain period of time?', 'Who are the employees of this organization?', 'Who has met who in this facility at a certain time?'.
 
@@
 
+To take on an example assume we are analyzing a sentence from the internet such as ``\underline{Boris Berezovsky} made his fortune in Russia in the 1990s when the country went through privatisation of state property and `robber capitalism', and passed away March 2013.''  First we have to pay attemtion that there are two \textit{Boris Berezovsky} entities in WP, one a businessman and the other a pianist.
+Any slot value extraction shall take this into account and try to come up with a viable distinguishing policy (Entity Resolution).
+Then, we match the sentence to find a slot value such as \textit{DateOfDeath} valued at March 2013.
+Other examples that this system can answer could be `Who a person has met during a certain period of time?', `Who are the employees of this organization?', `Who has met who in this facility at a certain time?'.
+
+Entities from three categories of \textit{person}, \textit{organization} and \textit{facility} are considered.
+The challenges that we address are: first finding documents that contain useful information about the entity (avoid spams, documents that do not have direct information about the entity even though they mention them, etc), the scale where \textit{stream processing} nature of the system makes it suitable to avoid batch processing natures of Hadoop and operate in the realm of streams such as twitter storm~\footnote{http://storm-project.net/} which similarly processes unblounded streams of twitter data or Spark Streaming~\footnote{http://spark.incubator.apache.org/}.
+Further, this is called streaming because data is being generated as time goes
+on and for each extraction we should only consider current or past data.
+As other Natural Language Processing tasks, precision and recall of the extent we can extract slot values are very important metrics that we will discuss later on.
+Having to balance between infamous and obscure enitities, dealing with slots that can be very broad (e.g.\ things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).
+
+In this paper we develop an efficient query-driven slot value extraction for given Wikipedia.org (WP) entities from a timely stream of documents on internet as they are being created.
+Slot value extraction is formally defined as follows: match each sentence to the generic sentence structure of [\textit{Subject} - \textit{Verb} - \textit{Adverbial/Complement}]\cite{sentencePatterns08}, where  \textit{Subject} represents the entity and \textit{Verb} is the relation type we are interested in (e.g.
+Table~\ref{table:slotNameOntology}).
+If a sentence matches these two components of the sentence pattern, \textit{Adverbial/Complement} would be returned as the other side of the relation (which we refer to as slot value).
+Slot value extraction is a challenging task in current state of the art Knowldge Bases (KB).
+Popular graphical KB such as Freebase or DBPedia keep data in structured format where entities are connected via relationships (\textit{Verb}) and the associated attributes (\textit{Adverbial/Compelement}).
+Our system can be used to automatically populate such KBs or even fill-in the information boxes at entity WP page itself.
+
 Our system contains three main components.
-First, we pre-process the data and build models representing the KB entries.
+First, we pre-process the data and build models representing the WP query entities.
 Next, we use the models to filter a stream of documents so they only contain candidate citations.

### 2013-11-05 paper/flairs27/content/results.tex
Some table shortenning

@@
 
-\begin{table*}
+\begin{table}
 \caption{Document Chunks Distribution }
@@
 \hline 
-10988 & 	arxiv (full text, abstracts in StreamItem.other\_content) \\ \hline
-34887 & CLASSIFIED (spinn3r)  \\ \hline
-77674 & FORUM (spinn3r)  \\ \hline
-12947 & linking (reprocessed from kba-stream-corpus-2012, same stream\_id)  \\ \hline
-141936 & MAINSTREAM\_NEWS (spinn3r)  \\ \hline
-4137 & MEMETRACKER (spinn3r)  \\ \hline
-280629 & news (reprocessed from kba-stream-corpus-2012, same stream\_id)  \\ \hline
-6347 &  REVIEW (spinn3r) \\ \hline
-688848 & 	 social (reprocessed from kba-stream-corpus-2012 plus extension, same stream\_id)  \\ \hline
-740987 & WEBLOG (spinn3r)  \\ \hline
+10988 & 	arxiv  \\ \hline
+34887 & Classified \\ \hline
+77674 & Forum  \\ \hline
+12947 & Linking  \\ \hline
+141936 & Mainstream News  \\ \hline
+4137 & Memetracker \\ \hline
+280629 & News \\ \hline
+6347 &  Review \\ \hline
+688848 & 	 Social  \\ \hline
+740987 & Weblog \\ \hline
 
@@
 \end{tabular} 
-\end{table*}
+\end{table}
 
@@
 \label{table:serverspec}
-\begin{tabular}{| c | p{5cm} |}
+\begin{tabular}{| c | p{4.8cm} |}
 \hline 
@@
 
-\begin{table}
+\begin{table}[htp]
 \caption{SSF Performance Measure on \textit{initial\_submission} }
@@
 
-\begin{table*}    
+\begin{table}[h]
+
 \caption{Recall Measure on \textit{submission\_infer}: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
@@
 \label{table:finalresultrecall}
-\begin{tabular}{|l|p{3.5cm}|p{4cm}|}
+\begin{tabular}{|l|c|c|}
 \hline 
- \textbf{Slot Name} & \textbf{Total instances of slot value found} & \textbf{\# of entities covered by slot value} \\ 
+ \textbf{Slot Name} & \textbf{Instances Found} & \textbf{Entity Coverage} \\ 
 \hline 
@@
 CauseOfDeath & 0 & 0 \\ \hline 
-Contact\_Meet\_Entity & 191 & 8 \\ \hline 
-Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
+{\tiny Contact\_Meet\_Entity} & 191 & 8 \\ \hline 
+{\tiny Contact\_Meet\_PlaceTime} & 5974 & 109 \\ \hline 
 DateOfDeath & 87 & 14 \\ \hline 
@@
 \end{tabular}
-\end{table*}
 
-\begin{table*}
 \caption{SSF Accuracy Measure on \textit{submission\_infer}: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}
@@
 \label{table:finalresultaccuracy}
-\begin{tabular}{|l|c|c|c|}
+\begin{tabular}{|l|c|c|p{13mm}|}
 \hline 
- \textbf{Slot Name}  & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
+ \textbf{Slot Name}  & \textbf{Correct} & \textbf{Wrong Entity} & {\small \textbf{Incorrect Value}} \\ 
 \hline 
@@
 CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
-Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 
-Contact\_Meet\_PlaceTime & 5\% & 20\% & 85\%  \\ \hline 
+{\tiny Contact\_Meet\_Entity} & 21\% & 42\% & 37\%  \\ \hline 
+{\tiny Contact\_Meet\_PlaceTime} & 5\% & 20\% & 85\%  \\ \hline 
 DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 

### 2013-11-05 paper/flairs27/content/results.tex
Some table moving arounds

@@
 
-\begin{table}
+\begin{table}[b]
 \caption{Document Chunks Distribution }
@@
 
-\begin{tabular}{|c|l|}
+\begin{tabular}{|l|c|c|}
 \hline 
-\textbf{\# of Documents} & \textbf{Document Type}\\ 
+\textbf{\# of Documents} & \textbf{Document Type} & \textbf{Slots Found}\\ 
 \hline 
-10988 & 	arxiv  \\ \hline
-34887 & Classified \\ \hline
-77674 & Forum  \\ \hline
-12947 & Linking  \\ \hline
-141936 & Mainstream News  \\ \hline
-4137 & Memetracker \\ \hline
-280629 & News \\ \hline
-6347 &  Review \\ \hline
-688848 & 	 Social  \\ \hline
-740987 & Weblog \\ \hline
+	Arxiv & 10988 & \\ \hline
+ Classified & 34887 & \\ \hline
+ Forum & 77674 & \\ \hline
+ Linking & 12947 & \\ \hline
+ Mainstream News & 141936 & \\ \hline
+ Memetracker & 4137 & \\ \hline
+ News & 280629 & \\ \hline
+ Review & 6347 & \\ \hline
+ 	 Social & 688848 & \\ \hline
+ Weblog & 740987 & \\ \hline
 
@@
 
-We have 135 extraction patterns coverin each slot-name/entity-type combinations.
+We have 135 extraction patterns covering each slot-name/entity-type combinations.
 Our final submission was named \textit{submission\_infer}.
@@
 
-\begin{table}[htp]
+\begin{table}
 \caption{SSF Performance Measure on \textit{initial\_submission} }

### 2013-11-06 paper/flairs27/content/results.tex
More cleanup

@@
 %\ceg{We can add data on the total document size, The %number of each document type.  } 
+ The purpose of evaluation is to measure the effectiveness of extracting slot values for various entities, metrics such as precision and recall would be considered.
+We perform random samplings to extract these.
 Our system was developed on a 32-core server described in Table~\ref{table:serverspec}.
@@
 The total size of the data after XZ compression and GPG encryption is 4.5TB and just over 500M StreamItems \cite{s3}.
-Data is stored in directories the naming of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am) until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952 date-hour combinations, 4 months of data (October 2011 - February 2012) is for training purposes.
+Data is stored in directories the naming of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am) until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952 date-hour combinations.
+The first four months of data (October 2011 - February 2012) is for training purposes, and we use this portion to lookup sample lines and for system parameter settings purposes.
 This corpora consists of various media types the distribution of which can be found in Table~\ref{table:documentsDist}.
@@
 Some of the documents have null values for their annotation fields.
-The first portion of the data which ranges from October 2011 to February 2012 is considered as training data.
 The source code of our system is stored as an open source project where enthusiasts can also contribute to \cite{github}, also the relevant discussion mailing list is accessible here \cite{googlegroups}.
@@
 
-We have 135 extraction patterns covering each slot-name/entity-type combinations.
+We have 172 extraction patterns covering each slot-name/entity-type combinations.
 Our final submission was named \textit{submission\_infer}.
@@
 \begin{table}
-\caption{SSF Performance Measure on \textit{initial\_submission} }
+\caption{Initial Performance Measure }
 \centering
@@
 
-\caption{Recall Measure on \textit{submission\_infer}: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
+\caption{Recall Measure: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
 \centering
@@
 
-\caption{SSF Accuracy Measure on \textit{submission\_infer}: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}
+\caption{Accuracy Measure: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}
 \centering

### 2013-11-06 paper/flairs27/content/system.tex
Fix Table width
Some table moving arounds
More cleanup

@@
 \begin{figure}
+\hspace{-10mm}
   \centering
 %  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
-  \includegraphics[width=3in]{./images/System_Diagram_with_model_Vertical-crop.pdf}
+  \includegraphics[width=8.5cm]{./images/System_Diagram_with_model_Vertical-crop.pdf}
 % http://convert.neevia.com/pdfconvert/
@@
 \subsection{Wikipedia Citation}
-The main goal of CCR is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page.
+The main goal of this section is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page.
 We perform exact string matching and treat all the documents that mention an entity equally likely to be citable.
-One of the reasons for this is that in former TREC KBA reports \cite{JFrank12} there were observations of how non-mentioning documents have a low chance of being citable in Wikipedia.
+One of the reasons for this is that there have been observations of how non-mentioning documents have a low chance of being citable in Wikipedia \cite{JFrank12}.
 So we take on that and ignore non-citing documents.
@@
 Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textit{Document Chunks Indexer} and \textit{Document Filter}.
+The purpose of these indexes is to reduce I/O cost while generating slot values for various entities.
 Document chunks Indexer will generate indexes of the chunk files that contain a mention of any of the desired entities.
@@
 
-With the documents indexes generated by the Wikipedia Citation, we first fetch the sentences containing entites by using alias names and coreference information provided by Lingpipe tags\footnote{http://alias-i.com/lingpipe/}.
+With the documents indexes generated by the Wikipedia Citation, we first fetch the sentences containing entites by using alias names and coreference information provided by Lingpipe tags\footnote{Lingpipe (available in the dataset) provides entity tags and in-document correference.
+http://alias-i.com/lingpipe/}.
 Then use these senteces to match patterns and when patterns matched, generate SSF results.
@@
 %fields except the third field, which is extracted as the final result.
-The type of slot value may be the entity type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP or a hard-coded phrase.
+The type of slot value may be the entity type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP\footnote{OpenNLP was used for part of speech tagging.
+http://opennlp.apache.org/‎} or a hard-coded phrase.
 For these three kinds of patterns, we implement them in different
-ways accordingly. Next, we explain the patterns with more details, an example can be found in Figure~\ref{fig:pattern}.
+ways accordingly. Next, we explain the patterns with more details, an example of which can be found in Figure~\ref{fig:pattern}.
 
@@
 
-The SSF output of streaming slot value extraction is noisy.
+The output of streaming slot value extraction is noisy.
 The data contains duplicates and incorrect extractions.
@@
 But such extraction rules can be particularly noisy, so we check to see if the extracted values have good entity values.
-
-\subsubsection{A short discussion}

### 2013-11-06 paper/flairs27/content/discussion.tex

--- 2013-11-03 paper/flairs27/content/discussion.tex
@@
 
-When we evaluate the results of slot extraction, we find three kinds of problems for accuracy: 1) wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched by the patterns.
-We also have
-recall problems: 1) not enough good alias names to find all the entities.
-2) not enough and powerful patterns to capture all the slot values.
-We will use entity resolution methods and other advanced methods to improve
+As part of future work regarding enhancing precision, we can focus on fixing the wrong entities found, remove noisy tags by the Lingpipe or use more accurate NLP taggers such as Stanford NLP (Due to the fact that Stanford NLP is very slow we avoided using it, as due to speed its use was out of question) and finally use better patterns to enahnce results matched by the patterns.
+On the other hand to increase recall we need to find better aliases and go for more resources to discover other ways that an entity might be addressed (e.g.
+twitter id, website, etc), add powerful patterns that can capture more cases of slot values.
+We would also use entity resolution methods and other advanced methods to improve
 the accuracy and recall of entity extraction part.
@@
 
-About 50\% of twitter entities are not found by the system.
-One reason is those entities are not popular.
+Some of the entities are not popular.
 For example, a `Brenda Weiler' Google search result has 860,000 documents over the whole web.
@@
 We generate aliases for wikipedia entities using Wiki API and extract some aliases from wikipedia pages text itself.
-On twitter entities we extract aliases manually as it is part of the rule of the KBA track.
 We process documents that mention entities for slot value extraction.
@@
 Furthermore, on extracting slot values, pattern matching might not be the best options but definitely can produce some good results at hand.
-We have plans on generating classifiers for slot value extraction
-purposes.
+We have plans on generating classifiers for slot value extraction purposes.
 Entity resolution on the other hand was a topic we spent sometime on but could not get to stable grounds for it.
@@
 Further improvements on this component of the system are required.
+
+We sampled documents from the training data period to generate an initial set of patterns.
+We then use these patterns to generate  results.
+By manully looking at these results, we prune some patterns with poor ­performance and add more patterns that we identified from these results.
+We use several iterations to find the best patterns.
+We found that it is very time consuming to identity quality patterns.

### 2013-11-06 paper/flairs27/content/introduction.tex
rearranged and updated part of the introduction. Still there is a lot to do

@@
 
- An important challenge in maintaining WP, the most popular web-based, collaborative, multilingual KB on the internet, is making sure its contents are up-to-date.
-Presently, there is considerable time lag between the publication date of cited news and the date of an edit to WP creating the citation.
+Wikipedia.org (WP) is the largest and most popular general reference work on the Internet.
+The website is estimated to have nearly 365 million readers worldwide.
+An important part of keeping WP usable it to include new and current content.
+%An important challenge in maintaining WP, the most popular web-based, collaborative, multilingual KB on the internet, is making sure its contents are up-to-date.
+Presently, there is considerable time lag between the publication of an event and its citation in WP\@.
 The median time lag for a sample of about 60K web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail \cite{JFrank12}.
-Also, the majority of WP entities have updates on their associated article much less frequently than their mention frequency.
-Such stale entries are the norm in any large KB because the number of humans maintaining the KB is far fewer than the number of entities.
-%Further, the number of mentions is much larger than the number of entities~\cite{JFrank12}.
-Reducing latency keeps KBs and WP relevant and helpful to its users.
-Given an entity page, possible citations may come from a variety of sources.
+%Also, the majority of WP entities have updates on their associated article much less frequently than their mention frequency.
+Such stale entries are the norm in any large reference work because the number
+of humans maintaining the reference is far fewer than the number of entities.
+Reducing latency keeps WP relevant and helpful to its users.
+Given an entity page, such as \textit{wiki/Boris_Berezovsky_(businessman)}~\footnote{http://en.wikipedia.org/wiki/Boris_Berezovsky_(businessman)},
+possible citations may come from a variety of sources.
+Notable news may be derived from newspapers, tweets, blogs and a variety of different sources~\ref{}.
 The actual citable information is a small percentage of the total documents that appear on the web.
-We develop a system to read streaming data and filter out articles that are candidates for citations.
+%We develop a system to read streaming data and filter out articles that are candidates for citations. 
+The goal of this system is to read web documents and recommend citable facts for WP pages.
 
-To take on an example assume we are analyzing a sentence from the internet such as ``\underline{Boris Berezovsky} made his fortune in Russia in the 1990s when the country went through privatisation of state property and `robber capitalism', and passed away March 2013.''  First we have to pay attemtion that there are two \textit{Boris Berezovsky} entities in WP, one a businessman and the other a pianist.
-Any slot value extraction shall take this into account and try to come up with a viable distinguishing policy (Entity Resolution).
-Then, we match the sentence to find a slot value such as \textit{DateOfDeath} valued at March 2013.
-Other examples that this system can answer could be `Who a person has met during a certain period of time?', `Who are the employees of this organization?', `Who has met who in this facility at a certain time?'.
-
+Discovering arbitrary web pages that contain information that is relevant and citable 
+to the WP entities is a non trivial task.
 Entities from three categories of \textit{person}, \textit{organization} and \textit{facility} are considered.
+% Reorder this paragraph
 The challenges that we address are: first finding documents that contain useful information about the entity (avoid spams, documents that do not have direct information about the entity even though they mention them, etc), the scale where \textit{stream processing} nature of the system makes it suitable to avoid batch processing natures of Hadoop and operate in the realm of streams such as twitter storm~\footnote{http://storm-project.net/} which similarly processes unblounded streams of twitter data or Spark Streaming~\footnote{http://spark.incubator.apache.org/}.
@@
 As other Natural Language Processing tasks, precision and recall of the extent we can extract slot values are very important metrics that we will discuss later on.
-Having to balance between infamous and obscure enitities, dealing with slots that can be very broad (e.g.\ things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).
+Having to balance between infamous and obscure entities, dealing with slots that can be very broad (e.g.\ things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).
+
+As an example, take a sentence from the internet \texttt{\underline{Boris Berezovsky} made his fortune in Russia in the 1990s when the country went through privatisation of state property and `robber capitalism', and passed away March 2013.}
+First we have to pay attentions that there are two \textit{Boris Berezovsky} entities in WP, one a businessman and the other a pianist.
+Any slot value extraction shall take this into account and try to come up with a viable distinguishing policy (Entity Resolution).
+Then, we match the sentence to find a slot value such as \textit{DateOfDeath} valued at March 2013.
+Other examples that this system can answer could be `Who a person has met during a certain period of time?', `Who are the employees of this organization?', `Who has met who in this facility at a certain time?'.
 
@@
 If a sentence matches these two components of the sentence pattern, \textit{Adverbial/Complement} would be returned as the other side of the relation (which we refer to as slot value).
-Slot value extraction is a challenging task in current state of the art Knowldge Bases (KB).
+Slot value extraction is a challenging task in current state of the art Knowledge Bases (KB).
 Popular graphical KB such as Freebase or DBPedia keep data in structured format where entities are connected via relationships (\textit{Verb}) and the associated attributes (\textit{Adverbial/Compelement}).

### 2013-11-06 paper/flairs27/content/introduction.tex
3 quarters rewrite of the introduction

@@
 Presently, there is considerable time lag between the publication of an event and its citation in WP\@.
-The median time lag for a sample of about 60K web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail \cite{JFrank12}.
+The median time lag for a sample of about 60K web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail~\cite{JFrank12}.
 %Also, the majority of WP entities have updates on their associated article much less frequently than their mention frequency.
@@
 Reducing latency keeps WP relevant and helpful to its users.
-Given an entity page, such as \textit{wiki/Boris_Berezovsky_(businessman)}~\footnote{http://en.wikipedia.org/wiki/Boris_Berezovsky_(businessman)},
+Given an entity page, such as \textit{wiki/Boris\_Berezovsky\_(businessman)}\footnote{http://en.wikipedia.org/wiki/Boris\_Berezovsky\_(businessman)},
 possible citations may come from a variety of sources.
@@
 
-Discovering arbitrary web pages that contain information that is relevant and citable 
-to the WP entities is a non trivial task.
-Entities from three categories of \textit{person}, \textit{organization} and \textit{facility} are considered.
+Previous approaches are able to find relevant documents given a list of WP entities as query nodes \cite{}.
+Entities of three categories \textit{person}, \textit{organization} and \textit{facility} are considered.
+This task involves processing large sets of information to determine which facts may contain references to a WP entity. 
+This problem becomes increasingly more difficult when we look to extract specific relevant task from
+each document.
+Each relevant document must now be parsed and processed to determine if a sentence or paragraph is worth being cited.
 % Reorder this paragraph
-The challenges that we address are: first finding documents that contain useful information about the entity (avoid spams, documents that do not have direct information about the entity even though they mention them, etc), the scale where \textit{stream processing} nature of the system makes it suitable to avoid batch processing natures of Hadoop and operate in the realm of streams such as twitter storm~\footnote{http://storm-project.net/} which similarly processes unblounded streams of twitter data or Spark Streaming~\footnote{http://spark.incubator.apache.org/}.
+%The challenges that we address are: first finding documents that contain useful information about the entity (avoid spams, documents that do not have direct information about the entity even though they mention them, etc), the scale where \textit{stream processing} nature of the system makes it suitable to avoid batch processing natures of Hadoop and operate in the realm of streams such as twitter storm~\footnote{http://storm-project.net/} which similarly processes unblounded streams of twitter data or Spark Streaming~\footnote{http://spark.incubator.apache.org/}.
 Further, this is called streaming because data is being generated as time goes
-on and for each extraction we should only consider current or past data.
+%on and for each extraction we should only consider current or past data.
 As other Natural Language Processing tasks, precision and recall of the extent we can extract slot values are very important metrics that we will discuss later on.
@@
 
-As an example, take a sentence from the internet \texttt{\underline{Boris Berezovsky} made his fortune in Russia in the 1990s when the country went through privatisation of state property and `robber capitalism', and passed away March 2013.}
-First we have to pay attentions that there are two \textit{Boris Berezovsky} entities in WP, one a businessman and the other a pianist.
-Any slot value extraction shall take this into account and try to come up with a viable distinguishing policy (Entity Resolution).
-Then, we match the sentence to find a slot value such as \textit{DateOfDeath} valued at March 2013.
-Other examples that this system can answer could be `Who a person has met during a certain period of time?', `Who are the employees of this organization?', `Who has met who in this facility at a certain time?'.
+Discovering facts from the Internet that are relevant and citable to the WP entities is a non-trivial task.
+For example, take a sentence from the internet \texttt{Boris Berezovsky made his fortune in Russia in the 1990s when the country went through privatisation of state property and `robber capitalism', and passed away March 2013.}
+First, we must realize that there are two \textit{Boris Berezovsky} entities in WP, one a businessman and the other a pianist.
+Any extraction needs to take this into account and employ a viable distinguishing policy (entity resolution).
+Then, we match the sentence to find a topic (slot) such as \textit{DateOfDeath} valued at March 2013.
+Each of these operations is expensive so an intelligent efficient framework is necessary to execute these operations at web scale.
+%Other examples that this system can answer could be `Who a person has met during a certain period of time?', `Who are the employees of this organization?', `Who has met who in this facility at a certain time?'.
 
-In this paper we develop an efficient query-driven slot value extraction for given Wikipedia.org (WP) entities from a timely stream of documents on internet as they are being created.
-Slot value extraction is formally defined as follows: match each sentence to the generic sentence structure of [\textit{Subject} - \textit{Verb} - \textit{Adverbial/Complement}]\cite{sentencePatterns08}, where  \textit{Subject} represents the entity and \textit{Verb} is the relation type we are interested in (e.g.
+In this paper we develop an efficient query-driven slot extraction for given WP entities from a timely stream of documents on internet as they are being created.
+Slot or fact extraction is formally defined as follows: match each sentence to the generic sentence structure of [\textit{Subject} - \textit{Verb} - \textit{Adverbial/Complement}]~\cite{sentencePatterns08}, where  \textit{Subject} represents the entity and \textit{Verb} is the relation type we are interested in (e.g.
 Table~\ref{table:slotNameOntology}).

### 2013-11-06 paper/flairs27/content/introduction.tex
many changes and additions to the introduction

@@
 of humans maintaining the reference is far fewer than the number of entities.
+
 Reducing latency keeps WP relevant and helpful to its users.
-Given an entity page, such as \textit{wiki/Boris\_Berezovsky\_(businessman)}\footnote{http://en.wikipedia.org/wiki/Boris\_Berezovsky\_(businessman)},
+Given an entity page, such as \texttt{wiki/Boris\_Berezovsky\_(businessman)}\footnote{http://en.wikipedia.org/wiki/Boris\_Berezovsky\_(businessman)},
 possible citations may come from a variety of sources.
-Notable news may be derived from newspapers, tweets, blogs and a variety of different sources~\ref{}.
+Notable news may be derived from newspapers, tweets, blogs and a variety of
+different sources include Twitter, Facebook, iBlogs, arxiv, etc.\
 The actual citable information is a small percentage of the total documents that appear on the web.
@@
 
-Previous approaches are able to find relevant documents given a list of WP entities as query nodes \cite{}.
+Previous approaches are able to find relevant documents given a list of WP
+entities as query nodes \cite{mcnamee2012hltcoe, dalton2013bi,
+Bonnefoy:2013:WDE:2484028.2484180, Balog:2013:CCR:2484028.2484151,ji2011knowledge}.
 Entities of three categories \textit{person}, \textit{organization} and \textit{facility} are considered.
@@
 Discovering facts from the Internet that are relevant and citable to the WP entities is a non-trivial task.
-For example, take a sentence from the internet \texttt{Boris Berezovsky made his fortune in Russia in the 1990s when the country went through privatisation of state property and `robber capitalism', and passed away March 2013.}
+For example, take a sentence from the Internet:
+
+%\texttt{Boris Berezovsky made his fortune in Russia in the 1990s when the
+%country went through privatisation of state property and `robber capitalism', and passed away March 2013.}
+``\texttt{Boris Berezovsky, who made his fortune in Russia in the 1990s, passed away March 2013.}''
+
 First, we must realize that there are two \textit{Boris Berezovsky} entities in WP, one a businessman and the other a pianist.
@@
 
-In this paper we develop an efficient query-driven slot extraction for given WP entities from a timely stream of documents on internet as they are being created.
+In this paper we develop an efficient query-driven slot extraction for given WP entities from a time oriented stream of Internet documents.
 Slot or fact extraction is formally defined as follows: match each sentence to the generic sentence structure of [\textit{Subject} - \textit{Verb} - \textit{Adverbial/Complement}]~\cite{sentencePatterns08}, where  \textit{Subject} represents the entity and \textit{Verb} is the relation type we are interested in (e.g.

### 2013-11-07 paper/flairs27/content/introduction.tex
updated introduction, integrated milenko's comments

@@
 Reducing latency keeps WP relevant and helpful to its users.
-Given an entity page, such as \texttt{wiki/Boris\_Berezovsky\_(businessman)}\footnote{http://en.wikipedia.org/wiki/Boris\_Berezovsky\_(businessman)},
+Given an entity page, such as \textsl{wiki/Boris\_Berezovsky\_(businessman)}\footnote{http://en.wikipedia.org/wiki/Boris\_Berezovsky\_(businessman)},
 possible citations may come from a variety of sources.
@@
 This task involves processing large sets of information to determine which facts may contain references to a WP entity. 
-This problem becomes increasingly more difficult when we look to extract specific relevant task from
+This problem becomes increasingly more difficult when we look to extract relevant facts from
 each document.
@@
 
-Discovering facts from the Internet that are relevant and citable to the WP entities is a non-trivial task.
-For example, take a sentence from the Internet:
+Discovering facts across the Internet that are relevant and citable to the WP entities is a non-trivial task.
+%For example, a take a sentence from the Internet:
+Here we produce an example sentence from a new website:
 
@@
 %country went through privatisation of state property and `robber capitalism', and passed away March 2013.}
-``\texttt{Boris Berezovsky, who made his fortune in Russia in the 1990s, passed away March 2013.}''
+``{\small \texttt{Boris Berezovsky, who made his fortune in Russia in the 1990s, passed away March 2013.}}''
 
@@
 Any extraction needs to take this into account and employ a viable distinguishing policy (entity resolution).
-Then, we match the sentence to find a topic (slot) such as \textit{DateOfDeath} valued at March 2013.
+Then, we match the sentence to find a topic such as \textit{DateOfDeath} valued at \textit{March 2013}.
 Each of these operations is expensive so an intelligent efficient framework is necessary to execute these operations at web scale.
@@
 
-In this paper we develop an efficient query-driven slot extraction for given WP entities from a time oriented stream of Internet documents.
-Slot or fact extraction is formally defined as follows: match each sentence to the generic sentence structure of [\textit{Subject} - \textit{Verb} - \textit{Adverbial/Complement}]~\cite{sentencePatterns08}, where  \textit{Subject} represents the entity and \textit{Verb} is the relation type we are interested in (e.g.
+In this paper we develop an efficient query-driven slot extraction for given WP entities from a time oriented document stream.
+Fact or slot extraction is defined as follows: match each sentence to the generic sentence structure of [\textit{subject} - \textit{verb} - \textit{adverbial/complement}]~\cite{sentencePatterns08}, where  \textit{subject} represents the entity and \textit{verb} is the relation type (slot) we are interested in (e.g.
 Table~\ref{table:slotNameOntology}).
-If a sentence matches these two components of the sentence pattern, \textit{Adverbial/Complement} would be returned as the other side of the relation (which we refer to as slot value).
-Slot value extraction is a challenging task in current state of the art Knowledge Bases (KB).
-Popular graphical KB such as Freebase or DBPedia keep data in structured format where entities are connected via relationships (\textit{Verb}) and the associated attributes (\textit{Adverbial/Compelement}).
-Our system can be used to automatically populate such KBs or even fill-in the information boxes at entity WP page itself.
+The third component, \textit{adverbial/complement}, represents the value of the enity slot.
+In our example sentence, the entity of the sentence is \textit{Boris Berezovsky} and the slot we extract is
+\textit{DateOfDeath} with a slot valye of \text{March 2013}.
+
+%Slot extraction is a challenging task in current state of the art Knowledge Bases (KB).
+%Popular graphical KB such as Freebase or DBPedia keep data in structured format where entities
+%are connected via relationships (slots) and the associated attributes
+%(slot values).
+%Our system can be used as an aid to recommend factual updates to such KBs.
 
@@
 First, we pre-process the data and build models representing the WP query entities.
-Next, we use the models to filter a stream of documents so they only contain candidate citations.
+Next, we use the models to filter a large stream of documents so they only contain candidate citations.
 Lastly, we processes sentences from candidate extractions and return slot values. 
@@
 \begin{itemize}[noitemsep,nolistsep]
-\item Introduce a method to build models of name variations
-\item Built a system to filter a large amount of diverse documents
-\item Extract, infer and filter entity-slot-value triples of information to be added to KB 
+\item Introduce a method to build models of WP name variations (Section~\ref{});
+\item Built a system to filter a large amount of diverse documents using a natural language processing rule-based extraction system (Section~\ref{});
+\item Extract, infer and filter entity-slot-value triples of information to be added to KB (Section~\ref{}).
 \end{itemize}

### 2013-11-07 paper/flairs27/content/system.tex
Updated the title and the System and Model section

@@
 
-To walk you through the steps we take, assume we only care about on single WP entity, the first step is to extract aliases of the entity.
-We use several approaches to get as many viable aliases as possible.
-Then we look into the stream of content that is being generated on the internet, apply two levels of filtering to finally end up with the documents are central to that entity.
-To extract the relevnat slot values we perform pattern matching in each sentence or coreferent sentence to see if we can find a match.
-As a match is found from the content of the sentence to the patterns that we have generated regarding slot name, the associated slot value is extracted as a final result.
+If we are looking to discover facts for a single WP entity, the first step is to extract aliases of the entity.
+%We use several approaches to get as many viable aliases as possible.
+We extract several name variations from the Wikipedia api and from the WP entity page.
+Also, if the entity type is \textit{person} we can change the order of user names to increase coverage (e.g. `Boris Berezovsky' $\rightarrow$ `Berezovsky, Boris').
+Next, we iterator over documents in the stream and filter out all document that are not central to the entity.
+To extract relevant facts we perform pattern matching in each sentence that matches the entity based on a dictionary
+of patterns.
+If the sentence can activate on of the patterns in the dictionary we emit this sentence as a candidate contribution
+to the WP entity.
+With the candidate set, we infer new facts from the set and clean up the set
+by removing the set that violate a list of constraints such as duplicates.
+Lastly, we try to infer a new set of facts based on a list of rules.
+
+%As a match is found from the content of the sentence to the patterns that we have generated regarding slot name, the associated slot value is extracted as a final result.
 
@@
 
-\subsection{Model}
+\subsection{Entity Model}
 
-We use Wikipedia API to get these aliases automatically.
-This is done by retrieving backlink references (redirects of a wiki entity), e.g.
-William Henry Gates is an alias for Bill Gates in WP as a backlink reference.
-Unfortunately this is not good enough and to enhance recall we need more aliases.
-To have better use of a wiki page we parse HTML DOM of the page, then use regular expressions to extract the bold phrases of the first paragraph as alias of the actual entity.
-Based on our observation this is a very accurate heuristic and provides us with lots of famous aliases of the entities.
-As an example of when this might not wirk, is that there might be occasions that some other topic is written in bold typesetting in the first paraph apart from the entity aliases itself but these are very rare.
+We use Wikipedia API to automatically retrieve aliases. 
+The API allows us to requests pages that redirect users to an entity page.
+For example, if a WP user tries to access the \textsl{William Henry Gates} they are sent to the page for 
+\textsl{Bill Gates} therefore we treat these two names as aliases. 
+To extract more aliases  is we parse the HTML source of a WP entity page.
+Then using regular expressions we extract the bold phrases of the initial paragraph as aliases.
+Based on our observation this is a very accurate method and it provides several entities of 
+WP entities \ceg{Do we know how many additional aliases this method provides?}.
+\ceg{Do you want to give a more concrete example of how this might now work? It may be TMI.}
+%As an example of when this might not wirk, is that there might be occasions that some other topic is written in bold typesetting in the first paraph apart from the entity aliases itself but these are very rare.
 
-Once aliases are available we pass them through rules of generating proper name orders which will produce various forms of writing a name.
-As a basic example Bill Gates can be written as Gates, Bill also.
-This will allow the system to capture various notation forms of aliases.
-We refer to this part as \textit{Alias Order Generator}.
+We pass the full set of \textit{person} entities through rules for generating proper name orders.
+This module produces various forms of writing entity names and titles.
+For example, \textsl{Bill Gates} can be written as \textsl{Gates, Bill}.
+This allows the system to capture various notation forms of aliases that appear in text documents.
+%We refer to this part as \textit{Alias Order Generator}.
 

### 2013-11-07 paper/flairs27/content/system.tex
updated the wikipedia citation section

@@
 \subsection{Wikipedia Citation}
-The main goal of this section is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page.
-We perform exact string matching and treat all the documents that mention an entity equally likely to be citable.
-One of the reasons for this is that there have been observations of how non-mentioning documents have a low chance of being citable in Wikipedia \cite{JFrank12}.
-So we take on that and ignore non-citing documents.
+The goal of this section is to use the models created to discover a set of documents that are relevant to the WP entity.
+%We perform exact string matching and treat all the documents that mention an entity equally likely to be citable.
+As a stream of documents come in we first perform a string match between the model aliases and document text. 
+We use this technique as a first filter with confidence because previous work has stated non-mentioning
+documents have a low chance of being citable in Wikipedia \cite{JFrank12}.
+Given our large number of aliases we can be confident if an alias does not appear in a document it does not need to be cited.
 
-Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textit{Document Chunks Indexer} and \textit{Document Filter}.
-The purpose of these indexes is to reduce I/O cost while generating slot values for various entities.
-Document chunks Indexer will generate indexes of the chunk files that contain a mention of any of the desired entities.
-Document Filter on the other hand will index documents that contain a mention of a given entity respectively.
-This two level indexing will eliminate the need to process each and every chunk file/document for every entity.
-The reason for splitting this task into two steps is that not all chunk files contain any mention of the entities and we want to get rid of them as soon as possible.
-Document Chunks Indexer which discards non-mentioning chunk files and will stop further processing a chunk file as soon as it finds a mention there.
-Each chunk file can contain up to thousands of documents which can be so time consuming if we were to process them in our Java base code.
-Processing StreamItems on the other hand is done in Java with ideas in mind for later on extensibility by adding other Java libraries.
+Our stream system receives documents in the from of chunk files.
+Each chunk file contains thousands of documents.
+This corpus of documents is processed by a two-layer filter system referred to as \textit{Document Chunk Filter} and \textit{Document Filter}.
+The purpose of these filters is to reduce I/O cost while generating slot values for various entities.
+Document Chunk Filter removes the chunk files that do not contain a mention of any of the desired entities.
+Each chunk file may contain thousands of documents --- each document is expensive to process.
+The Document Filter removes documents that do not contain a mention of an  entity.
+This two-level filter allows us to perform detailed slower processing over a smaller set of documents.
+Not all chunk files contain mention of the entities so filtering out large chunk files early saves no I/O and processing.
+Document Chunk Filter discards non-mentioning chunk files and promotes chunk files as soon as an entity mention is found.
+%Processing StreamItems on the other hand is done in Java with ideas in mind for later on extensibility by adding other Java libraries.
+The document filter additionally notes the sentences that contain entity mentions.
+This data is passed to the Slot Filling system.
 

### 2013-11-08 paper/flairs27/content/system.tex
add chamhes up the old formal patterns section

@@
 %\ceg{See the previous note.}
-The purpose of SSF is to extract proper values for relations of interest, which can be found in Table~\ref{table:slotNameOntology}.
-In Figure~\ref{fig:system} we refer to this as \textit{Slot Filling}.
+Streaming Slot Filling (SSF) extracts fact values from sentences according to a list of pattern.
+Table~\ref{table:slotNameOntology} list the slot relationships that we looks to extract.
+In Figure~\ref{fig:system} we refer to this task as \textit{Slot Filling}.
 
-Slot filling is done by pattern matching documents with manually produced patterns for slots of interest.
-The way we do this is by observing a sentence that has a mention of the entity or one of its coreferences.
-An anchor word in the sentence related to the slot name is located and we match either left or right of the anchor word for potential slot values.
+%Slot filling is done by pattern matching documents with manually produced patterns for slots of interest.
+%The way we do this is by observing a sentence that has a mention of the entity or one of its coreference.
+%An anchor word in the sentence related to the slot name is located and we match either left or right of
+%the anchor word for potential slot values.
 
@@
 % cropped pdf created using $ pdfcrop Pattern.pdf
-\vspace*{-.1in} \caption{Pattern Matching with Slot Value on the Right Side of Entity. }\label{fig:pattern}
+\vspace*{-.1in} \caption{Pattern Matching with Slot Value on the Right Side of Entity.}\label{fig:pattern}
 \vspace*{-.2in}
@@
 
-In the data set, we are given a date range of documents as training data. Instead of building a classifier we use pattern matching methods to find corresponding slot values for entities. 
-Pattern matching is simple to manipulate results and implement. Additionally, a classifier approach is more difficult to evaluate and explain results due to the lack of proper training data.
+%In the data set, we are given a date range of documents as training data. Instead of building a classifier we use pattern matching methods to find corresponding slot values for entities. 
+%Pattern matching is simple to manipulate results and implement. Additionally, a classifier approach is more difficult to evaluate and explain results due to the lack of proper training data.
 
-With the documents indexes generated by the Wikipedia Citation, we first fetch the sentences containing entites by using alias names and coreference information provided by Lingpipe tags\footnote{Lingpipe (available in the dataset) provides entity tags and in-document correference.
-http://alias-i.com/lingpipe/}.
-Then use these senteces to match patterns and when patterns matched, generate SSF results.
+SSF reads documents filtered by the Wikipedia Citation step and fetches and tags sentences containing WP entities.
+All entities are extracted from the document using a natural language processing
+tool\footnote{Lingpipe (available in the dataset) provides entity tags
+and in-document coreference. \url{http://alias-i.com/lingpipe/}}.
+In the next section, we describe how WP entities are matched against the set of patterns.
+Following, we discuss out approach to inference over the extracted facts.
 
@@
 
-\textbf{Format of Patterns.} A pattern is defined as a record representing knowledge going to be added to a KB.
+%\textbf{Format of Patterns.}
+A pattern is as a record representing knowledge going to be added to a WP entity.
 A pattern $\mathcal{P}$ is represented as a five-tuple $\mathcal{P} = \langle p_1, p_2, p_3, p_4, p_5 \rangle$.

### 2013-11-08 paper/flairs27/content/system.tex
rewrote up to the pattern type section.

@@
 
-\begin{figure}
-\centering
-%\includegraphics[width=4.5in]{./images/system.eps}
-%\includegraphics[width=6in]{./images/Pattern.eps}
-%\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
-\includegraphics[width = 13cm]{./images/Pattern-crop.pdf}
-% cropped pdf created using $ pdfcrop Pattern.pdf
-\vspace*{-.1in} \caption{Pattern Matching with Slot Value on the Right Side of Entity.}\label{fig:pattern}
-\vspace*{-.2in}
-\end{figure}
-
 %In the data set, we are given a date range of documents as training data. Instead of building a classifier we use pattern matching methods to find corresponding slot values for entities. 
@@
   \textbf{List of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
-  \textbf{List of streamitems containing entities $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
+  \textbf{List of documents containing entities $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
 
@@
     \IF{Contains($sentence$, $entity$)}
-          %%\IF{check\_pattern(sentence, pattern)}
     \FOR{$pattern \in P $ suitable for $entity$} 
@@
 The first value, $p_1$ represents the type of entity.
-These entity types are in the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC} represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER} represents a person.
-\texttt{FAC}, \texttt{ORG} and \texttt{PER} are Lingpipe entity types.
+These entity types are in the set $\{\text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC} represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER} represents a person.
+%\texttt{FAC}, \texttt{ORG} and \texttt{PER} are Lingpipe entity types.
 The $p_2$ represents a slot name.
 A list of slot names is present in Table~\ref{table:slotNameOntology}.
-The third element $p_3$ is the pattern content.
-This is a string found in the sentence.
-The extractor looks for this exact string or pattern in a sentence.
+The third element $p_3$ is the pattern content --- 
+a string found in the sentence that identifies a slot name.
+The extractor looks specifically for a pattern content.
 The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in $p_4$ to explore sentence.
-The final element $p_5$ represent the slot value of a pattern.
-This %When we match one pattern, we match all the
+The final element $p_5$ represents the slot value of a pattern. 
+%When we match one pattern, we match all the 
 %fields except the third field, which is extracted as the final result.
-The type of slot value may be the entity type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP\footnote{OpenNLP was used for part of speech tagging.
-http://opennlp.apache.org/‎} or a hard-coded phrase.
-For these three kinds of patterns, we implement them in different
-ways accordingly. Next, we explain the patterns with more details, an example of which can be found in Figure~\ref{fig:pattern}.
+The type of slot value may be the entity type labeled by the named entity extractor,
+a noun phrase (\texttt{NP}) tagged by a part of speech tagger\footnote{OpenNLP was used for part of speech tagging. \url{http://opennlp.apache.org/}} or a phrase described in the pattern list.
+%For these three kinds of patterns, we implement them in different ways accordingly.
 
-\textbf{Types of patterns}
+%Next, we explain the patterns with more details, an example of which can be found in Figure~\ref{fig:pattern}. 
+Figure~\ref{fig:pattern} contains the example sentence from the introduction labeled by the rule engine.
+
+%\textbf{Types of patterns}
 There are three types of patterns distinguished by different types of slot values in the patterns.
-The matching methods using these three types of patterns are implememented according to the different information and structures of slot values.
+The matching methods using these three types of patterns are implemented according to the different structures of slot values.
 
-\textbf{Type I.} This pattern type is driven by the slot value type, a pattern tagged by Lingpipe.
-For example, pattern $\langle$\texttt{PER, FounderOf, \textit{founder}, right, ORG}$\rangle$.
-\texttt{PER} means
-that the entity we are finding slot values for a PER entity; \texttt{FounderOf} means this is a pattern for FounderOf slot.
-\textit{founder} is the anchor word we are match in a sentence; \texttt{right} means that we are going to the right part of the sentence to match the pattern and find the slot value; ORG means the slot value should be a ORG entity.
+\begin{figure}
+\centering
+%\includegraphics[width=4.5in]{./images/system.eps}
+%\includegraphics[width=6in]{./images/Pattern.eps}
+%\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
+\includegraphics[width = 13cm]{./images/Pattern-crop.pdf}
+% cropped pdf created using $ pdfcrop Pattern.pdf
+\vspace*{-.1in}
+\caption{Pattern matching for rule evaluation. The slot value is on the right side of the 
+entity. The pattern context discovered is `passed away' with a value of `March 2013'. }\label{fig:pattern}
+\vspace*{-.2in}
+\end{figure}
 
-\textbf{Type II.} This pattern type is unique because it only looks for a slot value tagged as noun phrase (NP) by OpenNLP.\@ For example, pattern $\langle$\texttt{PER, AwardsWon, \textit{awarded}, right, NP}$\rangle$.
-This pattern can be interpreted as that we are looking for a noun phrase after the \textit{awarded} since that noun phrase may represent an award.
-Titles and awards are usually not the Lingpipe entities, hence the use of the OpenNLP noun phrase chunker to fetch the noun phrases.
+\textbf{Type I.} This pattern type is driven by the entity type.
+For example, in pattern $\langle$\texttt{PER, FounderOf, \textit{founder}, right, ORG}$\rangle$ the \texttt{PER} 
+tag means the entity we are finding slot values for a PER entity;
+\texttt{FounderOf} means this is a pattern for FounderOf slot.
+\textit{founder} is the anchor word we are match in a sentence;
+\texttt{right} means that we are going to the right part of the sentence to match the pattern and find the slot value;
+ORG means the slot value should be a ORG entity to the right of the entity.
 
-\textbf{Type III.} Some relations are best discovered by hard coding the slot values.
+\textbf{Type II.} This pattern type, after finding a matching pattern content, looks for a noun phrase (NP)
+that is representative of the slot value.
+For example, pattern $\langle$\texttt{PER, AwardsWon, \textit{awarded}, right, NP}$\rangle$
+is looking for a noun phrase after the \textit{awarded} that may represent an award.
+Titles and awards are not named entity tagged hence the use of the part of speech tagger to fetch the noun phrases.
+
+\textbf{Type III.} These type of facts are best discovered by hard coding the slot values.
 Examples of these include time phrases: $\langle$\texttt{PER, DateOfDeath, \textit{died}, right, \textit{last night}}$\rangle$.
-In this pattern, \textit{last night} means we are looking for exactly the phrase \textit{last night} to the right of \textit{died}.
-This pattern is inspired by the intuition that in news articles, people often mention that somebody died last night instead of mentioning the accurate date information and Lingpipe tends not to tag phrases like \textit{last night} as a DATE entity.
+In this pattern, the phrase \textit{last night} is exactly searched in the text {last night} to the right of the term \textit{died}.
+This intuition behind this pattern is in news articles that report events in the past relative to the article. 
+For example, an article will mention that  
+a person died `last night' instead of mentioning precise date-time information.
+Additionally, part of speech taggers and and name entity extractors did not label these terms such as 
+\textit{last night} as a DATE entity.
 

### 2013-11-09 paper/flairs27/content/system.tex
Updated the constraints section.

@@
 a person died `last night' instead of mentioning precise date-time information.
-Additionally, part of speech taggers and and name entity extractors did not label these terms such as 
+Additionally, part of speech taggers and name entity extractors did not label these terms such as 
 \textit{last night} as a DATE entity.
 
-\subsubsection{Constraints - Inference}
+\subsubsection{Constraints and Inference}\ceg{what specifically about the algorithm causes duplicates and errors?}
 
-The output of streaming slot value extraction is noisy.
+The fact extractions match patterns that are general and highly susceptible to noisy.
 The data contains duplicates and incorrect extractions.
-We can define rules to sanitize the output only using the information present at this stage.
-The input file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy.
+We define rules to read ordered sets of facts to sanitize the output.
+The input is processed in time order, in a tuple-at-a-time fashion to allow rules to discover noisy slots 
+that appears in close proximity.
+%We found that the proximity of an extraction has a high correlation on the presence of duplicates. 
 We define two classes of rules: \textit{deduplication} and \textit{inference} rules.
@@
 Duplicates can be present in a window of rows; we use a window size of 2 meaning we only be adjacent rows.
-Two rows are duplicates if they have the same exact extraction, or if the rows have the same slot name and a similar slot value or if the extracted sentence for a particular slot types come from the same sentence.
+Two rows are duplicates if they have the same exact extraction or if the rows have the same slot name and a similar slot value or if the extracted sentence for a particular slot types come from the same sentence.
 
@@
 A safe assumption is these slot names are biconditional logical connectives with the entities and slot values.
-Therefore, we can express a rule ``X FounderOf Y'' equals ``Y FoundedBy X'' where X and Y are single unique entities.
+Therefore, we can express a rule ``$X$ FounderOf $Y$'' $\leftrightarrow$ ``$Y$ FoundedBy $X$'' where $X$ and $Y$ are single unique entities.
 Additionally, we found that the slot names ``Contact\_Meet\_PlaceTime'' could be inferred as ``Contact\_Meet\_Entity'' if the Entity was a FAC and the extracted sentence contained an additional ORG/FAC tag.
-We also remove erronious slots that have extractions that are several pages in length or tool small.
-Errors of extracting long sentences can typically be
-attributed to poor sentence parsing of web documents.
-We have some valid ``small'' extractions.
-For example a comma may separate a name and a title (e.g.
-``John, Professor at MIT'').
+We also remove erroneous slots that have extractions that are thousands of characters in length or tool small.
+Errors of extracting long sentences can typically be attributed to poor sentence parsing of web documents.
+We have some valid ``small'' extractions. For example, a comma may separate a name and a title (e.g. ``John, Professor at MIT'').
 But such extraction rules can be particularly noisy, so we check to see if the extracted values have good entity values.

### 2013-11-10 paper/flairs27/content/results.tex
merge

@@
 \label{table:finalresultrecall}
-\begin{tabular}{|l|c|c|}
+\begin{tabular}{|l|p{13mm}|p{22mm}|}
 \hline 
- \textbf{Slot Name} & \textbf{Instances Found} & \textbf{Entity Coverage} \\ 
+ \textbf{Slot Name} & \textbf{Instances Found} & \textbf{Entity \hspace{5 mm} Coverage} \\ 
 \hline 
@@
 CauseOfDeath & 0 & 0 \\ \hline 
-{\tiny Contact\_Meet\_Entity} & 191 & 8 \\ \hline 
-{\tiny Contact\_Meet\_PlaceTime} & 5974 & 109 \\ \hline 
+Contact\_Meet\_Entity & 191 & 8 \\ \hline 
+Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
 DateOfDeath & 87 & 14 \\ \hline 
@@
 \label{table:finalresultaccuracy}
-\begin{tabular}{|l|c|c|p{13mm}|}
+\begin{tabular}{|l|p{10mm}|p{10mm}|p{11mm}|}
 \hline 
@@
 CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
-{\tiny Contact\_Meet\_Entity} & 21\% & 42\% & 37\%  \\ \hline 
-{\tiny Contact\_Meet\_PlaceTime} & 5\% & 20\% & 85\%  \\ \hline 
+Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 
+Contact\_Meet\_PlaceTime & 5\% & 20\% & 85\%  \\ \hline 
 DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 

### 2013-11-11 paper/flairs27/content/system.tex
Minor fixes

@@
 Based on our observation this is a very accurate method and it provides several entities of 
-WP entities \ceg{Do we know how many additional aliases this method provides?}.
-\ceg{Do you want to give a more concrete example of how this might now work? It may be TMI.}
+WP with more inline aliases from the wiki page itself.
+As an example, for `Boris Berezovski' which was mentioned early-on, there is an alias of `Boris Abramovich Berezovsky' given in bold in the wiki page which will be obtained via thi method.
+
+%\ceg{Do we know how many additional aliases this method provides?}.
+%\ceg{Do you want to give a more concrete example of how this might now work? It may be TMI.}
 %As an example of when this might not wirk, is that there might be occasions that some other topic is written in bold typesetting in the first paraph apart from the entity aliases itself but these are very rare.
@@
 %\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
-\includegraphics[width = 13cm]{./images/Pattern-crop.pdf}
+\includegraphics[width = 11cm]{./images/Pattern-crop.pdf}
 % cropped pdf created using $ pdfcrop Pattern.pdf
@@
 
-\subsubsection{Constraints and Inference}\ceg{what specifically about the algorithm causes duplicates and errors?}
+\subsubsection{Constraints and Inference}\ceg{what specifically about the algorithm causes duplicates and errors?
+--- I asked Yang to elaborate on this as he is more familiar but still not sure what's causing those issues}
 

### 2013-11-11 paper/flairs27/content/discussion.tex

@@
 
-We noticed that some tools that claim to be performant for using the hardware capabilities at hand sometimes don't really work as claimed and you should not always rely on one without a thorough A/B testing of performance which we ended up in generating our in-house system for processing the corpus and generating the index.
+We noticed that some tools that claim to be performant for using the hardware capabilities at hand sometimes don't really work as claimed and you should not always rely on one without a thorough A/B testing of performance which we ended up in generating our in-house system for processing the corpus and passing through the filter.
 Furthermore, on extracting slot values, pattern matching might not be the best options but definitely can produce some good results at hand.

### 2013-11-11 paper/flairs27/content/results.tex
made many changes and rewrites. Just need to do the discussion section

@@
 
-%\ceg{We can add data on the total document size, The %number of each document type.  } 
- The purpose of evaluation is to measure the effectiveness of extracting slot values for various entities, metrics such as precision and recall would be considered.
-We perform random samplings to extract these.
+We evaluate the effectiveness of extracting slot values for 139 entities.
+We look at the baseline coverage for entities and slot names we present in a 500M page snapshot of the English web.
+We estimate the precision and recall of our extractions over several extracted fact.
+
 Our system was developed on a 32-core server described in Table~\ref{table:serverspec}.
-The corpus is a snapshot of the web in English.
-Each document is annotated using lingpipe and is called StreamItem, a bundle of StreamItems are put together and serialized as Apache Thrift objects, then compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
-The total size of the data after XZ compression and GPG encryption is 4.5TB and just over 500M StreamItems \cite{s3}.
-Data is stored in directories the naming of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am) until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952 date-hour combinations.
-The first four months of data (October 2011 - February 2012) is for training purposes, and we use this portion to lookup sample lines and for system parameter settings purposes.
-This corpora consists of various media types the distribution of which can be found in Table~\ref{table:documentsDist}.
-To have a sense of the scale of objects and compression as an example a 6mb gpg.xz files would become 45 mb thrift objects which can contain a couple of thousand StreamItems depending on their size.
-Some of the documents have null values for their annotation fields.
+Each document is annotated using a name entity extraction and in document coreference.
+A bundle of documents are serialized into chunks and encrypted.
+The total size of the data after compression and encryption is 4.5TB~\footnote{TREC Knowledge base acceleration stream corpus is available  \url{http://aws-publicdatasets.s3.amazonaws.com/trec/kba/index.html}}.
+Data is ordered into 11952 date-hour buckets ranged from 2011-10-05-00 (5th of October 2011, 12am)
+until 2013-02-13-23 (13th of Feburary 2013, 11pm).
+The first four months of data (October 2011 - February 2012) is for training purposes, 
+and we use this portion for rule and pattern creation and tuning.
+The data set contains text from several web page types as listed in Table~\ref{table:documentsDist}.
+%To have a sense of the scale of objects and compression as an example a 6mb gpg.xz files would become 45 mb thrift objects which can contain a couple of thousand StreamItems depending on their size.
+%Some of the documents have null values for their annotation fields.
 The source code of our system is stored as an open source project where enthusiasts can also contribute to \cite{github}, also the relevant discussion mailing list is accessible here \cite{googlegroups}.
 
-\begin{table}[b]
-\caption{Document Chunks Distribution }
-\centering
-\label{table:documentsDist}
-
-\begin{tabular}{|l|c|c|}
-\hline 
-\textbf{\# of Documents} & \textbf{Document Type} & \textbf{Slots Found}\\ 
-\hline 
-	Arxiv & 10988 & \\ \hline
- Classified & 34887 & \\ \hline
- Forum & 77674 & \\ \hline
- Linking & 12947 & \\ \hline
- Mainstream News & 141936 & \\ \hline
- Memetracker & 4137 & \\ \hline
- News & 280629 & \\ \hline
- Review & 6347 & \\ \hline
- 	 Social & 688848 & \\ \hline
- Weblog & 740987 & \\ \hline
-
-\hline 
-\end{tabular} 
-\end{table}
-
-We have 172 extraction patterns covering each slot-name/entity-type combinations.
-Our final submission was named \textit{submission\_infer}.
-Our results are as follows: Document extraction using query entity matching with aliases, sentence extraction using alias matching and co-reference.
-Slot extraction using patterns, NER tags and NP tags.
-158,052 documents with query entities, 17885 unique extracted slot values for 8 slots and 139 entities, 4 slots and 31 entities missing.
-
-On the performance of our initial submission run we performed random sampling via two processes, the results of which are according to Table~\ref{table:initialresult}.
-You can view that we have had an accuracy of around 55\%, and about 15\% wrong entity identified and 30\% incorrect value extracted across all entities and slot types.
-Most of our issues for this submission were regarding poor slot value extraction patterns and incomplete aliases whih were tried to be mtigated later on.
-For our final submission, we provide a more detailed statistics, which has been elaborated in Table~\ref{table:finalresultrecall} and Table~\ref{table:finalresultaccuracy}.
-Table~\ref{table:finalresultrecall} shows the extent of search outreach for
-each slot name.
-You can see that \textit{Affiliate} has been the slot name with highest hits and \textit{CauseOfDeath} our lowest hit with 0 instances found matching our patterns, after that \textit{AwardsWon} has been the next with 38 instances found.
-Affiliate is a very generic term and extracting real affiliates can be quite challenging using the extraction patterns provided.
-This can lead to noisy results.
-On the other hand for more precise terms our accuracy increases but we have less recall.
-Table~\ref{table:finalresultaccuracy} addresses the relative accuracy measure per slot value.
-There you can view that we have had the highest accuracy of 63.6\% for \textit{AssociateOf} and the lowest of 1\% - 5\%  for \textit{Affiliate}, \textit{Contact\_Meet\_PlaceTime} and \textit{EmployeeOf}.
-
 \begin{table}
-\caption{Benchmark Server Specifications }
+\caption{Benchmark Server Specifications}
 \centering
@@
 \begin{table}
-\caption{Initial Performance Measure }
+\caption{Document Chunks Distribution }
+\centering
+\label{table:documentsDist}
+
+\begin{tabular}{|l|l|c|}
+\hline 
+\textbf{Document Type} & \textbf{\# of Documents} &  \textbf{Slots Found}\\ 
+\hline 
+Arxiv & 10988 & \\ \hline
+ Classified & 34887 & \\ \hline
+ Forum & 77674 & \\ \hline
+ Linking & 12947 & \\ \hline
+ Mainstream News & 141936 & \\ \hline
+ Memetracker & 4137 & \\ \hline
+ News & 280629 & \\ \hline
+ Review & 6347 & \\ \hline
+ Social & 688848 & \\ \hline
+ Weblog & 740987 & \\ \hline
+\hline 
+\end{tabular} 
+\end{table}
+
+We develop 172 extraction patterns covering each slot-name/entity-type combinations.
+%Our final submission was named \textit{submission\_infer}. 
+%Our results are as follows: Document extraction using query entity matching with aliases, sentence extraction using alias matching and co-reference.
+%Slot extraction using patterns, NER tags and NP tags.
+Out of the 500 M documents  and 139 entities we found 158,052 documents containing query entities, 17,885 unique extracted slot values for 8 different slots.
+We did not get any results from 31 entities missing and 4 slots.
+
+%On the performance of our initial submission run we performed random sampling via two processes, the results of which are according to Table~\ref{table:initialresult}.
+In Table~\ref{table:initialresult} we performed two samples of a baseline submission and estimate the correctness of the extraction.
+\ceg{Add here how the baseline is different from the final submission}
+We our methods produced an accuracies of  54\% and 55\%.
+We classify the errors into two sets, an incorrect entities and incorrect extractions.
+We found 15\% and 17\% incorrect entity names and we identified 27\% and 30\% incorrect value extracted across all entities and slot types.
+The majority of errors were regarding poor slot value extraction patterns and incomplete aliases.
+
+\begin{table}
+\caption{Sampled accuracy of the results of the extracted facts.}
 \centering
@@
 
-\begin{tabular}{ | c | c | p{2cm} | p{13mm} |}
+\begin{tabular}{| c | c | p{2cm} | p{13mm} |}
 \hline 
@@
 
-\begin{table}[h]
+\ceg{Probably should add again here a reason why our method is different from the baseline.}
+Using our methods, we provide we provide more detailed statistics, as displayed in Table~\ref{table:finalresultrecall} and Table~\ref{table:finalresultaccuracy}.
+Table~\ref{table:finalresultrecall} shows the recall for each slot name. \ceg{(define `entity coverage' here)}
+The slot name \textit{Affiliate} has was extracted the most number of times and \textit{CauseOfDeath} was extracted the
+fewest with 0 instances found matching the pattern list. \textit{AwardsWon} contained the next fewest with 38 instances found. 
+Affiliate is a generic slot name, using patterns to extract these relationships is difficult because almost any
+two items can be affiliated in some way.
+\ceg{Define the affiliate slot name.}
+Our patterns for this relationship led to noisy results.
+On the other hand for more precise slot names our accuracy increases but we have less recall.
+Table~\ref{table:finalresultaccuracy} addresses the relative accuracy measure per slot value.
+\textit{AssociateOf} has the highest accuracy with 63.6\% and  \textit{Affiliate}, \textit{Contact\_Meet\_PlaceTime} and \textit{EmployeeOf} have the lowest with lowest of 1\%, 1\% and 5\% accuracy respectively.
 
+\begin{table}
 \caption{Recall Measure: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}

### 2013-11-11 paper/flairs27/paper.tex
More cleanup
Updated the title and the System and Model section
Minor fixes
made many changes and rewrites. Just need to do the discussion section

@@
 \usepackage{algorithm}
-\usepackage{algorithmic}
+\usepackage[noend]{algorithmic} % noend will ksip printing end of blocks
 
@@
 
-\title{Central Slot Value Extraction from Internet for Wikipedia Entities}
+\title{Streaming Slot-Value Extraction for Wikipedia Entities at Web-Scale}
 
@@
 
-\input{content/implementation.tex}
+%\input{content/implementation.tex}
 
@@
 
-\input{content/conclusion.tex}
+%\input{content/conclusion.tex}
 
 \section*{Acknowledgements}
-Christan Grant is funded by a National Science Foundation Graduate Research
-Fellowship under Grant No. DGE-0802270.
+We would like to thank John Frank and TREC for providing the data set.
+Christan Grant is funded by a National Science Foundation Graduate Research Fellowship under Grant No. DGE-0802270.
 
@@
 
-\input{content/appendix.tex}
+%\input{content/appendix.tex}
 

### 2013-11-12 paper/flairs27/content/discussion.tex
Worked on the discussion version of the paper, added lots of comments

--- 2013-11-06 paper/flairs27/content/discussion.tex
@@
 
-Table~\ref{table:finalresultrecall} show a varied distribution of extracted slot names.
+Table~\ref{table:finalresultrecall} shows the distribution of extracted slot names.
+The number of extraction between slot names vary greatly.
 Some slots naturally have more results than other slots.
-For example, AssociateOf and Affiliate have more slot values than DateOfDeath and CauseOfDeath, since there are only so few entities that are deceased.
-Also, some patterns are more general causing more extractions.
-For example, for Affiliate, we use \textit{and}, \textit{with} as anchor words.
-These words are more common than \textit{dead} or \textit{died} or \textit{founded} in other patterns.
+For example DateOfDeath and CauseOfDeath have some of the fewest entities because only a few entities are deceased.
+Some patterns use common words as as part of their patterns causing more extractions.
+For example, Affiliate looks for common words like  \textit{and} and  \textit{with} as part of the pattern content.
+These words are more common than \textit{dead}, \textit{died} or \textit{founded} in other patterns.
 
-As part of future work regarding enhancing precision, we can focus on fixing the wrong entities found, remove noisy tags by the Lingpipe or use more accurate NLP taggers such as Stanford NLP (Due to the fact that Stanford NLP is very slow we avoided using it, as due to speed its use was out of question) and finally use better patterns to enahnce results matched by the patterns.
-On the other hand to increase recall we need to find better aliases and go for more resources to discover other ways that an entity might be addressed (e.g.
-twitter id, website, etc), add powerful patterns that can capture more cases of slot values.
+%As part of future work regarding enhancing precision, we can focus on fixing the wrong entities found, remove noisy tags by the Lingpipe or use more accurate NLP taggers such as Stanford NLP (Due to the fact that Stanford NLP is very slow we avoided using it, as due to speed its use was out of question) and finally use better patterns to enahnce results matched by the patterns.
+%On the other hand to increase recall we need to find better aliases and go for more resources to discover other ways that an entity might be addressed (e.g.\ twitter id, website, etc), add powerful patterns that can capture more cases of slot values.
 We would also use entity resolution methods and other advanced methods to improve
-the accuracy and recall of entity extraction part.
+%the accuracy and recall of entity extraction part.
 
-For slot extraction, to improve the performance, we need: 1) Using multi-class classifiers instead of pattern matching method to extract slot values in order to increase both recall and accuracy for slots ``Affiliate'', ``AssociateOf'', ``FounderOf'', ``EmployeeOf'', ``FoundedBy'', ``TopMembers'', ``Contact\_Meet\_Entity'' and so on.
+%For slot extraction, to improve the performance, we need: 1) Using multi-class classifiers instead of pattern matching method to extract slot values in order to increase both recall and accuracy for slots ``Affiliate'', ``AssociateOf'', ``FounderOf'', ``EmployeeOf'', ``FoundedBy'', ``TopMembers'', ``Contact\_Meet\_Entity'' and so on.
 2) For special slots, like ``Titles'', ``DateOfDeath'', ``CauseOfDeath'', ``AwardsWon'', using different kind of advanced methods, e.g.\ classifiers, matching methods.
@@
 
-Some of the entities are not popular.
-For example, a `Brenda Weiler' Google search result has 860,000 documents over the whole web.
+Some of the entities are popular and appear at a greater frequency in the data set.
+For example, a `Brenda Weiler' Google search results in 860,000 documents.
+\ceg{Add an example of someone who is either much larger of smaller.}
 For our small portion of the web it might make sense.
-The histogram of the entities shows that more than half of the entities have appeared in less than 10 StreamItems.
-A good portion have appeared only once.
+The histogram of the entities shows that more than half of the entities have appeared in less than 10 documents.
+\ceg{Can we add this figure}
+A large portion have appeared only once.
 
@@
 
-Alltogether, We experimented through different tools and approaches to best process the massive amounts of data on the platform that we had available to us.
-We generate aliases for wikipedia entities using Wiki API and extract some aliases from wikipedia pages text itself.
+In this paper we described an approach to perform fact extraction over one of the largest data sets to date. 
+We generate aliases for Wikipedia entities using an API and extract some aliases from Wikipedia pages text itself.
 We process documents that mention entities for slot value extraction.
@@
 
-We noticed that some tools that claim to be performant for using the hardware capabilities at hand sometimes don't really work as claimed and you should not always rely on one without a thorough A/B testing of performance which we ended up in generating our in-house system for processing the corpus and generating the index.
+We sampled documents from the training data period to generate an initial set of patterns and then use these patterns to generate results.
+After manually examining the results, we prune patterns with poor performance and add patterns that may add to extraction coverage.
+We use several iterations to find the best patterns.
+%We found that it is very time consuming to identify quality patterns.
+
+%We noticed that some tools that claim to be performant for using the hardware capabilities at hand sometimes don't really work as claimed and you should not always rely on one without a thorough A/B testing of performance which we ended up in generating our in-house system for processing the corpus and passing through the filter.
 Furthermore, on extracting slot values, pattern matching might not be the best options but definitely can produce some good results at hand.
@@
 
-We sampled documents from the training data period to generate an initial set of patterns.
-We then use these patterns to generate  results.
-By manully looking at these results, we prune some patterns with poor ­performance and add more patterns that we identified from these results.
-We use several iterations to find the best patterns.
-We found that it is very time consuming to identity quality patterns.
+We look to continue exploration of streaming extraction models over this large data set.
+Our models are simple and provide a great baseline framework to develop and compare innovative techniques.

### 2013-11-13 paper/flairs27/content/discussion.tex
Fix writing issues

@@
 Some of the entities are popular and appear at a greater frequency in the data set.
-For example, a `Brenda Weiler' Google search results in 860,000 documents.
-\ceg{Add an example of someone who is either much larger of smaller.}
-For our small portion of the web it might make sense.
-The histogram of the entities shows that more than half of the entities have appeared in less than 10 documents.
-\ceg{Can we add this figure}
-A large portion have appeared only once.
+For example, a `Corn Belt Power Cooperative' Google search results in 86,800 documents, where as `William H. Gates' returns 3,880,000 documents. 
+%\ceg{Add an example of someone who is either much larger of smaller.}
+We observed that more than half of the entities have appeared in less than 10 documents.
+%\ceg{Can we add this figure - } 
+A large portion have appeared only once. This magnificient change in coverage support the viability of our seach and filter schemes.
 

### 2013-11-13 paper/flairs27/content/results.tex
Fix writing issues

@@
 In Table~\ref{table:initialresult} we performed two samples of a baseline submission and estimate the correctness of the extraction.
-\ceg{Add here how the baseline is different from the final submission}
-We our methods produced an accuracies of  54\% and 55\%.
+%\ceg{Add here how the baseline is different from the final submission}
+The first was addressing the overall performance measures of the system, e.g.
+precision and recall but the latter experiment was an enhanced version of the system with automating the alias generation process along with several other enhancements and more detailed e.g.
+producing per slot value results.
+We produced accuracies in range of  54\% and 55\%.
 We classify the errors into two sets, an incorrect entities and incorrect extractions.
@@
 
-\ceg{Probably should add again here a reason why our method is different from the baseline.}
-Using our methods, we provide we provide more detailed statistics, as displayed in Table~\ref{table:finalresultrecall} and Table~\ref{table:finalresultaccuracy}.
-Table~\ref{table:finalresultrecall} shows the recall for each slot name. \ceg{(define `entity coverage' here)}
+%\ceg{Probably should add again here a reason why our method is different from the baseline.}
+After enahncing the system via better and more extraction patterns  we provide more detailed statistics, as displayed in Table~\ref{table:finalresultrecall} and Table~\ref{table:finalresultaccuracy}.
+Table~\ref{table:finalresultrecall} shows the recall for each slot name. 
+Entities can have different coverages across the entire web, some are more popular such as William H.
+Gates or less well known such as Stevens Cooperative School; similarly slot names have various coverages e.g.
+being an \textit{Affiliate} is much more probable across the entities vs \textit{AwardsWon}.
+%\ceg{(define `entity coverage' here)}
 The slot name \textit{Affiliate} has was extracted the most number of times and \textit{CauseOfDeath} was extracted the
 fewest with 0 instances found matching the pattern list. \textit{AwardsWon} contained the next fewest with 38 instances found. 
-Affiliate is a generic slot name, using patterns to extract these relationships is difficult because almost any
+Affiliate is a generic slot name, to be more concrete, regading affiliations of an organization the following cases have been enumerated \cite{tackbp}:
+
+\begin{itemize}
+\item  Any relation that is not of parent-child form, e.g. a sub-organization of an organization is not an affiliate of that organization but rather a member of.
+\item  A relationship consisting solely of the two groups
+interacting in a specific event context is not enough evidence to constitute a religious/political affiliation. 
+\item Former political or religious affiliations are correct responses for this slot.
+
+\end{itemize}
+
+To extract relationships such as affiliate is difficult because almost any
 two items can be affiliated in some way.
-\ceg{Define the affiliate slot name.}
+%\ceg{Define the affiliate slot name.}
 Our patterns for this relationship led to noisy results.

### 2013-11-13 paper/flairs27/content/system.tex

@@
 
-\subsubsection{Constraints and Inference}\ceg{what specifically about the algorithm causes duplicates and errors?
+\subsubsection{Constraints and Inference}%\ceg{what specifically about the algorithm causes duplicates and errors?
 --- I asked Yang to elaborate on this as he is more familiar but still not sure what's causing those issues}
 
-The fact extractions match patterns that are general and highly susceptible to noisy.
+Due to duplicate crawls of the same webpages in the dataset or reasons such as incompelete taggings in sentences we end up with lots of duplicates or highly similar content in slot values list. 
+We implement a filter to remove duplicates or The fact extractions match patterns that are general and highly susceptible to noisy.
 The data contains duplicates and incorrect extractions.

### 2013-11-14 paper/flairs27/content/results.tex
made updates after morteza. we need to cut the paper down to 6 pages

@@
 %\ceg{Add here how the baseline is different from the final submission}
-The first was addressing the overall performance measures of the system, e.g.
-precision and recall but the latter experiment was an enhanced version of the system with automating the alias generation process along with several other enhancements and more detailed e.g.
-producing per slot value results.
 We produced accuracies in range of  54\% and 55\%.
-We classify the errors into two sets, an incorrect entities and incorrect extractions.
-We found 15\% and 17\% incorrect entity names and we identified 27\% and 30\% incorrect value extracted across all entities and slot types.
-The majority of errors were regarding poor slot value extraction patterns and incomplete aliases.
+The errors present can be classified into two sets, incorrect entities and incorrect extractions.
+We found 15\% and 17\% incorrect entity names and we identified 27\% and 30\% incorrect values extracted across all entities and slot types.
+The majority of these errors were the result of poor extraction patterns and an incomplete alias set.
 
@@
 %\ceg{Probably should add again here a reason why our method is different from the baseline.}
-After enahncing the system via better and more extraction patterns  we provide more detailed statistics, as displayed in Table~\ref{table:finalresultrecall} and Table~\ref{table:finalresultaccuracy}.
-Table~\ref{table:finalresultrecall} shows the recall for each slot name. 
-Entities can have different coverages across the entire web, some are more popular such as William H.
-Gates or less well known such as Stevens Cooperative School; similarly slot names have various coverages e.g.
-being an \textit{Affiliate} is much more probable across the entities vs \textit{AwardsWon}.
-%\ceg{(define `entity coverage' here)}
+After the implementation of the baseline system, we developed an enhanced version. 
+In this version we increased the number of extraction patterns and a generate a larger set of aliases.
+More detailed statistics are available in Table~\ref{table:finalresultrecall} and Table~\ref{table:finalresultaccuracy}.
+Table~\ref{table:finalresultrecall} shows the recall of each slot name. 
+Entities can have different coverages across the entire web, some are more popular such as William H. Gates or less well known such as Stevens Cooperative School.
+Similarly slot names have various coverages --- \textit{Affiliate} is more frequent compared to \textit{AwardsWon}. 
+More sentences describing affiliate relationships exist across the WP entities than
+sentences describing awards won. %\ceg{(define `entity coverage' here)}
 The slot name \textit{Affiliate} has was extracted the most number of times and \textit{CauseOfDeath} was extracted the
 fewest with 0 instances found matching the pattern list. \textit{AwardsWon} contained the next fewest with 38 instances found. 
-Affiliate is a generic slot name, to be more concrete, regading affiliations of an organization the following cases have been enumerated \cite{tackbp}:
+Affiliate slot has a broad definition; any relation that directly connects an entity to another entity of any type can describe an Affiliate relationship.
 
-\begin{itemize}
-\item  Any relation that is not of parent-child form, e.g. a sub-organization of an organization is not an affiliate of that organization but rather a member of.
-\item  A relationship consisting solely of the two groups
-interacting in a specific event context is not enough evidence to constitute a religious/political affiliation. 
-\item Former political or religious affiliations are correct responses for this slot.
-
-\end{itemize}
+%\begin{itemize}
+%\item  any relation that is not of parent-child form, e.g. a sub-organization of an organization is not an affiliate of that organization but rather a member of.
+%\item  A relationship consisting solely of the two groups
+%interacting in a specific event context is not enough evidence to constitute a religious/political affiliation. 
+%\item Former political or religious affiliations are correct responses for this slot. 
+%\end{itemize}
 
@@
 \textit{AssociateOf} has the highest accuracy with 63.6\% and  \textit{Affiliate}, \textit{Contact\_Meet\_PlaceTime} and \textit{EmployeeOf} have the lowest with lowest of 1\%, 1\% and 5\% accuracy respectively.
+A discussion of different slots is available in literature \cite{tackbp}.
 

### 2013-11-14 paper/flairs27/content/system.tex
made updates after morteza. we need to cut the paper down to 6 pages

--- 2013-11-11 paper/flairs27/content/system.tex
@@
 
-\subsubsection{Constraints and Inference}\ceg{what specifically about the algorithm causes duplicates and errors?
+\subsubsection{Constraints and Inference}%\ceg{what specifically about the algorithm causes duplicates and errors?
 --- I asked Yang to elaborate on this as he is more familiar but still not sure what's causing those issues}
 
-The fact extractions match patterns that are general and highly susceptible to noisy.
+Our data set contains some duplicate webpages, webpage texts with similar content, 
+and some of the entity tags are incomplete.
+This cause some duplicates or highly similar content in the extracted list. 
+We implement a filter to remove duplicates or the fact extractions match patterns that are general and highly susceptible to noisy.
 The data contains duplicates and incorrect extractions.

### 2013-11-14 paper/flairs27/content/conclusion.tex
added the paper for FLAIRS27. It needs a LOT of work
remove extra newlines instead of wrap
New review, check image
added a conclusion section

--- 2013-09-16 paper/kbanotebook2013/content/conclusion.tex
@@
 \section{Conclusions}
+
+In this paper we described an approach to perform fact extraction over one of the largest data sets to date. 
+We generate aliases for Wikipedia entities using an API and extract some aliases from Wikipedia pages text itself.
+We process documents that mention entities for slot value extraction.
+Slot values are determined using pattern matching over tagged entities in sentences.
+Finally post processing will filter, cleanup and infers some new slot values to enhance recall and accuracy.
+
+We sampled documents from the training data period to generate an initial set of patterns and then use these patterns to generate results.
+After manually examining the results, we prune patterns with poor performance and add patterns that may add to extraction coverage.
+We use several iterations to find the best patterns.
+%We found that it is very time consuming to identify quality patterns.
+
+%We noticed that some tools that claim to be performant for using the hardware capabilities at hand sometimes don't really work as claimed and you should not always rely on one without a thorough A/B testing of performance which we ended up in generating our in-house system for processing the corpus and passing through the filter.
+Furthermore, on extracting slot values, pattern matching might not be the best options but definitely can produce some good results at hand.
+We have plans on generating classifiers for slot value extraction purposes.
+Entity resolution on the other hand was a topic we spent sometime on but could not get to stable grounds for it.
+Entity resolution will distinguish between entities of the same name but different contexts.
+Further improvements on this component of the system are required.
+
+We look to continue exploration of streaming extraction models over this large data set.
+Our models are simple and provide a great baseline framework to develop and compare innovative techniques.
 

### 2013-11-14 paper/flairs27/content/discussion.tex
made updates after morteza. we need to cut the paper down to 6 pages
added a conclusion section

@@
-\section{Discussions}
+\section{Discussion}
 
@@
 %\ceg{Add an example of someone who is either much larger of smaller.}
-We observed that more than half of the entities have appeared in less than 10 documents.
+We observed that more than half of the entities appear in less than 10 documents in the data set;
 %\ceg{Can we add this figure - } 
-A large portion have appeared only once. This magnificient change in coverage support the viability of our seach and filter schemes.
+a large portion have appeared only once. This magnificient change in coverage support the viability of our seach and filter schemes.
 
@@
 % Answer the `why' question about all the trends in the results section.
-
-In this paper we described an approach to perform fact extraction over one of the largest data sets to date. 
-We generate aliases for Wikipedia entities using an API and extract some aliases from Wikipedia pages text itself.
-We process documents that mention entities for slot value extraction.
-Slot values are determined using pattern matching over coreferences of entities in sentences.
-Finally post processing will filter, cleanup and infers some new slot values to enhance recall and accuracy.
-
-We sampled documents from the training data period to generate an initial set of patterns and then use these patterns to generate results.
-After manually examining the results, we prune patterns with poor performance and add patterns that may add to extraction coverage.
-We use several iterations to find the best patterns.
-%We found that it is very time consuming to identify quality patterns.
-
-%We noticed that some tools that claim to be performant for using the hardware capabilities at hand sometimes don't really work as claimed and you should not always rely on one without a thorough A/B testing of performance which we ended up in generating our in-house system for processing the corpus and passing through the filter.
-Furthermore, on extracting slot values, pattern matching might not be the best options but definitely can produce some good results at hand.
-We have plans on generating classifiers for slot value extraction purposes.
-Entity resolution on the other hand was a topic we spent sometime on but could not get to stable grounds for it.
-Entity resolution will distinguish between entities of the same name but different contexts.
-Further improvements on this component of the system are required.
-
-We look to continue exploration of streaming extraction models over this large data set.
-Our models are simple and provide a great baseline framework to develop and compare innovative techniques.

### 2013-11-15 paper/flairs27/content/introduction.tex
merge

@@
 DateOfDeath \\ 
-CauseOfDeath\\
 Titles\\

### 2013-11-15 paper/flairs27/content/results.tex

--- 2013-11-13 paper/flairs27/content/results.tex
@@
 %\ceg{(define `entity coverage' here)}
-The slot name \textit{Affiliate} has was extracted the most number of times and \textit{CauseOfDeath} was extracted the
-fewest with 0 instances found matching the pattern list. \textit{AwardsWon} contained the next fewest with 38 instances found. 
+The slot name \textit{Affiliate} has was extracted the most number of times; \textit{AwardsWon} contained the next fewest with 38 instances found. 
 Affiliate is a generic slot name, to be more concrete, regading affiliations of an organization the following cases have been enumerated \cite{tackbp}:
@@
 AwardsWon & 38 & 14 \\ \hline 
-CauseOfDeath & 0 & 0 \\ \hline 
 Contact\_Meet\_Entity & 191 & 8 \\ \hline 
@@
 AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
-CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
 Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 

### 2013-11-16 paper/flairs27/content/introduction.tex
Paper review

@@
 %We develop a system to read streaming data and filter out articles that are candidates for citations. 
-The goal of this system is to read web documents and recommend citable facts for WP pages.
+The goal of this system is to read web documents and recommend citable facts (attributes) for WP pages.
 
@@
 Entities of three categories \textit{person}, \textit{organization} and \textit{facility} are considered.
-This task involves processing large sets of information to determine which facts may contain references to a WP entity. 
+This work involves processing large sets of information to determine which facts may contain references to a WP entity. 
 This problem becomes increasingly more difficult when we look to extract relevant facts from
@@
 Then, we match the sentence to find a topic such as \textit{DateOfDeath} valued at \textit{March 2013}.
-Each of these operations is expensive so an intelligent efficient framework is necessary to execute these operations at web scale.
+Each of these operations is expensive so an intelligent and efficient framework is necessary to execute these operations at web scale.
 %Other examples that this system can answer could be `Who a person has met during a certain period of time?', `Who are the employees of this organization?', `Who has met who in this facility at a certain time?'.
@@
 In our example sentence, the entity of the sentence is \textit{Boris Berezovsky} and the slot we extract is
-\textit{DateOfDeath} with a slot valye of \text{March 2013}.
+\textit{DateOfDeath} with a slot value of \text{March 2013}.
 

### 2013-11-16 paper/flairs27/content/system.tex
merge

@@
 Our system is built with a pipeline architecture in mind giving it the advantage to run each section separately to allow stream processing without blocking the data flow of components (Figure~\ref{fig:system}).
-The three logical components include sections on \textit{Model} for entity resolution purposes, \textit{Wiki Citation} to annotate cite-worthy documents, \textit{Slot Filling} to generate the actual slot values.
+The three logical components include sections on \textit{Model} for entity resolution purposes, \textit{Wiki Citation} to annotate cite-worthy documents, and \textit{Slot Filling} to generate the actual slot values.
 
@@
 %We use several approaches to get as many viable aliases as possible.
-We extract several name variations from the Wikipedia api and from the WP entity page.
+We extract several name variations from the Wikipedia API and from the WP entity page.
 Also, if the entity type is \textit{person} we can change the order of user names to increase coverage (e.g. `Boris Berezovsky' $\rightarrow$ `Berezovsky, Boris').
-Next, we iterator over documents in the stream and filter out all document that are not central to the entity.
+Next, we iterator over documents in the stream and filter out all documents that are not directly citable for the entity.
 To extract relevant facts we perform pattern matching in each sentence that matches the entity based on a dictionary
 of patterns.
-If the sentence can activate on of the patterns in the dictionary we emit this sentence as a candidate contribution
+If the sentence can activate one of the patterns in the dictionary we emit this sentence as a candidate contribution
 to the WP entity.
 With the candidate set, we infer new facts from the set and clean up the set
-by removing the set that violate a list of constraints such as duplicates.
+by removing the set of values that violate a list of constraints such as duplicates.
 Lastly, we try to infer a new set of facts based on a list of rules.
@@
 \textsl{Bill Gates} therefore we treat these two names as aliases. 
-To extract more aliases  is we parse the HTML source of a WP entity page.
-Then using regular expressions we extract the bold phrases of the initial paragraph as aliases.
+To extract more aliases we parse the HTML source of a WP entity page.
+Using regular expressions we extract the bold phrases of the initial paragraph as aliases.
 Based on our observation this is a very accurate method and it provides several entities of 
 WP with more inline aliases from the wiki page itself.
-As an example, for `Boris Berezovski' which was mentioned early-on, there is an alias of `Boris Abramovich Berezovsky' given in bold in the wiki page which will be obtained via thi method.
+As an example, for `Boris Berezovski' which was mentioned early-on, there is an alias of `Boris Abramovich Berezovsky' given in bold in the wiki page which will be obtained via this method.
 
@@
 This two-level filter allows us to perform detailed slower processing over a smaller set of documents.
-Not all chunk files contain mention of the entities so filtering out large chunk files early saves no I/O and processing.
+Not all chunk files contain mention of the entities so filtering out large chunk files early saves on I/O and processing.
 Document Chunk Filter discards non-mentioning chunk files and promotes chunk files as soon as an entity mention is found.
@@
 %\ceg{See the previous note.}
-Streaming Slot Filling (SSF) extracts fact values from sentences according to a list of pattern.
-Table~\ref{table:slotNameOntology} list the slot relationships that we looks to extract.
+Streaming Slot Filling (SSF) extracts fact values from sentences according to a list of patterns.
+Table~\ref{table:slotNameOntology} lists the slot relationships that we looks to extract.
 In Figure~\ref{fig:system} we refer to this task as \textit{Slot Filling}.
@@
 %\texttt{FAC}, \texttt{ORG} and \texttt{PER} are Lingpipe entity types.
-The $p_2$ represents a slot name.
+ $p_2$ represents a slot name.
 A list of slot names is present in Table~\ref{table:slotNameOntology}.
@@
 Figure~\ref{fig:pattern} contains the example sentence from the introduction labeled by the rule engine.
+The matching pattern is $\langle$\texttt{PER, DateOfDeath, \textit{passed away}, right, NP}$\rangle$.
+In the figure, `Boris Berezovsky' matches as an alias for WP entity \textsl{wiki/Boris\_Berezovsky\_(businessman)}, DateOfDeath is the slot name, `passed away' is the content of the pattern, direction is `Right' and the actual value of the slot is `March 2013' which is a Noun Phrase.
 
@@
 \caption{Pattern matching for rule evaluation. The slot value is on the right side of the 
-entity. The pattern context discovered is `passed away' with a value of `March 2013'. }\label{fig:pattern}
+entity. The pattern context discovered is `passed away' with a value of `March 2013'. This conforms to type II of our pattern categories.}\label{fig:pattern}
 \vspace*{-.2in}
@@
 For example, in pattern $\langle$\texttt{PER, FounderOf, \textit{founder}, right, ORG}$\rangle$ the \texttt{PER} 
-tag means the entity we are finding slot values for a PER entity;
+tag means the entity we are finding slot values for is a PER entity;
 \texttt{FounderOf} means this is a pattern for FounderOf slot.
-\textit{founder} is the anchor word we are match in a sentence;
+\textit{founder} is the word we match in a sentence - the content of pattern occuring in the sentence;
 \texttt{right} means that we are going to the right part of the sentence to match the pattern and find the slot value;
@@
 
-\textbf{Type III.} These type of facts are best discovered by hard coding the slot values.
+\textbf{Type III.} These types of facts are best discovered by hard coding the slot values.
 Examples of these include time phrases: $\langle$\texttt{PER, DateOfDeath, \textit{died}, right, \textit{last night}}$\rangle$.
 In this pattern, the phrase \textit{last night} is exactly searched in the text {last night} to the right of the term \textit{died}.
-This intuition behind this pattern is in news articles that report events in the past relative to the article. 
+The intuition behind this pattern is in news articles that report events in the past relative to the article. 
 For example, an article will mention that  
@@
 This cause some duplicates or highly similar content in the extracted list. 
-We implement a filter to remove duplicates or the fact extractions match patterns that are general and highly susceptible to noisy.
+We implement a filter to remove duplicates or the fact extractions that match patterns that are general and highly susceptible to be noisy.
 The data contains duplicates and incorrect extractions.

### 2013-11-16 paper/flairs27/paper.tex
Worked on the discussion version of the paper, added lots of comments
added a conclusion section
Made small changes to the paper.tex to prepare for submission

@@
 
-\newcommand\ceg[1]{\textcolor{red}{#1}} % Red marker to declare errors.
+\newcommand\ceg[1]{\textcolor{red}{#1 -- CEG}} % Red marker to declare errors.
+\newcommand\hide[2]{#2}
 
@@
 
-\author{Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{University of Florida, Gainesville, Florida, USA}, Milenko Petrovic\footnote{Institute for Human and Machine Cognition, Ocala, Florida, USA}\\
-       \\
-       {\{msnia, cgrant, ypeng, daisyw\}@cise.ufl.edu,}
-       {mpetrovic@ihmc.us}
-}
+%\author{Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{University of Florida, Gainesville, Florida, USA}, Milenko Petrovic\footnote{Institute for Human and Machine Cognition, Ocala, Florida, USA}\\
+%       \\
+%       {\{msnia, cgrant, ypeng, daisyw\}@cise.ufl.edu,}
+%       {mpetrovic@ihmc.us}
+%}
+\author{XXX}
 
@@
 
-%\input{content/conclusion.tex}
+\input{content/conclusion.tex}
 
 \section*{Acknowledgements}
-We would like to thank John Frank and TREC for providing the data set.
-Christan Grant is funded by a National Science Foundation Graduate Research Fellowship under Grant No. DGE-0802270.
+We would like to thank \hide{John Frank}{XXX} and \hide{NIST}{XXX} for providing the data set.
+\hide{Christan Grant}{XXXX} is funded by \hide{a National Science Foundation Graduate Research Fellowship under Grant No. DGE-0802270}{XXXX}.
 

### 2013-11-17 paper/flairs27/content/introduction.tex
Made several changes and clarifications. Removed some authorname information for double blind reviewing

@@
 Notable news may be derived from newspapers, tweets, blogs and a variety of
-different sources include Twitter, Facebook, iBlogs, arxiv, etc.\
-The actual citable information is a small percentage of the total documents that appear on the web.
+different sources include Twitter, Facebook, iBlogs, arxiv, etc.
+However, the actual citable information is a small percentage of the total documents that appear on the web.
 %We develop a system to read streaming data and filter out articles that are candidates for citations. 
-The goal of this system is to read web documents and recommend citable facts (attributes) for WP pages.
+%The goal of this system is to read web documents and recommend citable facts (attributes) for WP pages.
+To help WP editors, a system is needed to parse through terabytes of documents 
+and select facts that can be recommended to particular WP pages.
 
@@
 %For example, a take a sentence from the Internet:
-Here we produce an example sentence from a new website:
+Here we produce an example sentence from a webpage:
 
@@
 
-First, we must realize that there are two \textit{Boris Berezovsky} entities in WP, one a businessman and the other a pianist.
+After parsing the sentence, we must first note that there are two entities named \textit{Boris Berezovsky} WP; one a businessman and the other a pianist.
 Any extraction needs to take this into account and employ a viable distinguishing policy (entity resolution).
 Then, we match the sentence to find a topic such as \textit{DateOfDeath} valued at \textit{March 2013}.
-Each of these operations is expensive so an intelligent and efficient framework is necessary to execute these operations at web scale.
+Each of these operations is expensive so an efficient framework is necessary to execute these operations at web scale.
 %Other examples that this system can answer could be `Who a person has met during a certain period of time?', `Who are the employees of this organization?', `Who has met who in this facility at a certain time?'.
 
-In this paper we develop an efficient query-driven slot extraction for given WP entities from a time oriented document stream.
-Fact or slot extraction is defined as follows: match each sentence to the generic sentence structure of [\textit{subject} - \textit{verb} - \textit{adverbial/complement}]~\cite{sentencePatterns08}, where  \textit{subject} represents the entity and \textit{verb} is the relation type (slot) we are interested in (e.g.
-Table~\ref{table:slotNameOntology}).
-The third component, \textit{adverbial/complement}, represents the value of the enity slot.
+In this paper, we introduce an efficient fact extraction system or given WP entities from a time-ordered document stream.
+Fact extraction is defined as follows: match each sentence to the generic sentence structure of \{\textit{subject} --- \textit{verb} --- \textit{adverbial/complement}\}~\cite{sentencePatterns08}.
+The first \textit{subject} represents the entity (WP entity) and \textit{verb} is the relation type (slot) we are interested in (e.g. Table~\ref{table:slotNameOntology}).
+The third component, \textit{adverbial/complement}, represents the value of the associated slot.
 In our example sentence, the entity of the sentence is \textit{Boris Berezovsky} and the slot we extract is
 \textit{DateOfDeath} with a slot value of \text{March 2013}.
+The resulting extraction containing an entity, slot name and slot value is a \emph{fact}.
 
@@
 \begin{itemize}[noitemsep,nolistsep]
-\item Introduce a method to build models of WP name variations (Section~\ref{});
-\item Built a system to filter a large amount of diverse documents using a natural language processing rule-based extraction system (Section~\ref{});
-\item Extract, infer and filter entity-slot-value triples of information to be added to KB (Section~\ref{}).
+\item Introduce a method to build models of WP name variations;% (Section~\ref{sec:entitymodel});
+\item Built a system to filter a large amount of diverse documents using a natural language processing rule-based extraction system;% (Section~\ref{sec:slotfilling});
+\item Extract, infer and filter entity-slot-value triples of information to be added to KB.%(Section~\ref{sec:constraintsandinference}).
 \end{itemize}
@@
 \begin{table}
-\caption{Ontology of Slots }
+\caption{The set of possible slot name for each entity type.}
 \centering
@@
 
-\setlength{\tabcolsep}{2pt}
+\setlength{\tabcolsep}{1pt}
 
@@
 \hline 
-\textbf{Person} & \textbf{Facility} & \textbf{Organization} \\ 
+\textbf{{\small Person}} & \textbf{{\small Facility}} & \textbf{{\small Organization}} \\ 
 \hline 
-\begin{tabular}{@{}l@{}}Affiliate \\ AssociateOf \\  {\tiny Contact\_Meet\_PlaceTime} \\ AwardsWon \\ 
-DateOfDeath \\ 
-Titles\\
-FounderOf\\
-EmployeeOf\end{tabular}
+\begin{tabular}{@{}l@{}}{\small Affiliate }\\ {\small AssociateOf }\\  {\small Contact\_Meet\_PlaceTime} \\ {\small AwardsWon }\\ 
+{\small DateOfDeath }\\ 
+{\small Titles}\\
+{\small FounderOf}\\
+{\small EmployeeOf}\end{tabular}
   &
-   \begin{tabular}[b]{l}Affiliate \\ {\small Contact\_Meet\_Entity} \end{tabular} 
+   \begin{tabular}[b]{l}{\small Affiliate }\\ {\small Contact\_Meet\_Entity} \end{tabular} 
    & 
-   \begin{tabular}{@{}l@{}}Affiliate \\ {\small TopMembers} \\ FoundedBy\end{tabular} \\ 
+   \begin{tabular}{@{}l@{}}{\small Affiliate }\\ {\small TopMembers} \\ {\small FoundedBy}\end{tabular} \\ 
 \hline 

### 2013-11-17 paper/flairs27/content/results.tex
Paper review
Made several changes and clarifications. Removed some authorname information for double blind reviewing

@@
 %Slot extraction using patterns, NER tags and NP tags.
-Out of the 500 M documents and 139 entities we found 158,052 documents containing query entities, 17,885 unique extracted slot values for 8 different slots.
+Out of the 500M documents and 139 entities we found 158,052 documents containing query entities, 17,885 unique extracted slot values for 8 different slots.
 We did not get any results from 31 entities missing and 4 slots.
@@
 %On the performance of our initial submission run we performed random sampling via two processes, the results of which are according to Table~\ref{table:initialresult}.
-In Table~\ref{table:initialresult} we performed two samples of a baseline submission and estimate the correctness of the extraction.
+In Table~\ref{table:initialresult} we performed two samples of a baseline and estimate the correctness of the extractions.
 %\ceg{Add here how the baseline is different from the final submission}
-The first was addressing the overall performance measures of the system, e.g.
-precision and recall but the latter experiment was an enhanced version of the system with automating the alias generation process along with several other enhancements and more detailed e.g.
-producing per slot value results.
+The first was addressing the overall performance measures of the system, e.g.\ precision and recall.
+The latter experiment was performed over an enhanced version of the system; we included the aliases from WP API, the alias generation process, and some additional patterns. 
 We produced accuracies in range of  54\% and 55\%.
@@
 Table~\ref{table:finalresultrecall} shows the recall for each slot name. 
-Entities can have different coverages across the entire web, some are more popular such as William H.
-Gates or less well known such as Stevens Cooperative School; similarly slot names have various coverages e.g.
-being an \textit{Affiliate} is much more probable across the entities vs \textit{AwardsWon}.
-%\ceg{(define `entity coverage' here)}
+Entities can have different coverages across the entire web, some were more popular (William H. Gates) or less well known such as (Stevens Cooperative School).
+Similarly, slot names have various coverages for example \textit{Affiliate} is more probable across the entities when compared to \textit{AwardsWon}. %\ceg{(define `entity coverage' here)}
 The slot name \textit{Affiliate} has was extracted the most number of times; \textit{AwardsWon} contained the next fewest with 38 instances found. 
-Affiliate is a generic slot name, to be more concrete, regading affiliations of an organization the following cases have been enumerated \cite{tackbp}:
+,  affiliations of an organization the following cases have been enumerated \cite{tackbp}:
 
+An affiliate relationship can be defined in three general ways~\cite{tackbp}:
 \begin{itemize}
-\item  Any relation that is not of parent-child form, e.g. a sub-organization of an organization is not an affiliate of that organization but rather a member of.
 \item  A relationship consisting solely of the two groups
-interacting in a specific event context is not enough evidence to constitute a religious/political affiliation. 
-\item Former political or religious affiliations are correct responses for this slot.
+interacting in a specific event context is not enough evidence to constitute a religious/political affiliation; 
+\item Former political or religious affiliations are correct responses for this slot;
+\item  Any relation that is not of parent-child form; a sub-organization is not an affiliate its parent organization but rather a Memberof.
+\end{itemize}
+Affiliate is a generic slot name; extracting affiliate relationships is difficult because the actual relationship must be determined.
+Our patterns for this relationship led to noisy results.
 
-\end{itemize}
+However, less ambiguous slot names (AssociateOf) obtained higher accuracy but we have recall.
+We developed patterns that explicitly expressed these relationships but we did not create enough patterns to 
+express all forms of those slot names.
 
-To extract relationships such as affiliate is difficult because almost any
-two items can be affiliated in some way.
-%\ceg{Define the affiliate slot name.}
-Our patterns for this relationship led to noisy results.
-On the other hand for more precise slot names our accuracy increases but we have less recall.
 Table~\ref{table:finalresultaccuracy} addresses the relative accuracy measure per slot value.

### 2013-11-17 paper/flairs27/content/system.tex
Made several changes and clarifications. Removed some authorname information for double blind reviewing

@@
 In this section, we introduce the main components of the system.
-Our system is built with a pipeline architecture in mind giving it the advantage to run each section separately to allow stream processing without blocking the data flow of components (Figure~\ref{fig:system}).
-The three logical components include sections on \textit{Model} for entity resolution purposes, \textit{Wiki Citation} to annotate cite-worthy documents, and \textit{Slot Filling} to generate the actual slot values.
+Our system is built with a pipeline style architecture giving it the advantage to run each section separately to allow stream processing without blocking the data flow of components (Figure~\ref{fig:system}).
+The three logical components are divided into sections entitled \textit{Model} for entity resolution purposes,
+\textit{Wikipedia Citation} to annotate cite-worthy documents,
+and \textit{Slot Filling} to generate the actual slot values.
 
-If we are looking to discover facts for a single WP entity, the first step is to extract aliases of the entity.
+To discover facts for a single WP entity, the first step is to extract aliases of the entity.
 %We use several approaches to get as many viable aliases as possible.
-We extract several name variations from the Wikipedia API and from the WP entity page.
+We extract several name variations from the Wikipedia.org API and from the WP entity page.
 Also, if the entity type is \textit{person} we can change the order of user names to increase coverage (e.g. `Boris Berezovsky' $\rightarrow$ `Berezovsky, Boris').
-Next, we iterator over documents in the stream and filter out all documents that are not directly citable for the entity.
-To extract relevant facts we perform pattern matching in each sentence that matches the entity based on a dictionary
+Next, we iterate over documents in the stream and filter out all documents that do not explicitly contain a string matching 
+the list of entities.
+To extract relevant facts we perform pattern matching over each sentence that matches the entity based on a dictionary
 of patterns.
-If the sentence can activate one of the patterns in the dictionary we emit this sentence as a candidate contribution
-to the WP entity.
+If a sentence activates one of the patterns in the dictionary we emit this sentence as a candidate contribution
+for the WP entity.
 With the candidate set, we infer new facts from the set and clean up the set
 by removing the set of values that violate a list of constraints such as duplicates.
-Lastly, we try to infer a new set of facts based on a list of rules.
+%Lastly, we try to infer a new set of facts based on a list of rules.
 
@@
 \subsection{Entity Model}
+\label{sec:entitymodel}
 
-We use Wikipedia API to automatically retrieve aliases. 
+We use the Wikipedia.org API to retrieve aliases. 
 The API allows us to requests pages that redirect users to an entity page.
-For example, if a WP user tries to access the \textsl{William Henry Gates} they are sent to the page for 
-\textsl{Bill Gates} therefore we treat these two names as aliases. 
+For example, if a WP user tries to access the \textsl{William Henry Gates} entry they are sent to the page for 
+\textsl{Bill Gates} --- we treat  such redirects as aliases. 
 To extract more aliases we parse the HTML source of a WP entity page.
 Using regular expressions we extract the bold phrases of the initial paragraph as aliases.
-Based on our observation this is a very accurate method and it provides several entities of 
-WP with more inline aliases from the wiki page itself.
-As an example, for `Boris Berezovski' which was mentioned early-on, there is an alias of `Boris Abramovich Berezovsky' given in bold in the wiki page which will be obtained via this method.
+This method provides several inline aliases from the wiki page.
+In WP page for the businesman `Boris Berezovski' , there is a mention of `Boris Abramovich Berezovsky' given in bold in the wiki page which obtained by regular expression extraction.
 
@@
 
-We pass the full set of \textit{person} entities through rules for generating proper name orders.
-This module produces various forms of writing entity names and titles.
+We pass the full set of \textit{person} entities through rules for generating alternate name orders.
+This module produces various forms of expressing entity names and titles.
 For example, \textsl{Bill Gates} can be written as \textsl{Gates, Bill}.
@@
 As a stream of documents come in we first perform a string match between the model aliases and document text. 
-We use this technique as a first filter with confidence because previous work has stated non-mentioning
+We use this technique as a first filter with confidence because previous work states non-mentioning
 documents have a low chance of being citable in Wikipedia \cite{JFrank12}.
-Given our large number of aliases we can be confident if an alias does not appear in a document it does not need to be cited.
+Given our large number of aliases we can be confident that if an alias does not appear in a document it does not need to be cited.
 
-Our stream system receives documents in the from of chunk files.
+Our system streams in documents in the form of chunk files.
 Each chunk file contains thousands of documents.
@@
 \subsection{Slot Filling}
+\label{sec:slotfilling}
 %\ceg{See the previous note.}
@@
 %\textbf{Format of Patterns.}
-A pattern is as a record representing knowledge going to be added to a WP entity.
+A pattern is a template of a fact to be extracted and added to a WP entity.
+Patterns are used to find and extract facts from text.
 A pattern $\mathcal{P}$ is represented as a five-tuple $\mathcal{P} = \langle p_1, p_2, p_3, p_4, p_5 \rangle$.
@@
 a string found in the sentence that identifies a slot name.
-The extractor looks specifically for a pattern content.
+The extractor looks specifically for pattern content.
 The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in $p_4$ to explore sentence.
@@
 %\textbf{Types of patterns}
-There are three types of patterns distinguished by different types of slot values in the patterns.
+There are three types of patterns, each distinguished by different types of slot values ($p_5$) in the patterns.
 The matching methods using these three types of patterns are implemented according to the different structures of slot values.
@@
 
-\subsubsection{Constraints and Inference}%\ceg{what specifically about the algorithm causes duplicates and errors?
+\subsection{Constraints and Inference}%\ceg{what specifically about the algorithm causes duplicates and errors?
 --- I asked Yang to elaborate on this as he is more familiar but still not sure what's causing those issues}
+\label{sec:constraintsandinference}
 
@@
 and some of the entity tags are incomplete.
-This cause some duplicates or highly similar content in the extracted list. 
+This causes some duplicates or highly similar content in the extracted list. 
 We implement a filter to remove duplicates or the fact extractions that match patterns that are general and highly susceptible to be noisy.

### 2013-11-18 paper/flairs27/content/results.tex
Ready for submission

@@
 
-\begin{tabular}{|l|l|c|}
+\begin{tabular}{|p{3.8cm}|p{3cm}|}
 \hline 
-\textbf{Document Type} & \textbf{\# of Documents} &  \textbf{Slots Found}\\ 
+\textbf{Document Type} & \textbf{\# of Documents}\\ 
 \hline 
-Arxiv & 10988 & \\ \hline
- Classified & 34887 & \\ \hline
- Forum & 77674 & \\ \hline
- Linking & 12947 & \\ \hline
- Mainstream News & 141936 & \\ \hline
- Memetracker & 4137 & \\ \hline
- News & 280629 & \\ \hline
- Review & 6347 & \\ \hline
- Social & 688848 & \\ \hline
- Weblog & 740987 & \\ \hline
+Arxiv & 10988  \\ \hline
+ Classified & 34887  \\ \hline
+ Forum & 77674  \\ \hline
+ Linking & 12947  \\ \hline
+ Mainstream News & 141936  \\ \hline
+ Memetracker & 4137  \\ \hline
+ News & 280629  \\ \hline
+ Review & 6347 \\ \hline
+ Social & 688848 \\ \hline
+ Weblog & 740987  \\ \hline
 \hline 
@@
 
-\begin{table}
+\begin{table}[t]
 \caption{Recall Measure: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}

### 2013-11-18 paper/flairs27/paper.tex
Made several changes and clarifications. Removed some authorname information for double blind reviewing
title change
Ready for submission

--- 2013-11-11 paper/flairs27/paper.tex
@@
 
+\usepackage{balance}
+
 \pagenumbering{gobble} %Do not print page numbers
 
-\newcommand\ceg[1]{\textcolor{red}{#1}} % Red marker to declare errors.
+\newcommand\ceg[1]{\textcolor{red}{#1 -- CEG}} % Red marker to declare errors.
+\newcommand\hide[2]{#2}
 
@@
 
-\title{Streaming Slot-Value Extraction for Wikipedia Entities at Web-Scale}
+\title{Streaming Fact Extraction for Wikipedia Entities at Web-Scale}
 
@@
 }
+%\author{XXX}
 
@@
 
-%\input{content/conclusion.tex}
+\input{content/conclusion.tex}
 
 \section*{Acknowledgements}
-We would like to thank John Frank and TREC for providing the data set.
+%We would like to thank \hide{John Frank}{XXX} and \hide{NIST}{XXX} for providing the data set.
+%\hide{Christan Grant}{XXXX} is funded by \hide{a National Science Foundation Graduate Research Fellowship under Grant No. DGE-0802270}{XXXX}.
+
 Christan Grant is funded by a National Science Foundation Graduate Research Fellowship under Grant No. DGE-0802270.

### 2013-11-18 paper/flairs27/content/abstract.tex
updated abstract. Re-writted, most jargon removed.

@@
 
-In this paper we address extracting slot values from internet pertinent to entities in wikipedia, which is the most popular web-based, colaborative multilingual encyclopieda on the internet.
+%In this paper we address extracting slot values from internet pertinent to entities in wikipedia, which is the most popular web-based, colaborative multilingual encyclopieda on the internet.
 This is comparable to Freebase in a query-driven manner.
@@
 
+Wikipedia.org is the largest online resource for free information and maintained by a small number of volunteer editors.
+Because of its large size, information on some pages can easily be neglected and can easily become out of date.
+To address the issues of stale articles we create a system that is able to read
+in a stream in a web of diverse documents from across the web and recommend
+facts to be added to specified Wikipedia pages.
+We developed a three-stage stream system to create models of entities,
+filter out irrelevant documents and 
+extract facts from documents mentioning entities.
+The systems over a 4.5 TB web document corpus data set over 16 months and 139 Wikipedia pages.
+Our results show a promising framework for fact extraction from arbitrary web pages for Wikipedia pages.
+
 \end{abstract}

### 2013-11-18 paper/flairs27/content/abstract.tex
Update abstract.tex

@@
 
-Wikipedia.org is the largest online resource for free information and maintained by a small number of volunteer editors.
+Wikipedia.org is the largest online resource for free information and is maintained by a small number of volunteer editors.
 Because of its large size, information on some pages can easily be neglected and can easily become out of date.
@@
 extract facts from documents mentioning entities.
-The systems over a 4.5 TB web document corpus data set over 16 months and 139 Wikipedia pages.
+The systems over a 500 million web document corpus data set over 16 months and 139 Wikipedia pages.
 Our results show a promising framework for fact extraction from arbitrary web pages for Wikipedia pages.

### 2013-11-18 paper/flairs27/content/results.tex
get back authors
change machine model to the processor information

@@
 \textbf{Spec} & \textbf{Details} \\ \hline
-Model & Dell xxx 32 cores \\ \hline 
+Processor & 32 core AMD Opteron\textsuperscript{TM} 6272 \\ \hline 
 OS & CentOS release 6.4 Final \\ \hline 
@@
  Weblog & 740987  \\ \hline
-\hline 
+%\hline 
 \end{tabular} 

### 2013-11-18 paper/flairs27/content/discussion.tex
Made several changes and clarifications. Removed some authorname information for double blind reviewing
added a comment on the speed of the system

@@
 Some slots naturally have more results than other slots.
-For example DateOfDeath and CauseOfDeath have some of the fewest entities because only a few entities are deceased.
+For example, DateOfDeath and CauseOfDeath have some of the fewest entities because only a few entities are deceased.
 Some patterns use common words as as part of their patterns causing more extractions.
@@
 % Answer the `why' question about all the trends in the results section.
+
+The system pipeline architecture is an efficient method of processing the stream of data.
+Each hour of in the corpus contains and average of 380 MB of compressed data.
+It takes and hour for the system to extract facts from 140 hours worth of data fom the KBA corpus.

### 2013-11-18 paper/flairs27/content/abstract.tex
much needed language rewrite of the abstract

@@
 Wikipedia.org is the largest online resource for free information and is maintained by a small number of volunteer editors.
-Because of its large size, information on some pages can easily be neglected and can easily become out of date.
-To address the issues of stale articles we create a system that is able to read
-in a stream in a web of diverse documents from across the web and recommend
+The site contains 4.3 million english articles; these pages can easily be neglected, becoming out of date.
+Any news-worthy event may require an update of several pages.
+To address this issue of stale articles we create a system that reads
+in a stream diverse web documents and recommends
 facts to be added to specified Wikipedia pages.
-We developed a three-stage stream system to create models of entities,
-filter out irrelevant documents and 
-extract facts from documents mentioning entities.
-The systems over a 500 million web document corpus data set over 16 months and 139 Wikipedia pages.
-Our results show a promising framework for fact extraction from arbitrary web pages for Wikipedia pages.
+We developed a three-stage streaming system that creates models of Wikipedia pages,
+filters out irrelevant documents and 
+extracts facts that are relevant to Wikipedia pages.
+The systems is evaluated over a 500M page web corpus and 139 Wikipedia pages.
+Our results show a promising framework for fast fact extraction from arbitrary web pages for Wikipedia.
 

### 2014-01-28 paper/flairs27_AuthorKit/paper.tex
Up to 'system' entered

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algorithmic} 
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Streaming Fact Extraction for Wikipedia Entities at Web-Scale)
/Author (Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang, Milenko Petrovic)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Streaming Fact Extraction for Wikipedia Entities at Web-Scale}
\author{Morteza Shahriari Nia, Christan Grant, \\
\bf \large Yang Peng, Daisy Zhe Wang\\
Data Science Research Lab\\
University of Florida\\\
Gainesville, Florida 32611\\
\And Milenko Petrovic\\
Institute for Human and Machine Cognition\\ 15 SE Osceola Ave \\\ Ocala, Florida 34471
}

\maketitle
\begin{abstract}
\begin{quote}
Wikipedia.org is the largest online resource for free information and is maintained by a small number of volunteer editors.
The site contains 4.3 million english articles; these pages can easily be neglected, becoming out of date.
Any news-worthy event may require an update of several pages.
To address this issue of stale articles we create a system that reads
in a stream diverse web documents and recommends
facts to be added to specified Wikipedia pages.
We developed a three-stage streaming system that creates models of Wikipedia pages,
filters out irrelevant documents and 
extracts facts that are relevant to Wikipedia pages.
The systems is evaluated over a 500M page web corpus and 139 Wikipedia pages.
Our results show a promising framework for fast fact extraction from arbitrary web pages for Wikipedia.

\end{quote}
\end{abstract}

\noindent

Wikipedia.org (WP) is the largest and most popular general reference work on the Internet.
The website is estimated to have nearly 365 million readers worldwide.
An important part of keeping WP usable it to include new and current content.
%An important challenge in maintaining WP, the most popular web-based, collaborative, multilingual KB on the internet, is making sure its contents are up-to-date.
Presently, there is considerable time lag between the publication of an event and its citation in WP\@.
The median time lag for a sample of about 60K web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail~\cite{JFrank12}.
%Also, the majority of WP entities have updates on their associated article much less frequently than their mention frequency.
Such stale entries are the norm in any large reference work because the number
of humans maintaining the reference is far fewer than the number of entities.

Reducing latency keeps WP relevant and helpful to its users.
Given an entity page, such as \textsl{wiki/Boris\_Berezovsky\_(businessman)}\footnote{http://en.wikipedia.org/wiki/Boris\_Berezovsky\_(businessman)},
possible citations may come from a variety of sources.
Notable news may be derived from newspapers, tweets, blogs and a variety of
different sources include Twitter, Facebook, iBlogs, arxiv, etc.
However, the actual citable information is a small percentage of the total documents that appear on the web.
%We develop a system to read streaming data and filter out articles that are candidates for citations. 
%The goal of this system is to read web documents and recommend citable facts (attributes) for WP pages.
To help WP editors, a system is needed to parse through terabytes of documents 
and select facts that can be recommended to particular WP pages.

Previous approaches are able to find relevant documents given a list of WP
entities as query nodes \cite{mcnamee2012hltcoe, dalton2013bi,
Bonnefoy:2013:WDE:2484028.2484180, Balog:2013:CCR:2484028.2484151,ji2011knowledge}.
Entities of three categories \textit{person}, \textit{organization} and \textit{facility} are considered.
This work involves processing large sets of information to determine which facts may contain references to a WP entity. 
This problem becomes increasingly more difficult when we look to extract relevant facts from
each document.
Each relevant document must now be parsed and processed to determine if a sentence or paragraph is worth being cited.
% Reorder this paragraph
%The challenges that we address are: first finding documents that contain useful information about the entity (avoid spams, documents that do not have direct information about the entity even though they mention them, etc), the scale where \textit{stream processing} nature of the system makes it suitable to avoid batch processing natures of Hadoop and operate in the realm of streams such as twitter storm~\footnote{http://storm-project.net/} which similarly processes unblounded streams of twitter data or Spark Streaming~\footnote{http://spark.incubator.apache.org/}. Further, this is called streaming because data is being generated as time goes
%on and for each extraction we should only consider current or past data. As other Natural Language Processing tasks, precision and recall of the extent we can extract slot values are very important metrics that we will discuss later on. Having to balance between infamous and obscure entities, dealing with slots that can be very broad (e.g.\ things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).

Discovering facts across the Internet that are relevant and citable to the WP entities is a non-trivial task.
%For example, a take a sentence from the Internet:
Here we produce an example sentence from a webpage:

%\texttt{Boris Berezovsky made his fortune in Russia in the 1990s when the
%country went through privatisation of state property and `robber capitalism', and passed away March 2013.}
``{\small \texttt{Boris Berezovsky, who made his fortune in Russia in the 1990s, passed away March 2013.}}''

After parsing the sentence, we must first note that there are two entities named \textit{Boris Berezovsky} WP; one a businessman and the other a pianist.
Any extraction needs to take this into account and employ a viable distinguishing policy (entity resolution).
Then, we match the sentence to find a topic such as \textit{DateOfDeath} valued at \textit{March 2013}.
Each of these operations is expensive so an efficient framework is necessary to execute these operations at web scale.
%Other examples that this system can answer could be `Who a person has met during a certain period of time?', `Who are the employees of this organization?', `Who has met who in this facility at a certain time?'.

In this paper, we introduce an efficient fact extraction system or given WP entities from a time-ordered document stream.
Fact extraction is defined as follows: match each sentence to the generic sentence structure of \{\textit{subject} --- \textit{verb} --- \textit{adverbial/complement}\}~\cite{sentencePatterns08}.
The first \textit{subject} represents the entity (WP entity) and \textit{verb} is the relation type (slot) we are interested in (e.g. Table~\ref{table:slotNameOntology}).
The third component, \textit{adverbial/complement}, represents the value of the associated slot.
In our example sentence, the entity of the sentence is \textit{Boris Berezovsky} and the slot we extract is
\textit{DateOfDeath} with a slot value of \textit{March 2013}.
The resulting extraction containing an entity, slot name and slot value is a \emph{fact}.

%Slot extraction is a challenging task in current state of the art Knowledge Bases (KB).
%Popular graphical KB such as Freebase or DBPedia keep data in structured format where entities
%are connected via relationships (slots) and the associated attributes
%(slot values).
%Our system can be used as an aid to recommend factual updates to such KBs.

Our system contains three main components.
First, we pre-process the data and build models representing the WP query entities.
Next, we use the models to filter a large stream of documents so they only contain candidate citations.
Lastly, we processes sentences from candidate extractions and return slot values. 
% EITHER SAY WHAT IT MEANS OR GIVE EXAMPLES OR COMMENT IT
%We build a modular system that allows us to explore the nuances of the training data and queries. 
Overall, we contribute the following:
\begin{itemize} %[noitemsep,nolistsep]
\item Introduce a method to build models of WP name variations;% (Section~\ref{sec:entitymodel});
\item Built a system to filter a large amount of diverse documents using a natural language processing rule-based extraction system;% (Section~\ref{sec:slotfilling});
\item Extract, infer and filter entity-slot-value triples of information to be added to KB.%(Section~\ref{sec:constraintsandinference}).
\end{itemize}

\begin{table}
\caption{The set of possible slot name for each entity type.}
\centering
\label{table:slotNameOntology}

\setlength{\tabcolsep}{1pt}

\begin{tabular}{|c|c|c|}
\hline 
\textbf{{\small Person}} & \textbf{{\small Facility}} & \textbf{{\small Organization}} \\ 
\hline 
\begin{tabular}{@{}l@{}}{\small Affiliate }\\ {\small AssociateOf }\\  {\small Contact\_Meet\_PlaceTime} \\ {\small AwardsWon }\\ 
{\small DateOfDeath }\\ 
{\small Titles}\\
{\small FounderOf}\\
{\small EmployeeOf}\end{tabular}
  &
   \begin{tabular}[b]{l}{\small Affiliate }\\ {\small Contact\_Meet\_Entity} \end{tabular} 
   & 
   \begin{tabular}{@{}l@{}}{\small Affiliate }\\ {\small TopMembers} \\ {\small FoundedBy}\end{tabular} \\ 
\hline 
\end{tabular} 
\end{table}

\section{System}

In this section, we introduce the main components of the system.
Our system is built with a pipeline style architecture giving it the advantage to run each section separately to allow stream processing without blocking the data flow of components (Figure~\ref{fig:system}).
The three logical components are divided into sections entitled \textit{Model} for entity resolution purposes,
\textit{Wikipedia Citation} to annotate cite-worthy documents,
and \textit{Slot Filling} to generate the actual slot values.

To discover facts for a single WP entity, the first step is to extract aliases of the entity.
%We use several approaches to get as many viable aliases as possible.
We extract several name variations from the Wikipedia.org API and from the WP entity page.
Also, if the entity type is \textit{person} we can change the order of user names to increase coverage (e.g. `Boris Berezovsky' $\rightarrow$ `Berezovsky, Boris').
Next, we iterate over documents in the stream and filter out all documents that do not explicitly contain a string matching 
the list of entities.
To extract relevant facts we perform pattern matching over each sentence that matches the entity based on a dictionary
of patterns.
If a sentence activates one of the patterns in the dictionary we emit this sentence as a candidate contribution
for the WP entity.
With the candidate set, we infer new facts from the set and clean up the set
by removing the set of values that violate a list of constraints such as duplicates.
%Lastly, we try to infer a new set of facts based on a list of rules.

%As a match is found from the content of the sentence to the patterns that we have generated regarding slot name, the associated slot value is extracted as a final result.

%\ceg{Discuss current system first. If you want to keep the decisions points that led to the current architecture, make it a subsection.}

\begin{figure}
\hspace{-10mm}
  \centering
%  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
  \includegraphics[width=8.5cm]{./images/System_Diagram_with_model_Vertical-crop.pdf}
% http://convert.neevia.com/pdfconvert/
  \vspace*{-.1in} 
  \caption{System Architecture.
  Components are logical groups noted with dotted boxes.}
  \label{fig:system}
  \vspace*{-.2in}
\end{figure}

\subsection{Entity Model}
\label{sec:entitymodel}

We use the Wikipedia.org API to retrieve aliases. 
The API allows us to requests pages that redirect users to an entity page.
For example, if a WP user tries to access the \textsl{William Henry Gates} entry they are sent to the page for 
\textsl{Bill Gates} --- we treat  such redirects as aliases. 
To extract more aliases we parse the HTML source of a WP entity page.
Using regular expressions we extract the bold phrases of the initial paragraph as aliases.
This method provides several inline aliases from the wiki page.
In WP page for the businesman `Boris Berezovski' , there is a mention of `Boris Abramovich Berezovsky' given in bold in the wiki page which obtained by regular expression extraction.

%\ceg{Do we know how many additional aliases this method provides?}.
%\ceg{Do you want to give a more concrete example of how this might now work? It may be TMI.}
%As an example of when this might not wirk, is that there might be occasions that some other topic is written in bold typesetting in the first paraph apart from the entity aliases itself but these are very rare.

We pass the full set of \textit{person} entities through rules for generating alternate name orders.
This module produces various forms of expressing entity names and titles.
For example, \textsl{Bill Gates} can be written as \textsl{Gates, Bill}.
This allows the system to capture various notation forms of aliases that appear in text documents.
%We refer to this part as \textit{Alias Order Generator}.

\subsection{Wikipedia Citation}
The goal of this section is to use the models created to discover a set of documents that are relevant to the WP entity.
%We perform exact string matching and treat all the documents that mention an entity equally likely to be citable.
As a stream of documents come in we first perform a string match between the model aliases and document text. 
We use this technique as a first filter with confidence because previous work states non-mentioning
documents have a low chance of being citable in Wikipedia \cite{JFrank12}.
Given our large number of aliases we can be confident that if an alias does not appear in a document it does not need to be cited.

Our system streams in documents in the form of chunk files.
Each chunk file contains thousands of documents.
This corpus of documents is processed by a two-layer filter system referred to as \textit{Document Chunk Filter} and \textit{Document Filter}.
The purpose of these filters is to reduce I/O cost while generating slot values for various entities.
Document Chunk Filter removes the chunk files that do not contain a mention of any of the desired entities.
Each chunk file may contain thousands of documents --- each document is expensive to process.
The Document Filter removes documents that do not contain a mention of an entity.
This two-level filter allows us to perform detailed slower processing over a smaller set of documents.
Not all chunk files contain mention of the entities so filtering out large chunk files early saves on I/O and processing.
Document Chunk Filter discards non-mentioning chunk files and promotes chunk files as soon as an entity mention is found.
%Processing StreamItems on the other hand is done in Java with ideas in mind for later on extensibility by adding other Java libraries.
The document filter additionally notes the sentences that contain entity mentions.
This data is passed to the Slot Filling system.

% Note: Describe the algorithms of each phase
% Talk in abstract terms not implementation.
% Use formal representations (Math, SQL etc)

%\ceg{This section should be structured as follows:
%1: Introduce CCR (Motivation, Expectations)
%2: Our high level approach
%3: Discussion of our design (Like already discussed)
%}

\subsection{Slot Filling}
\label{sec:slotfilling}
%\ceg{See the previous note.}
Streaming Slot Filling (SSF) extracts fact values from sentences according to a list of patterns.
Table~\ref{table:slotNameOntology} lists the slot relationships that we looks to extract.
In Figure~\ref{fig:system} we refer to this task as \textit{Slot Filling}.

%Slot filling is done by pattern matching documents with manually produced patterns for slots of interest.
%The way we do this is by observing a sentence that has a mention of the entity or one of its coreference.
%An anchor word in the sentence related to the slot name is located and we match either left or right of
%the anchor word for potential slot values.

%In the data set, we are given a date range of documents as training data. Instead of building a classifier we use pattern matching methods to find corresponding slot values for entities. 
%Pattern matching is simple to manipulate results and implement. Additionally, a classifier approach is more difficult to evaluate and explain results due to the lack of proper training data.

SSF reads documents filtered by the Wikipedia Citation step and fetches and tags sentences containing WP entities.
All entities are extracted from the document using a natural language processing
tool\footnote{Lingpipe (available in the dataset) provides entity tags
and in-document coreference. http://alias-i.com/lingpipe/}.
In the next section, we describe how WP entities are matched against the set of patterns.
Following, we discuss our approach to inference over the extracted facts.

\begin{algorithm}
  \caption{Slot Value Extraction Pseudocode}
  \textbf{List of entities $\mathcal{E} = \{e_0, \ldots, e_{170}\}$}\\
  \textbf{List of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
  \textbf{List of documents containing entities $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\

  \begin{algorithmic}%[1]
    \FOR{$si \in \mathcal{S}$}
    \FOR{$sentence \in si$}
    \FOR{$entity \in \mathcal{E}$}
    \IF{Contains($sentence$, $entity$)}
    \FOR{$pattern \in P $ suitable for $entity$} 
    \IF{Satisfies($sentence$, $pattern$)}
    \STATE Emit($sentence$, $pattern$)
  \ENDIF
\ENDFOR
          \ENDIF
        \ENDFOR
      \ENDFOR
    \ENDFOR
  \end{algorithmic}
\end{algorithm}

\subsubsection{Rule Engine}

%\textbf{Format of Patterns.}
A pattern is a template of a fact to be extracted and added to a WP entity.
Patterns are used to find and extract facts from text.
A pattern $\mathcal{P}$ is represented as a five-tuple $\mathcal{P} = \langle p_1, p_2, p_3, p_4, p_5 \rangle$.

The first value, $p_1$ represents the type of entity.
These entity types are in the set
 $ \{ \texttt{FAC}, \texttt{ORG}, \texttt{PER} \}$ 
where \texttt{FAC} represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER} represents a person.
%\texttt{FAC}, \texttt{ORG} and \texttt{PER} are Lingpipe entity types.
 $p_2$ represents a slot name.
A list of slot names is present in Table~\ref{table:slotNameOntology}.
The third element $p_3$ is the pattern content --- 
a string found in the sentence that identifies a slot name.
The extractor looks specifically for pattern content.
The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in $p_4$ to explore sentence.
The final element $p_5$ represents the slot value of a pattern. 
%When we match one pattern, we match all the 
%fields except the third field, which is extracted as the final result.
The type of slot value may be the entity type labeled by the named entity extractor,
a noun phrase (\texttt{NP}) tagged by a part of speech tagger
\footnote{OpenNLP was used for part of speech tagging. http://opennlp.apache.org/} or a phrase described in the pattern list.
%For these three kinds of patterns, we implement them in different ways accordingly.

%Next, we explain the patterns with more details, an example of which can be found in Figure~\ref{fig:pattern}. 
Figure~\ref{fig:pattern} contains the example sentence from the introduction labeled by the rule engine. The matching pattern is $\langle$\texttt{PER, DateOfDeath, \textit{passed away}, right, NP}$\rangle$. In the figure, `Boris Berezovsky' matches as an alias for WP entity \textsl{wiki/Boris\_Berezovsky\_(businessman)}, DateOfDeath is the slot name, `passed away' is the content of the pattern, direction is `Right' and the actual value of the slot is `March 2013' which is a Noun Phrase.

%\textbf{Types of patterns}
There are three types of patterns, each distinguished by different types of slot values ($p_5$) in the patterns.
The matching methods using these three types of patterns are implemented according to the different structures of slot values.

\begin{figure}
\centering
%\includegraphics[width=4.5in]{./images/system.eps}
%\includegraphics[width=6in]{./images/Pattern.eps}
%\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
\includegraphics[width = 11cm]{./images/Pattern-crop.pdf}
% cropped pdf created using $ pdfcrop Pattern.pdf
\vspace*{-.1in}
\caption{Pattern matching for rule evaluation. The slot value is on the right side of the 
entity. The pattern context discovered is `passed away' with a value of `March 2013'. This conforms to type II of our pattern categories.}\label{fig:pattern}
\vspace*{-.2in}
\end{figure}

\textbf{Type I.} This pattern type is driven by the entity type.
For example, in pattern $\langle$\texttt{PER, FounderOf, \textit{founder}, right, ORG}$\rangle$ the \texttt{PER} 
tag means the entity we are finding slot values for is a PER entity;
\texttt{FounderOf} means this is a pattern for FounderOf slot.
\textit{founder} is the word we match in a sentence - the content of pattern occuring in the sentence;
\texttt{right} means that we are going to the right part of the sentence to match the pattern and find the slot value;
ORG means the slot value should be a ORG entity to the right of the entity.

\textbf{Type II.} This pattern type, after finding a matching pattern content, looks for a noun phrase (NP)
that is representative of the slot value.
For example, pattern $\langle$\texttt{PER, AwardsWon, \textit{awarded}, right, NP}$\rangle$
is looking for a noun phrase after the \textit{awarded} that may represent an award.
Titles and awards are not named entity tagged hence the use of the part of speech tagger to fetch the noun phrases.

\textbf{Type III.} These types of facts are best discovered by hard coding the slot values.
Examples of these include time phrases: $\langle$\texttt{PER, DateOfDeath, \textit{died}, right, \textit{last night}}$\rangle$.
In this pattern, the phrase \textit{last night} is exactly searched in the text {last night} to the right of the term \textit{died}.
The intuition behind this pattern is in news articles that report events in the past relative to the article. 
For example, an article will mention that  
a person died `last night' instead of mentioning precise date-time information.
Additionally, part of speech taggers and name entity extractors did not label these terms such as 
\textit{last night} as a DATE entity.

\subsection{Constraints and Inference}%\ceg{what specifically about the algorithm causes duplicates and errors? --- I asked Yang to elaborate on this as he is more familiar but still not sure what's causing those issues} 
\label{sec:constraintsandinference}

Our data set contains some duplicate webpages, webpage texts with similar content, 
and some of the entity tags are incomplete.
This causes some duplicates or highly similar content in the extracted list. 
We implement a filter to remove duplicates or the fact extractions that match patterns that are general and highly susceptible to be noisy.
The data contains duplicates and incorrect extractions.
We define rules to read ordered sets of facts to sanitize the output.
The input is processed in time order, in a tuple-at-a-time fashion to allow rules to discover noisy slots 
that appears in close proximity.
%We found that the proximity of an extraction has a high correlation on the presence of duplicates. 
We define two classes of rules: \textit{deduplication} and \textit{inference} rules.

The output contains many duplicate entries.
As we read the list of extracted slots we create rules to define ``duplicate''.
Duplicates can be present in a window of rows; we use a window size of 2 meaning we only be adjacent rows.
Two rows are duplicates if they have the same exact extraction or if the rows have the same slot name and a similar slot value or if the extracted sentence for a particular slot types come from the same sentence.

New slots can be deduced from existing slots by defining inference rules.
For example, two slots for the task are ``FounderOf'' and ``FoundedBy''.
A safe assumption is these slot names are biconditional logical connectives with the entities and slot values.
Therefore, we can express a rule ``$X$ FounderOf $Y$'' $\leftrightarrow$ ``$Y$ FoundedBy $X$'' where $X$ and $Y$ are single unique entities.
Additionally, we found that the slot names ``Contact\_Meet\_PlaceTime'' could be inferred as ``Contact\_Meet\_Entity'' if the Entity was a FAC and the extracted sentence contained an additional ORG/FAC tag.
We also remove erroneous slots that have extractions that are thousands of characters in length or tool small.
Errors of extracting long sentences can typically be attributed to poor sentence parsing of web documents.
We have some valid ``small'' extractions. For example, a comma may separate a name and a title (e.g. ``John, Professor at MIT'').
But such extraction rules can be particularly noisy, so we check to see if the extracted values have good entity values.

\section{Formatting Requirements in Brief}
We need source and PDF files that can be used in a variety of ways and can be output on a variety of devices. AAAI imposes some requirements on your source and PDF files that must be followed. Most of these requirements are based on our efforts to standardize conference manuscript properties and layout. These requirements are as follows, and all papers submitted to AAAI for publication must comply:

\begin{itemize}
\item Your .tex file must compile in PDF\LaTeX{} --- \textbf{ no .ps or .eps figure files.}
\item All fonts must be embedded in the PDF file --- \textbf{ this includes your figures.}
\item Modifications to the style sheet (or your document) in an effort to avoid extra page charges are NOT allowed.
\item No type 3 fonts may be used (even in illustrations).
\item Your title must follow US capitalization rules.
\item \LaTeX{} documents must use the Times or Nimbus font package (do not use Computer Modern for the text of your paper).
\item No \LaTeX{} 209 documents may be used or submitted.
\item Fonts that require non-English language support (CID and Identity-H) must be converted to outlines or removed from the document (even if they are in a graphics file embedded in the document). 
\item Two-column format in AAAI style is required for all papers.
\item The paper size for final submission must be US letter. No exceptions.
\item The source file must exactly match the PDF.
\item The document margins must be as specified in the formatting instructions.
\item The number of pages and the file size must be as specified for your event.
\item No document may be password protected.
\item Neither the PDFs nor the source may contain any embedded links or bookmarks.
\item Your source and PDF must not have any page numbers, footers, or headers.
\item Your PDF must be compatible with Acrobat 5 or higher.
\item Your \LaTeX{} source file (excluding references) must consist of a \textbf{single} file (use of the ``input" command is not allowed.
\item Your graphics must be sized appropriately outside of \LaTeX{} (do not use the ``clip" command) .
\end{itemize}

If you do not follow the above requirements, it is likely that we will be unable to publish your paper.

\section{What Files to Submit}
You must submit the following items to ensure that your paper is published:
\begin{itemize}
\item A fully-compliant PDF file.
\item Your  \LaTeX{}  source file submitted as a \textbf{single} .tex file (do not use the ``input" command to include sections of your paper --- every section must be in the single source file). The only exception is the bibliography, which you may include separately. Your source must compile on our system, which includes the standard \LaTeX{} support files.
\item All your graphics files.
\item The \LaTeX{}-generated files (e.g. .aux and .bib file, etc.) for your compiled source.
\item All the nonstandard style files (ones not commonly found in standard \LaTeX{} installations) used in your document (including, for example, old algorithm style files). If in doubt, include it.
\end{itemize}

Your \LaTeX{} source will be reviewed and recompiled on our system (if it does not compile, you may incur late fees).   \textbf{Do not submit your source in multiple text files.} Your single \LaTeX{} source file must include all your text, your bibliography (formatted using aaai.bst), and any custom macros. Accompanying this source file, you must also supply any nonstandard (or older) referenced style files and all your referenced graphics files.

Your files should work without any supporting files (other than the program itself) on any computer with a standard \LaTeX{} distribution. Place your PDF and source files in a single tar, zipped, gzipped, stuffed, or compressed archive. Name your source file with your last (family) name.

\textbf{Do not send files that are not actually used in the paper.} We don't want you to send us any files not needed for compiling your paper, including, for example, this instructions file, unused graphics files, and so forth.  A shell script (created by an AAAI member --- it might not work without modification on your system) that might help you create the \LaTeX{} source package is included in the Author Kit.

\section{Using \LaTeX{} to Format Your Paper}

The latest version of the AAAI style file is available on AAAI's website. Download this file and place it in a file named ``aaai.sty" in the \TeX\ search path. Placing it in the same directory as the paper should also work. You must download the latest version of the complete author kit so that you will have the latest instruction set.

\subsection{Document Preamble}

In the \LaTeX{} source for your paper, you \textbf{must} place the following lines as shown in the example in this subsection. This command set-up is for three authors. Add or subtract author and address lines as necessary, and uncomment the portions that apply to you. In most instances, this is all you need to do to format your paper in the Times font. The helvet package will cause Helvetica to be used for sans serif, and the courier package will cause Courier to be used for the typewriter font. These files are part of the PSNFSS2e package, which is freely available from many Internet sites (and is often part of a standard installation).

Leave the setcounter for section number depth commented out and set at 0 unless you want to add section numbers to your paper. If you do add section numbers, you must uncomment this line and change the number to 1 (for section numbers), or 2 (for section and subsection numbers). The style file will not work properly with numbering of subsubsections, so do not use a number higher than 2.

\begin{quote}
\begin{small}
\textbackslash documentclass[letterpaper]{article}\\
\% \textit{Required Packages}\\
\textbackslash usepackage\{aaai\}\\
\textbackslash usepackage\{times\}\\
\textbackslash usepackage\{helvet\}\\
\textbackslash usepackage\{courier\}\\
\textbackslash setlength\{\textbackslash pdfpagewidth\}\{8.5in\}
\textbackslash setlength\{\textbackslash pdfpageheight\}\{11in\}\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{PDFINFO for PDF\LaTeX{}}\\
\% Uncomment and complete the following for metadata (your paper must compile with PDF\LaTeX{})\\
\textbackslash pdfinfo\{\\
/Title (Input Your Paper Title Here)\\
/Author (John Doe, Jane Doe)\\
/Keywords (Input your paper's keywords in this optional area)\\
\}\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{Section Numbers}\\
\% Uncomment if you want to use section numbers\\
\% and change the 0 to a 1 or 2\\
\% \textbackslash setcounter\{secnumdepth\}\{0\}\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{Title, Author, and Address Information}\\
\textbackslash title\{Title\}\\
\textbackslash author\{Author 1 \textbackslash and Author 2\textbackslash\textbackslash \\ 
Address line\textbackslash\textbackslash\\ Address line\textbackslash\textbackslash \\
\textbackslash And\\
Author 3\textbackslash\textbackslash\\ Address line\textbackslash\textbackslash\\ Address line\}\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{Body of Paper Begins}\\
\textbackslash begin\{document\}\\
\textbackslash maketitle\\
...\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{References and End of Paper}\\
\textbackslash bibliography\{Bibliography-File\}\\
\textbackslash bibliographystyle\{aaai\}\\
\textbackslash end\{document\}
\end{small}
\end{quote}

\subsection{Inserting Document Metadata with \LaTeX{}}
PDF files contain document summary information that enables us to create an Acrobat index (pdx) file, and also allows search engines to locate and present your paper more accurately. \textbf{Document Metadata  for Author and Title are REQUIRED.}

If your paper includes illustrations that are not compatible with PDF\TeX{} (such as .eps or .ps documents), you will need to convert them. The epstopdf package will usually work for eps files. You will need to convert your ps files to PDF however.

\textit{Important:} Do not include \textit{any} \LaTeX{} code or nonascii characters (including accented characters) in the metadata. The data in the metadata must be completely plain ascii. It may not include slashes, accents, linebreaks, unicode, or any \LaTeX{} commands. Type the title exactly as it appears on the paper (minus all formatting). Input the author names in the order in which they appear on the paper (minus all accents), separating each author by a comma. You may also include keywords in the Keywords field.

\subsection{Preparing Your Paper}

After the preamble above, you should prepare your paper as follows:

\begin{quote}
\begin{small}
\textbackslash begin\{document\}\\
\textbackslash maketitle\\
...\\
\textbackslash bibliography\{Bibliography-File\}\\
\textbackslash bibliographystyle\{aaai\}\\
\textbackslash end\{document\}\\
\end{small}
\end{quote}
\subsection{Incompatible Packages}
The following packages are incompatible with aaai.sty and/or aaai.bst and must not be used (this list is not exhaustive --- there are others as well):
\begin{itemize}
\item hyperref
\item natbib
\item geometry
\item titlesec
\item layout
\item caption
\item titlesec
\item T1 fontenc package (install the CM super fonts package instead)
\end{itemize}

\subsection{Illegal Commands}
The following commands may not be used in your paper:
\begin{itemize}
\item \textbackslash input
\item \textbackslash vspace (when used before or after a section or subsection)
\item \textbackslash addtolength 
\item \textbackslash columnsep
\item \textbackslash top margin (or text height or addsidemargin or even side margin)
\end{itemize}

\subsection{Paper Size, Margins, and Column Width}
Papers must be formatted to print in two-column format on 8.5 x 11 inch US letter-sized paper. The margins must be exactly as follows: 
\begin{itemize}
\item Top margin: .75 inches
\item Left margin: .75 inches
\item Right margin: .75 inches
\item Bottom margin: 1.25 inches
\end{itemize}

The default paper size in most installations of \LaTeX{} is A4. However, because we require that your electronic paper be formatted in US letter size, you will need to alter the default for this paper to US letter size. Assuming you are using the 2e version of \LaTeX{}, you can do this by including the [letterpaper] option at the beginning of your file: 
\textbackslash documentclass[letterpaper]{article}.

This command is usually sufficient to change the format. Sometimes, however, it may not work. Use PDF\LaTeX{} and include
\textbackslash setlength\{\textbackslash pdfpagewidth\}\{8.5in\}
\textbackslash setlength\{\textbackslash pdfpageheight\}\{11in\}
in your preamble.

\textbf{Do not use the Geometry package to alter the page size.} Use of this style file alters aaai.sty and will result in your paper being rejected.

\subsubsection{Column Width and Margins.}
To ensure maximum readability, your paper must include two columns. Each column should be 3.3 inches wide (slightly more than 3.25 inches), with a .375 inch (.952 cm) gutter of white space between the two columns. The aaai.sty file will automatically create these columns for you.

\subsection{Overlength Papers}
If your paper is too long, turn on \textbackslash frenchspacing, which will reduce the space after periods. Next,  shrink the size of your graphics. Use \textbackslash centering instead of \textbackslash begin\{center\} in your figure environment. If these two methods don't work, you may minimally use the following. For floats (tables and figures), you may minimally reduce \textbackslash floatsep, \textbackslash textfloatsep, \textbackslash abovecaptionskip, and \textbackslash belowcaptionskip. For mathematical environments, you may minimally reduce \textbackslash abovedisplayskip, \textbackslash belowdisplayskip, and \textbackslash arraycolsep. You may also alter the size of your bibliography by inserting \textbackslash fontsize\{9.5pt\}\{10.5pt\} \textbackslash selectfont
right before the bibliography.

Commands that alter page layout are forbidden. These include \textbackslash columnsep, \textbackslash topmargin, \textbackslash topskip, \textbackslash textheight, \textbackslash textwidth, \textbackslash oddsidemargin, and \textbackslash evensizemargin (this list is not exhaustive). If you alter page layout, you will be required to pay the page fee \textit{plus} a reformatting fee. Other commands that are questionable and may cause your paper to be rejected include  \textbackslash parindent, and \textbackslash parskip. Commands that alter the space between sections are also questionable. The title sec package is not allowed. Regardless of the above, if your paper is obviously ``squeezed" it is not going to to be accepted. Before using every trick you know to make your paper a certain length, try reducing the size of your graphics or cutting text instead or (if allowed) paying the extra page charge. It will be cheaper in the long run.

\subsection{Figures}
Your paper must compile in PDF\LaTeX{}. Consequently, all your figures must be .jpg, .png, or .pdf. You may not use the .gif (the resolution is too low), .ps, or .eps file format for your figures.

When you include your figures, you must crop them \textbf{outside} of \LaTeX{}. The command \textbackslash includegraphics*[clip=true, viewport 0 0 10 10]{...} might result in a PDF that looks great, but the image is \textbf{not really cropped.} The full image can reappear when page numbers are applied or color space is standardized.

\subsection{Type Font and Size}
Your paper must be formatted in Times Roman or Nimbus. We will not accept papers formatted using Computer Modern or Palatino or some other font as the text or heading typeface. Sans serif, when used, should be Courier. Use Symbol or Lucida or Computer Modern for \textit{mathematics only. }

Do not use type 3 fonts for any portion of your paper, including graphics. Type 3 bitmapped fonts are designed for fixed resolution printers. Most print at 300 dpi even if the printer resolution is 1200 dpi or higher. They also often cause high resolution imagesetter devices and our PDF indexing software to crash. Consequently, AAAI will not accept electronic files containing obsolete type 3 fonts. Files containing those fonts (even in graphics) will be rejected.

Fortunately, there are effective workarounds that will prevent your file from embedding type 3 bitmapped fonts. The easiest workaround is to use the required times, helvet, and courier packages with \LaTeX{}2e. (Note that papers formatted in this way will still use Computer Modern for the mathematics. To make the math look good, you'll either have to use Symbol or Lucida, or you will need to install type 1 Computer Modern fonts --- for more on these fonts, see the section ``Obtaining Type 1 Computer Modern.")

If you are unsure if your paper contains type 3 fonts, view the PDF in Acrobat Reader. The Properties/Fonts window will display the font name, font type, and encoding properties of all the fonts in the document. If you are unsure if your graphics contain type 3 fonts (and they are PostScript or encapsulated PostScript documents), create PDF versions of them, and consult the properties window in Acrobat Reader.

The default size for your type should be ten-point with twelve-point leading (line spacing). Start all pages (except the first) directly under the top margin. (See the next section for instructions on formatting the title page.) Indent ten points when beginning a new paragraph, unless the paragraph begins directly below a heading or subheading.

\subsubsection{Obtaining Type 1 Computer Modern for \LaTeX{}.}

If you use Computer Modern for the mathematics in your paper (you cannot use it for the text) you may need to download type 1 Computer fonts. They are available without charge from the American Mathematical Society:
http://www.ams.org/tex/type1-fonts.html.

\subsection{Title and Authors}
Your title must appear in mixed case (nouns, pronouns, and verbs are capitalized) near the top of the first page, centered over both columns in sixteen-point bold type (twenty-four point leading). This style is called ``mixed case." Author's names should appear below the title of the paper, centered in twelve-point type (with fifteen point leading), along with affiliation(s) and complete address(es) (including electronic mail address if available) in nine-point roman type (the twelve point leading). (If the title is long, or you have many authors, you may reduce the specified point sizes by up to two points.) You should begin the two-column format when you come to the abstract.

\subsubsection{Formatting Author Information}
Author information can be set in a number of different styles, depending on the number of authors and the number of affiliations you need to display. For several authors from the same institution, use \textbackslash and:

\begin{quote}
\begin{small}
\textbackslash author\{Author 1 \textbackslash and  ...  \textbackslash and Author \textit{n}\textbackslash \textbackslash  \\
Address line \textbackslash \textbackslash ~... \textbackslash \textbackslash ~Address line\}
\end{small}
\end{quote}

\noindent If the names do not fit well on one line use:

\begin{quote}
\begin{small}
\textbackslash author\{Author 1\}\textbackslash \textbackslash \\ \{\textbackslash bf Author 2\}\textbackslash \textbackslash ~ 
... \textbackslash \textbackslash ~\{\textbackslash bf Author \textit{n}\}\textbackslash \textbackslash \\
Address line \textbackslash \textbackslash ~ ... \textbackslash \textbackslash ~ Address line\}
\end{small}
\end{quote}

\noindent For authors from different institutions, use \textbackslash And:

\begin{quote}
\begin{small}
\textbackslash author\{Author 1\textbackslash \textbackslash ~ Address line \textbackslash \textbackslash ~...  \textbackslash \textbackslash ~ Address line
\textbackslash And  ...  
\textbackslash And
Author \textit{n}\textbackslash \textbackslash \\ Address line\textbackslash \textbackslash ~
... \textbackslash \textbackslash ~
Address line\}
\end{small}
\end{quote}

\noindent To start a separate ``row" of authors, use \textbackslash AND:
\begin{quote}
\begin{small}
\textbackslash author\{Author 1\textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\
\textbackslash AND\\
Author 2 \textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\
\textbackslash And\\
Author 3 \textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\\}
\end{small}
\end{quote}

\noindent If the title and author information does not fit in the area allocated, place
\textbackslash setlength\textbackslash titlebox\{\textit{height}\}
after the \textbackslash documentclass line where \{\textit{height}\} is something like 2.5in.

\subsection{\LaTeX{} Copyright Notice}
The copyright notice automatically appears if you use aaai.sty. If you are creating a technical report, it is not necessary to include this notice. You may disable the copyright line using the \verb+\+nocopyrightcommand. To change the entire text of the copyright slug, use:
\textbackslash copyrighttext \{\emph{text}\}.
Either of these must appear before \textbackslash maketitle. Please be advised, however, that \textit{if you disable or change the copyright line and transfer of copyright is required, your paper will not be published.}

\subsection{Credits}
Any credits to a sponsoring agency should appear in the acknowledgments section, unless the agency requires different placement. If it is necessary to include this information on the front page, use
\textbackslash thanks in either the \textbackslash author or \textbackslash title commands.
For example:
\begin{quote}
\begin{small}
\textbackslash title\{Very Important Results in AI\textbackslash thanks\{This work is
 supported by everybody.\}\}
\end{small}
\end{quote}
Multiple \textbackslash thanks commands can be given. Each will result in a separate footnote indication in the author or title with the corresponding text at the botton of the first column of the document. Note that the \textbackslash thanks command is fragile. You will need to use \textbackslash protect.

Please do not include \textbackslash pubnote commands in your document.

\subsection{Abstract}
The abstract must be placed at the beginning of the first column, indented ten points from the left and right margins. The title “Abstract” should appear in ten-point bold type, centered above the body of the abstract. The abstract should be set in nine-point type with ten-point leading. This concise, one-paragraph summary should describe the general thesis and conclusion of your paper. A reader should be able to learn the purpose of the paper and the reason for its importance from the abstract. The abstract should be no more than two hundred words in length. (Authors who are submitting short one- or two-page extended extracts should provide a short abstract of only a sentence or so.) \textbf{Do not include references in your abstract!}

\subsection{Page Numbers}

Do not \textbf{ever} print any page numbers on your paper.

\subsection{Text }
The main body of the paper must be formatted in ten-point with twelve-point leading (line spacing).

\subsection{Citations}
Citations within the text should include the author's last name and year, for example (Newell 1980). Append lower-case letters to the year in cases of ambiguity. Multiple authors should be treated as follows: (Feigenbaum and Engelmore 1988) or (Ford, Hayes, and Glymour 1992). In the case of four or more authors, list only the first author, followed by et al. (Ford et al. 1997).

\subsection{Extracts}
Long quotations and extracts should be indented ten points from the left and right margins.

\begin{quote}
This is an example of an extract or quotation. Note the indent on both sides. Quotation marks are not necessary if you offset the text in a block like this, and properly identify and cite the quotation in the text.

\end{quote}

\subsection{Footnotes}
Avoid footnotes as much as possible; they interrupt the reading of the text. When essential, they should be consecutively numbered throughout with superscript Arabic numbers. Footnotes should appear at the bottom of the page, separated from the text by a blank line space and a thin, half-point rule.

\subsection{Headings and Sections}
When necessary, headings should be used to separate major sections of your paper. Remember, you are writing a short paper, not a lengthy book! An overabundance of headings will tend to make your paper look more like an outline than a paper.

First-level heads should be twelve-point Times Roman bold type, mixed case (initial capitals followed by lower case on all words except articles, conjunctions, and prepositions, which should appear entirely in lower case), with fifteen-point leading, centered, with one blank line preceding them and three additional points of leading following them. Second-level headings should be eleven-point Times Roman bold type, mixed case, with thirteen-point leading, flush left, with one blank line preceding them and three additional points of leading following them. Do not skip a line between paragraphs. Third-level headings should be run in with the text, ten-point Times Roman bold type, mixed case, with twelve-point leading, flush left, with six points of additional space preceding them and no additional points of leading following them.

\subsubsection{Section Numbers}
The use of section numbers in AAAI Press papers is optional. To use section numbers in \LaTeX{}, uncomment the setcounter line in your document preamble and change the 0 to a 1 or 2. Section numbers should not be used in short poster papers.

\subsubsection{Section Headings.}
Sections should be arranged and headed as follows:

\subsubsection{Acknowledgments.}
The acknowledgments section, if included, appears after the main body of text and is headed ``Acknowledgments." This section includes acknowledgments of help from associates and colleagues, credits to sponsoring agencies, financial support, and permission to publish. Please acknowledge other contributors, grant support, and so forth, in this section. Do not put acknowledgments in a footnote on the first page. If your grant agency requires acknowledgment of the grant on page 1, limit the footnote to the required statement, and put the remaining acknowledgments at the back. Please try to limit acknowledgments to no more than three sentences.

\subsubsection{Appendices.}
Any appendices follow the acknowledgments, if included, or after the main body of text if no acknowledgments appear.

\subsubsection{References}
The references section should be labeled ``References" and should appear at the very end of the paper (don't end the paper with references, and then put a figure by itself on the last page). A sample list of references is given later on in these instructions. Please use a consistent format for references. Poorly prepared or sloppy references reflect badly on the quality of your paper and your research. Please prepare complete and accurate citations.

\subsection{Illustrations and Figures}
Figures, drawings, tables, and photographs should be placed throughout the paper near the place where they are first discussed. Do not group them together at the end of the paper. If placed at the top or bottom of the paper, illustrations may run across both columns. Figures must not invade the top, bottom, or side margin areas. Figures must be inserted using the \textbackslash usepackage\{graphicx\}. Number figures sequentially, for example, figure 1, and so on.

The illustration number and caption should appear under the illustration. Labels, and other text in illustrations must be at least nine-point type.

\subsubsection{Low-Resolution Bitmaps.}
You may not use low-resolution (such as 72 dpi) screen-dumps and GIF files---these files contain so few pixels that they are always blurry, and illegible when printed. If they are color, they will become an indecipherable mess when converted to black and white. This is always the case with gif files, which should never be used. The resolution of screen dumps can be increased by reducing the print size of the original file while retaining the same number of pixels. You can also enlarge files by manipulating them in software such as PhotoShop. Your figures should be a minimum of 266 dpi when incorporated into your document.

\subsubsection{\LaTeX{} Overflow.}
\LaTeX{} users please beware: \LaTeX{} will sometimes put portions of the figure or table or an equation in the margin. If this happens, you need to scale the figure or table down, or reformat the equation. Check your log file! You must fix any overflow into the margin (that means no overfull boxes in \LaTeX{}). If you don't, the overflow text will simply be eliminated. \textbf{Nothing is permitted to intrude into the margins.}

\subsubsection{Using Color.}
Your paper will be printed in black and white and grayscale. Consequently, because conversion to grayscale can cause undesirable effects (red changes to black, yellow can disappear, and so forth), we strongly suggest you avoid placing color figures in your document. Of course, any reference to color will be indecipherable to your reader.

\subsubsection{Drawings.}
We suggest you use computer drawing software (such as Adobe Illustrator or, (if unavoidable), the drawing tools in Microsoft Word) to create your illustrations. Do not use Microsoft Publisher. These illustrations will look best if all line widths are uniform (half- to two-point in size), and you do not create labels over shaded areas. Shading should be 133 lines per inch if possible. Use Times Roman or Helvetica for all figure call-outs. \textbf{Do not use hairline width lines} --- be sure that the stroke width of all lines is at least .5 pt. Zero point lines will print on a laser printer, but will completely disappear on the high-resolution devices used by our printers.

\subsubsection{Photographs and Images.}
Photographs and other images should be in grayscale (color photographs will not reproduce well; for example, red tones will reproduce as black, yellow may turn to white, and so forth) and set to a minimum of 266 dpi. Do not prescreen images.

\subsubsection{Resizing Graphics.}
Resize your graphics \textbf{before} you include them with LaTeX. You may \textbf{not} use trim or clip options as part of your \textbackslash includgraphics command. Resize the media box of your PDF using a graphics program instead.

\subsubsection{Fonts in Your Illustrations}
You must embed all fonts in your graphics before including them in your LaTeX document.

\subsection{References} 
The aaai.sty file includes a set of definitions for use in formatting references with BibTeX. These definitions make the bibliography style fairly close to the one specified below. To use these definitions, you also need the BibTeX style file ``aaai.bst," available in the author kit on the AAAI web site. Then, at the end of your paper but before \textbackslash end{document}, you need to put the following lines:

\begin{quote}
\begin{small}
\textbackslash bibliographystyle\{aaai\}
\textbackslash bibliography\{bibfile1,bibfile2,...\}
\end{small}
\end{quote}

The list of files in the \textbackslash  bibliography command should be the names of your BibTeX source files (that is, the .bib files referenced in your paper).

The following commands are available for your use in citing references:
\begin{quote}
\begin{small}
\textbackslash cite: Cites the given reference(s) with a full citation. This appears as ``(Author Year)'' for one reference, or ``(Author Year; Author Year)'' for multiple references.\\
\textbackslash shortcite: Cites the given reference(s) with just the year. This appears as ``(Year)'' for one reference, or ``(Year; Year)'' for multiple references.\\
\textbackslash citeauthor: Cites the given reference(s) with just the author name(s) and no parentheses.\\
\textbackslash citeyear: Cites the given reference(s) with just the date(s) and no parentheses.
\end{small}
\end{quote}

\textbf{Warning:} The aaai.sty file is incompatible with the hyperref and natbib packages. If you use either, your references will be garbled.

Formatted bibliographies should look like the following examples.

\smallskip \noindent \textit{Book with Multiple Authors}\\
Engelmore, R., and Morgan, A. eds. 1986. \textit{Blackboard Systems.} Reading, Mass.: Addison-Wesley.

\smallskip \noindent \textit{Journal Article}\\
Robinson, A. L. 1980a. New Ways to Make Microcircuits Smaller. \textit{Science} 208: 1019--1026.

\smallskip \noindent \textit{Magazine Article}\\
Hasling, D. W.; Clancey, W. J.; and Rennels, G. R. 1983. Strategic Explanations in Consultation. \textit{The International Journal of Man-Machine Studies} 20(1): 3--19.

\smallskip \noindent \textit{Proceedings Paper Published by a Society}\\
Clancey, W. J. 1983b. Communication, Simulation, and Intelligent Agents: Implications of Personal Intelligent Machines for Medical Education. In Proceedings of the Eighth International Joint Conference on Artificial Intelligence, 556--560. Menlo Park, Calif.: International Joint Conferences on Artificial Intelligence, Inc.

\smallskip \noindent \textit{Proceedings Paper Published by a Press or Publisher}\\
Clancey, W. J. 1984. Classification Problem Solving. In \textit{Proceedings of the Fourth National Conference on Artificial Intelligence,} 49--54. Menlo Park, Calif.: AAAI Press.

\smallskip \noindent \textit{University Technical Report}\\
Rice, J. 1986. Poligon: A System for Parallel Problem Solving, Technical Report, KSL-86-19, Dept. of Computer Science, Stanford Univ.

\smallskip \noindent \textit{Dissertation or Thesis}\\
Clancey, W. J. 1979b. Transfer of Rule-Based Expertise through a Tutorial Dialogue. Ph.D. diss., Dept. of Computer Science, Stanford Univ., Stanford, Calif.

\smallskip \noindent \textit{Forthcoming Publication}\\
Clancey, W. J. 1986a. The Engineering of Qualitative Models. Forthcoming.

\section{Producing Reliable PDF\\Documents with \LaTeX{}}
Generally speaking, PDF files are platform independent and accessible to everyone. When creating a paper for a proceedings or publication in which many PDF documents must be merged and then printed on high-resolution PostScript RIPs, several requirements must be met that are not normally of concern. Thus to ensure that your paper will look like it does when printed on your own machine, you must take several precautions:
\begin{itemize}
\item Use type 1 fonts (not type 3 fonts)
\item Use only standard Times, Nimbus, and CMR font packages (not fonts like F3 or fonts with tildes in the names or fonts---other than Computer Modern---that are created for specific point sizes, like Times\~{}19) or fonts with strange combinations of numbers and letters
\item Embed all fonts when producing the PDF
\item Do not use the [T1]{fontenc} package (install the CM super fonts package instead)
\end{itemize}

\subsection{Creating Output Using PDF\LaTeX{} Is Required}
By using the PDF\TeX{} program instead of straight \LaTeX{} or \TeX{}, you will probably avoid the type 3 font problem altogether (unless you use a package that calls for metafont). PDF\LaTeX{} enables you to create a PDF document directly from \LaTeX{} source. The one requirement of this software is that all your graphics and images must be available in a format that PDF\LaTeX{} understands (normally PDF).

PDF\LaTeX{}'s default is to create documents with type 1 fonts. If you find that it is not doing so in your case, it is likely that one or more fonts are missing from your system or are not in a path that is known to PDF\LaTeX{}.

\subsubsection{dvipdf Script}
Scripts such as dvipdf which ostensibly bypass the Postscript intermediary should not be used since they generally do not instruct dvips to use the config.pdf file.

\subsubsection{dvipdfm}
Do not use this dvi-PDF conversion package if your document contains graphics (and we recommend you avoid it even if your document does not contain graphics).

\subsection{Ghostscript}
\LaTeX{} users should not use GhostScript to create their PDFs.

\subsection{Graphics}
If you are still finding type 3 fonts in your PDF file, look at your graphics! \LaTeX{} users should check all their imported graphics files as well for font problems.

\section{Proofreading Your PDF}
Please check all the pages of your PDF file. Is the page size A4? Are there any type 3, Identity-H, or CID fonts? Are all the fonts embedded? Are there any areas where equations or figures run into the margins? Did you include all your figures? Did you follow mixed case capitalization rules for your title? Did you include a copyright notice? Do any of the pages scroll slowly (because the graphics draw slowly on the page)? Are URLs underlined and in color? You will need to fix these common errors before submitting your file.

\section{Improperly Formatted Files }
In the past, AAAI has corrected improperly formatted files submitted by the authors. Unfortunately, this has become an increasingly burdensome expense that we can no longer absorb. Consequently, if your file is improperly formatted, it may not be possible to include your paper in the publication. If time allows, however, you will be notified via e-mail (with a copy to the program chair) of the problems with your file and given the option of correcting the file yourself (and paying a late fee) or asking that AAAI have the file corrected for you, for an additional fee. If you opt to correct the file yourself, please note that we cannot provide you with any additional advice beyond that given in your packet. Files that are not corrected after a second attempt will be withdrawn.

\subsection{\LaTeX{} 209 Warning}
If you use \LaTeX{} 209 we will not be able to publish your paper. Convert your paper to \LaTeX{}2e.

\section{Naming Your Electronic File}
We request that you name your \LaTeX{} source file with your last name (family name) so that it can easily be differentiated from other submissions. If you name your files with the name of the event or ``aaai" or ``paper" or ``camera-ready" or some other generic or indecipherable name, you bear all risks of loss --- it is extremely likely that your file may be overwritten.

\section{Submitting Your Electronic Files to AAAI}
Submitting your files to AAAI is a two-step process. It is explained fully in the author registration and submission instructions. Please consult this document for details on how to submit your paper.

\section{Inquiries} 
If you have any questions about the preparation or submission of your paper as instructed in this document, please contact AAAI Press at the address given below. If you have technical questions about implementation of the aaai style file, please contact an expert at your site. We do not provide technical support for \LaTeX{} or any other software package. To avoid problems, please keep your paper simple, and do not incorporate complicated macros and style files.

\begin{quote}
\noindent AAAI Press\\
2275 East Bayshore Road, Suite 160\\
Palo Alto, California 94303\\ 
\textit{Telephone:} (650) 328-3123\\ 
\textit{E-mail:} See the submission instructions for your particular conference or event.
\end{quote}

\section{Additional Resources}
\LaTeX{} is a difficult program to master. If you've used that software, and this document didn't help or some items were not explained clearly, we recommend you read Michael Shell's excellent document (testflow doc.txt V1.0a 2002/08/13) about obtaining correct PS/PDF output on \LaTeX{} systems. (It was written for another purpose, but it has general application as well). It is available at www.ctan.org in the tex-archive.

\section{ Acknowledgments}
AAAI is especially grateful to Peter Patel Schneider for his work in implementing the aaai.sty file, liberally using the ideas of other style hackers, including Barbara Beeton. We also acknowledge with thanks the work of George Ferguson for his guide to using the style and BibTeX files --- which has been incorporated into this document  --- and Hans Guesgen, who provided several timely modifications, as well as the many others who have, from time to time, sent in suggestions on improvements to the AAAI style.

The preparation of the \LaTeX{} and Bib\TeX{} files that implement these instructions was supported by Schlumberger Palo Alto Research, AT\&T Bell Laboratories, Morgan Kaufmann Publishers, The Live Oak Press, LLC, and AAAI Press. Bibliography style changes were added by Sunil Issar. \verb+\+pubnote was added by J. Scott Penberthy. George Ferguson added support for printing the AAAI copyright slug. Additional changes to aaai.sty and aaai.bst have been made by the AAAI staff.

\bigskip
\noindent Thank you for reading these instructions carefully. We look forward to receiving your electronic files!

\end{document}

### 2014-01-28 paper/flairs27_AuthorKit/paper.tex
All added, dealing with one error. ! LaTeX Error: Something's wrong--perhaps a missing \item.

@@
 \usepackage[noend]{algorithmic} 
+\usepackage{cite }
+
 \frenchspacing
@@
 
-\section{Formatting Requirements in Brief}
-We need source and PDF files that can be used in a variety of ways and can be output on a variety of devices.
-AAAI imposes some requirements on your source and PDF files that must be followed.
-Most of these requirements are based on our efforts to standardize conference manuscript properties and layout.
-These requirements are as follows, and all papers submitted to AAAI for publication must comply:
+\section{Evaluation}
+\label{sec:results}
 
+We evaluate the effectiveness of extracting slot values for 139 entities.
+We look at the baseline coverage for entities and slot names we present in a 500M page snapshot of the English web.
+We estimate the precision and recall of our extractions over several extracted fact.
+
+Our system was developed on a 32-core server described in Table~\ref{table:serverspec}.
+Each document is annotated using a name entity extraction and in document coreference.
+A bundle of documents are serialized into chunks and encrypted.
+The total size of the data after compression and encryption is 4.5TB~\footnote{TREC Knowledge base acceleration stream corpus is available  http://aws-publicdatasets.s3.amazonaws.com/trec/kba/index.html}.
+Data is ordered into 11952 date-hour buckets ranged from 2011-10-05-00 (5th of October 2011, 12am)
+until 2013-02-13-23 (13th of Feburary 2013, 11pm).
+The first four months of data (October 2011 - February 2012) is for training purposes, 
+and we use this portion for rule and pattern creation and tuning.
+The data set contains text from several web page types as listed in Table~\ref{table:documentsDist}.
+%To have a sense of the scale of objects and compression as an example a 6mb gpg.xz files would become 45 mb thrift objects which can contain a couple of thousand StreamItems depending on their size.
+%Some of the documents have null values for their annotation fields.
+The source code of our system is stored as an open source project where enthusiasts can also contribute to \cite{github}, also the relevant discussion mailing list is accessible here \cite{googlegroups}.
+
+\begin{table}
+\caption{Benchmark Server Specifications}
+\centering
+\label{table:serverspec}
+\begin{tabular}{| c | p{4.8cm} |}
+\hline 
+\textbf{Spec} & \textbf{Details} \\ \hline
+Processor & 32 core AMD Opteron\textsuperscript{TM} 6272 \\ \hline 
+OS & CentOS release 6.4 Final \\ \hline 
+Software Stack & GCC version 4.4.7, Java 1.7.0\_25, Scala 2.9.2, SBT 0.12.3 \\ \hline 
+ RAM & 64GB\\ \hline 
+ Drives & 2x2.7TB disks, 6Gbps, 7200RPM\\ \hline 
+\end{tabular} 
+\end{table}
+
+\begin{table}
+\caption{Document Chunks Distribution }
+\centering
+\label{table:documentsDist}
+
+\begin{tabular}{|p{3.8cm}|p{3cm}|}
+\hline 
+\textbf{Document Type} & \textbf{\# of Documents}\\ 
+\hline 
+Arxiv & 10988  \\ \hline
+ Classified & 34887  \\ \hline
+ Forum & 77674  \\ \hline
+ Linking & 12947  \\ \hline
+ Mainstream News & 141936  \\ \hline
+ Memetracker & 4137  \\ \hline
+ News & 280629  \\ \hline
+ Review & 6347 \\ \hline
+ Social & 688848 \\ \hline
+ Weblog & 740987  \\ \hline
+%\hline 
+\end{tabular} 
+\end{table}
+
+We develop 172 extraction patterns covering each slot-name/entity-type combinations.
+%Our final submission was named \textit{submission\_infer}. 
+%Our results are as follows: Document extraction using query entity matching with aliases, sentence extraction using alias matching and co-reference.
+%Slot extraction using patterns, NER tags and NP tags.
+Out of the 500M documents and 139 entities we found 158,052 documents containing query entities, 17,885 unique extracted slot values for 8 different slots.
+We did not get any results from 31 entities missing and 4 slots.
+
+%On the performance of our initial submission run we performed random sampling via two processes, the results of which are according to Table~\ref{table:initialresult}.
+In Table~\ref{table:initialresult} we performed two samples of a baseline and estimate the correctness of the extractions.
+%\ceg{Add here how the baseline is different from the final submission}
+The first was addressing the overall performance measures of the system, e.g.\ precision and recall.
+The latter experiment was performed over an enhanced version of the system; we included the aliases from WP API, the alias generation process, and some additional patterns. 
+We produced accuracies in range of  54\% and 55\%.
+We classify the errors into two sets, an incorrect entities and incorrect extractions.
+We found 15\% and 17\% incorrect entity names and we identified 27\% and 30\% incorrect value extracted across all entities and slot types.
+The majority of errors were regarding poor slot value extraction patterns and incomplete aliases.
+
+\begin{table}
+\caption{Sampled accuracy of the results of the extracted facts.}
+\centering
+\label{table:initialresult}
+
+\begin{tabular}{| c | c | p{2cm} | p{13mm} |}
+\hline 
+ & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
+\hline 
+Sampling \#1 & 55\% & 17\% & 27\% \\ 
+\hline Sampling \#2 & 54\% & 15\% & 31\%  \\ 
+\hline 
+\end{tabular} 
+\end{table}
+
+%\ceg{Probably should add again here a reason why our method is different from the baseline.}
+After enahncing the system via better and more extraction patterns  we provide more detailed statistics, as displayed in Table~\ref{table:finalresultrecall} and Table~\ref{table:finalresultaccuracy}.
+Table~\ref{table:finalresultrecall} shows the recall for each slot name. 
+Entities can have different coverages across the entire web, some were more popular (William H. Gates) or less well known such as (Stevens Cooperative School).
+Similarly, slot names have various coverages for example \textit{Affiliate} is more probable across the entities when compared to \textit{AwardsWon}. %\ceg{(define `entity coverage' here)}
+The slot name \textit{Affiliate} has was extracted the most number of times; \textit{AwardsWon} contained the next fewest with 38 instances found. 
+,  affiliations of an organization the following cases have been enumerated \cite{tackbp}:
+
+An affiliate relationship can be defined in three general ways~\cite{tackbp}:
 \begin{itemize}
-\item Your .tex file must compile in PDF\LaTeX{} --- \textbf{ no .ps or .eps figure files.}
-\item All fonts must be embedded in the PDF file --- \textbf{ this includes your figures.}
-\item Modifications to the style sheet (or your document) in an effort to avoid extra page charges are NOT allowed.
-\item No type 3 fonts may be used (even in illustrations).
-\item Your title must follow US capitalization rules.
-\item \LaTeX{} documents must use the Times or Nimbus font package (do not use Computer Modern for the text of your paper).
-\item No \LaTeX{} 209 documents may be used or submitted.
-\item Fonts that require non-English language support (CID and Identity-H) must be converted to outlines or removed from the document (even if they are in a graphics file embedded in the document). 
-\item Two-column format in AAAI style is required for all papers.
-\item The paper size for final submission must be US letter. No exceptions.
-\item The source file must exactly match the PDF.
-\item The document margins must be as specified in the formatting instructions.
-\item The number of pages and the file size must be as specified for your event.
-\item No document may be password protected.
-\item Neither the PDFs nor the source may contain any embedded links or bookmarks.
-\item Your source and PDF must not have any page numbers, footers, or headers.
-\item Your PDF must be compatible with Acrobat 5 or higher.
-\item Your \LaTeX{} source file (excluding references) must consist of a \textbf{single} file (use of the ``input" command is not allowed.
-\item Your graphics must be sized appropriately outside of \LaTeX{} (do not use the ``clip" command) .
+\item  A relationship consisting solely of the two groups
+interacting in a specific event context is not enough evidence to constitute a religious/political affiliation; 
+\item Former political or religious affiliations are correct responses for this slot;
+\item  Any relation that is not of parent-child form; a sub-organization is not an affiliate its parent organization but rather a Memberof.
 \end{itemize}
+Affiliate is a generic slot name; extracting affiliate relationships is difficult because the actual relationship must be determined.
+Our patterns for this relationship led to noisy results.
 
-If you do not follow the above requirements, it is likely that we will be unable to publish your paper.
+However, less ambiguous slot names (AssociateOf) obtained higher accuracy but we have recall.
+We developed patterns that explicitly expressed these relationships but we did not create enough patterns to 
+express all forms of those slot names.
 
-\section{What Files to Submit}
-You must submit the following items to ensure that your paper is published:
-\begin{itemize}
-\item A fully-compliant PDF file.
-\item Your  \LaTeX{}  source file submitted as a \textbf{single} .tex file (do not use the ``input" command to include sections of your paper --- every section must be in the single source file).
-The only exception is the bibliography, which you may include separately.
-Your source must compile on our system, which includes the standard \LaTeX{} support files.
-\item All your graphics files.
-\item The \LaTeX{}-generated files (e.g. .aux and .bib file, etc.) for your compiled source.
-\item All the nonstandard style files (ones not commonly found in standard \LaTeX{} installations) used in your document (including, for example, old algorithm style files). If in doubt, include it.
-\end{itemize}
+Table~\ref{table:finalresultaccuracy} addresses the relative accuracy measure per slot value.
+\textit{AssociateOf} has the highest accuracy with 63.6\% and \textit{Affiliate}, \textit{Contact\_Meet\_PlaceTime} and \textit{EmployeeOf} have the lowest with lowest of 1\%, 1\% and 5\% accuracy respectively.
 
-Your \LaTeX{} source will be reviewed and recompiled on our system (if it does not compile, you may incur late fees).
-\textbf{Do not submit your source in multiple text files.} Your single \LaTeX{} source file must include all your text, your bibliography (formatted using aaai.bst), and any custom macros.
-Accompanying this source file, you must also supply any nonstandard (or older) referenced style files and all your referenced graphics files.
+\begin{table}[t]
+\caption{Recall Measure: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
+\centering
+\label{table:finalresultrecall}
+\begin{tabular}{|l|p{13mm}|p{22mm}|}
+\hline 
+ \textbf{Slot Name} & \textbf{Instances Found} & \textbf{Entity \hspace{5 mm} Coverage} \\ 
+\hline 
+Affiliate & 108598 & 80 \\ \hline 
+AssociateOf & 25278 & 106 \\ \hline 
+AwardsWon & 38 & 14 \\ \hline 
+Contact\_Meet\_Entity & 191 & 8 \\ \hline 
+Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
+DateOfDeath & 87 & 14 \\ \hline 
+EmployeeOf & 75 & 16 \\ \hline 
+FoundedBy & 326 & 30 \\ \hline 
+FounderOf & 302 &  29 \\ \hline 
+Titles & 26823 & 118 \\ \hline 
+TopMembers & 314 & 26 \\ \hline
 
-Your files should work without any supporting files (other than the program itself) on any computer with a standard \LaTeX{} distribution.
-Place your PDF and source files in a single tar, zipped, gzipped, stuffed, or compressed archive.
-Name your source file with your last (family) name.
+\end{tabular}
 
-\textbf{Do not send files that are not actually used in the paper.} We don't want you to send us any files not needed for compiling your paper, including, for example, this instructions file, unused graphics files, and so forth.
-A shell script (created by an AAAI member --- it might not work without modification on your system) that might help you create the \LaTeX{} source package is included in the Author Kit.
+\caption{Accuracy Measure: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}
+\centering
+\label{table:finalresultaccuracy}
+\begin{tabular}{|l|p{10mm}|p{10mm}|p{11mm}|}
+\hline 
+ \textbf{Slot Name}  & \textbf{Correct} & \textbf{Wrong Entity} & {\small \textbf{Incorrect Value}} \\ 
+\hline 
+Affiliate & 1\% & 95\% & 5\% \\ \hline 
+AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
+AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
+Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 
+Contact\_Meet\_PlaceTime & 5\% & 20\% & 85\%  \\ \hline 
+DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
+EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
+FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
+FounderOf & 50\% & 0\% & 50\%  \\ \hline 
+Titles & 55\% & 0\% & 45\%  \\ \hline 
+TopMembers & 33\% & 17\% & 50\%  \\ \hline
 
-\section{Using \LaTeX{} to Format Your Paper}
+\end{tabular} 
+\end{table}
 
-The latest version of the AAAI style file is available on AAAI's website.
-Download this file and place it in a file named ``aaai.sty" in the \TeX\ search path.
-Placing it in the same directory as the paper should also work.
-You must download the latest version of the complete author kit so that you will have the latest instruction set.
+\section{Discussion}
 
-\subsection{Document Preamble}
+%In this section we address some of the challenges that we faced during the course of this project. We started 
+%off by trying to use the off-the-shelf tools for this task. We started 
+%by using Scala/Spark~\cite{ferc11} to benefit from the parallelization 
+%performance there. Unfortunately Spark was not performant and the distributed reliability overhead 
+%was much more than tolerable. We moved on to use Scala parallelization  framework itself, and unfortunately it did not satisfy our needs as well; there was 
+%excessive memory overhead on map-reduce jobs. We migrated the core of the 
+%system to Java Parallelism APIs and that was not good enough either, we still demanded 
+%better. So we built our own parallel system which in actual performance had 
+%the least of overhead, the least memory consumption and the most robust memory 
+%model which avoided unpredictable CPU stalls on garbage collections in 
+%processing the corpus.
 
-In the \LaTeX{} source for your paper, you \textbf{must} place the following lines as shown in the example in this subsection.
-This command set-up is for three authors.
-Add or subtract author and address lines as necessary, and uncomment the portions that apply to you.
-In most instances, this is all you need to do to format your paper in the Times font.
-The helvet package will cause Helvetica to be used for sans serif, and the courier package will cause Courier to be used for the typewriter font.
-These files are part of the PSNFSS2e package, which is freely available from many Internet sites (and is often part of a standard installation).
+Table~\ref{table:finalresultrecall} shows the distribution of extracted slot names.
+The number of extraction between slot names vary greatly.
+Some slots naturally have more results than other slots.
+For example, DateOfDeath and CauseOfDeath have some of the fewest entities because only a few entities are deceased.
+Some patterns use common words as as part of their patterns causing more extractions.
+For example, Affiliate looks for common words like  \textit{and} and  \textit{with} as part of the pattern content.
+These words are more common than \textit{dead}, \textit{died} or \textit{founded} in other patterns.
 
-Leave the setcounter for section number depth commented out and set at 0 unless you want to add section numbers to your paper.
-If you do add section numbers, you must uncomment this line and change the number to 1 (for section numbers), or 2 (for section and subsection numbers).
-The style file will not work properly with numbering of subsubsections, so do not use a number higher than 2.
+%As part of future work regarding enhancing precision, we can focus on fixing the wrong entities found, remove noisy tags by the Lingpipe or use more accurate NLP taggers such as Stanford NLP (Due to the fact that Stanford NLP is very slow we avoided using it, as due to speed its use was out of question) and finally use better patterns to enahnce results matched by the patterns.
+%On the other hand to increase recall we need to find better aliases and go for more resources to discover other ways that an entity might be addressed (e.g.\ twitter id, website, etc), add powerful patterns that can capture more cases of slot values.
+We would also use entity resolution methods and other advanced methods to improve
+%the accuracy and recall of entity extraction part.
 
-\begin{quote}
-\begin{small}
-\textbackslash documentclass[letterpaper]{article}\\
-\% \textit{Required Packages}\\
-\textbackslash usepackage\{aaai\}\\
-\textbackslash usepackage\{times\}\\
-\textbackslash usepackage\{helvet\}\\
-\textbackslash usepackage\{courier\}\\
-\textbackslash setlength\{\textbackslash pdfpagewidth\}\{8.5in\}
-\textbackslash setlength\{\textbackslash pdfpageheight\}\{11in\}\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{PDFINFO for PDF\LaTeX{}}\\
-\% Uncomment and complete the following for metadata (your paper must compile with PDF\LaTeX{})\\
-\textbackslash pdfinfo\{\\
-/Title (Input Your Paper Title Here)\\
-/Author (John Doe, Jane Doe)\\
-/Keywords (Input your paper's keywords in this optional area)\\
-\}\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{Section Numbers}\\
-\% Uncomment if you want to use section numbers\\
-\% and change the 0 to a 1 or 2\\
-\% \textbackslash setcounter\{secnumdepth\}\{0\}\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{Title, Author, and Address Information}\\
-\textbackslash title\{Title\}\\
-\textbackslash author\{Author 1 \textbackslash and Author 2\textbackslash\textbackslash \\ 
-Address line\textbackslash\textbackslash\\ Address line\textbackslash\textbackslash \\
-\textbackslash And\\
-Author 3\textbackslash\textbackslash\\ Address line\textbackslash\textbackslash\\ Address line\}\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{Body of Paper Begins}\\
-\textbackslash begin\{document\}\\
-\textbackslash maketitle\\
-...\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{References and End of Paper}\\
-\textbackslash bibliography\{Bibliography-File\}\\
-\textbackslash bibliographystyle\{aaai\}\\
-\textbackslash end\{document\}
-\end{small}
-\end{quote}
+%For slot extraction, to improve the performance, we need: 1) Using multi-class classifiers instead of pattern matching method to extract slot values in order to increase both recall and accuracy for slots ``Affiliate'', ``AssociateOf'', ``FounderOf'', ``EmployeeOf'', ``FoundedBy'', ``TopMembers'', ``Contact\_Meet\_Entity'' and so on.
+2) For special slots, like ``Titles'', ``DateOfDeath'', ``CauseOfDeath'', ``AwardsWon'', using different kind of advanced methods, e.g.\ classifiers, matching methods.
+3) Using other NLP tools or using classifiers to overcome the drawbacks of the LingPipe?s inaccurate tags.
+The first and second tasks are the most important tasks we need to do.
 
-\subsection{Inserting Document Metadata with \LaTeX{}}
-PDF files contain document summary information that enables us to create an Acrobat index (pdx) file, and also allows search engines to locate and present your paper more accurately.
-\textbf{Document Metadata  for Author and Title are REQUIRED.}
+Some of the entities are popular and appear at a greater frequency in the data set.
+For example, a `Corn Belt Power Cooperative' Google search results in 86,800 documents, where as `William H. Gates' returns 3,880,000 documents. 
+%\ceg{Add an example of someone who is either much larger of smaller.}
+We observed that more than half of the entities appear in less than 10 documents in the data set;
+%\ceg{Can we add this figure - } 
+a large portion have appeared only once. This magnificient change in coverage support the viability of our seach and filter schemes.
 
-If your paper includes illustrations that are not compatible with PDF\TeX{} (such as .eps or .ps documents), you will need to convert them.
-The epstopdf package will usually work for eps files.
-You will need to convert your ps files to PDF however.
+%A theory is that we are falling behind because we are using the cleansed (from HTML tags)
+%version of the corpus. We believe there has been a reason that TREC has 
+%included the actual HTML document as well as the cleansed version. This 
+%definitely will convey some information to us. If it was as easy as reading 
+%some clean text they wouldn't bother including so much data for teams to be 
+%useless. So we guess is that we are missing some information from not using 
+%the actual document. And, we are looking for tokens with entity value set 
+%which will depend us dramatically on the accuracy of lingpipe, which is a fast 
+%algorithm but is not as good as other NLP tools can be e.g. Stanford NLP.
 
-\textit{Important:} Do not include \textit{any} \LaTeX{} code or nonascii characters (including accented characters) in the metadata.
-The data in the metadata must be completely plain ascii.
-It may not include slashes, accents, linebreaks, unicode, or any \LaTeX{} commands.
-Type the title exactly as it appears on the paper (minus all formatting).
-Input the author names in the order in which they appear on the paper (minus all accents), separating each author by a comma.
-You may also include keywords in the Keywords field.
+% Note: Here we discuss why the results are the way they are
+% Give pros and cons, talk about how the implemented algorithms
+% performed in the actual implementation.
+% Answer the `why' question about all the trends in the results section.
 
-\subsection{Preparing Your Paper}
+The system pipeline architecture is an efficient method of processing the stream of data.
+Each hour of in the corpus contains and average of 380 MB of compressed data.
+It takes and hour for the system to extract facts from 140 hours worth of data fom the KBA corpus.
 
-After the preamble above, you should prepare your paper as follows:
+\section{Conclusion}
 
-\begin{quote}
-\begin{small}
-\textbackslash begin\{document\}\\
-\textbackslash maketitle\\
-...\\
-\textbackslash bibliography\{Bibliography-File\}\\
-\textbackslash bibliographystyle\{aaai\}\\
-\textbackslash end\{document\}\\
-\end{small}
-\end{quote}
-\subsection{Incompatible Packages}
-The following packages are incompatible with aaai.sty and/or aaai.bst and must not be used (this list is not exhaustive --- there are others as well):
-\begin{itemize}
-\item hyperref
-\item natbib
-\item geometry
-\item titlesec
-\item layout
-\item caption
-\item titlesec
-\item T1 fontenc package (install the CM super fonts package instead)
-\end{itemize}
+In this paper we described an approach to perform fact extraction over one of the largest data sets to date. 
+We generate aliases for Wikipedia entities using an API and extract some aliases from Wikipedia pages text itself.
+We process documents that mention entities for slot value extraction.
+Slot values are determined using pattern matching over tagged entities in sentences.
+Finally post processing will filter, cleanup and infers some new slot values to enhance recall and accuracy.
 
-\subsection{Illegal Commands}
-The following commands may not be used in your paper:
-\begin{itemize}
-\item \textbackslash input
-\item \textbackslash vspace (when used before or after a section or subsection)
-\item \textbackslash addtolength 
-\item \textbackslash columnsep
-\item \textbackslash top margin (or text height or addsidemargin or even side margin)
-\end{itemize}
+We sampled documents from the training data period to generate an initial set of patterns and then use these patterns to generate results.
+After manually examining the results, we prune patterns with poor performance and add patterns that may add to extraction coverage.
+We use several iterations to find the best patterns.
+%We found that it is very time consuming to identify quality patterns.
 
-\subsection{Paper Size, Margins, and Column Width}
-Papers must be formatted to print in two-column format on 8.5 x 11 inch US letter-sized paper. The margins must be exactly as follows: 
-\begin{itemize}
-\item Top margin: .75 inches
-\item Left margin: .75 inches
-\item Right margin: .75 inches
-\item Bottom margin: 1.25 inches
-\end{itemize}
+%We noticed that some tools that claim to be performant for using the hardware capabilities at hand sometimes don't really work as claimed and you should not always rely on one without a thorough A/B testing of performance which we ended up in generating our in-house system for processing the corpus and passing through the filter.
+Furthermore, on extracting slot values, pattern matching might not be the best options but definitely can produce some good results at hand.
+We have plans on generating classifiers for slot value extraction purposes.
+Entity resolution on the other hand was a topic we spent sometime on but could not get to stable grounds for it.
+Entity resolution will distinguish between entities of the same name but different contexts.
+Further improvements on this component of the system are required.
 
-The default paper size in most installations of \LaTeX{} is A4.
-However, because we require that your electronic paper be formatted in US letter size, you will need to alter the default for this paper to US letter size.
-Assuming you are using the 2e version of \LaTeX{}, you can do this by including the [letterpaper] option at the beginning of your file:
-\textbackslash documentclass[letterpaper]{article}.
+We look to continue exploration of streaming extraction models over this large data set.
+Our models are simple and provide a great baseline framework to develop and compare innovative techniques.
 
-This command is usually sufficient to change the format. Sometimes, however, it may not work. Use PDF\LaTeX{} and include
-\textbackslash setlength\{\textbackslash pdfpagewidth\}\{8.5in\}
-\textbackslash setlength\{\textbackslash pdfpageheight\}\{11in\}
-in your preamble.
+% Note: Give a summary of our efforts and the
+% high level contribution to society.
 
-\textbf{Do not use the Geometry package to alter the page size.} Use of this style file alters aaai.sty and will result in your paper being rejected.
+% Talk about the things we wanted to do and
+% didnt get to do.
 
-\subsubsection{Column Width and Margins.}
-To ensure maximum readability, your paper must include two columns.
-Each column should be 3.3 inches wide (slightly more than 3.25 inches), with a .375 inch (.952 cm) gutter of white space between the two columns.
-The aaai.sty file will automatically create these columns for you.
+\section*{Acknowledgements}
+We would like to thank John Frank and NIST for providing the data set.
+Christan Grant is funded by a National Science Foundation Graduate Research Fellowship under Grant No. DGE-0802270.
 
-\subsection{Overlength Papers}
-If your paper is too long, turn on \textbackslash frenchspacing, which will reduce the space after periods.
-Next,  shrink the size of your graphics.
-Use \textbackslash centering instead of \textbackslash begin\{center\} in your figure environment.
-If these two methods don't work, you may minimally use the following.
-For floats (tables and figures), you may minimally reduce \textbackslash floatsep, \textbackslash textfloatsep, \textbackslash abovecaptionskip, and \textbackslash belowcaptionskip.
-For mathematical environments, you may minimally reduce \textbackslash abovedisplayskip, \textbackslash belowdisplayskip, and \textbackslash arraycolsep.
-You may also alter the size of your bibliography by inserting \textbackslash fontsize\{9.5pt\}\{10.5pt\} \textbackslash selectfont
-right before the bibliography.
-
-Commands that alter page layout are forbidden.
-These include \textbackslash columnsep, \textbackslash topmargin, \textbackslash topskip, \textbackslash textheight, \textbackslash textwidth, \textbackslash oddsidemargin, and \textbackslash evensizemargin (this list is not exhaustive).
-If you alter page layout, you will be required to pay the page fee \textit{plus} a reformatting fee.
-Other commands that are questionable and may cause your paper to be rejected include  \textbackslash parindent, and \textbackslash parskip.
-Commands that alter the space between sections are also questionable.
-The title sec package is not allowed.
-Regardless of the above, if your paper is obviously ``squeezed" it is not going to to be accepted.
-Before using every trick you know to make your paper a certain length, try reducing the size of your graphics or cutting text instead or (if allowed) paying the extra page charge.
-It will be cheaper in the long run.
-
-\subsection{Figures}
-Your paper must compile in PDF\LaTeX{}. Consequently, all your figures must be .jpg, .png, or .pdf. You may not use the .gif (the resolution is too low), .ps, or .eps file format for your figures.
-
-When you include your figures, you must crop them \textbf{outside} of \LaTeX{}.
-The command \textbackslash includegraphics*[clip=true, viewport 0 0 10 10]{...} might result in a PDF that looks great, but the image is \textbf{not really cropped.} The full image can reappear when page numbers are applied or color space is standardized.
-
-\subsection{Type Font and Size}
-Your paper must be formatted in Times Roman or Nimbus.
-We will not accept papers formatted using Computer Modern or Palatino or some other font as the text or heading typeface.
-Sans serif, when used, should be Courier.
-Use Symbol or Lucida or Computer Modern for \textit{mathematics only.
-}
-
-Do not use type 3 fonts for any portion of your paper, including graphics.
-Type 3 bitmapped fonts are designed for fixed resolution printers.
-Most print at 300 dpi even if the printer resolution is 1200 dpi or higher.
-They also often cause high resolution imagesetter devices and our PDF indexing software to crash.
-Consequently, AAAI will not accept electronic files containing obsolete type 3 fonts.
-Files containing those fonts (even in graphics) will be rejected.
-
-Fortunately, there are effective workarounds that will prevent your file from embedding type 3 bitmapped fonts.
-The easiest workaround is to use the required times, helvet, and courier packages with \LaTeX{}2e.
-(Note that papers formatted in this way will still use Computer Modern for the mathematics.
-To make the math look good, you'll either have to use Symbol or Lucida, or you will need to install type 1 Computer Modern fonts --- for more on these fonts, see the section ``Obtaining Type 1 Computer Modern.")
-
-If you are unsure if your paper contains type 3 fonts, view the PDF in Acrobat Reader.
-The Properties/Fonts window will display the font name, font type, and encoding properties of all the fonts in the document.
-If you are unsure if your graphics contain type 3 fonts (and they are PostScript or encapsulated PostScript documents), create PDF versions of them, and consult the properties window in Acrobat Reader.
-
-The default size for your type should be ten-point with twelve-point leading (line spacing).
-Start all pages (except the first) directly under the top margin.
-(See the next section for instructions on formatting the title page.) Indent ten points when beginning a new paragraph, unless the paragraph begins directly below a heading or subheading.
-
-\subsubsection{Obtaining Type 1 Computer Modern for \LaTeX{}.}
-
-If you use Computer Modern for the mathematics in your paper (you cannot use it for the text) you may need to download type 1 Computer fonts.
-They are available without charge from the American Mathematical Society:
-http://www.ams.org/tex/type1-fonts.html.
-
-\subsection{Title and Authors}
-Your title must appear in mixed case (nouns, pronouns, and verbs are capitalized) near the top of the first page, centered over both columns in sixteen-point bold type (twenty-four point leading).
-This style is called ``mixed case." Author's names should appear below the title of the paper, centered in twelve-point type (with fifteen point leading), along with affiliation(s) and complete address(es) (including electronic mail address if available) in nine-point roman type (the twelve point leading).
-(If the title is long, or you have many authors, you may reduce the specified point sizes by up to two points.) You should begin the two-column format when you come to the abstract.
-
-\subsubsection{Formatting Author Information}
-Author information can be set in a number of different styles, depending on the number of authors and the number of affiliations you need to display.
-For several authors from the same institution, use \textbackslash and:
-
-\begin{quote}
-\begin{small}
-\textbackslash author\{Author 1 \textbackslash and  ...  \textbackslash and Author \textit{n}\textbackslash \textbackslash  \\
-Address line \textbackslash \textbackslash ~... \textbackslash \textbackslash ~Address line\}
-\end{small}
-\end{quote}
-
-\noindent If the names do not fit well on one line use:
-
-\begin{quote}
-\begin{small}
-\textbackslash author\{Author 1\}\textbackslash \textbackslash \\ \{\textbackslash bf Author 2\}\textbackslash \textbackslash ~ 
-... \textbackslash \textbackslash ~\{\textbackslash bf Author \textit{n}\}\textbackslash \textbackslash \\
-Address line \textbackslash \textbackslash ~ ... \textbackslash \textbackslash ~ Address line\}
-\end{small}
-\end{quote}
-
-\noindent For authors from different institutions, use \textbackslash And:
-
-\begin{quote}
-\begin{small}
-\textbackslash author\{Author 1\textbackslash \textbackslash ~ Address line \textbackslash \textbackslash ~...  \textbackslash \textbackslash ~ Address line
-\textbackslash And  ...  
-\textbackslash And
-Author \textit{n}\textbackslash \textbackslash \\ Address line\textbackslash \textbackslash ~
-... \textbackslash \textbackslash ~
-Address line\}
-\end{small}
-\end{quote}
-
-\noindent To start a separate ``row" of authors, use \textbackslash AND:
-\begin{quote}
-\begin{small}
-\textbackslash author\{Author 1\textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
-...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\
-\textbackslash AND\\
-Author 2 \textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
-...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\
-\textbackslash And\\
-Author 3 \textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
-...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\\}
-\end{small}
-\end{quote}
-
-\noindent If the title and author information does not fit in the area allocated, place
-\textbackslash setlength\textbackslash titlebox\{\textit{height}\}
-after the \textbackslash documentclass line where \{\textit{height}\} is something like 2.5in.
-
-\subsection{\LaTeX{} Copyright Notice}
-The copyright notice automatically appears if you use aaai.sty.
-If you are creating a technical report, it is not necessary to include this notice.
-You may disable the copyright line using the \verb+\+nocopyrightcommand.
-To change the entire text of the copyright slug, use:
-\textbackslash copyrighttext \{\emph{text}\}.
-Either of these must appear before \textbackslash maketitle.
-Please be advised, however, that \textit{if you disable or change the copyright line and transfer of copyright is required, your paper will not be published.}
-
-\subsection{Credits}
-Any credits to a sponsoring agency should appear in the acknowledgments section, unless the agency requires different placement. If it is necessary to include this information on the front page, use
-\textbackslash thanks in either the \textbackslash author or \textbackslash title commands.
-For example:
-\begin{quote}
-\begin{small}
-\textbackslash title\{Very Important Results in AI\textbackslash thanks\{This work is
- supported by everybody.\}\}
-\end{small}
-\end{quote}
-Multiple \textbackslash thanks commands can be given.
-Each will result in a separate footnote indication in the author or title with the corresponding text at the botton of the first column of the document.
-Note that the \textbackslash thanks command is fragile.
-You will need to use \textbackslash protect.
-
-Please do not include \textbackslash pubnote commands in your document.
-
-\subsection{Abstract}
-The abstract must be placed at the beginning of the first column, indented ten points from the left and right margins.
-The title “Abstract” should appear in ten-point bold type, centered above the body of the abstract.
-The abstract should be set in nine-point type with ten-point leading.
-This concise, one-paragraph summary should describe the general thesis and conclusion of your paper.
-A reader should be able to learn the purpose of the paper and the reason for its importance from the abstract.
-The abstract should be no more than two hundred words in length.
-(Authors who are submitting short one- or two-page extended extracts should provide a short abstract of only a sentence or so.) \textbf{Do not include references in your abstract!}
-
-\subsection{Page Numbers}
-
-Do not \textbf{ever} print any page numbers on your paper.
-
-\subsection{Text }
-The main body of the paper must be formatted in ten-point with twelve-point leading (line spacing).
-
-\subsection{Citations}
-Citations within the text should include the author's last name and year, for example (Newell 1980).
-Append lower-case letters to the year in cases of ambiguity.
-Multiple authors should be treated as follows: (Feigenbaum and Engelmore 1988) or (Ford, Hayes, and Glymour 1992).
-In the case of four or more authors, list only the first author, followed by et al.
-(Ford et al.
-1997).
-
-\subsection{Extracts}
-Long quotations and extracts should be indented ten points from the left and right margins.
-
-\begin{quote}
-This is an example of an extract or quotation.
-Note the indent on both sides.
-Quotation marks are not necessary if you offset the text in a block like this, and properly identify and cite the quotation in the text.
-
-\end{quote}
-
-\subsection{Footnotes}
-Avoid footnotes as much as possible; they interrupt the reading of the text.
-When essential, they should be consecutively numbered throughout with superscript Arabic numbers.
-Footnotes should appear at the bottom of the page, separated from the text by a blank line space and a thin, half-point rule.
-
-\subsection{Headings and Sections}
-When necessary, headings should be used to separate major sections of your paper.
-Remember, you are writing a short paper, not a lengthy book!
-An overabundance of headings will tend to make your paper look more like an outline than a paper.
-
-First-level heads should be twelve-point Times Roman bold type, mixed case (initial capitals followed by lower case on all words except articles, conjunctions, and prepositions, which should appear entirely in lower case), with fifteen-point leading, centered, with one blank line preceding them and three additional points of leading following them.
-Second-level headings should be eleven-point Times Roman bold type, mixed case, with thirteen-point leading, flush left, with one blank line preceding them and three additional points of leading following them.
-Do not skip a line between paragraphs.
-Third-level headings should be run in with the text, ten-point Times Roman bold type, mixed case, with twelve-point leading, flush left, with six points of additional space preceding them and no additional points of leading following them.
-
-\subsubsection{Section Numbers}
-The use of section numbers in AAAI Press papers is optional.
-To use section numbers in \LaTeX{}, uncomment the setcounter line in your document preamble and change the 0 to a 1 or 2.
-Section numbers should not be used in short poster papers.
-
-\subsubsection{Section Headings.}
-Sections should be arranged and headed as follows:
-
-\subsubsection{Acknowledgments.}
-The acknowledgments section, if included, appears after the main body of text and is headed ``Acknowledgments." This section includes acknowledgments of help from associates and colleagues, credits to sponsoring agencies, financial support, and permission to publish.
-Please acknowledge other contributors, grant support, and so forth, in this section.
-Do not put acknowledgments in a footnote on the first page.
-If your grant agency requires acknowledgment of the grant on page 1, limit the footnote to the required statement, and put the remaining acknowledgments at the back.
-Please try to limit acknowledgments to no more than three sentences.
-
-\subsubsection{Appendices.}
-Any appendices follow the acknowledgments, if included, or after the main body of text if no acknowledgments appear.
-
-\subsubsection{References}
-The references section should be labeled ``References" and should appear at the very end of the paper (don't end the paper with references, and then put a figure by itself on the last page).
-A sample list of references is given later on in these instructions.
-Please use a consistent format for references.
-Poorly prepared or sloppy references reflect badly on the quality of your paper and your research.
-Please prepare complete and accurate citations.
-
-\subsection{Illustrations and Figures}
-Figures, drawings, tables, and photographs should be placed throughout the paper near the place where they are first discussed.
-Do not group them together at the end of the paper.
-If placed at the top or bottom of the paper, illustrations may run across both columns.
-Figures must not invade the top, bottom, or side margin areas.
-Figures must be inserted using the \textbackslash usepackage\{graphicx\}.
-Number figures sequentially, for example, figure 1, and so on.
-
-The illustration number and caption should appear under the illustration. Labels, and other text in illustrations must be at least nine-point type.
-
-\subsubsection{Low-Resolution Bitmaps.}
-You may not use low-resolution (such as 72 dpi) screen-dumps and GIF files---these files contain so few pixels that they are always blurry, and illegible when printed.
-If they are color, they will become an indecipherable mess when converted to black and white.
-This is always the case with gif files, which should never be used.
-The resolution of screen dumps can be increased by reducing the print size of the original file while retaining the same number of pixels.
-You can also enlarge files by manipulating them in software such as PhotoShop.
-Your figures should be a minimum of 266 dpi when incorporated into your document.
-
-\subsubsection{\LaTeX{} Overflow.}
-\LaTeX{} users please beware: \LaTeX{} will sometimes put portions of the figure or table or an equation in the margin.
-If this happens, you need to scale the figure or table down, or reformat the equation.
-Check your log file!
-You must fix any overflow into the margin (that means no overfull boxes in \LaTeX{}).
-If you don't, the overflow text will simply be eliminated.
-\textbf{Nothing is permitted to intrude into the margins.}
-
-\subsubsection{Using Color.}
-Your paper will be printed in black and white and grayscale.
-Consequently, because conversion to grayscale can cause undesirable effects (red changes to black, yellow can disappear, and so forth), we strongly suggest you avoid placing color figures in your document.
-Of course, any reference to color will be indecipherable to your reader.
-
-\subsubsection{Drawings.}
-We suggest you use computer drawing software (such as Adobe Illustrator or, (if unavoidable), the drawing tools in Microsoft Word) to create your illustrations.
-Do not use Microsoft Publisher.
-These illustrations will look best if all line widths are uniform (half- to two-point in size), and you do not create labels over shaded areas.
-Shading should be 133 lines per inch if possible.
-Use Times Roman or Helvetica for all figure call-outs.
-\textbf{Do not use hairline width lines} --- be sure that the stroke width of all lines is at least .5 pt.
-Zero point lines will print on a laser printer, but will completely disappear on the high-resolution devices used by our printers.
-
-\subsubsection{Photographs and Images.}
-Photographs and other images should be in grayscale (color photographs will not reproduce well; for example, red tones will reproduce as black, yellow may turn to white, and so forth) and set to a minimum of 266 dpi.
-Do not prescreen images.
-
-\subsubsection{Resizing Graphics.}
-Resize your graphics \textbf{before} you include them with LaTeX.
-You may \textbf{not} use trim or clip options as part of your \textbackslash includgraphics command.
-Resize the media box of your PDF using a graphics program instead.
-
-\subsubsection{Fonts in Your Illustrations}
-You must embed all fonts in your graphics before including them in your LaTeX document.
-
-\subsection{References} 
-The aaai.sty file includes a set of definitions for use in formatting references with BibTeX.
-These definitions make the bibliography style fairly close to the one specified below.
-To use these definitions, you also need the BibTeX style file ``aaai.bst," available in the author kit on the AAAI web site.
-Then, at the end of your paper but before \textbackslash end{document}, you need to put the following lines:
-
-\begin{quote}
-\begin{small}
-\textbackslash bibliographystyle\{aaai\}
-\textbackslash bibliography\{bibfile1,bibfile2,...\}
-\end{small}
-\end{quote}
-
-The list of files in the \textbackslash  bibliography command should be the names of your BibTeX source files (that is, the .bib files referenced in your paper).
-
-The following commands are available for your use in citing references:
-\begin{quote}
-\begin{small}
-\textbackslash cite: Cites the given reference(s) with a full citation. This appears as ``(Author Year)'' for one reference, or ``(Author Year; Author Year)'' for multiple references.\\
-\textbackslash shortcite: Cites the given reference(s) with just the year. This appears as ``(Year)'' for one reference, or ``(Year; Year)'' for multiple references.\\
-\textbackslash citeauthor: Cites the given reference(s) with just the author name(s) and no parentheses.\\
-\textbackslash citeyear: Cites the given reference(s) with just the date(s) and no parentheses.
-\end{small}
-\end{quote}
-
-\textbf{Warning:} The aaai.sty file is incompatible with the hyperref and natbib packages. If you use either, your references will be garbled.
-
-Formatted bibliographies should look like the following examples.
-
-\smallskip \noindent \textit{Book with Multiple Authors}\\
-Engelmore, R., and Morgan, A. eds. 1986. \textit{Blackboard Systems.} Reading, Mass.: Addison-Wesley.
-
-\smallskip \noindent \textit{Journal Article}\\
-Robinson, A. L. 1980a. New Ways to Make Microcircuits Smaller. \textit{Science} 208: 1019--1026.
-
-\smallskip \noindent \textit{Magazine Article}\\
-Hasling, D. W.; Clancey, W. J.; and Rennels, G. R. 1983. Strategic Explanations in Consultation. \textit{The International Journal of Man-Machine Studies} 20(1): 3--19.
-
-\smallskip \noindent \textit{Proceedings Paper Published by a Society}\\
-Clancey, W.
-J.
-1983b.
-Communication, Simulation, and Intelligent Agents: Implications of Personal Intelligent Machines for Medical Education.
-In Proceedings of the Eighth International Joint Conference on Artificial Intelligence, 556--560.
-Menlo Park, Calif.: International Joint Conferences on Artificial Intelligence, Inc.
-
-\smallskip \noindent \textit{Proceedings Paper Published by a Press or Publisher}\\
-Clancey, W. J. 1984. Classification Problem Solving. In \textit{Proceedings of the Fourth National Conference on Artificial Intelligence,} 49--54. Menlo Park, Calif.: AAAI Press.
-
-\smallskip \noindent \textit{University Technical Report}\\
-Rice, J. 1986. Poligon: A System for Parallel Problem Solving, Technical Report, KSL-86-19, Dept. of Computer Science, Stanford Univ.
-
-\smallskip \noindent \textit{Dissertation or Thesis}\\
-Clancey, W. J. 1979b. Transfer of Rule-Based Expertise through a Tutorial Dialogue. Ph.D. diss., Dept. of Computer Science, Stanford Univ., Stanford, Calif.
-
-\smallskip \noindent \textit{Forthcoming Publication}\\
-Clancey, W. J. 1986a. The Engineering of Qualitative Models. Forthcoming.
-
-\section{Producing Reliable PDF\\Documents with \LaTeX{}}
-Generally speaking, PDF files are platform independent and accessible to everyone.
-When creating a paper for a proceedings or publication in which many PDF documents must be merged and then printed on high-resolution PostScript RIPs, several requirements must be met that are not normally of concern.
-Thus to ensure that your paper will look like it does when printed on your own machine, you must take several precautions:
-\begin{itemize}
-\item Use type 1 fonts (not type 3 fonts)
-\item Use only standard Times, Nimbus, and CMR font packages (not fonts like F3 or fonts with tildes in the names or fonts---other than Computer Modern---that are created for specific point sizes, like Times\~{}19) or fonts with strange combinations of numbers and letters
-\item Embed all fonts when producing the PDF
-\item Do not use the [T1]{fontenc} package (install the CM super fonts package instead)
-\end{itemize}
-
-\subsection{Creating Output Using PDF\LaTeX{} Is Required}
-By using the PDF\TeX{} program instead of straight \LaTeX{} or \TeX{}, you will probably avoid the type 3 font problem altogether (unless you use a package that calls for metafont).
-PDF\LaTeX{} enables you to create a PDF document directly from \LaTeX{} source.
-The one requirement of this software is that all your graphics and images must be available in a format that PDF\LaTeX{} understands (normally PDF).
-
-PDF\LaTeX{}'s default is to create documents with type 1 fonts.
-If you find that it is not doing so in your case, it is likely that one or more fonts are missing from your system or are not in a path that is known to PDF\LaTeX{}.
-
-\subsubsection{dvipdf Script}
-Scripts such as dvipdf which ostensibly bypass the Postscript intermediary should not be used since they generally do not instruct dvips to use the config.pdf file.
-
-\subsubsection{dvipdfm}
-Do not use this dvi-PDF conversion package if your document contains graphics (and we recommend you avoid it even if your document does not contain graphics).
-
-\subsection{Ghostscript}
-\LaTeX{} users should not use GhostScript to create their PDFs.
-
-\subsection{Graphics}
-If you are still finding type 3 fonts in your PDF file, look at your graphics! \LaTeX{} users should check all their imported graphics files as well for font problems.
-
-\section{Proofreading Your PDF}
-Please check all the pages of your PDF file.
-Is the page size A4?
-Are there any type 3, Identity-H, or CID fonts?
-Are all the fonts embedded?
-Are there any areas where equations or figures run into the margins?
-Did you include all your figures?
-Did you follow mixed case capitalization rules for your title?
-Did you include a copyright notice?
-Do any of the pages scroll slowly (because the graphics draw slowly on the page)?
-Are URLs underlined and in color?
-You will need to fix these common errors before submitting your file.
-
-\section{Improperly Formatted Files }
-In the past, AAAI has corrected improperly formatted files submitted by the authors.
-Unfortunately, this has become an increasingly burdensome expense that we can no longer absorb.
-Consequently, if your file is improperly formatted, it may not be possible to include your paper in the publication.
-If time allows, however, you will be notified via e-mail (with a copy to the program chair) of the problems with your file and given the option of correcting the file yourself (and paying a late fee) or asking that AAAI have the file corrected for you, for an additional fee.
-If you opt to correct the file yourself, please note that we cannot provide you with any additional advice beyond that given in your packet.
-Files that are not corrected after a second attempt will be withdrawn.
-
-\subsection{\LaTeX{} 209 Warning}
-If you use \LaTeX{} 209 we will not be able to publish your paper. Convert your paper to \LaTeX{}2e.
-
-\section{Naming Your Electronic File}
-We request that you name your \LaTeX{} source file with your last name (family name) so that it can easily be differentiated from other submissions.
-If you name your files with the name of the event or ``aaai" or ``paper" or ``camera-ready" or some other generic or indecipherable name, you bear all risks of loss --- it is extremely likely that your file may be overwritten.
-
-\section{Submitting Your Electronic Files to AAAI}
-Submitting your files to AAAI is a two-step process. It is explained fully in the author registration and submission instructions. Please consult this document for details on how to submit your paper.
-
-\section{Inquiries} 
-If you have any questions about the preparation or submission of your paper as instructed in this document, please contact AAAI Press at the address given below.
-If you have technical questions about implementation of the aaai style file, please contact an expert at your site.
-We do not provide technical support for \LaTeX{} or any other software package.
-To avoid problems, please keep your paper simple, and do not incorporate complicated macros and style files.
-
-\begin{quote}
-\noindent AAAI Press\\
-2275 East Bayshore Road, Suite 160\\
-Palo Alto, California 94303\\ 
-\textit{Telephone:} (650) 328-3123\\ 
-\textit{E-mail:} See the submission instructions for your particular conference or event.
-\end{quote}
-
-\section{Additional Resources}
-\LaTeX{} is a difficult program to master.
-If you've used that software, and this document didn't help or some items were not explained clearly, we recommend you read Michael Shell's excellent document (testflow doc.txt V1.0a 2002/08/13) about obtaining correct PS/PDF output on \LaTeX{} systems.
-(It was written for another purpose, but it has general application as well).
-It is available at www.ctan.org in the tex-archive.
-
-\section{ Acknowledgments}
-AAAI is especially grateful to Peter Patel Schneider for his work in implementing the aaai.sty file, liberally using the ideas of other style hackers, including Barbara Beeton.
-We also acknowledge with thanks the work of George Ferguson for his guide to using the style and BibTeX files --- which has been incorporated into this document  --- and Hans Guesgen, who provided several timely modifications, as well as the many others who have, from time to time, sent in suggestions on improvements to the AAAI style.
-
-The preparation of the \LaTeX{} and Bib\TeX{} files that implement these instructions was supported by Schlumberger Palo Alto Research, AT\&T Bell Laboratories, Morgan Kaufmann Publishers, The Live Oak Press, LLC, and AAAI Press.
-Bibliography style changes were added by Sunil Issar.
-\verb+\+pubnote was added by J.
-Scott Penberthy.
-George Ferguson added support for printing the AAAI copyright slug.
-Additional changes to aaai.sty and aaai.bst have been made by the AAAI staff.
-
-\bigskip
-\noindent Thank you for reading these instructions carefully. We look forward to receiving your electronic files!
+\bibliography{citation}{99}
+\bibliographystyle{aaai}
 

### 2014-01-29 paper/flairs27_AuthorKit/paper.tex
Fixed all errors
Figuring out why .bib is not recognized

@@
 \usepackage{cite }
+%\usepackage{natbib}
 
@@
 Presently, there is considerable time lag between the publication of an event and its citation in WP\@.
-The median time lag for a sample of about 60K web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail~\cite{JFrank12}.
+The median time lag for a sample of about 60K web pages cited by
+ WP articles in the \textit{living\_people} category is over a year
+ and the distribution has a long and heavy tail~
+ \cite{frank2013building}.
 %Also, the majority of WP entities have updates on their associated article much less frequently than their mention frequency.
@@
 Previous approaches are able to find relevant documents given a list of WP
-entities as query nodes \cite{mcnamee2012hltcoe, dalton2013bi,
+entities as query nodes \cite{mcnamee2012hltcoe}
+ \cite{dalton2013bi}\,
+\cite{
 Bonnefoy:2013:WDE:2484028.2484180, Balog:2013:CCR:2484028.2484151,ji2011knowledge}.
@@
 % http://convert.neevia.com/pdfconvert/
-  \vspace*{-.1in} 
+  %\vspace*{-.1in} 
   \caption{System Architecture.
@@
   \label{fig:system}
-  \vspace*{-.2in}
+  %\vspace*{-.2in}
 \end{figure}
@@
 We use this technique as a first filter with confidence because previous work states non-mentioning
-documents have a low chance of being citable in Wikipedia \cite{JFrank12}.
+documents have a low chance of being citable in Wikipedia \cite{frank2013building}.
 Given our large number of aliases we can be confident that if an alias does not appear in a document it does not need to be cited.
@@
 % cropped pdf created using $ pdfcrop Pattern.pdf
-\vspace*{-.1in}
+%\vspace*{-.1in}
 \caption{Pattern matching for rule evaluation. The slot value is on the right side of the 
 entity. The pattern context discovered is `passed away' with a value of `March 2013'. This conforms to type II of our pattern categories.}\label{fig:pattern}
-\vspace*{-.2in}
+%\vspace*{-.2in}
 \end{figure}
@@
 
-\bibliography{citation}{99}
+\bibliography{citation}
 \bibliographystyle{aaai}

### 2014-01-29 paper/flairs27_AuthorKit/paper.tex
Adding authors contributed equally.

@@
 \usepackage[noend]{algorithmic} 
-\usepackage{cite }
+%\usepackage{cite }
 %\usepackage{natbib}
-
 \frenchspacing
@@
 \title{Streaming Fact Extraction for Wikipedia Entities at Web-Scale}
-\author{Morteza Shahriari Nia, Christan Grant, \\
-\bf \large Yang Peng, Daisy Zhe Wang\\
+\author{Morteza Shahriari Nia$*$, Christan Grant$*$, \\
+\bf \large Yang Peng\footnote{All authors contributed equally.}, Daisy Zhe Wang\\
 Data Science Research Lab\\
@@
  WP articles in the \textit{living\_people} category is over a year
- and the distribution has a long and heavy tail~
+ and the distribution has a long and heavy tail
  \cite{frank2013building}.
@@
 Notable news may be derived from newspapers, tweets, blogs and a variety of
-different sources include Twitter, Facebook, iBlogs, arxiv, etc.
+different sources include Twitter, Facebook, Blogs, arxiv, etc.
 However, the actual citable information is a small percentage of the total documents that appear on the web.
@@
  \cite{dalton2013bi}\,
-\cite{
-Bonnefoy:2013:WDE:2484028.2484180, Balog:2013:CCR:2484028.2484151,ji2011knowledge}.
+\cite{Bonnefoy:2013:WDE:2484028.2484180, Balog:2013:CCR:2484028.2484151,ji2011knowledge}.
 Entities of three categories \textit{person}, \textit{organization} and \textit{facility} are considered.
@@
 
-\bibliography{citation}
 \bibliographystyle{aaai}
 
+\bibliography{citation}
+
 \end{document}

### 2014-01-29 paper/flairs27_AuthorKit/paper.tex

@@
 \title{Streaming Fact Extraction for Wikipedia Entities at Web-Scale}
-\author{Morteza Shahriari Nia$*$, Christan Grant$*$, \\
-\bf \large Yang Peng\footnote{All authors contributed equally.}, Daisy Zhe Wang\\
+\author{Morteza Shahriari Nia$^*$, Christan Grant$^*$, \\
+\bf \large Yang Peng\thanks{All authors contributed equally.}, Daisy Zhe Wang\\
 Data Science Research Lab\\
@@
 \begin{figure}
-\hspace{-10mm}
+%\hspace{-10mm}
   \centering

### 2014-01-31 paper/flairs27_AuthorKit/paper.tex
Flairs camera read. Added funding from darpa

@@
 Previous approaches are able to find relevant documents given a list of WP
-entities as query nodes \cite{mcnamee2012hltcoe}
- \cite{dalton2013bi}\,
-\cite{Bonnefoy:2013:WDE:2484028.2484180, Balog:2013:CCR:2484028.2484151,ji2011knowledge}.
+entities as query nodes \cite{mcnamee2012hltcoe,dalton2013bi,Bonnefoy:2013:WDE:2484028.2484180,Balog:2013:CCR:2484028.2484151,ji2011knowledge} 
+%,\cite{balog2013cumulative}
+.
 Entities of three categories \textit{person}, \textit{organization} and \textit{facility} are considered.
@@
 \begin{figure}
-%\hspace{-10mm}
   \centering
-%  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
-  \includegraphics[width=8.5cm]{./images/System_Diagram_with_model_Vertical-crop.pdf}
-% http://convert.neevia.com/pdfconvert/
-  %\vspace*{-.1in} 
+  %\includegraphics{./images/sr.pdf}
+  \includegraphics{./images/s_cropped_preview.jpg} % created using adjust size in Mac Preview app.
   \caption{System Architecture.
@@
   \label{fig:system}
-  %\vspace*{-.2in}
 \end{figure}
@@
 \centering
-%\includegraphics[width=4.5in]{./images/system.eps}
-%\includegraphics[width=6in]{./images/Pattern.eps}
-%\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
-\includegraphics[width = 11cm]{./images/Pattern-crop.pdf}
-% cropped pdf created using $ pdfcrop Pattern.pdf
-%\vspace*{-.1in}
+\includegraphics{./images/pattern-crop_2.jpg}
 \caption{Pattern matching for rule evaluation. The slot value is on the right side of the 
 entity. The pattern context discovered is `passed away' with a value of `March 2013'. This conforms to type II of our pattern categories.}\label{fig:pattern}
-%\vspace*{-.2in}
 \end{figure}
@@
 We would like to thank John Frank and NIST for providing the data set.
-Christan Grant is funded by a National Science Foundation Graduate Research Fellowship under Grant No. DGE-0802270.
+Christan Grant is funded by a National Science Foundation Graduate Research Fellowship under Grant No. DGE-0802270. This work has also been supported in part by DARPA under
+FA8750-12-2-0348-2 (DEFT/CUBISM).
 
